### 2016-04-05 verifying-winner.tex
Before coding the two tests

\documentclass[11pt]{article}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{amsthm}
\usepackage{caption}
\usepackage{cleveref}
\usepackage{enumitem}
\usepackage[totalwidth=480pt, totalheight=680pt]{geometry}
\usepackage{mathrsfs}
\usepackage{tikz}

\captionsetup{width=0.8\textwidth}
\DeclareMathOperator*{\argmax}{arg\,max}
\newtheorem{definition}{Definition}
\newtheorem{lemma}{Lemma}
\newtheorem{theorem}{Theorem}
\setlength{\tabcolsep}{1em}
\setlist{listparindent=\parindent, parsep=0pt}

\newcommand{\EE}{\mathbb{E}}
\newcommand{\PP}{\mathbb{P}}
\newcommand{\RR}{\mathbb{R}}

\begin{document}

\title{Rank verification for exponential families}
\author{Kenneth Hung \and William Fithian}
\date{\today}
\maketitle

\begin{abstract}
This paper deals with the selective inference problem encountered in rank verification --- verifying the order of the natural parameters in exponential families. We constructed a selective level-$\alpha$ test for verifying the largest natural parameter, which provides familywise error rate (FWER) and false discovery rate (FDR) control as we extend it into a step-down procedure. We also provide selective confidence bound for the difference between the largest and the second largest natural parameters.
\end{abstract}

\section{Introduction}
\label{sec:introduction}

We often make observations that form a joint exponential family distribution. While it might be relatively obvious in the independent case, the observations can well be dependent and hinge on the natural parameters. Comparison of these natural parameters can produce useful inferences.

A classic question is on how to statistically verify empirical rankings based on simple exponential family models. As motivation, consider a 2016 Quinnipiac University poll of $890$ Iowa Republicans Poll. \cite{quinnipiac} The poll found that Trump was in the lead with $31\%$ of the vote, Cruz is the first runner-up with $24\%$, followed by Rubio at $17\%$. The other ten candidates, including ``Don't know'', trailed behind. \Cref{tbl:poll} shows the results of the poll. Note that we have made a simplifying assumption that poll represents a random sample of Iowa Republicans --- i.e.\ that the data are multinomial, with parameter $\left(\pi_{\text{Trump}}, \pi_{\text{Cruz}}, \pi_{\text{Rubio}}, \ldots\right)$ representing their support in the Iowa Republican population. In reality, Quinnipiac University Poll Institute has processed the data to make the sample more representative of the population of likely voters.

\begin{table}[htbp]
\begin{center}
\begin{tabular}{c c c c}
	\hline
	Rank & Candidate & Result & Votes \\
	\hline
	$1$ * & Trump & $31\%$ & $276$ \\
	$2$ * & Cruz & $24\%$ & $214$ \\
	$3$ * & Rubio & $17\%$ & $151$ \\
	$4$ * & Carson & $8\%$ & $71$ \\
	$5$ & Paul & $4\%$ & $36$ \\
	$6$ & Bush & $4\%$ & $36$ \\
	$7$ & Huckabee & $3\%$ & $27$ \\
	$\vdots$ & $\vdots$ & $\vdots $ & $\vdots$ \\
	\hline
\end{tabular}
\end{center}
\caption{Results from a February 1, 2016 Quinnipiac University poll of $890$ Iowa Republicans. To compute the last column (Votes), we make the simplifying assumption that the reported percentages in the third column (Result) correspond to raw vote shares among survey respondents. The asterisks indicate that the rank is verified through a step-down procedure.}
\label{tbl:poll}
\end{table}

Having observed that Trump received the most votes in this poll, we want to ask whether he is actually in the lead in the population of all Iowa Republicans. Intuitively, we would compare Trump to Cruz, as well as the other candidate. This intuitive method however has a few issues.

\begin{enumerate}

\item This has a hidden upward selection bias, or ``winner's curse'', as we are only testing this hypothesis as Trump is leading in the polls. In other words, the hypothesis itself is random. Alternatively, we can note that the marginal type I error rate is indeed not so straightfoward. If the null hypothesis is ``$H_0: \text{Leader in polls has most support}$'', then for any distribution $F$ the marginal type I error rate is

\begin{equation}
\PP_F\left(\text{reject } H_0\right) = \sum_{j \text{ is a candidate}} \PP_F\left(\text{reject } H_0 \middle| j \text{ leads in polls}\right) \PP_F \left(j \text{ leads in polls}\right).
\label{eqn:marginal_error}
\end{equation}

\item Comparing Trump to all other candidates involves multiple comparisons. Without considering the structure of this problem, common methods like Tukey's correction \cite{Tukey:1951} may largely decrease the test power.

\end{enumerate}

We will construct a test as outlined by Fithian, Sun and Taylor in \cite{Fithian:2014ws}. The fundamental idea is to consider the selective type I error rate
$$\PP_F\left(\text{reject } H_0 \middle| j \text{ leads in polls} \right), ~~~~~~~~ \text{where $j$ is a candidate,}$$
instead. Note that controlling this selective type I error rate at $\alpha$ provides control of the marginal type I error rate given in \Cref{eqn:marginal_error} at $\alpha$ too.

Surprisingly, this also tackles the second issue above. The test reduces the multiple comparison problem into one comparison between Trump and Cruz. In fact, if 100 John Does entered the race with practically no support from the Iowa Republicans, the change in number of candidates will not change the test.

More generally, when we observe a random vector $(X_1, \ldots, X_n)$ from an exponential family, and whichever random variable is largest, we want to test whether it is in fact stochastically larger than the other random variables.

\subsection{Related work}

Gutmann and Maymin \cite{Gutmann:1987fk} has worked on a similar question where the observations are from a location family, and the location parameters are compared. In contrast, a related paper by Karnnan and Panchapakesan \cite{Karnnan:2009iv} discussed a scale family instead, comparing the scale parameters. Bofinger \cite{Bofinger:1991hv} gave a location-scale family generated by the exponential distribution as well. However, as location-scale families have limited overlap with exponential families, the counterpart question for exponential families have remained unaddressed. Location-scale families assumed independence between observations, while this is not required in exponential families. A follow-up paper by Maymin and Gutmann \cite{Maymin:1992fz} gave a slightly more general result, applicable to more than location-scale families, yet still under the constraints of independence.

In the vicinity of the polling problem above, Nettleton \cite{Nettleton:2009ht} provided an asymptotic test for multinomial distribution, imposing the selection by considering intersection-union tests. Ng and Panchapakesan \cite{Ng:2007cn} also analyzed the multinomial case for an exact test, but with an additional restriction that maximum observation is a known constant.

The subset selection problem solved in \cite{Gupta:1967wg} by Gupta and Nagel can indeed be used to solve the multinomial case. They selected a subset that contains the largest, or ``tagged'', parameter with probability $1-\alpha$. Confirming the largest parameter is thus equivalent to asserting the selected subset has size $1$. \Cref{sec:multinomial_example} includes a comparison of our proposed test and their test.

\subsection{Main result}

In this paper, we focus on Schur-concave exponential family, a broad class of distribution that is defined in \Cref{sec:exponential_families} and includes various examples listed in \Cref{sec:applications}. We constructed a selective level-$\alpha$ test for verifying that the largest observation is stochastically largest as well. The test provides selective type I error control, as well as enables us to construct confidence bound on the differences between the natural parameters and verify the order of the rest of natural parameters.

\subsection{Outline}

\Cref{sec:multinomial_example} gives an exploratory example based on the multinomial distribution, along with a comparison to an earlier method by Gupta and Nagel. \Cref{sec:exponential_families} gives an in-depth discussion and proof of the main result. \Cref{sec:selective_confidence_bound,sec:step_down_procedure} extend the main result to construct confidence bounds for the gap between natural parameters and a step-down procedure that verifies the order of the rest of the natural parameters with FWER and FDR control, respectively. \Cref{sec:applications} provides a few applications, including both distributions with known tests and those without.

\section{Multinomial example}
\label{sec:multinomial_example}

Suppose we observe
$$\left(X_1, \ldots, X_n\right) \sim \text{Multinomial}\left(N, \pi\right)$$
and we want to test
$$H_{0j}: \pi_j \le \max_{k \ne j} \pi_k = \bigcup_{k \ne j} H_{0jk}: \pi_j \le \pi_k$$
when $X_j$ is larger than all other $X_k$. To break ties, we introduce independent auxiliary random variable $U_j \sim U\left[0,1\right]$, and opt to test $H_{0j}$ in the event of
$$A_j = \left\{X_j + U_j > \max_{k \ne j} X_k + U_k\right\}.$$
The distribution, written in an exponential family format, is
$$\exp\left(X_1 \log \pi_1 + \cdots + X_n \log \pi_n\right) \frac{1_{X_1 + \cdots + X_n = N}}{X_1! \cdots X_n!}.$$

Without loss of generality, we will assume $X_1$ is considered largest with the tie-breaking method above in mind. Following the construction in \cite{Fithian:2014ws}, if we want to construct $p$-values $p_{1j}$ for $H_{01j}$, we need to first re-parametrize such that the selection event $A_1$ can be expressed as the sufficient statistic. The distribution is now
$$\exp\left(\frac{X_1 - X_j}{2} \left(\log \pi_1 - \log \pi_j\right) + \cdots + \frac{X_1 + X_j}{2} \left(\log \pi_1 + \log \pi_j\right) + \cdots + X_n\right) \frac{1_{X_1 + \cdots + X_n \log \pi_n = N}}{X_1! \cdots X_n!}.$$

Next we condition on the sufficient statistics that are multiplied to the the nuisance parameter, in other words, we consider the conditional law
$$\mathcal{L}_{\theta_1 = \theta_j}\left(\frac{X_1 - X_j}{2} \middle| X_2, \ldots, \frac{X_1 + X_j}{2}, \ldots, X_n, A_1\right),$$
or equivalently, the conditional law
$$\mathcal{L}_{\theta_1 = \theta_j}\left(X_1 \middle| X_2, \ldots, \frac{X_1 + X_j}{2}, \ldots, X_n, A_1\right),$$
which is the distribution $\text{Binomial}\left(X_1 + X_j, \frac{1}{2}\right)$ truncated by the event $A_1$. The one-sided $p$-value $p_{1j}$ is thus given as
$$\frac{\sum_{t = X_1}^{X_1 + X_j} \binom{X_1 + X_j}{t} \left(\frac{1}{2}\right)^{X_1 + X_j}}{\sum_{t = \left(X_1 + X_j\right)/2}^{X_1 + X_j} \binom{X_1 + X_j}{t} \left(\frac{1}{2}\right)^{X_1 + X_j}} = \frac{\sum_{t = X_1}^{X_1 + X_j} \binom{X_1 + X_j}{t}}{\sum_{t = \left(X_1 + X_j\right)/2}^{X_1 + X_j} \binom{X_1 + X_j}{t}},$$
and to account for the tie-breaking we adopted earlier, we
\begin{itemize}
\item multiply the first term in the numerator and the numerator by $1/m$ where $m$ is the number of observations tied for largest; otherwise,
\item multiply the first term in the denominator by $1/2$ if $X_1$ and $X_2$ has the same parity.
\end{itemize}
Noticing that if there are ties for the largest the $p$-value is $1$ and the denominator is really $1/2$ otherwise, we can write
$$p_{1j} = 1 \wedge 2 \sum_{t=X_1}^{X_1 + X_j} \binom{X_i + X_j}{t}.$$

It is possible to check that $p_{12} \ge p_{1j}$ for any $j > 2$. Since the null hypothesis we are testing is a union of these smaller null hypothesis, the type I error rate is
$$\PP_{H_{01}}\left(p_{12} < \alpha \middle| A_1\right) \le \max_{j>1} \PP_{H_{01j}}\left(p_{12} < \alpha \middle| A_1\right) \le \max_{j>1} \PP_{H_{01j}}\left(p_{1j} < \alpha \middle| A_1\right) \le \alpha,$$
meaning that it is sufficient to construct a one-sided test between $X_1$ and $X_2$ and consider only $p_{12}$.

\subsection{Connection with the subset selection problem}
\label{sec:compare_subset}

\section{Exponential families}
\label{sec:exponential_families}

We would like to extend the result from multinomials to exponential families. We henceforth focus on exponential distribution taking the form
\begin{equation}
X \sim \exp\left(\theta_1 X_1 + \cdots + \theta_n X_n\right) g\left(X\right) h\left(\theta\right).
\label{eqn:exp_family}
\end{equation}
It is reasonable to assume that the distribution is ``symmetric'', i.e.\ if $\theta_j = \theta_k$, then the probability distribution remains the same when $X_j$ and $X_k$ are swapped. This corresponds to requiring $g\left(X\right)$ to be symmetric. We would also like to introduce a fairly mild additional condition that $g$ is {\em Schur-concave}. But first we define the notion of {\em majorization}.

\begin{definition}
For two vectors $a$ and $b$ in $\RR^n$, suppose permuting the two vectors in descending order gives
$a_{\left(1\right)} \ge \cdots \ge a_{\left(n\right)}$ and $b_{\left(1\right)} \ge \cdots \ge b_{\left(n\right)}$. We say that $a \succeq b$ ($a$ majorizes $b$) if for $1 \le i < n$,
\begin{align*}
a_{\left(1\right)} + \cdots + a_{\left(i\right)} & \ge b_{\left(1\right)} + \cdots + b_{\left(i\right)} \\
a_{\left(1\right)} + \cdots + a_{\left(n\right)} & = b_{\left(1\right)} + \cdots + b_{\left(n\right)}
\end{align*}
This forms a partial order in $\RR^n$.
\end{definition}

Intuitively, majorization is a partial order that monitors the evenness of a vector: the more even a vector is, the ``smaller'' it is. There are two properties of majorization that we will use in this section.

\begin{lemma}
\label{lma:two_properties}
\begin{itemize}
\item Suppose $\left(x_1, x_2, x_3, \ldots\right)$ and $\left(x_1, x_2', x_3' \ldots\right)$ are two vectors in $\RR^n$. Then
$$\left(x_1, x_2, x_3, \ldots\right) \succeq \left(x_1, x_2', x_3', \ldots\right) \text{ if and only if } \left(x_2, x_3, \ldots\right) \succeq \left(x_2', x_3', \ldots\right).$$
\item (Principle of transfer) If $x_1 > x_2$ and $t \ge 0$, then
$$\left(x_1 + t, x_2, x_3, \ldots\right) \succeq \left(x_1, x_2 + t, x_3\right).$$
If the $t \le 0$, the majorization is reversed.
\end{itemize}
\end{lemma}

\begin{proof}
\begin{itemize}

\item The property follows from an equivalent formulation of majorization listed in Marshall, Olkin and Arnold \cite{Marshall:2010hb}, where $x \succeq y$ if and only if
$$\sum_{j=1}^n x_n = \sum_{j=1}^n y_n ~~~~ \text{ and } ~~~~ \sum_{j=1}^n \left(x_j - a\right)_+ \ge \sum_{j=1}^n \left(y_j - a\right)_+ \text{ for all } a \in \RR.$$

\item Proved in Marshall, Olkin and Arnold.

\end{itemize}
\end{proof}

\begin{definition}
A function $g$ is Schur-concave if $x \succeq y$ implies $g\left(x\right) \le g\left(y\right)$.
\end{definition}

A Schur-concave function is symmetric by default. Conversely a symmetric and log-concave function is Schur-concave, thus many common exponential family distributions lie in this class. Schur-concave function indeed appears a lot, \Cref{sec:applications} includes both continuous and discrete examples.

Now suppose the carrier distribution $g$ in \Cref{eqn:exp_family} is indeed Schur-concave. We hereon call the class of distribution satisfying this {\em Schur-concave exponential family}. Without loss of generality, we can assume $X_1 \ge X_2 \ge \max_{k > 2} X_k$. We will be testing the null hypothesis $H_{01}: \theta_1 \le \max_{j > 1} \theta_j$, which is the union of the null hypotheses $H_{0j}: \theta_1 \le \theta_j$ for $j > 1$.

Rejecting this hypothesis corresponds to inferring that $\theta_1 > \max_{j>1} \theta_j$. This is equivalent to $X_1$ being stochastically larger than $X_j$ for any $j > 1$.

\begin{theorem}
\label{thm:stoch}
$X_1$ is greater than $X_2$ is stochastic order if and only if $\theta_1 > \theta_2$.
\end{theorem}

\begin{proof}

We prove the ``if'' part first. For any fixed $a$, and $X_1 \ge a$ and $X_2 < a$, we have
$$\exp\left(\theta_1 X_1 + \theta_2 X_2 + \cdots + \theta_n X_n\right) g\left(X\right) h\left(\theta\right) \ge \exp\left(\theta_1 X_2 + \theta_2 X_1 + \cdots + \theta_n X_n\right) g\left(X\right) h\left(\theta\right).$$
Integrating both sides over the region $\left\{X: X_1 \ge a, X_2 < a\right\}$, summing instead if $X$ is a discrete vector, gives
$$\PP\left(X_1 \ge a, X_2 < a\right) \ge \PP\left(X_1 < a, X_2 \ge a\right).$$
Now adding $\PP\left(X_1 \ge a, X_2 \ge a\right)$ to both probabilities gives
$$\PP\left(X_1 \ge a\right) \ge \PP\left(X_2 \ge a\right),$$
meaning that $X_1$ is greater than $X_2$ in stochastic order. The converse follows from swapping the role of $\theta_1$ and $\theta_2$.

\end{proof}

We are now ready to state and prove our main result.

\begin{theorem}
Suppose we observe $X = \left(X_1, \ldots, X_n\right)$ from an exponential family with natural parameter $\theta = \left(\theta_1, \ldots, \theta_n\right)$, i.e.
$$X \sim \left(\theta_1 X_1 + \cdots + \theta_n X_n\right) g\left(X\right) h\left(\theta\right),$$
with a Schur-concave carrier measure $g$. Then there is a selective level-$\alpha$ test that verifies $\theta_{\left(1\right)} > \theta_{\left(2\right)}$ by comparing only $X_{\left(1\right)}$ and $X_{\left(2\right)}$. The test also verifies that $X_{\left(1\right)} \ge X_{\left(j\right)}$ stochastically for all $j > 1$. Here $X_{\left(j\right)}$ is the order statistic where $X_{\left(1\right)} \ge \cdots \ge X_{\left(n\right)}$.
\label{thm:main_result}
\end{theorem}

\begin{proof}

Without loss of generality, assume $X_1 \ge \ldots \ge X_n$. Following the framework in Fithian, Sun and Taylor \cite{Fithian:2014ws}, we consider the selection event $A_1 = \left\{X_1 \ge \max_{j > 1} X_j\right\}$. For convenience, we let
$$D_{jk} = \frac{X_j - X_k}{2} ~~~~ \text{ and } ~~~~ M_{jk} = \frac{X_j + X_k}{2}.$$

With the same strategy in \Cref{sec:multinomial_example}, we re-parametrize to replace $X_1$ and $X_j$ with $D_{1j}$ and $M_{1j}$ and consider
\begin{equation}
\mathcal{L}_{D_{1j} = \theta_1 - \theta_j = 0} \left(D_{1j} \middle| M_{1j}, X_2, \ldots, X_n, A_1\right), \text{ where } A_1 = \left\{D_{1j} \ge \max_{k \ne 1, j} X_k - M_{1j}\right\} \cap \left\{D_{1j} \ge 0\right\}.
\label{eqn:cond_law}
\end{equation}
The conditional law in \Cref{eqn:cond_law}, in particular, is a truncated distribution
\begin{align*}
D_{1j} & \sim \exp\left(\left(\theta_1 - \theta_j\right) D_{1j} + \theta_2 X_2 + \cdots + \left(\theta_1 + \theta_j\right) M_{1j} + \cdots + \theta_n X_n \right) \\
& ~~~~~~~~ g\left(M_{ij} + D_{ij}, X_2, \ldots, M_{ij} - D_{ij}, \ldots X_n\right) 1_{A_1} \\
& \sim g\left(M_{ij} + D_{ij}, X_2, \ldots, M_{ij} - D_{ij}, \ldots X_n\right) 1_{A_1}.
\end{align*}

The $p$-value for $H_{0j}$ is thus
\begin{equation}
p_{1j} = \frac{\int_{D_{1j}}^\infty g\left(M_{1j} + z, X_2, \ldots, M_{1j} - z, \ldots, X_n\right) \,dz}{\int_{\max\left\{X_2 - M_{1j}, 0\right\}}^\infty g\left(M_{1j} + z, X_2, \ldots, M_{1j} - z, \ldots, X_n\right) \,dz}.
\label{eqn:p1j}
\end{equation}

Without loss of generality, it is sufficient to show that $p_{12} \ge p_{13}$. In the computation of either $p$-values, $X_4, \ldots, X_n$ are all conditioned on. The first point in \Cref{lma:two_properties} says that we may assume $n = 3$ without affecting the Schur-concavity of $g$. This allows us to clean up our notation and
\begin{align*}
p_{12} & = \frac{\int_{D_{12}}^\infty g\left(M_{12} + z, M_{12} - z, X_3\right) \,dz}{\int_0^\infty g\left(M_{12} + z, M_{12} - z, X_3\right) \,dz} \\
p_{13} & = \frac{\int_{D_{13}}^\infty g\left(M_{13} + z, X_2, M_{13} - z\right) \,dz}{\int_{\max\left\{X_2 - M_{13}, 0\right\}}^\infty g\left(M_{13} + z, X_2, M_{13} - z\right) \,dz}
\end{align*}

Suppose $X_2 < M_{13}$, then we can re-parametrize the integrals above to give
\begin{align*}
p_{12} & = \frac{\int_0^\infty g\left(X_1 + z, X_2 - z, X_3\right) \,dz}{\int_0^\infty g\left(M_{12} + z, M_{12} - z, X_3\right) \,dz} \\
p_{13} & = \frac{\int_0^\infty g\left(X_1 + z, X_2, X_3 - z\right) \,dz}{\int_0^\infty g\left(M_{13} + z, X_2, M_{13} - z\right) \,dz}
\end{align*}

\begin{figure}[htbp]
\begin{center}
\begin{tikzpicture}
	\draw[dashed, thick] (-3, 1.5) -- (-2, 1);
	\draw[->, thick] (-2, 1) -- (6, -3);
	\draw[->, thick] (-3, -2) -- (6, 4);
	\fill (0, 0) circle(2pt) node[right] {$\left(X_1, X_2, X_3\right)$};
	\fill (-2, 1) circle(2pt) node[above right] {$\left(M_{12}, M_{12}, X_3\right)$};
	\fill (-3, -2) circle(2pt) node[below] {$\left(M_{13}, X_2, M_{13}\right)$};
	\fill (-3, 1.5) circle(2pt) node[above] {$\left(M_{13}, X_2 + D_{13}, X_3\right)$};
	\draw[dotted, thick] (-3, 1.5) -- (-3, -2) node[midway, below, rotate=-90] {$\succeq$};
	\draw[dotted, thick] (-2, 1) -- (-2, -4/3) node[midway, below, rotate=-90] {$\succeq$};
	\draw[dotted, thick] (3, -1.5) -- (3, 2) node[midway, below, rotate=-90] {$\succeq$};
	\draw[dotted, thick] (5, -2.5) -- (5, 10/3) node[midway, below, rotate=-90] {$\succeq$};
\end{tikzpicture}
\end{center}
\caption{The two $p$-values constructed corresponds to taking integrals of $g$ along these rays, that lie on a level set of $x_1 + x_2 + x_3$. The dashed line corresponds to extending the integral in the denominator of \Cref{eqn:int_extension}. The dotted lines with the majorization symbols show the majorization relation between vectors on the two rays.}
\label{fig:rays}
\end{figure}

We can re-parametrize this further, thanks to some geometric intuition (ref.\ \Cref{fig:rays}) that both $p$-values are actually integrals of $g$ along intersecting rays. We have
\begin{align}
p_{12} & = \frac{\int_0^\infty g\left(X_1 + z, X_2 - z, X_3\right) \,dz}{\int_{-D_{12}}^\infty g\left(X_1 + z, X_2 - z, X_3\right) \,dz} \nonumber \\
& \ge \frac{\int_0^\infty g\left(X_1 + z, X_2 - z, X_3\right) \,dz}{\int_{-D_{13}}^\infty g\left(X_1 + z, X_2 - z, X_3\right) \,dz} \label{eqn:int_extension} \\
p_{13} & = \frac{\int_0^\infty g\left(X_1 + z, X_2, X_3 - z\right) \,dz}{\int_{-D_{13}}^\infty g\left(X_1 + z, X_2, X_3 - z\right) \,dz} \label{eqn:p13}
\end{align}

Indeed from the second point \Cref{lma:two_properties} we have
$$\left(X_1 + z, X_2 - z, X_3\right) \succeq \left(X_1 + z, X_2, X_3 - z\right)$$
for $z \le 0$ and the majorization reversed for $z \ge 0$. So Schur-concavity shows that
$$g\left(X_1 + z, X_2 - z, X_3\right) \le g\left(X_1 + z, X_2, X_3 - z\right)$$
for $z \le 0$, and the inequality reversed for $z \ge 0$. Consequently, $p_{12} \ge p_{13}$ by comparing \Cref{eqn:int_extension,eqn:p13}.

For the alternative case where $X_2 \ge M_{13}$, it follows from a similar proof. In either cases, $p_{12} \ge p_{13}$, or in generality, $p_{12} \ge p_{1j}$ for $j \ge 1$. A test based on only $X_1$ and $X_2$ is sufficient for the null hypothesis $H_{0j}$, if the carrying measure $g$ is Schur-concave. By \Cref{thm:stoch}, rejecting this null hypothesis is equivalent to inferring that $X_1 \ge X_j$ for all $j>1$ stochastically.

\end{proof}

As the construction of this test follows \cite{Fithian:2014ws}, it is also a uniformly most powerful unbiased selective level-$\alpha$ test.

If the distribution is discrete, the proof above holds true. Instead of performing integrals, the lattice points on the rays will be summed. If ties are broken independently and randomly, as in \Cref{sec:multinomial_example}, the end points on the rays can be considered as half a point.

\section{Selective confidence bound}
\label{sec:selective_confidence_bound}

We can take the idea above further and construct confidence bound for $\theta_1 - \max_{j>1} \theta_j$. This can be achieved by considering a statistical test, to see if $\theta_1 - \max_{j>1} \theta_j \le \delta$, followed by the duality of confidence interval and statistical test.

\begin{theorem}
In the same setup as \Cref{thm:main_result}, there is a selective level-$\alpha$ lower confidence bound for $\theta_{\left(1\right)} - \max_{j>1} \theta_{\left(j\right)}$.
\end{theorem}

\begin{proof}

Again we start with assuming $X_1 \ge \cdots \ge X_n$. The null hypothesis $H_{01}^\delta$ can be thought of as $\bigcup_{j > 1} H_{0j}^\delta$, where $H_{0j}^\delta$ is $\theta_1 - \theta_j \le \delta$. In other words, we focus on the conditional law
$$\mathcal{L}_{\theta_1 - \theta_j = \delta} \left(D_{1j} \middle| D_{1j}, X_2, \ldots, X_n, A\right),$$
which is the truncated distribution
\begin{align*}
D_{1j} & \sim \exp\left(\left(\theta_1 - \theta_j\right) D_{1j} + \theta_2 X_2 + \cdots + \left(\theta_1 + \theta_j\right) M_{1j} + \cdots + \theta_n X_n \right) \\
& ~~~~~~~~ g\left(M_{ij} + D_{ij}, X_2, \ldots, M_{ij} - D_{ij}, \ldots X_n\right) 1_{A_1} \\
& \sim \exp\left(\delta D_{ij}\right) g\left(M_{ij} + D_{ij}, X_2, \ldots, M_{ij} - D_{ij}, \ldots X_n\right) 1_{A_1}.
\end{align*}

The $p$-values thus are
$$p_{1j} = \frac{\int_{D_{1j}}^\infty \exp\left(\delta z\right) g\left(M_{1j} + z, X_2, \ldots, M_{1j} - z, \ldots, X_n\right) \,dz}{\int_{\max\left\{X_2 - M_{1j}, 0\right\}}^\infty \exp\left(\delta z\right) g\left(M_{1j} + z, X_2, \ldots, M_{1j} - z, \ldots, X_n\right) \,dz}.$$

As before in \Cref{sec:exponential_families}, without loss of generality we assume $n = 3$. Once again it is sufficient to show that $p_{12} \ge p_{13}$. We have the same two cases. If $X_2 < M_{13}$, then
\begin{align*}
p_{12} & = \frac{\int_0^\infty \exp\left(\delta \left(z + D_{12}\right)\right) g\left(X_1 + z, X_2 - z, X_3\right) \,dz}{\int_{-D_{12}}^\infty \exp\left(\delta \left(z + D_{12}\right)\right) g\left(X_1 + z, X_2 - z, X_3\right) \,dz} \\
& \ge \frac{\int_0^\infty \exp\left(\delta z\right) g\left(X_1 + z, X_2 - z, X_3\right) \,dz}{\int_{-D_{13}}^\infty \exp\left(\delta z\right) g\left(X_1 + z, X_2 - z, X_3\right) \,dz} \\
p_{13} & = \frac{\int_0^\infty \exp\left(\delta \left(z + D_{13}\right)\right) g\left(X_1 + z, X_2, X_3 - z\right) \,dz}{\int_{-D_{13}}^\infty \exp\left(\delta \left(z + D_{13}\right)\right) g\left(X_1 + z, X_2, X_3 - z\right) \,dz} \\
& = \frac{\int_0^\infty \exp\left(\delta z\right) g\left(X_1 + z, X_2, X_3 - z\right) \,dz}{\int_{-D_{13}}^\infty \exp\left(\delta z\right) g\left(X_1 + z, X_2, X_3 - z\right) \,dz}
\end{align*}

The same argument in \Cref{fig:rays} shows that $p_{12} \ge p_{13}$. This is again true for the case where $X_2 \ge M_{13}$ as well. This means that the bound can be constructed considering only $p_{12}$.

\end{proof}

\section{Step down procedure}
\label{sec:step_down_procedure}

If one is interested in verifying more than just the ``winner'', this selective test can also be extended as a step-down procedure to verify the ``first runner-up'' and ``second runner-up'' etc., while controlling the FWER and the FDR.

Formally, we wish to find the biggest $j$ such that we can infer
$$\theta_1 > \ldots > \theta_j > \max_{k>j} \theta_k.$$
If $j_0$ is the true value of $j$, the two error rates we mentioned above refer to
$$\text{FWER} = \PP\left(j \ne j_0\right) ~~~~ \text{ and } ~~~~ \text{FDR} = \EE\left[\frac{\left(j - j_0\right)_+}{j}\right],$$
where $\left(j - j_0\right)_+ / j$ is taken to be $0$ if $j = 0$.

\begin{theorem}
There is a step-down procedure that infers $j_0$ above with both the FWER and FDR controlled at $\alpha$.
\end{theorem}

\begin{proof}

This can be fitted into the selective sequential model selection framework proposed by Fithian, Taylor and Tibshirani \cite{Fithian:2015uj}. Given the observations $X_1 \ge \cdots \ge X_n$, drawn from an unknown distribution $F$, we consider the sequence of null hypothesis of
$$H_{0j}: \theta_j \le \max_{k > j} \theta_k.$$
Alternatively, we can think of them as a sequence of nested model
$$M_0\left(X\right) \subseteq M_1\left(X\right) \subseteq \cdots \subseteq M_n\left(X\right), ~~~~~~~~ M_j\left(X\right)^c = \left\{\theta_1 > \cdots > \theta_j > \max_{k > j} \theta_k\right\},$$
and the each $M_j$ depends on $X$ through the order of $X$. The step-down procedure for rejecting $H_{0j}$ is equivalent to selecting the smallest $j$ for which $F \in M_j\left(X\right)$.

We can construct selective $p$-values by conditioning on $M_j\left(X\right)$, as well as other nuisance parameters. Specifically, we are conditioning on the selection of the model $M_j\left(X\right)$. We can take $p_j$ to be the survival function of the conditional law
\begin{align}
&~ \mathcal{L}_{\theta_j = \theta_{j+1}} \left(D_{j\left(j+1\right)} \middle| M_j\left(X\right), X_1, \ldots, X_{j-1}, M_{j\left(j+1\right)}, X_{j+2}, \ldots, X_n\right) \nonumber \\
= &~ \mathcal{L}_{\theta_j = \theta_{j+1}} \left(D_{j\left(j+1\right)} \middle| \left\{X_1 > \ldots > X_j > \max_{k > j} X_k\right\}, X_1, \ldots, X_{j-1}, M_{j\left(j+1\right)}, X_{j+2}, \ldots, X_n\right) \nonumber \\
= &~ \mathcal{L}_{\theta_j = \theta_{j+1}} \left(D_{j\left(j+1\right)} \middle| \left\{X_{j-1} > X_j > M_{j\left(j+1\right)}\right\}, X_1, \ldots, X_{j-1}, M_{j\left(j+1\right)}, X_{j+2}, \ldots, X_n\right). \label{eqn:step_down_law}
\end{align}

\begin{figure}[htbp]
\begin{center}
\begin{tikzpicture}
	\draw[dashed, thick] (-3, 1.5) -- (-2, 1);
	\draw[thick] (-2, 1) -- (5, -2.5);
	\draw[thick] (-3, -2) -- (5, 10/3);
	\fill (0, 0) circle(2pt) node[right] {$\left(X_j, X_{j+1}, X_k\right)$};
	\fill (-2, 1) circle(2pt) node[above right] {$\left(M_{j\left(j+1\right)}, M_{j\left(j+1\right)}, X_k\right)$};
	\fill (-3, -2) circle(2pt) node[below] {$\left(M_{jk}, X_{\left(j+1\right)}, M_{jk}\right)$};
	\fill (-3, 1.5) circle(2pt) node[above] {$\left(M_{jk}, X_{j+1} + D_{jk}, X_k\right)$};
	\draw[dotted, thick] (-3, 1.5) -- (-3, -2) node[midway, below, rotate=-90] {$\succeq$};
	\draw[dotted, thick] (-2, 1) -- (-2, -4/3) node[midway, below, rotate=-90] {$\succeq$};
	\draw[dotted, thick] (3, -1.5) -- (3, 2) node[midway, above, rotate=-90] {$\succeq$};
	\draw[dotted, thick] (5, -3) -- (5, 4) node[midway, above, rotate=-90] {Truncation for $X_j < X_{j-1}$};
\end{tikzpicture}
\end{center}
\caption{The two $p$-values constructed corresponds to taking integrals of $g$ along these segments, that lie on a level set of $x_j + x_{j+1} + x_k$. The dashed line corresponds to extending the integral in the denominator of \Cref{eqn:int_extension}. The dotted line on the far right is the truncation that enforces $X_j < X_{j-1}$.}
\label{fig:crop_rays}
\end{figure}

Here we are only comparing $X_j$ to $X_{j+1}$ by \Cref{sec:exponential_families}. The upper truncation for $X_j$ can be represented by cropping \Cref{fig:rays} along a vertical line, shown in \Cref{fig:crop_rays}, thus the proof of \Cref{thm:main_result} on sufficiency to compare $X_1$ and $X_2$ remains valid with appropriate conditioning. Again we can construct the $p$-values as in \Cref{eqn:p1j} for $k>j$.

$$p_{jk} = \frac{\int_{D_{jk}}^{X_{j-1}} g\left(X_1, \ldots, M_{jk} + z, \ldots, M_{jk} - z, \ldots, X_n\right) \,dz}{\int_{\max\left\{X_{j+1} - M_{jk}, 0\right\}}^{X_{j-1}} g\left(X_1, \ldots, M_{jk} + z, \ldots, M_{jk} - z, \ldots, X_n\right) \,dz}.$$

Hence similar to the proof of \Cref{thm:main_result}, Schur-concavity ensures $p_{j\left(j+1\right)} \ge p_{jk}$ for all $k>j$, meaning that it is sufficient to compare $X_j$ and $X_{j+1}$. In fact, we can take $p_j = p_{j\left(j+1\right)}$. These are valid selective $p$-value as required in Fithian, Taylor and Tibshirani, as
$$\PP_F \left(p_j \le \alpha \middle| M_{j-1}\left(X\right)\right) \le \alpha \text{ a.s.}, ~~~~~~~~ F \in M_{j-1}\left(X\right)$$
by tower property.

The conditioning above indeed holds some significance. The sufficient filtration \cite{Fithian:2015uj} $\mathcal{F}_k$ is given as the $\sigma$-field
\begin{align*}
\mathscr{F}_k & = \sigma\left(M_0\left(X\right), \ldots, M_j\left(X\right), X_1, \ldots, X_{j-1}, \frac{X_j + X_{j+1}}{2}, X_{j+2}, \ldots, X_n\right) \\
& = \sigma\left(\left\{X_1 > \ldots > X_j > \max_{k>j} X_k\right\}, X_1, \ldots, X_{j-1}, \frac{X_j + X_{j+1}}{2}, X_{j+2}, \ldots, X_n\right) \\
& = \sigma\left(M_j\left(X\right), X_1, \ldots, X_{j-1}, \frac{X_j + X_{j+1}}{2}, X_{j+2}, \ldots, X_n\right),
\end{align*}
which is the conditioning we used just now. Hence the nested sequence of model satisfies the subpath sufficiency principle, and the $p$-values sequence $p_j$ is independent on nulls, as defined in and shown in Theorem 4 of \cite{Fithian:2015uj}. Thus the step-down procedure where we keep rejecting $H_{0j}$ until the first time that $p_j > \alpha$ controls FWER and FDR.

\end{proof}

\section{Applications}
\label{sec:applications}

Our result above applies to a wide range of joint distributions. Note that since multiplying $-1$ preserves the majorization partial order, the following examples also work in verifying the minimum.

\begin{enumerate}

\item Correlated Gaussian: Suppose $X \sim N\left(\mu, \Sigma\right)$, where
\begin{align*}
\mu & = \left(\mu_1, \ldots, \mu_n\right), \\
\Sigma & = \begin{pmatrix}
1 & p & \cdots & p \\
p & 1 & \ddots & \vdots \\
\vdots & \ddots & \ddots & p \\
p & \cdots & p & 1
\end{pmatrix}
\end{align*}
and $p$ is fixed. Then the natural parameter is ordered the same way as $\mu$. Our test can thus be used to verify the order of the mean.

\item Multinomial distribution, e.g.\ the Iowa Republican poll example in \Cref{sec:introduction}.
$$p\left(x\right) \propto \exp\left(x^T \left(\log \pi\right)\right) \frac{1_{\left\{x_1 + \cdots + x_n = N\right\}}}{x_1! \cdots x_n!}$$
Comparing $\pi_i$ is the same $\log \pi_i$, the natural parameters. Note that the multinomial coefficient is naturally Schur-concave. The step-down procedure is applied to verify the position of the other candidates. Note that for a multinomial distribution, the conditioning \Cref{eqn:step_down_law} is equivalent to conditioning only on $M_{j\left(j+1\right)}$. We summarize the test in \Cref{tbl:poll_analysis}.

\begin{table}[htbp]
\begin{center}
\begin{tabular}{c c c c c}
\hline
Rank ($j$) & $X_{j-1}$ & $X_j$ & $X_{j+1}$ & $p$-value \\
\hline
$1$ & $\infty$ & $276$ & $214$ & $0.0065$ \\
$2$ & $276$ & $214$ & $151$ & $0.0015$ \\
$3$ & $214$ & $151$ & $71$ & $1.1126 \times 10^{-7}$ \\
$4$ & $151$ & $71$ & $36$ & $0.0014$ \\
$5$ & $71$ & $36$ & $36$ & $1.0000$ \\
\hline
\end{tabular}
\end{center}
\caption{Applying the step-down procedure to the Iowa Republican caucus. Each $p$-value is constructed by considering the conditional law in \Cref{eqn:step_down_law}, a $\text{Binomial}\left(X_j + X_{j-1}, \frac{1}{2}\right)$ truncated at $X_{j-1}$. The result was also indicated in \Cref{tbl:poll}.}
\label{tbl:poll_analysis}
\end{table}

We can also construct selective confidence bound for $\log \pi_1 - \max_{j>1} \log \pi_j$, i.e.\ find a $\delta^*$ such that
$$\PP_{H_{01}^\delta} \left(\text{reject } H_{01}^\delta: \log \pi_1 - \max_{j>1} \log \pi_j \le \delta \middle| A_1\right) < 0.05,$$
according to \Cref{sec:selective_confidence_bound}.

Once again, for multinomial distribution, conditioning on $M_{12}, X_3, \ldots, X_n$ is the same as conditioning on $M_{12}$, which gives $X_1 \sim \text{Binomial}\left(X_1 + X_2, \frac{e^\delta}{e^\delta + 1}\right)$, truncated at $M_{12}$. There is a maximum $\delta^*$ for this truncated binomial distribution has a survival function of $0.05$ at $X_1$.

This gives $\delta^* = 0.103142$. This translates to $\log \pi_1 - \max_{j>1} \log \pi_j \ge 0.103142$, or $\pi_1 / \max_{j>1} \pi_j \ge 1.10865$, with $0.95$-confidence. Or in terms of the Iowa Republican poll example, Trump has relatively around $11\%$ more support than any other candidates. This is smaller than the number deduced from raw vote count, $\left(276 - 214\right) / 214 \approx 29\%$, accounting for selection bias.

\item Independent binomials
$$p\left(x\right) \propto \exp\left(x^T \left(\log p\right)\right) \frac{1}{p_1! \left(N-p_1\right)! \cdots p_n! \left(N-p_n\right)!}$$

\item Round robin tournaments with the Bradley--Terry model, where each player has a score $\theta_i$, and the probability of player $j$ winning against player $k$ is
$$\frac{e^{\theta_j - \theta_k}}{1 + e^{\theta_j - \theta_k}} = \frac{e^{\left(\theta_j - \theta_k\right) / 2}}{e^{\left(\theta_j - \theta_k\right) / 2} + e^{\left(\theta_k - \theta_j\right) / 2}}.$$

Suppose $Y_{jk} = 1$ if $j$ beats $k$ and $Y_{jk} = 0$ if $k$ beats $j$. We will also adopt the convention that $Y_{jk} + Y_{kj} = 1$. Thus the joint distribution of $\left(Y_{jk}\right)_{j, k}$ is
$$p\left(\left(y_{jk}\right)_{j, k}\right) \propto \exp\left(\sum_j 2\theta_j \sum_{k \ne j} y_{jk}\right)  = \exp\left(\theta^T x\right),$$
where $x_j = \sum_{k \ne j} y_{jk}$. In other words, $x_j$ is the number of wins by player $j$.

If the individual results are masked and we only know about the net wins, then
$$p\left(x\right) \propto \exp\left(2\theta^T x\right) g\left(x\right),$$
where $g\left(x\right)$ is a function that count number of possible tournament results giving the net win vector $x$. A bijection proof shows that $x$ is indeed Schur-concave, allowing to apply the main result in comparing $2\theta$ and thus $\theta$.

\end{enumerate}

\bibliographystyle{plain}
\bibliography{papers,additional}

\end{document}

### 2016-04-05 multinomialPower.m
Matlab code for simulating Gupta and Nagel vs selective included

@@ -1,0 +1,48 @@
+function [] = multinomialPower (m, n, alpha, numSample)
+    delta = 0:0.01:2;
+    gn = gnPower(m, n, delta, alpha, numSample);
+    sel = arrayfun(@(x) selectivePower(m, n, x, alpha, numSample), delta);
+    plot(delta, sel, delta, gn, '--');
+    legend('Selective', 'Gupta and Nagel', 'Location', 'southeast');
+    xlabel('\delta');
+    ylabel('Power');
+end
+
+function [power] = selectivePower(m, n, delta, alpha, numSample)
+    pi = pr(n, delta);
+    X = mnrnd(m, pi, numSample);
+    secX = max(X(:, 2:end), [], 2);
+    nX = secX + X(:, 1);
+    accepted = nnz(cdf('Binomial', secX, nX, 0.5) * 2 < alpha);
+    power = accepted / numSample;
+end
+
+function [power] = gnPower(m, n, delta, alpha, numSample)
+    dStar = -Inf;
+    for r = 2:n
+        pi = ones([1, r]) ./ r;
+        X = mnrnd(m, pi, numSample);
+        [maxX, I] = max(X, [], 2);
+        X(sub2ind(size(X), 1:numSample, transpose(I))) = -Inf;
+        secX = max(X, [], 2);
+        diffX = sort(maxX - secX);
+        d = ceil(quantile(diffX, 1 - alpha));
+        if dStar < d
+            dStar = d;
+        end
+    end
+    power = zeros(size(delta));
+    for i = 1:numel(delta)
+        pi = pr(n, delta(i));
+        X = mnrnd(m, pi, numSample);
+        secX = max(X(:, 2:end), [], 2);
+        accepted = nnz(X(:, 1) - dStar > secX);
+        power(i) = accepted / numSample;
+    end
+end
+
+function [pi] = pr(n, delta)
+    pi = ones([1, n]);
+    pi(1) = exp(delta);
+    pi = pi ./ norm(pi, 1);
+end

### 2016-04-05 multinomialPower.m
Commented the Matlab code

@@ -1,46 +1,82 @@
+% Plots the power of the selective test vs. Gupta & Nagel for multinomial
+% distribution
+% m = number of votes, i.e. X1 + ... + Xn
+% n = number of candidates
+% alpha = level of the test
+% numSample = number of samples to take for simulation purposes
 function [] = multinomialPower (m, n, alpha, numSample)
+    % delta ranges from 0 to 2
     delta = 0:0.01:2;
-    gn = gnPower(m, n, delta, alpha, numSample);
     sel = arrayfun(@(x) selectivePower(m, n, x, alpha, numSample), delta);
+    gn = gnPower(m, n, delta, alpha, numSample);
     plot(delta, sel, delta, gn, '--');
     legend('Selective', 'Gupta and Nagel', 'Location', 'southeast');
     xlabel('\delta');
     ylabel('Power');
 end
 
+% Finds the selective test power for multinomial distribution
+% m = number of votes
+% n = number of candidates
+% distribution is proportional to (exp(delta), 1, ..., 1)
+% alpha = level of the test
+% numSample = number of samples to take for simulation purposes
 function [power] = selectivePower(m, n, delta, alpha, numSample)
+    % Probability vector of multinomial distribution
     pi = pr(n, delta);
+    % Generates the sample
     X = mnrnd(m, pi, numSample);
+    % secX is max(Xj; j>1), i.e. X2
     secX = max(X(:, 2:end), [], 2);
+    % nX is X1 + X2
     nX = secX + X(:, 1);
     accepted = nnz(cdf('Binomial', secX, nX, 0.5) * 2 < alpha);
     power = accepted / numSample;
 end
 
+% Find the test power of Gutpa and Nagel for multinomial distribution
+% m = number of votes
+% n = number of candidates
+% delta is a vector listing all the deltas we want to plot
+% alpha = level of the test
+% numSample = number of samples to take for simulation purposes
 function [power] = gnPower(m, n, delta, alpha, numSample)
+    % Initialization; dStar is the biggest d
     dStar = -Inf;
     for r = 2:n
+        % Probability vector (1/r, ..., 1/r)
         pi = ones([1, r]) ./ r;
+        % Generates the sample
         X = mnrnd(m, pi, numSample);
+        % Takes the maximum of each row
         [maxX, I] = max(X, [], 2);
+        % Sets the maximum of each row to -Inf
         X(sub2ind(size(X), 1:numSample, transpose(I))) = -Inf;
[…]

### 2016-04-05 verifying-winner.tex
Figures added and bibTeX files included

@@
 \usepackage{enumitem}
+\usepackage{graphicx}
 \usepackage[totalwidth=480pt, totalheight=680pt]{geometry}
@@
 Next we condition on the sufficient statistics that are multiplied to the the nuisance parameter, in other words, we consider the conditional law
-$$\mathcal{L}_{\theta_1 = \theta_j}\left(\frac{X_1 - X_j}{2} \middle| X_2, \ldots, \frac{X_1 + X_j}{2}, \ldots, X_n, A_1\right),$$
+$$\mathcal{L}_{\pi_1 = \pi_j}\left(\frac{X_1 - X_j}{2} \middle| X_2, \ldots, \frac{X_1 + X_j}{2}, \ldots, X_n, A_1\right),$$
 or equivalently, the conditional law
-$$\mathcal{L}_{\theta_1 = \theta_j}\left(X_1 \middle| X_2, \ldots, \frac{X_1 + X_j}{2}, \ldots, X_n, A_1\right),$$
+$$\mathcal{L}_{\pi_1 = \pi_j}\left(X_1 \middle| X_2, \ldots, \frac{X_1 + X_j}{2}, \ldots, X_n, A_1\right),$$
 which is the distribution $\text{Binomial}\left(X_1 + X_j, \frac{1}{2}\right)$ truncated by the event $A_1$. The one-sided $p$-value $p_{1j}$ is thus given as
@@
 
+It may appear quite surprising that ``verifying a winner'' as we propose in this section requires no adjustment for multiplicity, in the sense that we only need to compare the winner to the runner- up, just as we would have done if $n = 2$.
+After all, we know that the winner suffer’s from a winner's curse: given $X_5$ is the winner, $X_5 / N$ would overestimate $\pi_5$, and the larger $n$ is, the more severe this bias is likely to be.
+However, if $X_9$ is the runner-up, then $X_9 / N$ is likely biased upward nearly as much as $X_5$.
+Informally, we might say that $X_9$ suffer’s from a “runner-up’s curse” that is nearly as bad as the winner's curse; as a result, $X_5 - X_9$ is actually not all that biased upward.
+By multiplying the $p$-value by $2$, or equivalently performing a two-tailed test, takes care of what little bias there is.
+Indeed, performing a two-tailed test can be viewed as a sort of ``correction for multiplicity'', albeit one that we would have to make even if $n = 2$.
+
 \subsection{Connection with the subset selection problem}
 \label{sec:compare_subset}
+
+Gupta and Nagel \cite{Gupta:1967wg} devised a rule to select a subset that includes the maximum $\pi_j$. In other words, if the selected subset is $J\left(X\right)$, they guaranteed
+$$\PP\left(\argmax_j \pi_j \in J\left(X\right)\right) \ge 1 - \alpha.$$
+This was achieved by finding an integer $D$, as a function on $N$ and $n$, and select by
+$$J\left(X\right) = \left\{j: X_j \ge \max_k X_k - D\right\}.$$
+Gupta and Nagel also provided the method to choose $D$, which we implemented.
+
+\Cref{fig:power} gives the power curves for $\text{Multinomial}\left(N, \pi\right)$ and
+$$\pi \propto \left(e^\delta, 1, \ldots, 1\right),$$
+for various combinations of $N$ and $n$. The two procedure coincide if $n = 2$ as there are is actual selection.
+
+\begin{figure}[htbp]
+\begin{center}
+\includegraphics[width = \textwidth]{plotMultinomialPower}
+\end{center}
+\caption{Power curves as a function of $\delta$. The plots in the first row all have $N = 50$ and the second row $N = 250$.}
+\label{fig:power}
+\end{figure}
 

### 2016-04-05 multinomialPower.m

@@ -10,7 +10,7 @@ function [] = multinomialPower (m, n, alpha, numSample)
     sel = arrayfun(@(x) selectivePower(m, n, x, alpha, numSample), delta);
     gn = gnPower(m, n, delta, alpha, numSample);
     plot(delta, sel, delta, gn, '--');
-    legend('Selective', 'Gupta and Nagel', 'Location', 'southeast');
+    % legend('Selective', 'Gupta and Nagel', 'Location', 'southeast');
     xlabel('\delta');
     ylabel('Power');
 end

### 2016-04-05 plotMultinomialPower.m

@@ -1,0 +1,32 @@
+numSample = 10000;
+alpha = 0.05;
+
+subplot(2, 3, 1);
+multinomialPower(50, 2, alpha, numSample);
+grid on;
+title('N = 50, n = 2');
+
+subplot(2, 3, 2);
+multinomialPower(50, 5, alpha, numSample);
+grid on;
+title('N = 50, n = 5');
+
+subplot(2, 3, 3);
+multinomialPower(50, 10, alpha, numSample);
+grid on;
+title('N = 50, n = 10');
+
+subplot(2, 3, 4);
+multinomialPower(500, 20, alpha, numSample);
+grid on;
+title('N = 250, n = 10');
+
+subplot(2, 3, 5);
+multinomialPower(500, 50, alpha, numSample);
+grid on;
+title('N = 250, n = 25');
+
+subplot(2, 3, 6);
+multinomialPower(500, 100, alpha, numSample);
+grid on;
+title('N = 250, n = 50');

### 2016-04-05 verifying-winner.tex
Expanded paragraph on power comparison

@@
 $$\pi \propto \left(e^\delta, 1, \ldots, 1\right),$$
-for various combinations of $N$ and $n$. The two procedure coincide if $n = 2$ as there are is actual selection.
+for various combinations of $N$ and $n$.
+The two procedure coincide if $n = 2$ as there are is actual selection.
+However as $n$ grows, the selective test shoes significantly more power than Gupta and Nagel's test.
 
@@
 \begin{center}
-\includegraphics[width = \textwidth]{plotMultinomialPower}
+\includegraphics[width = \textwidth, trim = {1.3in 0.7in 1.6in 0.6in}, clip]{plotMultinomialPower}
 \end{center}
-\caption{Power curves as a function of $\delta$. The plots in the first row all have $N = 50$ and the second row $N = 250$.}
+\caption{Power curves as a function of $\delta$.
+The plots in the first row all have $N = 50$ and the second row $N = 250$.
+The solid line is the power for the selective test and the dashed line Gupta and Nagel's test.}
 \label{fig:power}

### 2016-04-08 verifying-winner.tex
Gupta and Nagel now does X* - X1 instead of X* - X**

@@
 for various combinations of $N$ and $n$.
-The two procedure coincide if $n = 2$ as there are is actual selection.
-However as $n$ grows, the selective test shoes significantly more power than Gupta and Nagel's test.
+The procedure by Gupta and Nagel coincides with our procedure at $n = 2$ if we half our $\alpha$.
+However as $n$ grows, the selective test shoes significantly more power than Gupta and Nagel's test even for the same $\alpha$.
 

### 2016-04-08 multinomialPower.m

@@ -30,8 +30,8 @@ function [power] = selectivePower(m, n, delta, alpha, numSample)
     secX = max(X(:, 2:end), [], 2);
     % nX is X1 + X2
     nX = secX + X(:, 1);
-    accepted = nnz(cdf('Binomial', secX, nX, 0.5) * 2 < alpha);
-    power = accepted / numSample;
+    rejected = nnz(cdf('Binomial', secX, nX, 1/2) * 2 <= alpha);
+    power = rejected / numSample;
 end
 
 % Find the test power of Gutpa and Nagel for multinomial distribution
@@ -49,13 +49,9 @@ function [power] = gnPower(m, n, delta, alpha, numSample)
         % Generates the sample
         X = mnrnd(m, pi, numSample);
         % Takes the maximum of each row
-        [maxX, I] = max(X, [], 2);
-        % Sets the maximum of each row to -Inf
-        X(sub2ind(size(X), 1:numSample, transpose(I))) = -Inf;
-        % Takes the maximum of each row again, yielding second largest
-        secX = max(X, [], 2);
+        maxX = max(X, [], 2);
         % d for a given r is the upper alpha quantile, rounded up
-        d = ceil(quantile(maxX - secX, 1 - alpha));
+        d = ceil(quantile(maxX - X(:, 1), 1 - alpha));
         % Taking maximum over all r
         if dStar < d
             dStar = d;
@@ -71,8 +67,8 @@ function [power] = gnPower(m, n, delta, alpha, numSample)
         X = mnrnd(m, pi, numSample);
         % secX is max(Xj; j>1), i.e. X2
         secX = max(X(:, 2:end), [], 2);
-        accepted = nnz(X(:, 1) - dStar > secX);
-        power(i) = accepted / numSample;
+        rejected = nnz(X(:, 1) - secX > dStar);
+        power(i) = rejected / numSample;
     end
 end
 

### 2016-04-09 verifying-winner.tex
Correction factor for alpha included in Matlab code; Diagrams updated / added in paper

--- 2016-04-05 verifying-winner.tex
@@
 \usepackage{tikz}
+\usetikzlibrary{calc}
+\usepackage{xcolor}
 
@@
 
-We often make observations that form a joint exponential family distribution.
-While it might be relatively obvious in the independent case, the observations can well be dependent and hinge on the natural parameters.
-Comparison of these natural parameters can produce useful inferences.
+We often make observations that form a joint distribution.
+While it might be relatively obvious in the independent case, the observations can well be dependent, complicating comparisons of parameters.
+However, comparison of these parameters can produce useful inferences.
 
@@
 \begin{equation}
-\PP_F\left(\text{reject } H_0\right) = \sum_{j \text{ is a candidate}} \PP_F\left(\text{reject } H_0 \middle| j \text{ leads in polls}\right) \PP_F \left(j \text{ leads in polls}\right).
+\PP_F\left(\text{reject } H_0\right) = \sum_{\substack{j \text{ is a candidate} \\ j \text{ does not have most support}}} \PP_F\left(\text{reject } H_0 \middle| j \text{ leads in polls}\right) \PP_F \left(j \text{ leads in polls}\right).
 \label{eqn:marginal_error}
@@
 $$\PP_F\left(\text{reject } H_0 \middle| j \text{ leads in polls} \right), ~~~~~~~~ \text{where $j$ is a candidate,}$$
-instead. Note that controlling this selective type I error rate at $\alpha$ provides control of the marginal type I error rate given in \Cref{eqn:marginal_error} at $\alpha$ too.
+instead. Note that controlling this selective type I error rate at $\alpha$ provides control of the marginal type I error rate at $\alpha$ too. From \Cref{eqn:marginal_error},
+\begin{align}
+\PP_F\left(\text{reject } H_0\right) & = \sum_{\substack{j \text{ is a candidate} \\ j \text{ does not have most support}}} \PP_F\left(\text{reject } H_0 \middle| j \text{ leads in polls}\right) \PP_F \left(j \text{ leads in polls}\right).
+\nonumber \\
+& \le \sum_{\substack{j \text{ is a candidate} \\ j \text{ does not have most support}}} \alpha \PP_F \left(j \text{ leads in polls}\right). \nonumber \\
+& = \alpha \PP\left(\text{Leader in polls does not have most support}\right) \nonumber \\
+& \le \frac{n-1}{n} \alpha. \label{eqn:selective_vs_marginal}
+\end{align}
 
@@
 Suppose we observe
-$$\left(X_1, \ldots, X_n\right) \sim \text{Multinomial}\left(N, \pi\right)$$
+$$\left(X_1, \ldots, X_n\right) \sim \text{Multinomial}\left(m, \pi\right)$$
 and we want to test
@@
 The distribution, written in an exponential family format, is
-$$\exp\left(X_1 \log \pi_1 + \cdots + X_n \log \pi_n\right) \frac{1_{X_1 + \cdots + X_n = N}}{X_1! \cdots X_n!}.$$
+$$\exp\left(X_1 \log \pi_1 + \cdots + X_n \log \pi_n\right) \frac{1_{X_1 + \cdots + X_n = m}}{X_1! \cdots X_n!}.$$
 
@@
 The distribution is now
-$$\exp\left(\frac{X_1 - X_j}{2} \left(\log \pi_1 - \log \pi_j\right) + \cdots + \frac{X_1 + X_j}{2} \left(\log \pi_1 + \log \pi_j\right) + \cdots + X_n\right) \frac{1_{X_1 + \cdots + X_n \log \pi_n = N}}{X_1!
+$$\exp\left(\frac{X_1 - X_j}{2} \left(\log \pi_1 - \log \pi_j\right) + \cdots + \frac{X_1 + X_j}{2} \left(\log \pi_1 + \log \pi_j\right) + \cdots + X_n\right) \frac{1_{X_1 + \cdots + X_n = m}}{X_1!
 \cdots X_n!}.$$
@@
 which is the distribution $\text{Binomial}\left(X_1 + X_j, \frac{1}{2}\right)$ truncated by the event $A_1$. The one-sided $p$-value $p_{1j}$ is thus given as
-$$\frac{\sum_{t = X_1}^{X_1 + X_j} \binom{X_1 + X_j}{t} \left(\frac{1}{2}\right)^{X_1 + X_j}}{\sum_{t = \left(X_1 + X_j\right)/2}^{X_1 + X_j} \binom{X_1 + X_j}{t} \left(\frac{1}{2}\right)^{X_1 + X_j}} = \frac{\sum_{t = X_1}^{X_1 + X_j} \binom{X_1 + X_j}{t}}{\sum_{t = \left(X_1 + X_j\right)/2}^{X_1 + X_j} \binom{X_1 + X_j}{t}},$$
+\begin{align*}
+p_{ij}\left(x_1, \ldots, x_n\right) & = \PP\left(X_1 \ge x_1 \middle| X_2 = x_2, \ldots, \frac{X_1 + X_j}{2} = \frac{x_1 + x_j}{2}, \ldots, X_n = x_n, A_1\right) \\
+& = \frac{\sum_{t = x_1}^{x_1 + x_j} \binom{x_1 + x_j}{t} \left(\frac{1}{2}\right)^{x_1 + x_j}}{\sum_{t = \left(x_1 + x_j\right)/2}^{x_1 + x_j} \binom{x_1 + x_j}{t} \left(\frac{1}{2}\right)^{x_1 + x_j}} \\
+& = \frac{\sum_{t = x_1}^{x_1 + x_j} \binom{x_1 + x_j}{t}}{\sum_{t = \left(x_1 + x_j\right)/2}^{x_1 + x_j} \binom{x_1 + x_j}{t}},
+\end{align*}
 and to account for the tie-breaking we adopted earlier, we
 \begin{itemize}
-\item multiply the first term in the numerator and the numerator by $1/m$ where $m$ is the number of observations tied for largest; otherwise,
+\item multiply the first term in the numerator and the numerator by $1/k$ where $k$ is the number of observations tied for largest; otherwise,
 \item multiply the first term in the denominator by $1/2$ if $X_1$ and $X_2$ has the same parity.
@@
 It may appear quite surprising that ``verifying a winner'' as we propose in this section requires no adjustment for multiplicity, in the sense that we only need to compare the winner to the runner- up, just as we would have done if $n = 2$.
-After all, we know that the winner suffer’s from a winner's curse: given $X_5$ is the winner, $X_5 / N$ would overestimate $\pi_5$, and the larger $n$ is, the more severe this bias is likely to be.
-However, if $X_9$ is the runner-up, then $X_9 / N$ is likely biased upward nearly as much as $X_5$.
+After all, we know that the winner suffer’s from a winner's curse: given $X_5$ is the winner, $X_5 / m$ would overestimate $\pi_5$, and the larger $n$ is, the more severe this bias is likely to be.
+However, if $X_9$ is the runner-up, then $X_9 / m$ is likely biased upward nearly as much as $X_5$.
 Informally, we might say that $X_9$ suffer’s from a “runner-up’s curse” that is nearly as bad as the winner's curse; as a result, $X_5 - X_9$ is actually not all that biased upward.
@@
 $$\PP\left(\argmax_j \pi_j \in J\left(X\right)\right) \ge 1 - \alpha.$$
-This was achieved by finding an integer $D$, as a function on $N$ and $n$, and select by
-$$J\left(X\right) = \left\{j: X_j \ge \max_k X_k - D\right\}.$$
+This was achieved by finding an integer $D$, as a function on $m$, $n$ and $\alpha$, and select by
+\begin{equation}
+J\left(X\right) = \left\{j: X_j \ge \max_k X_k - D\right\} \tag{Procedure GN}.
+\label{eqn:gn}
+\end{equation}
 Gupta and Nagel also provided the method to choose $D$, which we implemented.
 
-\Cref{fig:power} gives the power curves for $\text{Multinomial}\left(N, \pi\right)$ and
+\Cref{fig:power} gives the power curves for $\text{Multinomial}\left(m, \pi\right)$ and
 $$\pi \propto \left(e^\delta, 1, \ldots, 1\right),$$
-for various combinations of $N$ and $n$.
-The two procedure coincide if $n = 2$ as there are is actual selection.
+for various combinations of $m$ and $n$.
+For \ref{eqn:gn}, we use $\alpha = 0.05$; but to account for the extra factor of $\frac{n-1}{n}$ in \Cref{eqn:selective_vs_marginal}, we will apply the selective procedure for with $\frac{n}{n-1} \alpha$ such that the marginal type I error rate for both procedures is controlled at $\alpha$.
+\ref{eqn:gn} coincides with our test at $n = 2$.
 However as $n$ grows, the selective test shoes significantly more power than Gupta and Nagel's test.
@@
 \begin{center}
-\includegraphics[width = \textwidth, trim = {1.3in 0.7in 1.6in 0.6in}, clip]{plotMultinomialPower}
+\includegraphics[width = \textwidth]{plotMultinomialPower}
 \end{center}
 \caption{Power curves as a function of $\delta$.
-The plots in the first row all have $N = 50$ and the second row $N = 250$.
+The plots in the first row all have $m = 50$ and the second row $m = 250$.
 The solid line is the power for the selective test and the dashed line Gupta and Nagel's test.}
@@
 \end{equation}
-It is reasonable to assume that the distribution is ``symmetric'', i.e.\ if $\theta_j = \theta_k$, then the probability distribution remains the same when $X_j$ and $X_k$ are swapped.
+It is reasonable to assume that the family is ``symmetric'', i.e.\ if $\theta_j = \theta_k$, then the probability distribution remains the same when $X_j$ and $X_k$ are swapped.
 This corresponds to requiring $g\left(X\right)$ to be symmetric.
@@
 p_{12} & = \frac{\int_0^\infty g\left(X_1 + z, X_2 - z, X_3\right) \,dz}{\int_0^\infty g\left(M_{12} + z, M_{12} - z, X_3\right) \,dz} \\
-p_{13} & = \frac{\int_0^\infty g\left(X_1 + z, X_2, X_3 - z\right) \,dz}{\int_0^\infty g\left(M_{13} + z, X_2, M_{13} - z\right) \,dz}
+& = \frac{\int_0^\infty g\left(X_1 + z, X_2 - z, X_3\right) \,dz}{\int_{-D_{12}}^\infty g\left(X_1 + z, X_2 - z, X_3\right) \,dz} \\
+p_{13} & = \frac{\int_0^\infty g\left(X_1 + z, X_2, X_3 - z\right) \,dz}{\int_0^\infty g\left(M_{13} + z, X_2, M_{13} - z\right) \,dz} \\
+& = \frac{\int_0^\infty g\left(X_1 + z, X_2, X_3 - z\right) \,dz}{\int_{-D_{13}}^\infty g\left(X_1 + z, X_2, X_3 - z\right) \,dz}
 \end{align*}
+To help see the re-parametrization, each of these integrals can be thought of in terms integrals along segments and rays.
+For example $p_{12}$ can be represented in terms integrals $A$ and $B$ in \Cref{fig:p-value}.
+Specifically,
+$$p_{12} = \frac{B}{A + B}$$
 
@@
 \begin{tikzpicture}
-	\draw[dashed, thick] (-3, 1.5) -- (-2, 1);
-	\draw[->, thick] (-2, 1) -- (6, -3);
-	\draw[->, thick] (-3, -2) -- (6, 4);
-	\fill (0, 0) circle(2pt) node[right] {$\left(X_1, X_2, X_3\right)$};
-	\fill (-2, 1) circle(2pt) node[above right] {$\left(M_{12}, M_{12}, X_3\right)$};
-	\fill (-3, -2) circle(2pt) node[below] {$\left(M_{13}, X_2, M_{13}\right)$};
-	\fill (-3, 1.5) circle(2pt) node[above] {$\left(M_{13}, X_2 + D_{13}, X_3\right)$};
-	\draw[dotted, thick] (-3, 1.5) -- (-3, -2) node[midway, below, rotate=-90] {$\succeq$};
-	\draw[dotted, thick] (-2, 1) -- (-2, -4/3) node[midway, below, rotate=-90] {$\succeq$};
-	\draw[dotted, thick] (3, -1.5) -- (3, 2) node[midway, below, rotate=-90] {$\succeq$};
-	\draw[dotted, thick] (5, -2.5) -- (5, 10/3) node[midway, below, rotate=-90] {$\succeq$};
+	\coordinate (C1) at (60:5);
+	\coordinate (C2) at (300:3);
+	\coordinate (A) at (60:3);
+	\coordinate (B) at ($(A) + (330:3)$);
+	\draw[dashed] (0, 0) -- (C1);
+	\draw[dashed] (0, 0) -- (C2);
+	\fill[yellow!50] (0, 0) -- (C1) -- ($(C1) + (7, 0)$) -- ($(C2) + (8, 0)$) -- (C2) -- cycle;
+	\node[above left] at ($(C2) + (8, 0)$) {$A_1$};
+	\draw[thick] (A) -- (B) node[midway, above right] {$A$};
+	\draw[thick, ->] (B) -- ++(330:5) node[midway, above right] {$B$};
+	\fill (A) circle(2pt) node[above left] {$\left(M_{12}, M_{12}, X_3\right)$};
+	\fill (B) circle(2pt) node[above right] {$\left(X_1, X_2, X_3\right)$};
+	\draw[thick, ->] (0, 0) -- (1, 0) node[right] {\tiny $\left(1, 0, 0\right)$};
+	\draw[thick, ->] (0, 0) -- (120:1) node[above] {\tiny $\left(0, 1, 0\right)$};
+	\draw[thick, ->] (0, 0) -- (240:1) node[below] {\tiny $\left(0, 0, 1\right)$};
 \end{tikzpicture}
 \end{center}
-\caption{The two $p$-values constructed corresponds to taking integrals of $g$ along these rays, that lie on a level set of $x_1 + x_2 + x_3$.
-The dashed line corresponds to extending the integral in the denominator of \Cref{eqn:int_extension}.
-The dotted lines with the majorization symbols show the majorization relation between vectors on the two rays.}
-\label{fig:rays}
+\caption{The $p$-value $p_{12}$ can be written in terms of integral $A$ along the segment and $B$ along the ray.
+The diagram is drawn a level set of $x_1 + x_2 + x_3$.
+The yellow region represents the selection event $A_1$.}
+\label{fig:p-value}
 \end{figure}
 
-We can re-parametrize this further, thanks to some geometric intuition (ref.\ \Cref{fig:rays}) that both $p$-values are actually integrals of $g$ along intersecting rays. We have
-\begin{align}
-p_{12} & = \frac{\int_0^\infty g\left(X_1 + z, X_2 - z, X_3\right) \,dz}{\int_{-D_{12}}^\infty g\left(X_1 + z, X_2 - z, X_3\right) \,dz} \nonumber \\
-& \ge \frac{\int_0^\infty g\left(X_1 + z, X_2 - z, X_3\right) \,dz}{\int_{-D_{13}}^\infty g\left(X_1 + z, X_2 - z, X_3\right) \,dz} \label{eqn:int_extension} \\
-p_{13} & = \frac{\int_0^\infty g\left(X_1 + z, X_2, X_3 - z\right) \,dz}{\int_{-D_{13}}^\infty g\left(X_1 + z, X_2, X_3 - z\right) \,dz} \label{eqn:p13}
-\end{align}
+\Cref{fig:compare_rays} have both the $p$-values shown on the same diagram. Proving $p_{12} \ge p_{13}$ is the same as proving
+$$\frac{B}{A+B} \ge \frac{D}{C+D} ~~~~ \Longleftrightarrow ~~~~ \frac{B}{A} \ge \frac{D}{C}.$$
+We will prove so be extending $A$ to include $A^*$ on the diagram. We denote the sum as $A'$. Formally,
+\begin{equation}
+A' = \int_{-D_{13}}^0 g\left(X_1 + z, X_2 - z, X_3\right) \,dz \ge \int_{-D_{12}}^0 g\left(X_1 + z, X_2 - z, X_3\right) \,dz = A.
+\label{eqn:int_extension}
+\end{equation}
+It is thus sufficient to show that $B \ge D$ and $C \ge A'$.
+
+\begin{figure}[htbp]
+\begin{center}
+\begin{tikzpicture}
+	\coordinate (C1) at (60:5);
+	\coordinate (C2) at (300:3);
+	\coordinate (A) at (60:3);
+	\coordinate (B) at ($(A) + (330:3)$);
+	\coordinate (C) at ($(0, 0)!(B)!(C2)$);
+	\coordinate (D) at ($(A) + (150:1)$);
+	\draw[dashed] (0, 0) -- (C1);
+	\draw[dashed] (0, 0) -- (C2);
+	\fill[yellow!50] (0, 0) -- (C1) -- ($(C1) + (7, 0)$) -- ($(C2) + (8, 0)$) -- (C2) -- cycle;
+	\node[above left] at ($(C2) + (8, 0)$) {$A_1$};
+	\draw[thick] (A) -- (B) node[midway, above right] {$A$};
+	\draw[thick, ->] (B) -- ++(330:5) node[midway, below left] {$B$};
+	\fill (A) circle(2pt) node[above right] {$\left(M_{12}, M_{12}, X_3\right)$};
+	\fill (B) circle(2pt) node[right] {$\left(X_1, X_2, X_3\right)$};
+	\draw[thick] (C) -- (B) node[midway, below right] {$C$};
+	\node[below] at (C) {$\left(M_{13}, X_2, M_{13}\right)$};
+	\draw[thick, ->] (B) -- ++(30:5) node[midway, above left] {$D$};
+	\fill ($(0, 0)!(B)!(C2)$) circle(2pt);
+	\draw[thick, dashed] (A) -- (D) node[midway, below left] {$A^*$};
+	\fill (D) circle(2pt) node[above] {$\left(M_{13}, X_2 + D_{13}, X_3\right)$};
+	\draw[thick, dotted] (C) -- (D) node[midway, below, rotate=-90] {$\succeq$};
+	\draw[thick, dotted] (A) -- ++(0, -3) node[midway, below, rotate=-90] {$\succeq$};
+	\draw[thick, dotted] ($(B) + (30:4)$) -- ($(B) + (330:4)$) node[midway, below, rotate=-90] {$\succeq$};
+\end{tikzpicture}
+\end{center}
+\caption{The $p$-value $p_{12}$ can be written in terms of integral $A$ along the segment and $B$ along the ray; and $p_{13}$ in terms of $C$ and $D$.
+$A'$ would refer to the sum of $A$ with the dashed line portion labeled as $A^*$, formally explained in \Cref{eqn:int_extension}.
+The majorization relation is indicated by the dotted line.}
+\label{fig:compare_rays}
+\end{figure}
 
@@
 $$\left(X_1 + z, X_2 - z, X_3\right) \succeq \left(X_1 + z, X_2, X_3 - z\right)$$
-for $z \le 0$ and the majorization reversed for $z \ge 0$. So Schur-concavity shows that
+for $z \le 0$ and the majorization reversed for $z \ge 0$. This majorization relation is indicated as the dotted line in \Cref{fig:compare_rays}. So Schur-concavity shows that
 $$g\left(X_1 + z, X_2 - z, X_3\right) \le g\left(X_1 + z, X_2, X_3 - z\right)$$
-for $z \le 0$, and the inequality reversed for $z \ge 0$. Consequently, $p_{12} \ge p_{13}$ by comparing \Cref{eqn:int_extension,eqn:p13}.
+for $z \le 0$, and the inequality reversed for $z \ge 0$. Taking integrals on both sides yields the desired inequality.
 
@@
 
-The same argument in \Cref{fig:rays} shows that $p_{12} \ge p_{13}$.
+The same argument in \Cref{fig:compare_rays} shows that $p_{12} \ge p_{13}$.
 This is again true for the case where $X_2 \ge M_{13}$ as well.
@@
 \begin{tikzpicture}
-	\draw[dashed, thick] (-3, 1.5) -- (-2, 1);
-	\draw[thick] (-2, 1) -- (5, -2.5);
-	\draw[thick] (-3, -2) -- (5, 10/3);
-	\fill (0, 0) circle(2pt) node[right] {$\left(X_j, X_{j+1}, X_k\right)$};
-	\fill (-2, 1) circle(2pt) node[above right] {$\left(M_{j\left(j+1\right)}, M_{j\left(j+1\right)}, X_k\right)$};
-	\fill (-3, -2) circle(2pt) node[below] {$\left(M_{jk}, X_{\left(j+1\right)}, M_{jk}\right)$};
-	\fill (-3, 1.5) circle(2pt) node[above] {$\left(M_{jk}, X_{j+1} + D_{jk}, X_k\right)$};
-	\draw[dotted, thick] (-3, 1.5) -- (-3, -2) node[midway, below, rotate=-90] {$\succeq$};
-	\draw[dotted, thick] (-2, 1) -- (-2, -4/3) node[midway, below, rotate=-90] {$\succeq$};
-	\draw[dotted, thick] (3, -1.5) -- (3, 2) node[midway, above, rotate=-90] {$\succeq$};
-	\draw[dotted, thick] (5, -3) -- (5, 4) node[midway, above, rotate=-90] {Truncation for $X_j < X_{j-1}$};
+	\coordinate (C1) at (60:5);
+	\coordinate (C2) at (300:3);
+	\coordinate (A) at (60:3);
+	\coordinate (B) at ($(A) + (330:3)$);
+	\coordinate (C) at ($(0, 0)!(B)!(C2)$);
+	\coordinate (D) at ($(A) + (150:1)$);
+	\coordinate (C3) at ($(B) + (330:5)$);
+	\coordinate (C4) at ($(B) + (30:5)$);
+	\coordinate (C5) at ($(C3)!(C1)!(C4)$);
+	\coordinate (C6) at ($(C3)!(C2)!(C4)$);
+	\draw[dashed] (0, 0) -- (C1);
+	\draw[dashed] (0, 0) -- (C2);
+	\draw[dashed] (C5) -- (C6) node[midway, above, rotate = -90] {Truncation for $X_j < X_{j-1}$};
+	\fill[yellow!50] (0, 0) -- (C1) -- (C5) -- (C6) -- (C2) -- cycle;
+	\node[above] at ($(C2)!0.7!(C6)$) {$A_1$};
+	\draw[thick] (A) -- (B) node[midway, above right] {$A$};
+	\draw[thick] (B) -- (C3) node[midway, below left] {$B$};
+	\fill (C3) circle(2pt);
+	\fill (A) circle(2pt) node[above right] {$\left(M_{12}, M_{12}, X_3\right)$};
+	\fill (B) circle(2pt) node[right] {$\left(X_1, X_2, X_3\right)$};
+	\draw[thick] (C) -- (B) node[midway, below right] {$C$};
+	\node[below] at (C) {$\left(M_{13}, X_2, M_{13}\right)$};
+	\draw[thick] (B) -- (C4) node[midway, above left] {$D$};
+	\fill (C4) circle(2pt);
+	\fill ($(0, 0)!(B)!(C2)$) circle(2pt);
+	\draw[thick, dashed] (A) -- (D) node[midway, below left] {$A^*$};
+	\fill (D) circle(2pt) node[above] {$\left(M_{13}, X_2 + D_{13}, X_3\right)$};
+	\draw[thick, dotted] (C) -- (D) node[midway, below, rotate=-90] {$\succeq$};
+	\draw[thick, dotted] (A) -- ++(0, -3) node[midway, below, rotate=-90] {$\succeq$};
+	\draw[thick, dotted] ($(B) + (30:4)$) -- ($(B) + (330:4)$) node[midway, below, rotate=-90] {$\succeq$};
 \end{tikzpicture}
@@
 \caption{The two $p$-values constructed corresponds to taking integrals of $g$ along these segments, that lie on a level set of $x_j + x_{j+1} + x_k$.
-The dashed line corresponds to extending the integral in the denominator of \Cref{eqn:int_extension}.
+The dashed line corresponds to extension in \Cref{eqn:int_extension}.
 The dotted line on the far right is the truncation that enforces $X_j < X_{j-1}$.}
@@
 Here we are only comparing $X_j$ to $X_{j+1}$ by \Cref{sec:exponential_families}.
-The upper truncation for $X_j$ can be represented by cropping \Cref{fig:rays} along a vertical line, shown in \Cref{fig:crop_rays}, thus the proof of \Cref{thm:main_result} on sufficiency to compare $X_1$ and $X_2$ remains valid with appropriate conditioning.
+The upper truncation for $X_j$ can be represented by cropping \Cref{fig:compare_rays} along a vertical line, shown in \Cref{fig:crop_rays}, thus the proof of \Cref{thm:main_result} on sufficiency to compare $X_1$ and $X_2$ remains valid with appropriate conditioning.
 Again we can construct the $p$-values as in \Cref{eqn:p1j} for $k>j$.
@@
 \item Multinomial distribution, e.g.\ the Iowa Republican poll example in \Cref{sec:introduction}.
-$$p\left(x\right) \propto \exp\left(x^T \left(\log \pi\right)\right) \frac{1_{\left\{x_1 + \cdots + x_n = N\right\}}}{x_1! \cdots x_n!}$$
+$$p\left(x\right) \propto \exp\left(x^T \left(\log \pi\right)\right) \frac{1_{\left\{x_1 + \cdots + x_n = m\right\}}}{x_1! \cdots x_n!}$$
 Comparing $\pi_i$ is the same $\log \pi_i$, the natural parameters.

### 2016-04-09 multinomialPower.m

@@ -7,7 +7,7 @@
 function [] = multinomialPower (m, n, alpha, numSample)
     % delta ranges from 0 to 2
     delta = 0:0.01:2;
-    sel = arrayfun(@(x) selectivePower(m, n, x, alpha, numSample), delta);
+    sel = arrayfun(@(x) selectivePower(m, n, x, alpha / (n-1) * n, numSample), delta);
     gn = gnPower(m, n, delta, alpha, numSample);
     plot(delta, sel, delta, gn, '--');
     % legend('Selective', 'Gupta and Nagel', 'Location', 'southeast');

### 2016-04-09 plotMultinomialPower.m

@@ -4,29 +4,29 @@ alpha = 0.05;
 subplot(2, 3, 1);
 multinomialPower(50, 2, alpha, numSample);
 grid on;
-title('N = 50, n = 2');
+title('m = 50, n = 2');
 
 subplot(2, 3, 2);
 multinomialPower(50, 5, alpha, numSample);
 grid on;
-title('N = 50, n = 5');
+title('m = 50, n = 5');
 
 subplot(2, 3, 3);
 multinomialPower(50, 10, alpha, numSample);
 grid on;
-title('N = 50, n = 10');
+title('m = 50, n = 10');
 
 subplot(2, 3, 4);
 multinomialPower(500, 20, alpha, numSample);
 grid on;
-title('N = 250, n = 10');
+title('m = 250, n = 10');
 
 subplot(2, 3, 5);
 multinomialPower(500, 50, alpha, numSample);
 grid on;
-title('N = 250, n = 25');
+title('m = 250, n = 25');
 
 subplot(2, 3, 6);
 multinomialPower(500, 100, alpha, numSample);
 grid on;
-title('N = 250, n = 50');
+title('m = 250, n = 50');

### 2016-04-09 verifying-winner.tex
Typos and grammar partially fixed

@@
 Intuitively, we would compare Trump to Cruz, as well as the other candidate.
-This intuitive method however has a few issues.
+This intuitive method however has a couple of issues.
 
@@
 In other words, the hypothesis itself is random.
-Alternatively, we can note that the marginal type I error rate is indeed not so straightfoward.
+Alternatively, we can note that the marginal type I error rate is indeed not so straightforward.
 If the null hypothesis is ``$H_0: \text{Leader in polls has most support}$'', then for any distribution $F$ the marginal type I error rate is
@@
 
-Gutmann and Maymin \cite{Gutmann:1987fk} has worked on a similar question where the observations are from a location family, and the location parameters are compared.
+Gutmann and Maymin \cite{Gutmann:1987fk} have worked on a similar question where the observations are from a location family, and the location parameters are compared.
 In contrast, a related paper by Karnnan and Panchapakesan \cite{Karnnan:2009iv} discussed a scale family instead, comparing the scale parameters.
@@
 The distribution is now
-$$\exp\left(\frac{X_1 - X_j}{2} \left(\log \pi_1 - \log \pi_j\right) + \cdots + \frac{X_1 + X_j}{2} \left(\log \pi_1 + \log \pi_j\right) + \cdots + X_n\right) \frac{1_{X_1 + \cdots + X_n = m}}{X_1!
+$$\exp\left(\frac{X_1 - X_j}{2} \left(\log \pi_1 - \log \pi_j\right) + \cdots + \frac{X_1 + X_j}{2} \left(\log \pi_1 + \log \pi_j\right) + \cdots + X_n \log \pi_n\right) \frac{1_{X_1 + \cdots + X_n = m}}{X_1!
 \cdots X_n!}.$$
@@
 \begin{itemize}
-\item multiply the first term in the numerator and the numerator by $1/k$ where $k$ is the number of observations tied for largest; otherwise,
+\item multiply the first term in the numerator and the denominator by $1/k$ where $k$ is the number of observations tied for largest; otherwise,
 \item multiply the first term in the denominator by $1/2$ if $X_1$ and $X_2$ has the same parity.
@@
 Informally, we might say that $X_9$ suffer’s from a “runner-up’s curse” that is nearly as bad as the winner's curse; as a result, $X_5 - X_9$ is actually not all that biased upward.
-By multiplying the $p$-value by $2$, or equivalently performing a two-tailed test, takes care of what little bias there is.
+By multiplying the $p$-value by $2$, or equivalently performing a two-tailed test, we take care of what little bias there is.
 Indeed, performing a two-tailed test can be viewed as a sort of ``correction for multiplicity'', albeit one that we would have to make even if $n = 2$.
@@
 This was achieved by finding an integer $D$, as a function on $m$, $n$ and $\alpha$, and select by
-\begin{equation}
-J\left(X\right) = \left\{j: X_j \ge \max_k X_k - D\right\} \tag{Procedure GN}.
-\label{eqn:gn}
-\end{equation}
-Gupta and Nagel also provided the method to choose $D$, which we implemented.
+$$J\left(X\right) = \left\{j: X_j \ge \max_k X_k - D\right\}.$$
+Gupta and Nagel also provided the method to choose $D$.
+The subset selection can be modified.
+Inherently, the event $\left\{J\left(X\right) = \left\{1\right\}\right\}$ is the same as inferring $\pi_1$ is the largest.
+We thus implemented their test for this purpose.
 
@@
 for various combinations of $m$ and $n$.
-For \ref{eqn:gn}, we use $\alpha = 0.05$; but to account for the extra factor of $\frac{n-1}{n}$ in \Cref{eqn:selective_vs_marginal}, we will apply the selective procedure for with $\frac{n}{n-1} \alpha$ such that the marginal type I error rate for both procedures is controlled at $\alpha$.
-\ref{eqn:gn} coincides with our test at $n = 2$.
-However as $n$ grows, the selective test shoes significantly more power than Gupta and Nagel's test.
+For Gupta and Nagel, we use $\alpha = 0.05$; but to account for the extra factor of $\frac{n-1}{n}$ in \Cref{eqn:selective_vs_marginal}, we will apply the selective procedure for with $\frac{n}{n-1} \alpha$ such that the marginal type I error rate such that both procedures are controlled at $\alpha$.
+Gupta and Nagel coincides with our test at $n = 2$; however as $n$ grows, the selective test shoes significantly more power than Gupta and Nagel's test.
 
@@
 The plots in the first row all have $m = 50$ and the second row $m = 250$.
-The solid line is the power for the selective test and the dashed line Gupta and Nagel's test.}
+The solid line and the dashed line are the power for the selective test and Gupta and Nagel's test, respectively.}
 \label{fig:power}
@@
 We would also like to introduce a fairly mild additional condition that $g$ is {\em Schur-concave}.
-But first we define the notion of {\em majorization}.
+But first we recall the notion of {\em majorization}.
 
@@
 
-We prove the ``if'' part first. For any fixed $a$, and $X_1 \ge a$ and $X_2 < a$, we have
+We prove the ``if'' part first. For any fixed $a$, and $X_1 \ge a$ and $X_2 < a$, we have $X_1 > X_2$ and
 $$\exp\left(\theta_1 X_1 + \theta_2 X_2 + \cdots + \theta_n X_n\right) g\left(X\right) h\left(\theta\right) \ge \exp\left(\theta_1 X_2 + \theta_2 X_1 + \cdots + \theta_n X_n\right) g\left(X\right) h\left(\theta\right).$$
@@
 
-\Cref{fig:compare_rays} have both the $p$-values shown on the same diagram. Proving $p_{12} \ge p_{13}$ is the same as proving
+\Cref{fig:compare_rays} has both the $p$-values shown on the same diagram. Proving $p_{12} \ge p_{13}$ is the same as proving
 $$\frac{B}{A+B} \ge \frac{D}{C+D} ~~~~ \Longleftrightarrow ~~~~ \frac{B}{A} \ge \frac{D}{C}.$$
-We will prove so be extending $A$ to include $A^*$ on the diagram. We denote the sum as $A'$. Formally,
+We will prove so by extending $A$ to include $\hat{A}$ on the diagram. We denote the sum $A + \hat{A}$ as $A'$. Formally,
 \begin{equation}
@@
 	\fill ($(0, 0)!(B)!(C2)$) circle(2pt);
-	\draw[thick, dashed] (A) -- (D) node[midway, below left] {$A^*$};
+	\draw[thick, dashed] (A) -- (D) node[midway, below left] {$\hat{A}$};
 	\fill (D) circle(2pt) node[above] {$\left(M_{13}, X_2 + D_{13}, X_3\right)$};
@@
 \caption{The $p$-value $p_{12}$ can be written in terms of integral $A$ along the segment and $B$ along the ray; and $p_{13}$ in terms of $C$ and $D$.
-$A'$ would refer to the sum of $A$ with the dashed line portion labeled as $A^*$, formally explained in \Cref{eqn:int_extension}.
+$A'$ would refer to the sum of $A$ with the dashed line portion labeled as $\hat{A}$, formally explained in \Cref{eqn:int_extension}.
 The majorization relation is indicated by the dotted line.}
@@
 
-The conditioning above indeed holds some significance. The sufficient filtration \cite{Fithian:2015uj} $\mathcal{F}_k$ is given as the $\sigma$-field
+The conditioning above indeed holds some significance. The sufficient filtration \cite{Fithian:2015uj} $\mathscr{F}_k$ is given as the $\sigma$-field
 \begin{align*}
@@
 $$p\left(x\right) \propto \exp\left(x^T \left(\log \pi\right)\right) \frac{1_{\left\{x_1 + \cdots + x_n = m\right\}}}{x_1! \cdots x_n!}$$
-Comparing $\pi_i$ is the same $\log \pi_i$, the natural parameters.
+Comparing $\pi_i$ is the same as comparing $\log \pi_i$, the natural parameters.
 Note that the multinomial coefficient is naturally Schur-concave.
@@
 \item Independent binomials
-$$p\left(x\right) \propto \exp\left(x^T \left(\log p\right)\right) \frac{1}{p_1! \left(N-p_1\right)! \cdots p_n! \left(N-p_n\right)!}$$
+$$p\left(x\right) \propto \exp\left(x^T \left(\log p\right)\right) \frac{1}{x_1! \left(m-x_1\right)! \cdots x_n! \left(m-p_x\right)!}$$
 

### 2016-04-13 verifying-winner.tex
added some comments on Section 3

@@
 \newcommand{\RR}{\mathbb{R}}
+
+%Commands for inline commenting that shows up on pdf
+\newcommand{\WFcomment}[1]{{\color{red}{(WF: \bf \sc #1) }}}
 
@@
 
-A Schur-concave function is symmetric by default.
-Conversely a symmetric and log-concave function is Schur-concave, thus many common exponential family distributions lie in this class.
+A Schur-concave function is symmetric by default \WFcomment{``since $a \succeq b$ and $b \succeq a$ if $b$ is a permutation of the coordinates of $a$''}.
+Conversely a symmetric and log-concave function is Schur-concave \WFcomment{Is this obvious?}, thus many common exponential family distributions lie in this class.
 Schur-concave function indeed appears a lot, \Cref{sec:applications} includes both continuous and discrete examples.
@@
 We hereon call the class of distribution satisfying this {\em Schur-concave exponential family}.
-Without loss of generality, we can assume $X_1 \ge X_2 \ge \max_{k > 2} X_k$.
-We will be testing the null hypothesis $H_{01}: \theta_1 \le \max_{j > 1} \theta_j$, which is the union of the null hypotheses $H_{0j}: \theta_1 \le \theta_j$ for $j > 1$.
+Without loss of generality, we can assume $X_1 \ge X_2 \ge \max_{k > 2} X_k$ \WFcomment{Careful here: I know what you mean but some people will find it confusing to ``assume'' that an event occurs.
+Maybe say ``without loss of generality, we consider the case where...; other cases follow by relabeling.}.
+We will be testing the null hypothesis $H_{01}: \theta_1 \le \max_{j > 1} \theta_j$, which is the union of the null hypotheses $H_{0j}: \theta_1 \le \theta_j$ for $j > 1$ \WFcomment{Notation could be confusing: $H_{01}$ is not a special case of $H_{0j}$}.
 
@@
 \label{thm:stoch}
-$X_1$ is greater than $X_2$ is stochastic order if and only if $\theta_1 > \theta_2$.
+$X_1$ is greater than $X_2$ in stochastic order if and only if $\theta_1 > \theta_2$.
 \end{theorem}
@@
 $$\exp\left(\theta_1 X_1 + \theta_2 X_2 + \cdots + \theta_n X_n\right) g\left(X\right) h\left(\theta\right) \ge \exp\left(\theta_1 X_2 + \theta_2 X_1 + \cdots + \theta_n X_n\right) g\left(X\right) h\left(\theta\right).$$
-Integrating both sides over the region $\left\{X: X_1 \ge a, X_2 < a\right\}$, summing instead if $X$ is a discrete vector, gives
+Integrating both sides over the region $\left\{X: X_1 \ge a, X_2 < a\right\}$, summing instead if $X$ is a discrete vector \WFcomment{it's not necessary to distinguish summing from integrating since summing is ``integrating wrt counting measure.'' Anyway the carrier measure could be neither discrete nor absolutely continuous}, gives
 $$\PP\left(X_1 \ge a, X_2 < a\right) \ge \PP\left(X_1 < a, X_2 \ge a\right).$$
@@
 with a Schur-concave carrier measure $g$.
-Then there is a selective level-$\alpha$ test that verifies $\theta_{\left(1\right)} > \theta_{\left(2\right)}$ by comparing only $X_{\left(1\right)}$ and $X_{\left(2\right)}$.
+Then there is a selective level-$\alpha$ test that verifies $\theta_{\left(1\right)} > \theta_{\left(2\right)}$ \WFcomment{I know what you mean here but notation could be confusing} by comparing only $X_{\left(1\right)}$ and $X_{\left(2\right)}$.
 The test also verifies that $X_{\left(1\right)} \ge X_{\left(j\right)}$ stochastically for all $j > 1$.
@@
 \end{theorem}
+
+\WFcomment{This result could be stated a bit more strongly, though I'm not certain exactly how to phrase it.
+In fact the test we perform is whatever is the ``usual'' two-sided level-$\alpha$ test for comparing $\theta_1$ vs.
+$\theta_2$.
+
+The proof and figures look great!}
 

### 2016-04-14 verifying-winner.tex
Addressed the comments, main result restated

--- 2016-04-09 verifying-winner.tex
@@
 
-A Schur-concave function is symmetric by default.
-Conversely a symmetric and log-concave function is Schur-concave, thus many common exponential family distributions lie in this class.
+A Schur-concave function is symmetric by default since $a \succeq b$ and $b \succeq a$ if and only if $b$ is a permutation of the coordinates of $a$.
+Conversely a symmetric and log-concave function is Schur-concave \cite{Marshall:2010hb}, thus many common exponential family distributions lie in this class.
 Schur-concave function indeed appears a lot, \Cref{sec:applications} includes both continuous and discrete examples.
@@
 We hereon call the class of distribution satisfying this {\em Schur-concave exponential family}.
-Without loss of generality, we can assume $X_1 \ge X_2 \ge \max_{k > 2} X_k$.
-We will be testing the null hypothesis $H_{01}: \theta_1 \le \max_{j > 1} \theta_j$, which is the union of the null hypotheses $H_{0j}: \theta_1 \le \theta_j$ for $j > 1$.
+Without loss of generality, otherwise by relabeling, we consider only the event $X_1 \ge X_2 \ge \max_{k > 2} X_k$.
+We will be testing the null hypothesis $H_{01}: \theta_1 \le \max_{j > 1} \theta_j$, which is the union of the null hypotheses $H_{01j}: \theta_1 \le \theta_j$ for $j > 1$.
 
@@
 $$\exp\left(\theta_1 X_1 + \theta_2 X_2 + \cdots + \theta_n X_n\right) g\left(X\right) h\left(\theta\right) \ge \exp\left(\theta_1 X_2 + \theta_2 X_1 + \cdots + \theta_n X_n\right) g\left(X\right) h\left(\theta\right).$$
-Integrating both sides over the region $\left\{X: X_1 \ge a, X_2 < a\right\}$, summing instead if $X$ is a discrete vector, gives
+Integrating both sides over the region $\left\{X: X_1 \ge a, X_2 < a\right\}$ gives
 $$\PP\left(X_1 \ge a, X_2 < a\right) \ge \PP\left(X_1 < a, X_2 \ge a\right).$$
@@
 with a Schur-concave carrier measure $g$.
-Then there is a selective level-$\alpha$ test that verifies $\theta_{\left(1\right)} > \theta_{\left(2\right)}$ by comparing only $X_{\left(1\right)}$ and $X_{\left(2\right)}$.
-The test also verifies that $X_{\left(1\right)} \ge X_{\left(j\right)}$ stochastically for all $j > 1$.
-Here $X_{\left(j\right)}$ is the order statistic where $X_{\left(1\right)} \ge \cdots \ge X_{\left(n\right)}$.
+Then a naive two-sided test comparing only $X_{j^*}$ and $\max_{j \ne j^*} X_j$, where $j^* = \argmax_{j} X_j$, can verify $\theta_{j^*} \ge \max_{j \ne j^*} \theta_{j}$ with selective level $\alpha$.
+The test also verifies that $X_{j^*} \ge X_j$ stochastically for all $j \ne j^*$.
 \label{thm:main_result}
@@
 
-The $p$-value for $H_{0j}$ is thus
+The $p$-value for $H_{01j}$ is thus
 \begin{equation}
@@
 For the alternative case where $X_2 \ge M_{13}$, it follows from a similar proof.
-In either cases, $p_{12} \ge p_{13}$, or in generality, $p_{12} \ge p_{1j}$ for $j \ge 1$.
-A test based on only $X_1$ and $X_2$ is sufficient for the null hypothesis $H_{0j}$, if the carrying measure $g$ is Schur-concave.
+In either cases, $p_{12} \ge p_{13}$, or in generality, $p_{12} \ge p_{1j}$ for $j > 1$.
+A test based on only $X_1$ and $X_2$ is sufficient for the null hypothesis $H_{01}$, if the carrying measure $g$ is Schur-concave.
+Indeed, since the denominator of $p_{12}$ under the null hypothesis, this one-sided test comparing $X_1$ and $X_2$ is identical to a naive two-sided test comparing $X_1$ and $X_2$.
 By \Cref{thm:stoch}, rejecting this null hypothesis is equivalent to inferring that $X_1 \ge X_j$ for all $j>1$ stochastically.
@@
 \begin{theorem}
-In the same setup as \Cref{thm:main_result}, there is a selective level-$\alpha$ lower confidence bound for $\theta_{\left(1\right)} - \max_{j>1} \theta_{\left(j\right)}$.
+In the same setup as \Cref{thm:main_result}, there is a selective level-$\alpha$ lower confidence bound for $\theta_{j^*} - \max_{j \ne j^*} \theta_j$.
 \end{theorem}
@@
 Again we start with assuming $X_1 \ge \cdots \ge X_n$.
-The null hypothesis $H_{01}^\delta$ can be thought of as $\bigcup_{j > 1} H_{0j}^\delta$, where $H_{0j}^\delta$ is $\theta_1 - \theta_j \le \delta$.
+The null hypothesis $H_{01}^\delta$ can be thought of as $\bigcup_{j > 1} H_{01j}^\delta$, where $H_{01j}^\delta$ is $\theta_1 - \theta_j \le \delta$.
 In other words, we focus on the conditional law

### 2016-04-14 verifying-winner.tex
added some comments to first two sections

@@
 Alternatively, we can note that the marginal type I error rate is indeed not so straightforward.
-If the null hypothesis is ``$H_0: \text{Leader in polls has most support}$'', then for any distribution $F$ the marginal type I error rate is
+If the null hypothesis is ``$H_0: \text{Leader in polls has most support}$'' \WFcomment{Careful, this is an event}, then for any distribution $F$ the marginal type I error rate is
 
@@
 \item Comparing Trump to all other candidates involves multiple comparisons.
-Without considering the structure of this problem, common methods like Tukey's correction \cite{Tukey:1951} may largely decrease the test power.
+Without considering the structure of this problem, common methods like Tukey's correction \cite{Tukey:1951} may largely decrease the test power \WFcomment{Tukey's correction doesn't directly cover this case unless we modify it somehow.
+But without discussing how we might carry out this modification, bringing up Tukey might confuse people.}
 
@@
 The test provides selective type I error control, as well as enables us to construct confidence bound on the differences between the natural parameters and verify the order of the rest of natural parameters.
+\WFcomment{Still feels a bit abstract when you discuss these goals here.}
 
@@
 $$H_{0j}: \pi_j \le \max_{k \ne j} \pi_k = \bigcup_{k \ne j} H_{0jk}: \pi_j \le \pi_k$$
-when $X_j$ is larger than all other $X_k$. To break ties, we introduce independent auxiliary random variable $U_j \sim U\left[0,1\right]$, and opt to test $H_{0j}$ in the event of
+when $X_j$ is larger than all other $X_k$.
+\WFcomment{This a long and overly-abstract way of saying ``we break ties randomly''} To break ties, we introduce independent auxiliary random variable $U_j \sim U\left[0,1\right]$, and opt to test $H_{0j}$ in the event of
 $$A_j = \left\{X_j + U_j > \max_{k \ne j} X_k + U_k\right\}.$$
@@
 Without loss of generality, we will assume $X_1$ is considered largest with the tie-breaking method above in mind.
-Following the construction in \cite{Fithian:2014ws}, if we want to construct $p$-values $p_{1j}$ for $H_{01j}$, we need to first re-parametrize such that the selection event $A_1$ can be expressed as the sufficient statistic.
+Following the construction in \cite{Fithian:2014ws}, if we want to construct $p$-values $p_{1j}$ for $H_{01j}$, we need to first re-parametrize such that the selection event $A_1$ can be expressed as the sufficient statistic \WFcomment{What does it mean that the selection event is expressed as a sufficient statistic?}.
 The distribution is now
@@
 \item multiply the first term in the numerator and the denominator by $1/k$ where $k$ is the number of observations tied for largest; otherwise,
-\item multiply the first term in the denominator by $1/2$ if $X_1$ and $X_2$ has the same parity.
+\item multiply the first term in the denominator by $1/2$ if $X_1$ and $X_2$ has the same parity \WFcomment{could be a bit clearer about why you do this}.
 \end{itemize}
-Noticing that if there are ties for the largest the $p$-value is $1$ and the denominator is really $1/2$ otherwise, we can write
+Noticing that if there are ties for the largest the $p$-value is $1$ and the denominator is really $1/2$ otherwise \WFcomment{I don't think that's true for $j \neq 2$, is it?}, we can write
 $$p_{1j} = 1 \wedge 2 \sum_{t=X_1}^{X_1 + X_j} \binom{X_i + X_j}{t}.$$
@@
 meaning that it is sufficient to construct a one-sided test between $X_1$ and $X_2$ and consider only $p_{12}$.
+\WFcomment{This derivation is a little unclear.
+Is the middle probability a well-defined probability?}
 
-It may appear quite surprising that ``verifying a winner'' as we propose in this section requires no adjustment for multiplicity, in the sense that we only need to compare the winner to the runner- up, just as we would have done if $n = 2$.
+It may appear quite surprising that ``verifying a winner'' as we propose in this section requires no adjustment for multiplicity, in the sense that we only need to compare the winner to the runner- up, just as we would have done if $n = 2$ \WFcomment{I don't think it's clear enough to readers why the test is ``just as we would have done if $n=2$''}.
 After all, we know that the winner suffer’s from a winner's curse: given $X_5$ is the winner, $X_5 / m$ would overestimate $\pi_5$, and the larger $n$ is, the more severe this bias is likely to be.
@@
 For Gupta and Nagel, we use $\alpha = 0.05$; but to account for the extra factor of $\frac{n-1}{n}$ in \Cref{eqn:selective_vs_marginal}, we will apply the selective procedure for with $\frac{n}{n-1} \alpha$ such that the marginal type I error rate such that both procedures are controlled at $\alpha$.
-Gupta and Nagel coincides with our test at $n = 2$; however as $n$ grows, the selective test shoes significantly more power than Gupta and Nagel's test.
+\WFcomment{Can we justify this?
+Our procedure has error $\alpha$ in the case where all $\pi_j$ are equal.} Gupta and Nagel coincides with our test at $n = 2$; however as $n$ grows, the selective test shoes significantly more power than Gupta and Nagel's test.
 
@@
 But first we recall the notion of {\em majorization}.
+\WFcomment{I think we're implicitly assuming here  that $g$ is a density wrt one of (a) Lebesgue or (b) counting measure.
+Is that right?
+And if so, do we need a couple sentences to explain why it works in the counting measure case?
+That is, we need the atoms of non-zero measure to match up with each other along the rays of interest, right?}
 
@@
 	\draw[dashed] (0, 0) -- (C2);
-	\fill[yellow!50] (0, 0) -- (C1) -- ($(C1) + (7, 0)$) -- ($(C2) + (8, 0)$) -- (C2) -- cycle;
+	\fill[yellow!90!gray] (0, 0) -- (C1) -- ($(C1) + (7, 0)$) -- ($(C2) + (8, 0)$) -- (C2) -- cycle;
 	\node[above left] at ($(C2) + (8, 0)$) {$A_1$};
@@
 	\draw[dashed] (C5) -- (C6) node[midway, above, rotate = -90] {Truncation for $X_j < X_{j-1}$};
-	\fill[yellow!50] (0, 0) -- (C1) -- (C5) -- (C6) -- (C2) -- cycle;
+	\fill[yellow!90!gray] (0, 0) -- (C1) -- (C5) -- (C6) -- (C2) -- cycle;
 	\node[above] at ($(C2)!0.7!(C6)$) {$A_1$};

### 2016-04-15 verifying-winner.tex
Comments added / addressed, color changed

--- 2016-04-14 verifying-winner.tex
@@
 \usepackage{xcolor}
+\definecolor{mid_green}{HTML}{99d8c9}
 
@@
 
-%Commands for inline commenting that shows up on pdf
+% Commands for inline commenting that shows up on pdf
 \newcommand{\WFcomment}[1]{{\color{red}{(WF: \bf \sc #1) }}}
+\newcommand{\KHcomment}[1]{{\color{green!60!black}{(KH: \bf \sc #1) }}}
 
@@
 Alternatively, we can note that the marginal type I error rate is indeed not so straightforward.
-If the null hypothesis is ``$H_0: \text{Leader in polls has most support}$'', then for any distribution $F$ the marginal type I error rate is
+Specifically, the null hypothesis is ``$H_0 \left(X\right): \text{Leader in polls has most support}$'', which is random and dependent on poll data $X$.
+Then for any distribution $F$ the marginal type I error rate is
 
@@
 \item Comparing Trump to all other candidates involves multiple comparisons.
-Without considering the structure of this problem, common methods like Tukey's correction \cite{Tukey:1951} may largely decrease the test power.
+Without considering the structure of this problem, common methods that perform multiple comparisons may largely decrease the test power.
 
@@
 We constructed a selective level-$\alpha$ test for verifying that the largest observation is stochastically largest as well.
-The test provides selective type I error control, as well as enables us to construct confidence bound on the differences between the natural parameters and verify the order of the rest of natural parameters.
+The test provides selective type I error control, as well as enables us to construct confidence bound on the differences between the natural parameters and verify the order of the rest of the natural parameters.
+\WFcomment{Still feels a bit abstract when you discuss these goals here.} \KHcomment{What if we don't mention the side results at all?}
 
@@
 $$H_{0j}: \pi_j \le \max_{k \ne j} \pi_k = \bigcup_{k \ne j} H_{0jk}: \pi_j \le \pi_k$$
-when $X_j$ is larger than all other $X_k$. To break ties, we introduce independent auxiliary random variable $U_j \sim U\left[0,1\right]$, and opt to test $H_{0j}$ in the event of
-$$A_j = \left\{X_j + U_j > \max_{k \ne j} X_k + U_k\right\}.$$
-The distribution, written in an exponential family format, is
+when $X_j$ is larger than all other $X_k$. In case of ties, we break them independently and randomly. The distribution, written in an exponential family format, is
 $$\exp\left(X_1 \log \pi_1 + \cdots + X_n \log \pi_n\right) \frac{1_{X_1 + \cdots + X_n = m}}{X_1! \cdots X_n!}.$$
@@
 Without loss of generality, we will assume $X_1$ is considered largest with the tie-breaking method above in mind.
-Following the construction in \cite{Fithian:2014ws}, if we want to construct $p$-values $p_{1j}$ for $H_{01j}$, we need to first re-parametrize such that the selection event $A_1$ can be expressed as the sufficient statistic.
+Following the construction in \cite{Fithian:2014ws}, if we want to construct $p$-values $p_{1j}$ for $H_{01j}$, we need to first re-parametrize such that the selection event $A_1$ can be expressed in terms of the sufficient statistic.
 The distribution is now
@@
 \item multiply the first term in the numerator and the denominator by $1/k$ where $k$ is the number of observations tied for largest; otherwise,
-\item multiply the first term in the denominator by $1/2$ if $X_1$ and $X_2$ has the same parity.
+\item multiply the first term in the denominator by $1/2$ if $X_1$ and $X_j$ has the same parity, as the sum starts $X_1 = X_j = \frac{x_1 + x_j}{2}$.
 \end{itemize}
-Noticing that if there are ties for the largest the $p$-value is $1$ and the denominator is really $1/2$ otherwise, we can write
+Noticing that if $X_1, \ldots, X_j$ all tied the $p$-value is $1$, and the denominator is really $1/2$ otherwise \WFcomment{I don't think that's true for $j \neq 2$, is it?} \KHcomment{The denominator should always be half of a binomial distribution I think}, we can write
 $$p_{1j} = 1 \wedge 2 \sum_{t=X_1}^{X_1 + X_j} \binom{X_i + X_j}{t}.$$
 
-It is possible to check that $p_{12} \ge p_{1j}$ for any $j > 2$. Since the null hypothesis we are testing is a union of these smaller null hypothesis, the type I error rate is
-$$\PP_{H_{01}}\left(p_{12} < \alpha \middle| A_1\right) \le \max_{j>1} \PP_{H_{01j}}\left(p_{12} < \alpha \middle| A_1\right) \le \max_{j>1} \PP_{H_{01j}}\left(p_{1j} < \alpha \middle| A_1\right) \le \alpha,$$
-meaning that it is sufficient to construct a one-sided test between $X_1$ and $X_2$ and consider only $p_{12}$.
+It is possible to check that $p_{12} \ge p_{1j}$ for any $j > 2$. The type I error rate is
+$$\PP_{H_{01}}\left(p_{12} < \alpha \middle| A_1\right) \stackrel{\text{(i)}}{=} \max_{j>1} \PP_{H_{01j}}\left(p_{12} < \alpha \middle| A_1\right) \stackrel{\text{(ii)}}{\le} \max_{j>1} \PP_{H_{01j}}\left(p_{1j} < \alpha \middle| A_1\right) \stackrel{\text{(iii)}}{\le} \alpha,$$
+where (i) follows from $H_{01} = \bigcup_{j>1} H_{01j}$; (ii) is true as $p_{12} \ge p_{1j}$ as long as $X_1 \ge X_2 \ge \max_{j>2} X_j$, which is guaranteed here as we conditioned on $A_1$; (iii) follows from the construction of $p_{1j}$.
+\KHcomment{I think the probability in the middle (between (i) and (ii)) is well-defined, as $p_{12}$ is just a random variable dependent on $X$.} Thus it is sufficient to construct a one-sided test between $X_1$ and $X_2$ and consider only $p_{12}$.
 
-It may appear quite surprising that ``verifying a winner'' as we propose in this section requires no adjustment for multiplicity, in the sense that we only need to compare the winner to the runner- up, just as we would have done if $n = 2$.
+It may appear quite surprising that ``verifying a winner'' as we propose in this section requires no adjustment for multiplicity, in the sense that we only need to compare the winner to the runner-up, just as we would have done if $n = 2$.
+When $n=2$, the observation $X_1$ follows Binomial$\left(X_1 + X_2, \frac{1}{2}\right)$, coinciding with the test we proposed.
 After all, we know that the winner suffer’s from a winner's curse: given $X_5$ is the winner, $X_5 / m$ would overestimate $\pi_5$, and the larger $n$ is, the more severe this bias is likely to be.
@@
 for various combinations of $m$ and $n$.
-For Gupta and Nagel, we use $\alpha = 0.05$; but to account for the extra factor of $\frac{n-1}{n}$ in \Cref{eqn:selective_vs_marginal}, we will apply the selective procedure for with $\frac{n}{n-1} \alpha$ such that the marginal type I error rate such that both procedures are controlled at $\alpha$.
-Gupta and Nagel coincides with our test at $n = 2$; however as $n$ grows, the selective test shoes significantly more power than Gupta and Nagel's test.
+For Gupta and Nagel, we use $\alpha = 0.05$; but to account for the extra factor of $\frac{n-1}{n}$ in \Cref{eqn:selective_vs_marginal}, we will apply the selective procedure for with $\frac{n}{n-1} \alpha$ such that the marginal type I error rate of both procedures are controlled at $\alpha$.
+\WFcomment{Can we justify this?
+Our procedure has error $\alpha$ in the case where all $\pi_j$ are equal.} \KHcomment{The selective error rate is $\alpha$, but Gupta and Nagel really only had marginal error rate.
+If all $\pi_j$ are equal, the marginal error rate is $\frac{n-1}{n} \alpha$.} Gupta and Nagel coincides with our test at $n = 2$; however as $n$ grows, the selective test shoes significantly more power than Gupta and Nagel's test.
 
@@
 \begin{equation}
-X \sim \exp\left(\theta_1 X_1 + \cdots + \theta_n X_n\right) g\left(X\right) h\left(\theta\right).
+X \sim \exp\left(\theta_1 X_1 + \cdots + \theta_n X_n\right) g\left(X\right) h\left(\theta\right),
 \label{eqn:exp_family}
 \end{equation}
+defined on the Lebesgue or counting measure.
 It is reasonable to assume that the family is ``symmetric'', i.e.\ if $\theta_j = \theta_k$, then the probability distribution remains the same when $X_j$ and $X_k$ are swapped.
@@
 We would also like to introduce a fairly mild additional condition that $g$ is {\em Schur-concave}.
-But first we recall the notion of {\em majorization}.
+But first we recall the notion of {\em majorization}, defined on both $\mathbb{R}^n$ and $\mathbb{Z}^n$.
+\WFcomment{I think we're implicitly assuming here  that $g$ is a density wrt one of (a) Lebesgue or (b) counting measure.
+Is that right?
+And if so, do we need a couple sentences to explain why it works in the counting measure case?
+That is, we need the atoms of non-zero measure to match up with each other along the rays of interest, right?} \KHcomment{I think we are making that assumption.
+Added a few more words there but not sure if it is explicit enough.}
 
@@
 	\draw[dashed] (0, 0) -- (C2);
-	\fill[yellow!50] (0, 0) -- (C1) -- ($(C1) + (7, 0)$) -- ($(C2) + (8, 0)$) -- (C2) -- cycle;
+	\fill[mid_green] (0, 0) -- (C1) -- ($(C1) + (7, 0)$) -- ($(C2) + (8, 0)$) -- (C2) -- cycle;
 	\node[above left] at ($(C2) + (8, 0)$) {$A_1$};
@@
 The diagram is drawn a level set of $x_1 + x_2 + x_3$.
-The yellow region represents the selection event $A_1$.}
+The green region represents the selection event $A_1$.}
 \label{fig:p-value}
@@
 	\draw[dashed] (C5) -- (C6) node[midway, above, rotate = -90] {Truncation for $X_j < X_{j-1}$};
-	\fill[yellow!50] (0, 0) -- (C1) -- (C5) -- (C6) -- (C2) -- cycle;
+	\fill[mid_green] (0, 0) -- (C1) -- (C5) -- (C6) -- (C2) -- cycle;
 	\node[above] at ($(C2)!0.7!(C6)$) {$A_1$};

### 2016-04-19 verifying-winner.tex
Minor changes: some rephrasing and some confusing notation fixed

@@
 
-Having observed that Trump received the most votes in this poll, we want to ask whether he is actually in the lead in the population of all Iowa Republicans.
+Having observed that Trump received the most votes in this poll, we want to ask whether he indeed enjoys the most support among all Iowa Republicans.
 Intuitively, we would compare Trump to Cruz, as well as the other candidate.
@@
 In other words, the hypothesis itself is random.
-Alternatively, we can note that the marginal type I error rate is indeed not so straightforward.
-Specifically, the null hypothesis is ``$H_0 \left(X\right): \text{Leader in polls has most support}$'', which is random and dependent on poll data $X$.
+Alternatively, we can note that the marginal type I error rate is not quite straightforward.
+Specifically, the null hypothesis is ``$H_0 \left(X\right): \text{Leader in polls has most support}$'', which is dependent on random poll data $X$ through $j^*\left(X\right)$, the leader in polls.
 Then for any distribution $F$ the marginal type I error rate is
@@
 $$H_{0j}: \pi_j \le \max_{k \ne j} \pi_k = \bigcup_{k \ne j} H_{0jk}: \pi_j \le \pi_k$$
-when $X_j$ is larger than all other $X_k$. In case of ties, we break them independently and randomly. The distribution, written in an exponential family format, is
+when $X_j$ is larger than all other $X_k$. In case of ties, we break them independently and randomly. The distribution, written in an exponential family format, and up to constant factors, is
 $$\exp\left(X_1 \log \pi_1 + \cdots + X_n \log \pi_n\right) \frac{1_{X_1 + \cdots + X_n = m}}{X_1! \cdots X_n!}.$$
 
-Without loss of generality, we will assume $X_1$ is considered largest with the tie-breaking method above in mind.
+Without loss of generality, we will assume $X_1$ is considered largest.
 Following the construction in \cite{Fithian:2014ws}, if we want to construct $p$-values $p_{1j}$ for $H_{01j}$, we need to first re-parametrize such that the selection event $A_1$ can be expressed in terms of the sufficient statistic.
@@
 
-Next we condition on the sufficient statistics that are multiplied to the the nuisance parameter, in other words, we consider the conditional law
+Next we condition on the sufficient statistics for the nuisance parameter, in other words, we consider the conditional law
 $$\mathcal{L}_{\pi_1 = \pi_j}\left(\frac{X_1 - X_j}{2} \middle| X_2, \ldots, \frac{X_1 + X_j}{2}, \ldots, X_n, A_1\right),$$
@@
 $$\PP_{H_{01}}\left(p_{12} < \alpha \middle| A_1\right) \stackrel{\text{(i)}}{=} \max_{j>1} \PP_{H_{01j}}\left(p_{12} < \alpha \middle| A_1\right) \stackrel{\text{(ii)}}{\le} \max_{j>1} \PP_{H_{01j}}\left(p_{1j} < \alpha \middle| A_1\right) \stackrel{\text{(iii)}}{\le} \alpha,$$
-where (i) follows from $H_{01} = \bigcup_{j>1} H_{01j}$; (ii) is true as $p_{12} \ge p_{1j}$ as long as $X_1 \ge X_2 \ge \max_{j>2} X_j$, which is guaranteed here as we conditioned on $A_1$; (iii) follows from the construction of $p_{1j}$.
+where (i) follows from $H_{01} = \bigcup_{j>1} H_{01j}$; (ii) is true as $p_{12} \ge p_{1j}$ as long as $X_1 \ge X_2 \ge X_j$; (iii) follows from the construction of $p_{1j}$.
 \KHcomment{I think the probability in the middle (between (i) and (ii)) is well-defined, as $p_{12}$ is just a random variable dependent on $X$.} Thus it is sufficient to construct a one-sided test between $X_1$ and $X_2$ and consider only $p_{12}$.
@@
 However, if $X_9$ is the runner-up, then $X_9 / m$ is likely biased upward nearly as much as $X_5$.
-Informally, we might say that $X_9$ suffer’s from a “runner-up’s curse” that is nearly as bad as the winner's curse; as a result, $X_5 - X_9$ is actually not all that biased upward.
+Informally, we might say that $X_9$ suffer’s from a ``runner-up's curse'' that is nearly as bad as the winner's curse; as a result, $X_5 - X_9$ is actually not all that biased upward.
 By multiplying the $p$-value by $2$, or equivalently performing a two-tailed test, we take care of what little bias there is.
@@
 for various combinations of $m$ and $n$.
-For Gupta and Nagel, we use $\alpha = 0.05$; but to account for the extra factor of $\frac{n-1}{n}$ in \Cref{eqn:selective_vs_marginal}, we will apply the selective procedure for with $\frac{n}{n-1} \alpha$ such that the marginal type I error rate of both procedures are controlled at $\alpha$.
+For Gupta and Nagel, we use $\alpha = 0.05$; but in light of the extra factor of $\frac{n-1}{n}$ in \Cref{eqn:selective_vs_marginal}, we will apply the selective procedure with $\frac{n}{n-1} \alpha$ such that the marginal type I error rate of both procedures are controlled at $\alpha$.
 \WFcomment{Can we justify this?
@@
 And if so, do we need a couple sentences to explain why it works in the counting measure case?
-That is, we need the atoms of non-zero measure to match up with each other along the rays of interest, right?} \KHcomment{I think we are making that assumption.
-Added a few more words there but not sure if it is explicit enough.}
+That is, we need the atoms of non-zero measure to match up with each other along the rays of interest, right?} \KHcomment{We are making those assumptions.
+For Lebesgue, there should be no atoms.
+For counting measure, they should all line up perfectly.
+I don't think this result generalizes very well for other measures.}
 
@@
 
-Now suppose the carrier distribution $g$ in \Cref{eqn:exp_family} is indeed Schur-concave.
-We hereon call the class of distribution satisfying this {\em Schur-concave exponential family}.
+Now suppose the carrier distribution $g$ in \Cref{eqn:exp_family} is indeed Schur-concave. We hereon call the class of such distribution satisfying this {\em Schur-concave exponential family}.
+
 Without loss of generality, otherwise by relabeling, we consider only the event $X_1 \ge X_2 \ge \max_{k > 2} X_k$.
 We will be testing the null hypothesis $H_{01}: \theta_1 \le \max_{j > 1} \theta_j$, which is the union of the null hypotheses $H_{01j}: \theta_1 \le \theta_j$ for $j > 1$.
-
-Rejecting this hypothesis corresponds to inferring that $\theta_1 > \max_{j>1} \theta_j$. This is equivalent to $X_1$ being stochastically larger than $X_j$ for any $j > 1$.
+Rejecting this hypothesis corresponds to inferring that $\theta_1 > \max_{j>1} \theta_j$.
+This is equivalent to $X_1$ being stochastically larger than $X_j$ for any $j > 1$.
 
@@
 \label{thm:stoch}
-$X_1$ is greater than $X_2$ in stochastic order if and only if $\theta_1 > \theta_2$.
+$X_1 \ge X_2$ in stochastic order if and only if $\theta_1 > \theta_2$.
 \end{theorem}
@@
 $$\frac{B}{A+B} \ge \frac{D}{C+D} ~~~~ \Longleftrightarrow ~~~~ \frac{B}{A} \ge \frac{D}{C}.$$
-We will prove so by extending $A$ to include $\hat{A}$ on the diagram. We denote the sum $A + \hat{A}$ as $A'$. Formally,
+We will prove so by extending $A$ to include $\tilde{A}$ on the diagram. We denote the sum $A + \tilde{A}$ as $A'$. Formally,
 \begin{equation}
@@
 	\fill ($(0, 0)!(B)!(C2)$) circle(2pt);
-	\draw[thick, dashed] (A) -- (D) node[midway, below left] {$\hat{A}$};
+	\draw[thick, dashed] (A) -- (D) node[midway, below left] {$\tilde{A}$};
 	\fill (D) circle(2pt) node[above] {$\left(M_{13}, X_2 + D_{13}, X_3\right)$};
@@
 \caption{The $p$-value $p_{12}$ can be written in terms of integral $A$ along the segment and $B$ along the ray; and $p_{13}$ in terms of $C$ and $D$.
-$A'$ would refer to the sum of $A$ with the dashed line portion labeled as $\hat{A}$, formally explained in \Cref{eqn:int_extension}.
+$A'$ would refer to the sum of $A$ with the dashed line portion labeled as $\tilde{A}$, formally explained in \Cref{eqn:int_extension}.
 The majorization relation is indicated by the dotted line.}
@@
 If the distribution is discrete, the proof above holds true.
-Instead of performing integrals, the lattice points on the rays will be summed.
-If ties are broken independently and randomly, as in \Cref{sec:multinomial_example}, the end points on the rays can be considered as half a point.
+Instead of performing integrals, the atoms on the rays will be summed.
+If ties are broken independently and randomly, as in \Cref{sec:multinomial_example}, the end points on the rays can be considered as ``half an atom''.
 
@@
 
-If one is interested in verifying more than just the ``winner'', this selective test can also be extended as a step-down procedure to verify the ``first runner-up'' and ``second runner-up'' etc., while controlling the FWER and the FDR.
+If one is interested in verifying more than just the ``winner'', this selective test can also be extended to a step-down procedure that verifies the ``first runner-up'' and ``second runner-up'' etc., while controlling the FWER and the FDR.
 

### 2016-04-19 verifying-winner.tex

--- 2016-04-15 verifying-winner.tex
@@
 \usepackage{xcolor}
+\usepackage[round]{natbib}
 \definecolor{mid_green}{HTML}{99d8c9}
@@
 \begin{abstract}
-This paper deals with the selective inference problem encountered in rank verification --- verifying the order of the natural parameters in exponential families.
-We constructed a selective level-$\alpha$ test for verifying the largest natural parameter, which provides familywise error rate (FWER) and false discovery rate (FDR) control as we extend it into a step-down procedure.
-We also provide selective confidence bound for the difference between the largest and the second largest natural parameters.
+Many statistical experiments involve comparing of multiple population groups.
+For example, a public opinion poll may ask which of several political candidates commands the most support in a given population, or a clinical trial may compare patient outcomes under several treatment conditions.
+This article concerns the problem of {\em rank verification} --- post hoc tests for whether the ordering discovered in the data is in fact statistically significant.
+For exponential family models, we show under mild conditions that an unadjusted two-tailed pairwise $p$-value comparing the ``winning'' candidate to the ``runner-up'' is a valid $p$-value for checking whether the winner is truly the best.
+We extend this result to provide lower confidence bounds on the gap between the ``winning'' population and the others, and propose a simple step-down algorithm for verifying ranks beyond the first.
 \end{abstract}
@@
 
-We often make observations that form a joint distribution.
-While it might be relatively obvious in the independent case, the observations can well be dependent, complicating comparisons of parameters.
-However, comparison of these parameters can produce useful inferences.
+\subsection{Motivation: Iowa Republican Caucus Poll}
 
-A classic question is on how to statistically verify empirical rankings based on simple exponential family models.
-As motivation, consider a 2016 Quinnipiac University poll of $890$ Iowa Republicans Poll.
-\cite{quinnipiac} The poll found that Trump was in the lead with $31\%$ of the vote, Cruz is the first runner-up with $24\%$, followed by Rubio at $17\%$.
-The other ten candidates, including ``Don't know'', trailed behind.
-\Cref{tbl:poll} shows the results of the poll.
-Note that we have made a simplifying assumption that poll represents a random sample of Iowa Republicans --- i.e.\ that the data are multinomial, with parameter $\left(\pi_{\text{Trump}}, \pi_{\text{Cruz}}, \pi_{\text{Rubio}}, \ldots\right)$ representing their support in the Iowa Republican population.
-In reality, Quinnipiac University Poll Institute has processed the data to make the sample more representative of the population of likely voters.
+On February 1, 2016, Quinnipiac University released a poll of 890 Iowa Republicans regarding their preferred candidate for the Republican presidential nomination \citep{quinnipiac}.
+The results, reproduced here in Table~\ref{tbl:poll}, showed Donald Trump in the lead with $31\%$ of the vote, with Ted Cruz in second with $24\%$, Marco Rubio in third with $17\%$, and ten other candidates including ``Don't know'' trailing behind.
+We make a simplifying assumption that the poll represents a simple random sample of Iowa Republicans, i.e., that the data are a multinomial sample of size $890$ and underlying probabilities $(\pi_{\text{Trump}}, \pi_{\text{Cruz}}, \pi_{\text{Rubio}}, \ldots)$\footnote{The reality is a bit more complicated: before releasing the data, Quinnipiac has processed it to make the reported result more representative of likely caucus-goers.}
 
@@
 
-Having observed that Trump received the most votes in this poll, we want to ask whether he is actually in the lead in the population of all Iowa Republicans.
-Intuitively, we would compare Trump to Cruz, as well as the other candidate.
-This intuitive method however has a couple of issues.
+Once we see the results of the poll, several salient questions will likely occur to us: Is Trump really winning, and if so by how much?
+And analogously, is Cruz really in second, is Rubio really in third, and so on?
+
+Note that there is implicitly a problem of multiple comparisons here, since we would be asking a different set of questions if Cruz had led the poll instead.
+Indeed, the selection issue appears especially pernicious due to the so-called ``winner's curse:'' given that Trump leads the poll, it more likely than not overestimates his support.
+
+Nevertheless, if we blithely ignore the selection issue, we might carry out the following analyses to answer the questions we posed before at significance level $\alpha=0.05$:
+\begin{enumerate}
+\item {\em Is Trump really winning?} If Trump and Cruz were in fact tied, then Trump's share of their combined 490 votes should be distributed as $\text{Binom}(490, 0.5)$.
+Because the (two-tailed) $p$-value for this test is $p=0.006$, we can reject the null and declare that, yes, Trump is really winning.
+\item {\em By how much?} Using an exact $95\%$ interval for the same binomial model, we conclude Trump has at least $7.5\%$ more support than Cruz (and by extension everyone else).
+\item {\em Is Cruz in second, Rubio in third, etc.?} We can next compare Cruz to Rubio just as we compared Trump to Cruz (again rejecting because 214 is significantly more than half of 365), then Rubio to Carson, and so on, as a stepdown procedure.
+The first four comparisons are all significant at level $0.05$, but Paul and Bush are tied so we stop.
+\end{enumerate}
+
+Surprisingly, the three procedures described above are all entirely valid despite the implicit multiple-comparisons issue. The remainder of this article is dedicated to justifying them.
 
@@
 Without considering the structure of this problem, common methods that perform multiple comparisons may largely decrease the test power.
-
 \end{enumerate}
@@
 \end{itemize}
-Noticing that if $X_1, \ldots, X_j$ all tied the $p$-value is $1$, and the denominator is really $1/2$ otherwise \WFcomment{I don't think that's true for $j \neq 2$, is it?} \KHcomment{The denominator should always be half of a binomial distribution I think}, we can write
+Noticing that if $X_1, \ldots, X_j$ all tied the $p$-value is $1$, and the denominator is really $1/2$ otherwise \WFcomment{I don't think that's true for $j \neq 2$: say $X=(100, 99, 10)$.
+Then the denominator is }, we can write
 $$p_{1j} = 1 \wedge 2 \sum_{t=X_1}^{X_1 + X_j} \binom{X_i + X_j}{t}.$$
@@
 Our procedure has error $\alpha$ in the case where all $\pi_j$ are equal.} \KHcomment{The selective error rate is $\alpha$, but Gupta and Nagel really only had marginal error rate.
-If all $\pi_j$ are equal, the marginal error rate is $\frac{n-1}{n} \alpha$.} Gupta and Nagel coincides with our test at $n = 2$; however as $n$ grows, the selective test shoes significantly more power than Gupta and Nagel's test.
+If all $\pi_j$ are equal, the marginal error rate is $\frac{n-1}{n} \alpha$.} \WFcomment{Yes OK I think you're right.
+Because for G \& N the ``marginal error rate'' is defined by arbitrarily marking one of the tied populations as the best and then asking whether that marked one gets into the confidence set.} Gupta and Nagel coincides with our test at $n = 2$; however as $n$ grows, the selective test shoes significantly more power than Gupta and Nagel's test.
 
@@
 But first we recall the notion of {\em majorization}, defined on both $\mathbb{R}^n$ and $\mathbb{Z}^n$.
-\WFcomment{I think we're implicitly assuming here  that $g$ is a density wrt one of (a) Lebesgue or (b) counting measure.
-Is that right?
-And if so, do we need a couple sentences to explain why it works in the counting measure case?
-That is, we need the atoms of non-zero measure to match up with each other along the rays of interest, right?} \KHcomment{I think we are making that assumption.
-Added a few more words there but not sure if it is explicit enough.}
-
 \begin{definition}
@@
 
-\bibliographystyle{plain}
+\bibliographystyle{plainnat}
 \bibliography{papers,additional}

### 2016-04-19 verifying-winner.tex

--- 2016-04-19 verifying-winner.tex
@@
 \begin{abstract}
-This paper deals with the selective inference problem encountered in rank verification --- verifying the order of the natural parameters in exponential families.
-We constructed a selective level-$\alpha$ test for verifying the largest natural parameter, which provides familywise error rate (FWER) and false discovery rate (FDR) control as we extend it into a step-down procedure.
-We also provide selective confidence bound for the difference between the largest and the second largest natural parameters.
+Many statistical experiments involve comparing of multiple population groups.
+For example, a public opinion poll may ask which of several political candidates commands the most support in a given population, or a clinical trial may compare patient outcomes under several treatment conditions.
+This article concerns the problem of {\em rank verification} --- post hoc tests of whether the ordering discovered in the data is in fact statistically significant.
+For exponential family models, we show under mild conditions that an unadjusted two-tailed pairwise $p$-value comparing the ``winning'' population to the ``runner-up'' is a valid $p$-value for checking whether the winner is truly the best.
+We extend this result to provide lower confidence bounds on the gap between the ``winning'' population and the others, and propose a simple step-down algorithm for verifying ranks beyond the first.
 \end{abstract}
@@
 
-We often make observations that form a joint distribution.
-While it might be relatively obvious in the independent case, the observations can well be dependent, complicating comparisons of parameters.
-However, comparison of these parameters can produce useful inferences.
+\subsection{Motivating Example: Iowa Republican Caucus Poll}\label{sec:iowa}
 
-A classic question is on how to statistically verify empirical rankings based on simple exponential family models.
-As motivation, consider a 2016 Quinnipiac University poll of $890$ Iowa Republicans Poll.
-\cite{quinnipiac} The poll found that Trump was in the lead with $31\%$ of the vote, Cruz is the first runner-up with $24\%$, followed by Rubio at $17\%$.
-The other ten candidates, including ``Don't know'', trailed behind.
-\Cref{tbl:poll} shows the results of the poll.
-Note that we have made a simplifying assumption that poll represents a random sample of Iowa Republicans --- i.e.\ that the data are multinomial, with parameter $\left(\pi_{\text{Trump}}, \pi_{\text{Cruz}}, \pi_{\text{Rubio}}, \ldots\right)$ representing their support in the Iowa Republican population.
-In reality, Quinnipiac University Poll Institute has processed the data to make the sample more representative of the population of likely voters.
+On February 1, 2016, Quinnipiac University released a poll of 890 Iowa Republicans regarding their preferred candidate for the Republican presidential nomination \citep{quinnipiac}.
+The results, shown in Table~\ref{tbl:poll}, placed Donald Trump in the lead with $31\%$ of the vote, with Ted Cruz in second with $24\%$, Marco Rubio in third with $17\%$, and ten other candidates including ``Don't know'' trailing behind.
+We assume for simplicity that the poll represents a simple random sample of Iowa Republicans, i.e., that the data are a multinomial sample of size $890$ and underlying probabilities $(\pi_{\text{Trump}}, \pi_{\text{Cruz}}, \pi_{\text{Rubio}}, \ldots)$.\footnote{The reality is a bit more complicated: before releasing the data, Quinnipiac has processed it to make the reported result more representative of likely caucus-goers.}
 
@@
 
-Having observed that Trump received the most votes in this poll, we want to ask whether he indeed enjoys the most support among all Iowa Republicans.
-Intuitively, we would compare Trump to Cruz, as well as the other candidate.
-This intuitive method however has a couple of issues.
+Seeing that Trump leads this poll, several salient questions may occur to us: Is Trump really winning, and if so by how much?
+And analogously, is Cruz really in second, is Rubio really in third, and so on?
 
+Note that there is implicitly a problem of multiple comparisons here, because if Cruz had led the poll instead, we would be asking a different set of questions.
+Indeed, the selection issue appears especially pernicious due to the so-called ``winner's curse:'' given that Trump leads the poll, it more likely than not overestimates his support.
+
+Nevertheless, if we blithely ignore the selection issue, we might carry out the following analyses to answer the questions we posed before at significance level $\alpha=0.05$:
 \begin{enumerate}
+\item {\em Is Trump really winning?} If Trump and Cruz were in fact tied, then Trump's share of their combined 490 votes would be distributed as $\text{Binom}(490, 0.5)$.
+Because the (two-tailed) $p$-value for this pairwise test is $p=0.006$, we reject the null and conclude that Trump is really winning.
+\item {\em By how much?} Using an exact $95\%$ interval for the same binomial model, we conclude Trump has at least $7.5\%$ more support than Cruz (i.e., $\pi_{\text{Trump}} \geq 1.075 \,\pi_{\text{Cruz}}$) and also leads the other candidates by at least as much.
+\item {\em Is Cruz in second, Rubio in third, etc.?} We can next compare Cruz to Rubio just as we compared Trump to Cruz (again rejecting because 214 is significantly more than half of 365), then Rubio to Carson, and so on, as a stepdown procedure.
+The first four comparisons are all significant at level $0.05$, but Paul and Bush are tied so we stop.
+\end{enumerate}
 
-\item This has a hidden upward selection bias, or ``winner's curse'', as we are only testing this hypothesis as Trump is leading in the polls.
+Surprisingly, the three procedures described above are all entirely valid despite the implicit multiple-comparisons issue.
+The remainder of this article is dedicated to justifying them for the multinomial family and many other settings.
+
+\subsection{Generic Problem Setting and Main Result}
+
+Generically, we will consider data drawn from an exponential family model with density
+\begin{equation}\label{eq:expfam}
+X \sim e^{\theta'x - \psi(\theta)}g(x),
+\end{equation}
+with respect to either the Lebesgue or counting measure on $\RR^n$.
+We assume further that $g(x)$ is symmetric.
+In addition to the multinomial family, \eqref{eq:expfam} also encompasses settings such as comparing independent binomial treatment outcomes in a clinical trial, competing sports teams under a Bradley-Terry model, entries of a Dirichlet distribution, and many more.
+\WFcomment{Also students taking a test in a Rasch model, after conditioning on how many get each question right.
+Or comparing the variances of different normal populations.} We will generically use the term {\em population} to refer to the treatment group, sports team, political candidate, etc.
+represented by a given random variable $X_j$.
+
+As we will see, $\theta_j > \theta_k$ if and only if $X_j$ is stochastically larger than $X_k$, so there is a well-defined stochastic ordering of the populations.
+We will refer to the population with maximal $\theta_j$ as the {\em best}, and the one with maximal $X_j$ as the {\em winner}.
+Following the convention in the ranking and selection literature, we assume that if there are multiple largest $\theta_j$, then one is arbitrarily marked as the best.
+Note that in cases where it is more interesting to ask which is the smallest population --- for example, if $X_j$ is the number of patients on treatment $j$ who suffer a heart attack during a trial --- we can change variables to $-X_j$.
+
+Write the order statistics of $X$ as
+\[
+X_{[1]} \geq X_{[2]} \geq \cdots \geq X_{[n]},
+\]
+and define $\theta_{[j]}$ as the entry of $\theta$ corresponding to the $j$th order statistic of $X$ (note $\theta_{[1]}$ might {\em not} equal $\max_j \theta_j$, for example).
+We assume any ties between entries of $X$ are broken randomly.
+
+In each of the above examples, there is an exact two-tailed pairwise test we would typically apply if testing $\theta_j=\theta_k$ for any two fixed indices.
+For example, for the multinomial, we would apply the conditional binomial test based on the combined total $X_j+X_k$ as discussed in the previous section, and for independent binomials we would apply Fisher's exact test.
+More generally, we can condition on the other $n-2$ indices (notated $X_{\setminus \{j,k\}}$) and $X_j+X_k$, and reject the null if $X_j$ is outside the $\alpha/2$ and $1-\alpha/2$ quantiles of the known conditional law $\mathcal{L}_{\theta_j=\theta_k}(X_j \mid X_j+X_k, X_{\setminus\{j,k\}})$.
+We call this test the (two-tailed) {\em unadjusted pairwise test} since it implicitly assumes the two indices $j,k$ are fixed and is therefore not adjusted for selection.
+Similarly, inverting this test for all values of $\theta_j-\theta_k$ yields an {\em unadjusted pairwise confidence interval}.\footnote{To avoid trivialities in the discrete case, we assume these procedures are appropriately randomized at the rejection thresholds to give exact level-$\alpha$ control.}
+
+Generalizing the procedures described in Section~\ref{sec:iowa} we obtain the following:
+\begin{enumerate}
+\item {\em Is the winner really the best?} Carry out the unadjusted pairwise test comparing the winner to the runner-up.
+If the test rejects at level $\alpha$, conclude that the winner is really the best.
+\item {\em By how much?} Construct the unadjusted pairwise confidence interval comparing the winner to the runner-up, and report the lower confidence bound obtained for $\theta_{[1]}-\theta_{[2]}$.
+\item {\em Is the runner-up really the second best, etc.?} Continue by comparing the runner-up to the second-runner-up, again using the unadjusted pairwise test, and so on down the list comparing adjacent values.
+Stop the first time the test accepts.
+\end{enumerate}
+
+We now state our main theorem: under a mild technical assumption, the three procedures described above are statistically valid, even accounting for the selection.
+\begin{theorem}\label{thm:main}
+Assume the model~\eqref{eq:expfam} holds and $g(x)$ is a Schur-concave function.
+The first procedure has level $\alpha$ conditional on the best population not winning (otherwise an error is impossible).
+The second procedure gives an exact $1-\alpha$ lower confidence bound for $\theta_{[1]} - \max_{j \neq [1]} \theta_{j}$.
+The third procedure is a conservative stepdown procedure with familywise error rate (FWER) no larger than $\alpha$.
+\end{theorem}
+
+We define Schur-concave functions and discuss their properties in Section~\ref{sec:maj}.
+Because any log-concave and symmetric function is Schur-concave, Theorem~\ref{thm:main} applies to all of the cases discussed above.
+
+Note that there is an implicit adjustment for selection here, since we are using two-tailed unadjusted tests.
+If we instead based our tests on an independent realization $X^*$, then we could (for example) use the right-tailed version of the unadjusted pairwise test for the first procedure.
+Having to use a two-tailed procedure is in some sense unsurprising: Even for $n=2$, it is intuitive that we should have to use the two-tailed test instead of the one-tailed.
+Indeed, the first procedure is exactly equivalent to the two-tailed test of the fixed hypothesis $\theta_1=\theta_2$.
+
+What may be more surprising is that, no matter how large $n$ is, we do not require any additional adjustment beyond what we already require for $n=2$.
+Informally, this can possibly be explained by noting that for large $n$, $X_{[2]}$ suffers from a positive selection bias --- a ``runner-up's curse,'' so to speak --- which is nearly as severe as the bias of $X_{[1]}$.
+
+% \begin{enumerate}
+
+% \item This has a hidden upward selection bias, or ``winner's curse'', as we are only testing this hypothesis as Trump is leading in the polls.
 In other words, the hypothesis itself is random.
@@
 
-\begin{equation}
-\PP_F\left(\text{reject } H_0\right) = \sum_{\substack{j \text{ is a candidate} \\ j \text{ does not have most support}}} \PP_F\left(\text{reject } H_0 \middle| j \text{ leads in polls}\right) \PP_F \left(j \text{ leads in polls}\right).
-\label{eqn:marginal_error}
-\end{equation}
+% \begin{equation}
+% \PP_F\left(\text{reject } H_0\right) = \sum_{\substack{j \text{ is a candidate} \\ j \text{ does not have most support}}} \PP_F\left(\text{reject } H_0 \middle| j \text{ leads in polls}\right) \PP_F \left(j \text{ leads in polls}\right).
+% \label{eqn:marginal_error}
+% \end{equation}
 
-\item Comparing Trump to all other candidates involves multiple comparisons.
+% \item Comparing Trump to all other candidates involves multiple comparisons.
 Without considering the structure of this problem, common methods that perform multiple comparisons may largely decrease the test power.
+% \end{enumerate}
 
-\end{enumerate}
+% We will construct a test as outlined by Fithian, Sun and Taylor in \cite{Fithian:2014ws}. The fundamental idea is to consider the selective type I error rate
+% $$\PP_F\left(\text{reject } H_0 \middle| j \text{ leads in polls} \right), ~~~~~~~~ \text{where $j$ is a candidate,}$$
+% instead. Note that controlling this selective type I error rate at $\alpha$ provides control of the marginal type I error rate at $\alpha$ too. From \Cref{eqn:marginal_error},
+% \begin{align}
+% \PP_F\left(\text{reject } H_0\right) & = \sum_{\substack{j \text{ is a candidate} \\ j \text{ does not have most support}}} \PP_F\left(\text{reject } H_0 \middle| j \text{ leads in polls}\right) \PP_F \left(j \text{ leads in polls}\right).
+\nonumber \\
+% & \le \sum_{\substack{j \text{ is a candidate} \\ j \text{ does not have most support}}} \alpha \PP_F \left(j \text{ leads in polls}\right). \nonumber \\
+% & = \alpha \PP\left(\text{Leader in polls does not have most support}\right) \nonumber \\
+% & \le \frac{n-1}{n} \alpha. \label{eqn:selective_vs_marginal}
+% \end{align}
 
-We will construct a test as outlined by Fithian, Sun and Taylor in \cite{Fithian:2014ws}. The fundamental idea is to consider the selective type I error rate
-$$\PP_F\left(\text{reject } H_0 \middle| j \text{ leads in polls} \right), ~~~~~~~~ \text{where $j$ is a candidate,}$$
-instead. Note that controlling this selective type I error rate at $\alpha$ provides control of the marginal type I error rate at $\alpha$ too. From \Cref{eqn:marginal_error},
-\begin{align}
-\PP_F\left(\text{reject } H_0\right) & = \sum_{\substack{j \text{ is a candidate} \\ j \text{ does not have most support}}} \PP_F\left(\text{reject } H_0 \middle| j \text{ leads in polls}\right) \PP_F \left(j \text{ leads in polls}\right).
-\nonumber \\
-& \le \sum_{\substack{j \text{ is a candidate} \\ j \text{ does not have most support}}} \alpha \PP_F \left(j \text{ leads in polls}\right). \nonumber \\
-& = \alpha \PP\left(\text{Leader in polls does not have most support}\right) \nonumber \\
-& \le \frac{n-1}{n} \alpha. \label{eqn:selective_vs_marginal}
-\end{align}
-
-Surprisingly, this also tackles the second issue above.
+% Surprisingly, this also tackles the second issue above.
 The test reduces the multiple comparison problem into one comparison between Trump and Cruz.
@@
 
-More generally, when we observe a random vector $(X_1, \ldots, X_n)$ from an exponential family, and whichever random variable is largest, we want to test whether it is in fact stochastically larger than the other random variables.
+% More generally, when we observe a random vector $(X_1, \ldots, X_n)$ from an exponential family, and whichever random variable is largest, we want to test whether it is in fact stochastically larger than the other random variables.
 
@@
 
-\subsection{Main result}
+% \subsection{Main result}
 
-In this paper, we focus on Schur-concave exponential family, a broad class of distribution that is defined in \Cref{sec:exponential_families} and includes various examples listed in \Cref{sec:applications}.
+% In this paper, we focus on Schur-concave exponential family, a broad class of distribution that is defined in \Cref{sec:exponential_families} and includes various examples listed in \Cref{sec:applications}.
 We constructed a selective level-$\alpha$ test for verifying that the largest observation is stochastically largest as well.
@@
 Our procedure has error $\alpha$ in the case where all $\pi_j$ are equal.} \KHcomment{The selective error rate is $\alpha$, but Gupta and Nagel really only had marginal error rate.
-If all $\pi_j$ are equal, the marginal error rate is $\frac{n-1}{n} \alpha$.} Gupta and Nagel coincides with our test at $n = 2$; however as $n$ grows, the selective test shoes significantly more power than Gupta and Nagel's test.
+If all $\pi_j$ are equal, the marginal error rate is $\frac{n-1}{n} \alpha$.}  \WFcomment{Yes OK I think you're right.
+Because for G \& N the ``marginal error rate'' is defined by arbitrarily marking one of the tied populations as the best and then asking whether that marked one gets into the confidence set.} Gupta and Nagel coincides with our test at $n = 2$; however as $n$ grows, the selective test shoes significantly more power than Gupta and Nagel's test.
 
@@
 But first we recall the notion of {\em majorization}, defined on both $\mathbb{R}^n$ and $\mathbb{Z}^n$.
-\WFcomment{I think we're implicitly assuming here  that $g$ is a density wrt one of (a) Lebesgue or (b) counting measure.
-Is that right?
-And if so, do we need a couple sentences to explain why it works in the counting measure case?
-That is, we need the atoms of non-zero measure to match up with each other along the rays of interest, right?} \KHcomment{We are making those assumptions.
+\KHcomment{We are making those assumptions.
 For Lebesgue, there should be no atoms.

### 2016-04-20 verifying-winner.tex

@@
 \begin{abstract}
-Many statistical experiments involve comparing of multiple population groups.
-For example, a public opinion poll may ask which of several political candidates commands the most support in a given population, or a clinical trial may compare patient outcomes under several treatment conditions.
+Many statistical experiments involve comparing multiple population groups.
+For example, a public opinion poll may ask which of several political candidates commands the most support, or a clinical trial may compare patient outcomes to determine the best of several treatment conditions.
 This article concerns the problem of {\em rank verification} --- post hoc tests of whether the ordering discovered in the data is in fact statistically significant.
-For exponential family models, we show under mild conditions that an unadjusted two-tailed pairwise $p$-value comparing the ``winning'' population to the ``runner-up'' is a valid $p$-value for checking whether the winner is truly the best.
-We extend this result to provide lower confidence bounds on the gap between the ``winning'' population and the others, and propose a simple step-down algorithm for verifying ranks beyond the first.
+For exponential family models, we show under mild conditions that an unadjusted two-tailed pairwise test comparing the ``winning'' population to the ``runner-up'' is a valid test of whether the winner is truly the best.
+We also propose comparably simple procedures to give lower confidence bounds on the gap between the winning population and the others, and to verify ranks beyond the first.
 \end{abstract}
@@
 
-On February 1, 2016, Quinnipiac University released a poll of 890 Iowa Republicans regarding their preferred candidate for the Republican presidential nomination \citep{quinnipiac}.
-The results, shown in Table~\ref{tbl:poll}, placed Donald Trump in the lead with $31\%$ of the vote, with Ted Cruz in second with $24\%$, Marco Rubio in third with $17\%$, and ten other candidates including ``Don't know'' trailing behind.
-We assume for simplicity that the poll represents a simple random sample of Iowa Republicans, i.e., that the data are a multinomial sample of size $890$ and underlying probabilities $(\pi_{\text{Trump}}, \pi_{\text{Cruz}}, \pi_{\text{Rubio}}, \ldots)$.\footnote{The reality is a bit more complicated: before releasing the data, Quinnipiac has processed it to make the reported result more representative of likely caucus-goers.}
+Table~\ref{tbl:poll} shows the result of a Quinnipiac University poll asking 890 Iowa Republicans their preferred candidate for the Republican presidential nomination \citep{quinnipiac}.
+Donald Trump led with $31\%$ of the vote, Ted Cruz came second with $24\%$, Marco Rubio third with $17\%$, and ten other candidates including ``Don't know'' trailed behind.
 
@@
 And analogously, is Cruz really in second, is Rubio really in third, and so on?
-
 Note that there is implicitly a problem of multiple comparisons here, because if Cruz had led the poll instead, we would be asking a different set of questions.
@@
 
-Nevertheless, if we blithely ignore the selection issue, we might carry out the following analyses to answer the questions we posed before at significance level $\alpha=0.05$:
+Nevertheless, if we blithely ignore the selection issue, we might carry out the following analyses to answer the questions we posed before at significance level $\alpha=0.05$.
+We assume for simplicity that the poll represents a simple random sample of Iowa Republicans, i.e., that the data are a multinomial sample of size $890$ and underlying probabilities $(\pi_{\text{Trump}}, \pi_{\text{Cruz}}, \ldots)$.\footnote{The reality is a bit more complicated: before releasing the data, Quinnipiac has processed it to make the reported result more representative of likely caucus-goers.}
 \begin{enumerate}
@@
 \item {\em By how much?} Using an exact $95\%$ interval for the same binomial model, we conclude Trump has at least $7.5\%$ more support than Cruz (i.e., $\pi_{\text{Trump}} \geq 1.075 \,\pi_{\text{Cruz}}$) and also leads the other candidates by at least as much.
-\item {\em Is Cruz in second, Rubio in third, etc.?} We can next compare Cruz to Rubio just as we compared Trump to Cruz (again rejecting because 214 is significantly more than half of 365), then Rubio to Carson, and so on, as a stepdown procedure.
+\item {\em Is Cruz in second, Rubio in third, etc.?} We can next compare Cruz to Rubio just as we compared Trump to Cruz (again rejecting because 214 is significantly more than half of 365), then Rubio to Carson, and so on, continuing until we fail to reject.
 The first four comparisons are all significant at level $0.05$, but Paul and Bush are tied so we stop.
@@
 
-Surprisingly, the three procedures described above are all entirely valid despite the implicit multiple-comparisons issue.
-The remainder of this article is dedicated to justifying them for the multinomial family and many other settings.
+Surprisingly, all of the three procedures described above are statistically valid despite ignoring the implicit multiple-comparisons issue.
+The remainder of this article is dedicated to justifying these procedures for the multinomial family and analogous procedures in other settings.
 
@@
 We assume further that $g(x)$ is symmetric.
-In addition to the multinomial family, \eqref{eq:expfam} also encompasses settings such as comparing independent binomial treatment outcomes in a clinical trial, competing sports teams under a Bradley-Terry model, entries of a Dirichlet distribution, and many more.
+In addition to the multinomial family, \eqref{eq:expfam} also encompasses settings such as comparing independent binomial treatment outcomes in a clinical trial, competing sports teams under a Bradley-Terry model, entries of a Dirichlet distribution, and many more; see Section~\ref{sec:examples} for these and other examples.
 \WFcomment{Also students taking a test in a Rasch model, after conditioning on how many get each question right.
-Or comparing the variances of different normal populations.} We will generically use the term {\em population} to refer to the treatment group, sports team, political candidate, etc.
+Or comparing the variances of different normal populations.}
+
+We will generically use the term {\em population} to refer to the treatment group, sports team, political candidate, etc.
 represented by a given random variable $X_j$.
-
-As we will see, $\theta_j > \theta_k$ if and only if $X_j$ is stochastically larger than $X_k$, so there is a well-defined stochastic ordering of the populations.
+As we will see, $\theta_j \geq \theta_k$ if and only if $X_j$ is stochastically larger than $X_k$; thus, there is a well-defined stochastic ordering of the populations that matches the ordering of the entries of $\theta$.
 We will refer to the population with maximal $\theta_j$ as the {\em best}, and the one with maximal $X_j$ as the {\em winner}.
 Following the convention in the ranking and selection literature, we assume that if there are multiple largest $\theta_j$, then one is arbitrarily marked as the best.
-Note that in cases where it is more interesting to ask which is the smallest population --- for example, if $X_j$ is the number of patients on treatment $j$ who suffer a heart attack during a trial --- we can change variables to $-X_j$.
+Note that in cases where it is more interesting to ask which is the smallest population --- for example, if $X_j$ is the number of patients on treatment $j$ who suffer a heart attack during a trial --- we can change variables to $-X$.
 
@@
 \]
-and define $\theta_{[j]}$ as the entry of $\theta$ corresponding to the $j$th order statistic of $X$ (note $\theta_{[1]}$ might {\em not} equal $\max_j \theta_j$, for example).
+and define $\theta_{[j]}$ as the entry of $\theta$ corresponding to the $j$th order statistic of $X$ (so $\theta_{[1]}$ might {\em not} equal $\max_j \theta_j$, for example).
 We assume any ties between entries of $X$ are broken randomly.
 
-In each of the above examples, there is an exact two-tailed pairwise test we would typically apply if testing $\theta_j=\theta_k$ for any two fixed indices.
-For example, for the multinomial, we would apply the conditional binomial test based on the combined total $X_j+X_k$ as discussed in the previous section, and for independent binomials we would apply Fisher's exact test.
-More generally, we can condition on the other $n-2$ indices (notated $X_{\setminus \{j,k\}}$) and $X_j+X_k$, and reject the null if $X_j$ is outside the $\alpha/2$ and $1-\alpha/2$ quantiles of the known conditional law $\mathcal{L}_{\theta_j=\theta_k}(X_j \mid X_j+X_k, X_{\setminus\{j,k\}})$.
-We call this test the (two-tailed) {\em unadjusted pairwise test} since it implicitly assumes the two indices $j,k$ are fixed and is therefore not adjusted for selection.
+In each of the above examples, there is a natural exact test we could apply to test $\theta_j=\theta_k$ for any two {\em fixed} populations $j$ and $k$.
+In the multinomial case, we would apply the conditional binomial test based on the combined total $X_j+X_k$ as discussed in the previous section.
+For the case of independent binomials we would apply Fisher's exact test, again conditioning on $X_j+X_k$.
+These are both examples of a generic UMPU pairwise test in which we condition on the other $n-2$ indices (notated $X_{\setminus \{j,k\}}$) and $X_j+X_k$, and reject the null if $X_j$ is outside the $\alpha/2$ and $1-\alpha/2$ quantiles of the known conditional law $\mathcal{L}_{\theta_j=\theta_k}(X_j \mid X_j+X_k, X_{\setminus\{j,k\}})$.
+We call this test the (two-tailed) {\em unadjusted pairwise test} since it makes no explicit adjustment for selection.
 Similarly, inverting this test for all values of $\theta_j-\theta_k$ yields an {\em unadjusted pairwise confidence interval}.\footnote{To avoid trivialities in the discrete case, we assume these procedures are appropriately randomized at the rejection thresholds to give exact level-$\alpha$ control.}
@@
 
-We now state our main theorem: under a mild technical assumption, the three procedures described above are statistically valid, even accounting for the selection.
+We now state our main theorem: under a mild technical assumption, Procedures 1--3 described above are statistically valid, even accounting for the selection.
 \begin{theorem}\label{thm:main}
-Assume the model~\eqref{eq:expfam} holds and $g(x)$ is a Schur-concave function.
-The first procedure has level $\alpha$ conditional on the best population not winning (otherwise an error is impossible).
-The second procedure gives an exact $1-\alpha$ lower confidence bound for $\theta_{[1]} - \max_{j \neq [1]} \theta_{j}$.
-The third procedure is a conservative stepdown procedure with familywise error rate (FWER) no larger than $\alpha$.
+Assume the model~\eqref{eq:expfam} holds and $g(x)$ is a Schur-concave function. Then:
+\begin{enumerate}
+\item Procedure 1 has level $\alpha$ conditional on the best population not winning (otherwise an error is impossible).
+\item Procedure 2 gives an exact $1-\alpha$ lower confidence bound for $\theta_{[1]} - \max_{j \neq [1]} \theta_{j}$.
+\item Procedure 3 is a conservative stepdown procedure with familywise error rate (FWER) no larger than $\alpha$.
+\end{enumerate}
 \end{theorem}
@@
 Because any log-concave and symmetric function is Schur-concave, Theorem~\ref{thm:main} applies to all of the cases discussed above.
+The proof relies on the conditional selective-inference framework of~\citet{Fithian:2014ws} combined with classical multiple-testing methods, as well as ideas involving majorization and Schur-concavity.
 
-Note that there is an implicit adjustment for selection here, since we are using two-tailed unadjusted tests.
-If we instead based our tests on an independent realization $X^*$, then we could (for example) use the right-tailed version of the unadjusted pairwise test for the first procedure.
-Having to use a two-tailed procedure is in some sense unsurprising: Even for $n=2$, it is intuitive that we should have to use the two-tailed test instead of the one-tailed.
-Indeed, the first procedure is exactly equivalent to the two-tailed test of the fixed hypothesis $\theta_1=\theta_2$.
+Note that these procedures make an implicit adjustment for selection because they use two-tailed unadjusted tests.
+If we instead based our tests on an independent realization $X^*$, then (for example) Procedure 1 could use a right-tailed version of the unadjusted pairwise test.
+In the case $n=2$ Procedure 1 amounts to a simple two-tailed test of the null hypothesis $\theta_1=\theta_2$, and it is intuitively clear that a one-tailed test would be anti-conservative.
+More surprising is that, no matter how large $n$ is, Procedures 1--3 require no further adjustment beyond what is required when $n=2$.
 
-What may be more surprising is that, no matter how large $n$ is, we do not require any additional adjustment beyond what we already require for $n=2$.
-Informally, this can possibly be explained by noting that for large $n$, $X_{[2]}$ suffers from a positive selection bias --- a ``runner-up's curse,'' so to speak --- which is nearly as severe as the bias of $X_{[1]}$.
+% Informally, this can possibly be explained by noting that for large $n$, $X_{[2]}$ suffers from a positive selection bias --- a ``runner-up's curse,'' so to speak --- which is nearly as severe as the bias of $X_{[1]}$.
 

### 2016-04-22 verifying-winner.tex
Fixed natbib quirks
Sections shuffled, paper unconcluded

@@
 \DeclareMathOperator*{\argmax}{arg\,max}
+\newtheorem{corollary}{Corollary}
 \newtheorem{definition}{Definition}
-\newtheorem{lemma}{Lemma}
-\newtheorem{theorem}{Theorem}
+\newtheorem{lemma}[corollary]{Lemma}
+\newtheorem{theorem}[corollary]{Theorem}
 \setlength{\tabcolsep}{1em}
@@
 \newcommand{\RR}{\mathbb{R}}
+\newcommand{\ZZ}{\mathbb{Z}}
 
@@
 
-\title{Rank verification for exponential families}
+\title{Rank Verification for Exponential Families}
 \author{Kenneth Hung \and William Fithian}
@@
 \section{Introduction}
-\label{sec:introduction}
+\label{sec:intro}
 
-\subsection{Motivating Example: Iowa Republican Caucus Poll}\label{sec:iowa}
+\subsection{Motivating Example: Iowa Republican Caucus Poll}
+\label{sec:iowa}
 
-Table~\ref{tbl:poll} shows the result of a Quinnipiac University poll asking 890 Iowa Republicans their preferred candidate for the Republican presidential nomination \citep{quinnipiac}.
+\Cref{tbl:poll} shows the result of a Quinnipiac University poll asking 890 Iowa Republicans their preferred candidate for the Republican presidential nomination \citep{quinnipiac}.
 Donald Trump led with $31\%$ of the vote, Ted Cruz came second with $24\%$, Marco Rubio third with $17\%$, and ten other candidates including ``Don't know'' trailed behind.
@@
 Note that there is implicitly a problem of multiple comparisons here, because if Cruz had led the poll instead, we would be asking a different set of questions.
-Indeed, the selection issue appears especially pernicious due to the so-called ``winner's curse:'' given that Trump leads the poll, it more likely than not overestimates his support.
+Indeed, the selection issue appears especially pernicious due to the so-called ``winner's curse'': given that Trump leads the poll, it more likely than not overestimates his support.
 
-Nevertheless, if we blithely ignore the selection issue, we might carry out the following analyses to answer the questions we posed before at significance level $\alpha=0.05$.
-We assume for simplicity that the poll represents a simple random sample of Iowa Republicans, i.e., that the data are a multinomial sample of size $890$ and underlying probabilities $(\pi_{\text{Trump}}, \pi_{\text{Cruz}}, \ldots)$.\footnote{The reality is a bit more complicated: before releasing the data, Quinnipiac has processed it to make the reported result more representative of likely caucus-goers.}
+Nevertheless, if we blithely ignore the selection issue, we might carry out the following analyses to answer the questions we posed before at significance level $\alpha = 0.05$.
+We assume for simplicity that the poll represents a simple random sample of Iowa Republicans, i.e., that the data are a multinomial sample of size $890$ and underlying probabilities $\left(\pi_{\text{Trump}}, \pi_{\text{Cruz}}, \ldots\right)$.\footnote{The reality is a bit more complicated: before releasing the data, Quinnipiac has processed it to make the reported result more representative of likely caucus-goers.}
+
 \begin{enumerate}
-\item {\em Is Trump really winning?} If Trump and Cruz were in fact tied, then Trump's share of their combined 490 votes would be distributed as $\text{Binom}(490, 0.5)$.
-Because the (two-tailed) $p$-value for this pairwise test is $p=0.006$, we reject the null and conclude that Trump is really winning.
-\item {\em By how much?} Using an exact $95\%$ interval for the same binomial model, we conclude Trump has at least $7.5\%$ more support than Cruz (i.e., $\pi_{\text{Trump}} \geq 1.075 \,\pi_{\text{Cruz}}$) and also leads the other candidates by at least as much.
-\item {\em Is Cruz in second, Rubio in third, etc.?} We can next compare Cruz to Rubio just as we compared Trump to Cruz (again rejecting because 214 is significantly more than half of 365), then Rubio to Carson, and so on, continuing until we fail to reject.
+\item {\em Is Trump really winning?} If Trump and Cruz were in fact tied, then Trump's share of their combined 490 votes would be distributed as $\text{Binom}\left(490, 0.5\right)$.
+Because the (two-tailed) $p$-value for this pairwise test is $p = 0.006$, we reject the null and conclude that Trump is really winning.
+
+\item {\em By how much?} Using an exact $95\%$ interval for the same binomial model, we conclude Trump has at least $7.5\%$ more support than Cruz (i.e., $\pi_{\text{Trump}} \ge 1.075 \,\pi_{\text{Cruz}}$) and also leads the other candidates by at least as much.
+
+\item {\em Is Cruz in second, Rubio in third, etc.?} We can next compare Cruz to Rubio just as we compared Trump to Cruz (again rejecting because $214$ is significantly more than half of 365), then Rubio to Carson, and so on, continuing until we fail to reject.
 The first four comparisons are all significant at level $0.05$, but Paul and Bush are tied so we stop.
@@
 \subsection{Generic Problem Setting and Main Result}
+\label{sec:probset}
 
 Generically, we will consider data drawn from an exponential family model with density
-\begin{equation}\label{eq:expfam}
-X \sim e^{\theta'x - \psi(\theta)}g(x),
+\begin{equation}
+X \sim \exp\left(\theta'x - \psi\left(\theta\right)\right) g\left(x\right),
+\tag{*}
+\label{eqn:expfam}
 \end{equation}
-with respect to either the Lebesgue or counting measure on $\RR^n$.
-We assume further that $g(x)$ is symmetric.
-In addition to the multinomial family, \eqref{eq:expfam} also encompasses settings such as comparing independent binomial treatment outcomes in a clinical trial, competing sports teams under a Bradley-Terry model, entries of a Dirichlet distribution, and many more; see Section~\ref{sec:examples} for these and other examples.
-\WFcomment{Also students taking a test in a Rasch model, after conditioning on how many get each question right.
-Or comparing the variances of different normal populations.}
+with respect to either the Lebesgue on $\RR^n$ or counting measure on $\ZZ^n$.
+We assume further that $g\left(x\right)$ is symmetric.
+In addition to the multinomial family, model~\eqref{eqn:expfam} also encompasses settings such as comparing independent binomial treatment outcomes in a clinical trial, competing sports teams under a Bradley--Terry model, entries of a Dirichlet distribution, and many more; see \Cref{sec:examples} for these and other examples.
 
@@
 represented by a given random variable $X_j$.
-As we will see, $\theta_j \geq \theta_k$ if and only if $X_j$ is stochastically larger than $X_k$; thus, there is a well-defined stochastic ordering of the populations that matches the ordering of the entries of $\theta$.
-We will refer to the population with maximal $\theta_j$ as the {\em best}, and the one with maximal $X_j$ as the {\em winner}.
+As we will see, $\theta_j \ge \theta_k$ if and only if $X_j$ is stochastically larger than $X_k$; thus, there is a well-defined stochastic ordering of the populations that matches the ordering of the entries of $\theta$.
+We will refer to the population with maximal $\theta_j$ as the {\em best}, the one with maximal $X_j$ as the {\em winner}, and the one with maximal $X_j$ other than the winner as the {\em runner-up}.
 Following the convention in the ranking and selection literature, we assume that if there are multiple largest $\theta_j$, then one is arbitrarily marked as the best.
@@
 Write the order statistics of $X$ as
-\[
-X_{[1]} \geq X_{[2]} \geq \cdots \geq X_{[n]},
-\]
-and define $\theta_{[j]}$ as the entry of $\theta$ corresponding to the $j$th order statistic of $X$ (so $\theta_{[1]}$ might {\em not} equal $\max_j \theta_j$, for example).
+$$X_{[1]} \ge X_{[2]} \ge \cdots \ge X_{[n]},$$
+where $[j]$ will denote the random index for the $j$-th order statistic.
+Define $\theta_{[j]}$ as the entry of $\theta$ corresponding to the $j$-th order statistic of $X$ (so $\theta_{[1]}$ might {\em not} equal $\max_j \theta_j$, for example).
 We assume any ties between entries of $X$ are broken randomly.
@@
 
-Generalizing the procedures described in Section~\ref{sec:iowa} we obtain the following:
+Generalizing the procedures described in \Cref{sec:iowa} we obtain the following:
 \begin{enumerate}
@@
 If the test rejects at level $\alpha$, conclude that the winner is really the best.
-\item {\em By how much?} Construct the unadjusted pairwise confidence interval comparing the winner to the runner-up, and report the lower confidence bound obtained for $\theta_{[1]}-\theta_{[2]}$.
+\item {\em By how much?} Construct the unadjusted pairwise confidence interval comparing the winner to the runner-up, and report the lower confidence bound obtained for $\theta_{[1]}-\theta_{[2]}$ if it were nonnegative, report $-\infty$ otherwise.
 \item {\em Is the runner-up really the second best, etc.?} Continue by comparing the runner-up to the second-runner-up, again using the unadjusted pairwise test, and so on down the list comparing adjacent values.
@@
 \end{enumerate}
+Here Procedure $2$ is modified due to technicalities. A less extreme modification is provided in this paper later.
 
 We now state our main theorem: under a mild technical assumption, Procedures 1--3 described above are statistically valid, even accounting for the selection.
-\begin{theorem}\label{thm:main}
-Assume the model~\eqref{eq:expfam} holds and $g(x)$ is a Schur-concave function. Then:
+\begin{theorem}
+Assume the model~\eqref{eqn:expfam} holds and $g\left(x\right)$ is a Schur-concave function. Then:
 \begin{enumerate}
 \item Procedure 1 has level $\alpha$ conditional on the best population not winning (otherwise an error is impossible).
-\item Procedure 2 gives an exact $1-\alpha$ lower confidence bound for $\theta_{[1]} - \max_{j \neq [1]} \theta_{j}$.
-\item Procedure 3 is a conservative stepdown procedure with familywise error rate (FWER) no larger than $\alpha$.
+\item Procedure 2 gives a conservative $1-\alpha$ lower confidence bound for $\theta_{[1]} - \max_{j \ne [1]} \theta_{j}$.
+\item Procedure 3 is a conservative step-down procedure with familywise error rate (FWER) no larger than $\alpha$.
 \end{enumerate}
+\label{thm:main}
 \end{theorem}
 
-We define Schur-concave functions and discuss their properties in Section~\ref{sec:maj}.
-Because any log-concave and symmetric function is Schur-concave, Theorem~\ref{thm:main} applies to all of the cases discussed above.
-The proof relies on the conditional selective-inference framework of~\citet{Fithian:2014ws} combined with classical multiple-testing methods, as well as ideas involving majorization and Schur-concavity.
+We define Schur-concave functions and discuss their properties in \Cref{sec:maj}.
+Because any log-concave and symmetric function is Schur-concave, \Cref{thm:main} applies to all of the cases discussed above.
+The proof relies on the conditional selective-inference framework of \citet{Fithian:2014ws} combined with classical multiple-testing methods, as well as ideas involving majorization and Schur-concavity.
 
 Note that these procedures make an implicit adjustment for selection because they use two-tailed unadjusted tests.
-If we instead based our tests on an independent realization $X^*$, then (for example) Procedure 1 could use a right-tailed version of the unadjusted pairwise test.
-In the case $n=2$ Procedure 1 amounts to a simple two-tailed test of the null hypothesis $\theta_1=\theta_2$, and it is intuitively clear that a one-tailed test would be anti-conservative.
-More surprising is that, no matter how large $n$ is, Procedures 1--3 require no further adjustment beyond what is required when $n=2$.
-
-% Informally, this can possibly be explained by noting that for large $n$, $X_{[2]}$ suffers from a positive selection bias --- a ``runner-up's curse,'' so to speak --- which is nearly as severe as the bias of $X_{[1]}$.
-
-% \begin{enumerate}
-
-% \item This has a hidden upward selection bias, or ``winner's curse'', as we are only testing this hypothesis as Trump is leading in the polls.
-In other words, the hypothesis itself is random.
-Alternatively, we can note that the marginal type I error rate is not quite straightforward.
-Specifically, the null hypothesis is ``$H_0 \left(X\right): \text{Leader in polls has most support}$'', which is dependent on random poll data $X$ through $j^*\left(X\right)$, the leader in polls.
-Then for any distribution $F$ the marginal type I error rate is
-
-% \begin{equation}
-% \PP_F\left(\text{reject } H_0\right) = \sum_{\substack{j \text{ is a candidate} \\ j \text{ does not have most support}}} \PP_F\left(\text{reject } H_0 \middle| j \text{ leads in polls}\right) \PP_F \left(j \text{ leads in polls}\right).
-% \label{eqn:marginal_error}
-% \end{equation}
-
-% \item Comparing Trump to all other candidates involves multiple comparisons.
-Without considering the structure of this problem, common methods that perform multiple comparisons may largely decrease the test power.
-% \end{enumerate}
-
-% We will construct a test as outlined by Fithian, Sun and Taylor in \cite{Fithian:2014ws}. The fundamental idea is to consider the selective type I error rate
-% $$\PP_F\left(\text{reject } H_0 \middle| j \text{ leads in polls} \right), ~~~~~~~~ \text{where $j$ is a candidate,}$$
-% instead. Note that controlling this selective type I error rate at $\alpha$ provides control of the marginal type I error rate at $\alpha$ too. From \Cref{eqn:marginal_error},
-% \begin{align}
-% \PP_F\left(\text{reject } H_0\right) & = \sum_{\substack{j \text{ is a candidate} \\ j \text{ does not have most support}}} \PP_F\left(\text{reject } H_0 \middle| j \text{ leads in polls}\right) \PP_F \left(j \text{ leads in polls}\right).
-\nonumber \\
-% & \le \sum_{\substack{j \text{ is a candidate} \\ j \text{ does not have most support}}} \alpha \PP_F \left(j \text{ leads in polls}\right). \nonumber \\
-% & = \alpha \PP\left(\text{Leader in polls does not have most support}\right) \nonumber \\
-% & \le \frac{n-1}{n} \alpha. \label{eqn:selective_vs_marginal}
-% \end{align}
-
-% Surprisingly, this also tackles the second issue above.
-The test reduces the multiple comparison problem into one comparison between Trump and Cruz.
-In fact, if 100 John Does entered the race with practically no support from the Iowa Republicans, the change in number of candidates will not change the test.
-
-% More generally, when we observe a random vector $(X_1, \ldots, X_n)$ from an exponential family, and whichever random variable is largest, we want to test whether it is in fact stochastically larger than the other random variables.
+If we instead based our tests on an independent realization $X^*$, then, for example, Procedure 1 could use a right-tailed version of the unadjusted pairwise test.
+In the case $n = 2$ Procedure 1 amounts to a simple two-tailed test of the null hypothesis $\theta_1 = \theta_2$, and it is intuitively clear that a one-tailed test would be anti-conservative.
+More surprising is that, no matter how large $n$ is, Procedures 1--3 require no further adjustment beyond what is required when $n = 2$.
 
@@
 
-Gutmann and Maymin \cite{Gutmann:1987fk} have worked on a similar question where the observations are from a location family, and the location parameters are compared.
-In contrast, a related paper by Karnnan and Panchapakesan \cite{Karnnan:2009iv} discussed a scale family instead, comparing the scale parameters.
-Bofinger \cite{Bofinger:1991hv} gave a location-scale family generated by the exponential distribution as well.
+\citet{Gutmann:1987fk} have worked on a similar question where the observations are from a location family, and the location parameters are compared.
+In contrast, a related paper by \citet{Karnnan:2009iv} discussed a scale family instead, comparing the scale parameters.
+\citet{Bofinger:1991hv} gave a location-scale family generated by the exponential distribution as well.
 However, as location-scale families have limited overlap with exponential families, the counterpart question for exponential families have remained unaddressed.
 Location-scale families assumed independence between observations, while this is not required in exponential families.
-A follow-up paper by Maymin and Gutmann \cite{Maymin:1992fz} gave a slightly more general result, applicable to more than location-scale families, yet still under the constraints of independence.
+A follow-up paper by \citet{Maymin:1992fz} gave a slightly more general result, applicable to more than location-scale families, yet still under the constraints of independence.
 
-In the vicinity of the polling problem above, Nettleton \cite{Nettleton:2009ht} provided an asymptotic test for multinomial distribution, imposing the selection by considering intersection-union tests.
-Ng and Panchapakesan \cite{Ng:2007cn} also analyzed the multinomial case for an exact test, but with an additional restriction that maximum observation is a known constant.
+In the vicinity of the polling problem above, \citet{Nettleton:2009ht} provided an asymptotic test for multinomial distribution, imposing the selection by considering intersection-union tests.
+\citet{Ng:2007cn} also analyzed the multinomial case for an exact test, but with an additional restriction that maximum observation is a known constant.
 
-The subset selection problem solved in \cite{Gupta:1967wg} by Gupta and Nagel can indeed be used to solve the multinomial case.
+The subset selection problem solved in \citet{Gupta:1967wg} can indeed be used to solve the multinomial case.
 They selected a subset that contains the largest, or ``tagged'', parameter with probability $1-\alpha$.
 Confirming the largest parameter is thus equivalent to asserting the selected subset has size $1$.
-\Cref{sec:multinomial_example} includes a comparison of our proposed test and their test.
-
-% \subsection{Main result}
-
-% In this paper, we focus on Schur-concave exponential family, a broad class of distribution that is defined in \Cref{sec:exponential_families} and includes various examples listed in \Cref{sec:applications}.
-We constructed a selective level-$\alpha$ test for verifying that the largest observation is stochastically largest as well.
-The test provides selective type I error control, as well as enables us to construct confidence bound on the differences between the natural parameters and verify the order of the rest of the natural parameters.
-\WFcomment{Still feels a bit abstract when you discuss these goals here.} \KHcomment{What if we don't mention the side results at all?}
+\Cref{sec:subsetsel} includes a comparison of our proposed test and their test.
 
 \subsection{Outline}
+\Cref{sec:maj} gives a formal definition of the condition we are imposing, as well as common examples satisfying the condition.
+\Cref{sec:winnerbest} proves that an unadjusted pairwise test comparing the winner to the runner-up is valid, as well as a demonstration of the power of this test.
+This section also explains the validity of level $\alpha$ conditional on the best population not winning.
+\Cref{sec:confbound,sec:stepdown} prove Procedure 2 and 3 are valid.
+We will finally examine a published study with our methods in \Cref{sec:conclusion}.
 
-\Cref{sec:multinomial_example} gives an exploratory example based on the multinomial distribution, along with a comparison to an earlier method by Gupta and Nagel.
-\Cref{sec:exponential_families} gives an in-depth discussion and proof of the main result.
-\Cref{sec:selective_confidence_bound,sec:step_down_procedure} extend the main result to construct confidence bounds for the gap between natural parameters and a step-down procedure that verifies the order of the rest of the natural parameters with FWER and FDR control, respectively.
-\Cref{sec:applications} provides a few applications, including both distributions with known tests and those without.
+\section{Majorization and Schur-concavity}
+\label{sec:maj}
 
-\section{Multinomial example}
-\label{sec:multinomial_example}
-
-Suppose we observe
-$$\left(X_1, \ldots, X_n\right) \sim \text{Multinomial}\left(m, \pi\right)$$
-and we want to test
-$$H_{0j}: \pi_j \le \max_{k \ne j} \pi_k = \bigcup_{k \ne j} H_{0jk}: \pi_j \le \pi_k$$
-when $X_j$ is larger than all other $X_k$. In case of ties, we break them independently and randomly. The distribution, written in an exponential family format, and up to constant factors, is
-$$\exp\left(X_1 \log \pi_1 + \cdots + X_n \log \pi_n\right) \frac{1_{X_1 + \cdots + X_n = m}}{X_1! \cdots X_n!}.$$
-
-Without loss of generality, we will assume $X_1$ is considered largest.
-Following the construction in \cite{Fithian:2014ws}, if we want to construct $p$-values $p_{1j}$ for $H_{01j}$, we need to first re-parametrize such that the selection event $A_1$ can be expressed in terms of the sufficient statistic.
-The distribution is now
-$$\exp\left(\frac{X_1 - X_j}{2} \left(\log \pi_1 - \log \pi_j\right) + \cdots + \frac{X_1 + X_j}{2} \left(\log \pi_1 + \log \pi_j\right) + \cdots + X_n \log \pi_n\right) \frac{1_{X_1 + \cdots + X_n = m}}{X_1!
-\cdots X_n!}.$$
-
-Next we condition on the sufficient statistics for the nuisance parameter, in other words, we consider the conditional law
-$$\mathcal{L}_{\pi_1 = \pi_j}\left(\frac{X_1 - X_j}{2} \middle| X_2, \ldots, \frac{X_1 + X_j}{2}, \ldots, X_n, A_1\right),$$
-or equivalently, the conditional law
-$$\mathcal{L}_{\pi_1 = \pi_j}\left(X_1 \middle| X_2, \ldots, \frac{X_1 + X_j}{2}, \ldots, X_n, A_1\right),$$
-which is the distribution $\text{Binomial}\left(X_1 + X_j, \frac{1}{2}\right)$ truncated by the event $A_1$. The one-sided $p$-value $p_{1j}$ is thus given as
-\begin{align*}
-p_{ij}\left(x_1, \ldots, x_n\right) & = \PP\left(X_1 \ge x_1 \middle| X_2 = x_2, \ldots, \frac{X_1 + X_j}{2} = \frac{x_1 + x_j}{2}, \ldots, X_n = x_n, A_1\right) \\
-& = \frac{\sum_{t = x_1}^{x_1 + x_j} \binom{x_1 + x_j}{t} \left(\frac{1}{2}\right)^{x_1 + x_j}}{\sum_{t = \left(x_1 + x_j\right)/2}^{x_1 + x_j} \binom{x_1 + x_j}{t} \left(\frac{1}{2}\right)^{x_1 + x_j}} \\
-& = \frac{\sum_{t = x_1}^{x_1 + x_j} \binom{x_1 + x_j}{t}}{\sum_{t = \left(x_1 + x_j\right)/2}^{x_1 + x_j} \binom{x_1 + x_j}{t}},
-\end{align*}
-and to account for the tie-breaking we adopted earlier, we
-\begin{itemize}
-\item multiply the first term in the numerator and the denominator by $1/k$ where $k$ is the number of observations tied for largest; otherwise,
-\item multiply the first term in the denominator by $1/2$ if $X_1$ and $X_j$ has the same parity, as the sum starts $X_1 = X_j = \frac{x_1 + x_j}{2}$.
-\end{itemize}
-Noticing that if $X_1, \ldots, X_j$ all tied the $p$-value is $1$, and the denominator is really $1/2$ otherwise \WFcomment{I don't think that's true for $j \neq 2$: say $X=(100, 99, 10)$.
-Then the denominator is }, we can write
-$$p_{1j} = 1 \wedge 2 \sum_{t=X_1}^{X_1 + X_j} \binom{X_i + X_j}{t}.$$
-
-It is possible to check that $p_{12} \ge p_{1j}$ for any $j > 2$. The type I error rate is
-$$\PP_{H_{01}}\left(p_{12} < \alpha \middle| A_1\right) \stackrel{\text{(i)}}{=} \max_{j>1} \PP_{H_{01j}}\left(p_{12} < \alpha \middle| A_1\right) \stackrel{\text{(ii)}}{\le} \max_{j>1} \PP_{H_{01j}}\left(p_{1j} < \alpha \middle| A_1\right) \stackrel{\text{(iii)}}{\le} \alpha,$$
-where (i) follows from $H_{01} = \bigcup_{j>1} H_{01j}$; (ii) is true as $p_{12} \ge p_{1j}$ as long as $X_1 \ge X_2 \ge X_j$; (iii) follows from the construction of $p_{1j}$.
-\KHcomment{I think the probability in the middle (between (i) and (ii)) is well-defined, as $p_{12}$ is just a random variable dependent on $X$.} Thus it is sufficient to construct a one-sided test between $X_1$ and $X_2$ and consider only $p_{12}$.
-
-It may appear quite surprising that ``verifying a winner'' as we propose in this section requires no adjustment for multiplicity, in the sense that we only need to compare the winner to the runner-up, just as we would have done if $n = 2$.
-When $n=2$, the observation $X_1$ follows Binomial$\left(X_1 + X_2, \frac{1}{2}\right)$, coinciding with the test we proposed.
-After all, we know that the winner suffer’s from a winner's curse: given $X_5$ is the winner, $X_5 / m$ would overestimate $\pi_5$, and the larger $n$ is, the more severe this bias is likely to be.
-However, if $X_9$ is the runner-up, then $X_9 / m$ is likely biased upward nearly as much as $X_5$.
-Informally, we might say that $X_9$ suffer’s from a ``runner-up's curse'' that is nearly as bad as the winner's curse; as a result, $X_5 - X_9$ is actually not all that biased upward.
-By multiplying the $p$-value by $2$, or equivalently performing a two-tailed test, we take care of what little bias there is.
-Indeed, performing a two-tailed test can be viewed as a sort of ``correction for multiplicity'', albeit one that we would have to make even if $n = 2$.
-
-\subsection{Connection with the subset selection problem}
-\label{sec:compare_subset}
-
-Gupta and Nagel \cite{Gupta:1967wg} devised a rule to select a subset that includes the maximum $\pi_j$. In other words, if the selected subset is $J\left(X\right)$, they guaranteed
-$$\PP\left(\argmax_j \pi_j \in J\left(X\right)\right) \ge 1 - \alpha.$$
-This was achieved by finding an integer $D$, as a function on $m$, $n$ and $\alpha$, and select by
-$$J\left(X\right) = \left\{j: X_j \ge \max_k X_k - D\right\}.$$
-Gupta and Nagel also provided the method to choose $D$.
-The subset selection can be modified.
-Inherently, the event $\left\{J\left(X\right) = \left\{1\right\}\right\}$ is the same as inferring $\pi_1$ is the largest.
-We thus implemented their test for this purpose.
-
-\Cref{fig:power} gives the power curves for $\text{Multinomial}\left(m, \pi\right)$ and
-$$\pi \propto \left(e^\delta, 1, \ldots, 1\right),$$
-for various combinations of $m$ and $n$.
-For Gupta and Nagel, we use $\alpha = 0.05$; but in light of the extra factor of $\frac{n-1}{n}$ in \Cref{eqn:selective_vs_marginal}, we will apply the selective procedure with $\frac{n}{n-1} \alpha$ such that the marginal type I error rate of both procedures are controlled at $\alpha$.
-\WFcomment{Can we justify this?
-Our procedure has error $\alpha$ in the case where all $\pi_j$ are equal.} \KHcomment{The selective error rate is $\alpha$, but Gupta and Nagel really only had marginal error rate.
-If all $\pi_j$ are equal, the marginal error rate is $\frac{n-1}{n} \alpha$.}  \WFcomment{Yes OK I think you're right.
-Because for G \& N the ``marginal error rate'' is defined by arbitrarily marking one of the tied populations as the best and then asking whether that marked one gets into the confidence set.} Gupta and Nagel coincides with our test at $n = 2$; however as $n$ grows, the selective test shoes significantly more power than Gupta and Nagel's test.
-
-\begin{figure}[htbp]
-\begin{center}
-\includegraphics[width = \textwidth]{plotMultinomialPower}
-\end{center}
-\caption{Power curves as a function of $\delta$.
-The plots in the first row all have $m = 50$ and the second row $m = 250$.
-The solid line and the dashed line are the power for the selective test and Gupta and Nagel's test, respectively.}
-\label{fig:power}
-\end{figure}
-
-\section{Exponential families}
-\label{sec:exponential_families}
-
-We would like to extend the result from multinomials to exponential families. We henceforth focus on exponential distribution taking the form
-\begin{equation}
-X \sim \exp\left(\theta_1 X_1 + \cdots + \theta_n X_n\right) g\left(X\right) h\left(\theta\right),
-\label{eqn:exp_family}
-\end{equation}
-defined on the Lebesgue or counting measure.
-It is reasonable to assume that the family is ``symmetric'', i.e.\ if $\theta_j = \theta_k$, then the probability distribution remains the same when $X_j$ and $X_k$ are swapped.
-This corresponds to requiring $g\left(X\right)$ to be symmetric.
-We would also like to introduce a fairly mild additional condition that $g$ is {\em Schur-concave}.
-But first we recall the notion of {\em majorization}, defined on both $\mathbb{R}^n$ and $\mathbb{Z}^n$.
-\KHcomment{We are making those assumptions.
-For Lebesgue, there should be no atoms.
-For counting measure, they should all line up perfectly.
-I don't think this result generalizes very well for other measures.}
+We start by reviewing the notion of {\em majorization}, defined on both $\RR^n$ and $\ZZ^n$.
 
 \begin{definition}
-For two vectors $a$ and $b$ in $\RR^n$, suppose permuting the two vectors in descending order gives
+For two vectors $a$ and $b$ in $\RR^n$ (or $\ZZ^n$), suppose permuting the two vectors in descending order gives
 $a_{\left(1\right)} \ge \cdots \ge a_{\left(n\right)}$ and $b_{\left(1\right)} \ge \cdots \ge b_{\left(n\right)}$. We say that $a \succeq b$ ($a$ majorizes $b$) if for $1 \le i < n$,
@@
 \end{align*}
-This forms a partial order in $\RR^n$.
+This forms a partial order in $\RR^n$ (or $\ZZ^n$).
 \end{definition}
@@
 Intuitively, majorization is a partial order that monitors the evenness of a vector: the more even a vector is, the ``smaller'' it is.
-There are two properties of majorization that we will use in this section.
+There are two properties of majorization that we will use in the proofs.
 
 \begin{lemma}
-\label{lma:two_properties}
-\begin{itemize}
+\begin{enumerate}
 \item Suppose $\left(x_1, x_2, x_3, \ldots\right)$ and $\left(x_1, x_2', x_3' \ldots\right)$ are two vectors in $\RR^n$. Then
@@
 If the $t \le 0$, the majorization is reversed.
-\end{itemize}
+\end{enumerate}
+\label{lma:twoprop}
 \end{lemma}
@@
 \begin{proof}
-\begin{itemize}
-
-\item The property follows from an equivalent formulation of majorization listed in Marshall, Olkin and Arnold \cite{Marshall:2010hb}, where $x \succeq y$ if and only if
+\begin{enumerate}
+\item The property follows from an equivalent formulation of majorization listed in \citet{Marshall:2010hb}, where $x \succeq y$ if and only if
 $$\sum_{j=1}^n x_n = \sum_{j=1}^n y_n ~~~~ \text{ and } ~~~~ \sum_{j=1}^n \left(x_j - a\right)_+ \ge \sum_{j=1}^n \left(y_j - a\right)_+ \text{ for all } a \in \RR.$$
 
-\item Proved in Marshall, Olkin and Arnold.
-
-\end{itemize}
+\item Proved in \citet{Marshall:2010hb}. \qedhere
+\end{enumerate}
 \end{proof}
@@
 Conversely a symmetric and log-concave function is Schur-concave \cite{Marshall:2010hb}, thus many common exponential family distributions lie in this class.
-Schur-concave function indeed appears a lot, \Cref{sec:applications} includes both continuous and discrete examples.
+Schur-concave functions indeed appear a lot, \Cref{sec:examples} includes both continuous and discrete examples.
 
-Now suppose the carrier distribution $g$ in \Cref{eqn:exp_family} is indeed Schur-concave. We hereon call the class of such distribution satisfying this {\em Schur-concave exponential family}.
+\Cref{thm:main} requires that $g\left(x\right)$ in model~\eqref{eqn:expfam} to be Schur-concave.
+It was stated in the ensuing discussion that this condition is mild, and that the examples are abundant.
+To name a few:
 
-Without loss of generality, otherwise by relabeling, we consider only the event $X_1 \ge X_2 \ge \max_{k > 2} X_k$.
-We will be testing the null hypothesis $H_{01}: \theta_1 \le \max_{j > 1} \theta_j$, which is the union of the null hypotheses $H_{01j}: \theta_1 \le \theta_j$ for $j > 1$.
-Rejecting this hypothesis corresponds to inferring that $\theta_1 > \max_{j>1} \theta_j$.
-This is equivalent to $X_1$ being stochastically larger than $X_j$ for any $j > 1$.
+\subsection{Examples}
+\label{sec:examples}
+
+\begin{enumerate}
+\item Independent binomial treatment outcome in a clinical trial.
+If each of the $n$ different treatments are applied $m$ patients independently, the number of positive outcomes $X_j$ for treatment $j$ can be modeled by $\text{Binomial}\left(m, p_j\right)$.
+The best treatment would be the treatment with the highest success probability $p_j$.
+The joint distribution of $X$ is given by
+$$p\left(x\right) \propto \exp\left(x' \left(\log p\right)\right) \frac{1}{x_1! \left(m-x_1\right)! \cdots x_n! \left(m-p_x\right)!}$$
+The carrier measure above is Schur-concave.
+
+\item Competing sports under Bradley--Terry model.
+Suppose $n$ players held a round robin tournaments with the Bradley--Terry model, where player $j$ has a score $\theta_j$, and the probability of player $j$ winning against player $k$ is
+$$\frac{e^{\theta_j - \theta_k}}{1 + e^{\theta_j - \theta_k}} = \frac{e^{\left(\theta_j - \theta_k\right) / 2}}{e^{\left(\theta_j - \theta_k\right) / 2} + e^{\left(\theta_k - \theta_j\right) / 2}}.$$
+
+Let $Y_{jk}$ be an indicator for the match between player $j$ and $k$, where we take $Y_{jk} = 1$ if $j$ beats $k$ and $Y_{jk} = 0$ if $k$ beats $j$.
+For symmetry, we will also adopt the convention that $Y_{jk} + Y_{kj} = 1$.
+Thus the joint distribution of $\left(Y_{jk}\right)_{j, k}$ is
+$$p\left(\left(y_{jk}\right)_{j, k}\right) \propto \exp\left(\sum_j 2\theta_j \sum_{k \ne j} y_{jk}\right)  = \exp\left(2\theta' x\right),$$
+where $x_j = \sum_{k \ne j} y_{jk}$. In other words, $x_j$ is the number of wins by player $j$.
+
+If the individual results are masked and we only know about the net wins, then
+$$p\left(x\right) \propto \exp\left(2\theta' x\right) g\left(x\right),$$
+where $g\left(x\right)$ is a function that count number of possible tournament results giving the net win vector $x$. A bijection proof shows that $x$ is indeed Schur-concave.
+
+\item Comparing the variances of different normal populations.
+Suppose there are $n$ normal population with laws $N\left(\mu_j, \sigma_j^2\right)$ and $m$ independent observations from each of them.
+The sample variance for population $j$ can be denoted as $r_j$.
+By Cochran's theorem, $\left(m-1\right) r_j \sim \sigma_j^2 \chi_{m-1}^2$, and thus the joint distribution of $r$ is
+\begin{align*}
+r & \sim \prod_{j=1}^n \left(\frac{\left(m-1\right) r_j}{\sigma_j^2}\right)^{\left(m-3\right) / 2} e^{-\left(m-1\right) r_j / 2 \sigma_j^2} 1_{\left\{r_j > 0 \right\}} \\
+& \propto \exp\left(-\frac{m-1}{2 \sigma_1^2} r_1 - \cdots - \frac{m-1}{2 \sigma_n^2} r_n\right) \prod_{j=1}^n r_j^{\left(m-3\right) / 2} 1_{\left\{r > 0\right\}}.
+\end{align*}
+The carrier measure is $\prod_{j=1}^n r_j^{\left(m-3\right) / 2} 1_{\left\{r > 0\right\}}$, which is Schur-concave.
+\end{enumerate}
+
+\section{Is the Winner Really the Best?}
+\label{sec:winnerbest}
+
+The following lemma should clarify the key idea in the proof of the theorem.
+
+\begin{lemma}
+If $p_j$ are valid $p$-values for testing null hypothesis $H_{0j}$, then $p_* = \max_j p_j$ is a valid $p$-value for the union null hypothesis $H_0 = \bigcup_j H_{0j}$.
+If all the $p$-values are exact, then $p_*$ is also an exact $p$-value.
+\label{lma:union}
+\end{lemma}
+
+\begin{proof}
+Since $p_j$ are all valid $p$-values,
+$$\PP_{H_{0j}}\left(p_j < \alpha\right) \le \alpha.$$
+S for the union null hypothesis
+$$\PP_{H_0}\left(p_* < \alpha\right) = \max_j \PP_{H_{0j}}\left(p_* < \alpha\right) \le \max_j \PP_{H_{0j}}\left(p_j < \alpha\right) \le \alpha.$$
+And thus $p_*$ is a valid $p$-value for the union null hypothesis. Now if $p_j$ are all exact, then equality holds above and $p_*$ is exact as well.
+\end{proof}
+
+We are now ready to prove our result for Procedure 1.
 
 \begin{theorem}
-\label{thm:stoch}
-$X_1 \ge X_2$ in stochastic order if and only if $\theta_1 > \theta_2$.
+Assume the model~\eqref{eqn:expfam} holds and $g\left(x\right)$ is a Schur-concave function.
+Procedure 1 (the unadjusted pairwise test) has level $\alpha$ conditional on the best population not winning.
+\label{thm:seltest}
 \end{theorem}
 
-\begin{proof}
+\begin{proof}[Proof of \Cref{thm:seltest}]
+Without loss of generality, otherwise by relabeling, we consider only the case where the winner is $1$ and the runner-up is $2$, etc., i.e.\ $X_1 \ge \cdots \ge X_n$.
+In this case, we will test the null hypothesis $H_{01}: \theta_1 \le \max_{j > 1} \theta_j$, which is the union of the null hypotheses $H_{01j}: \theta_1 \le \theta_j$ for $j > 1$.
+For each of these we can construct an exact $p$-value $p_{1j}$.
+Hence by \Cref{lma:union}, a test based on $p_{1*} = \max_j p_{1j}$ would be exact for $H_{01}$.
+Procedure 1 will perform an unadjusted pairwise test comparing $X_1$ to $X_2$.
+Hence it is sufficient to show that $p_{12} = p_{1*}$ and that the test based on $p_{12}$ coincides with the unadjusted pairwise test.
 
-We prove the ``if'' part first. For any fixed $a$, and $X_1 \ge a$ and $X_2 < a$, we have $X_1 > X_2$ and
-$$\exp\left(\theta_1 X_1 + \theta_2 X_2 + \cdots + \theta_n X_n\right) g\left(X\right) h\left(\theta\right) \ge \exp\left(\theta_1 X_2 + \theta_2 X_1 + \cdots + \theta_n X_n\right) g\left(X\right) h\left(\theta\right).$$
-Integrating both sides over the region $\left\{X: X_1 \ge a, X_2 < a\right\}$ gives
-$$\PP\left(X_1 \ge a, X_2 < a\right) \ge \PP\left(X_1 < a, X_2 \ge a\right).$$
-Now adding $\PP\left(X_1 \ge a, X_2 \ge a\right)$ to both probabilities gives
-$$\PP\left(X_1 \ge a\right) \ge \PP\left(X_2 \ge a\right),$$
-meaning that $X_1$ is greater than $X_2$ in stochastic order. The converse follows from swapping the role of $\theta_1$ and $\theta_2$.
-
-\end{proof}
-
-We are now ready to state and prove our main result.
-
-\begin{theorem}
-Suppose we observe $X = \left(X_1, \ldots, X_n\right)$ from an exponential family with natural parameter $\theta = \left(\theta_1, \ldots, \theta_n\right)$, i.e.
-$$X \sim \left(\theta_1 X_1 + \cdots + \theta_n X_n\right) g\left(X\right) h\left(\theta\right),$$
-with a Schur-concave carrier measure $g$.
-Then a naive two-sided test comparing only $X_{j^*}$ and $\max_{j \ne j^*} X_j$, where $j^* = \argmax_{j} X_j$, can verify $\theta_{j^*} \ge \max_{j \ne j^*} \theta_{j}$ with selective level $\alpha$.
-The test also verifies that $X_{j^*} \ge X_j$ stochastically for all $j \ne j^*$.
-\label{thm:main_result}
-\end{theorem}
-
-\begin{proof}
-
-Without loss of generality, assume $X_1 \ge \ldots \ge X_n$.
-Following the framework in Fithian, Sun and Taylor \cite{Fithian:2014ws}, we consider the selection event $A_1 = \left\{X_1 \ge \max_{j > 1} X_j\right\}$.
+Following the framework in \citet{Fithian:2014ws}, we consider the selection event where the winner is $1$: $$A_1 = \left\{X_1 \ge \max_{j > 1} X_j\right\}.$$
 For convenience, we let
@@
 
-With the same strategy in \Cref{sec:multinomial_example}, we re-parametrize to replace $X_1$ and $X_j$ with $D_{1j}$ and $M_{1j}$ and consider
+We start by re-parametrizing to replace $X_1$ and $X_j$ with $D_{1j}$ and $M_{1j}$ and consider
 \begin{equation}
-\mathcal{L}_{D_{1j} = \theta_1 - \theta_j = 0} \left(D_{1j} \middle| M_{1j}, X_2, \ldots, X_n, A_1\right), \text{ where } A_1 = \left\{D_{1j} \ge \max_{k \ne 1, j} X_k - M_{1j}\right\} \cap \left\{D_{1j} \ge 0\right\}.
-\label{eqn:cond_law}
+\mathcal{L}_{\theta_1 - \theta_j = 0} \left(D_{1j} \middle| M_{1j}, X_{\setminus\left\{1, j\right\}}, A_1\right), \text{ where } A_1 = \left\{D_{1j} \ge \max_{k \ne 1, j} X_k - M_{1j}\right\} \cap \left\{D_{1j} \ge 0\right\}.
+\label{eqn:condlaw}
 \end{equation}
-The conditional law in \Cref{eqn:cond_law}, in particular, is a truncated distribution
+The conditional law in \Cref{eqn:condlaw}, in particular, is a truncated distribution
 \begin{align*}
@@
 
+By construction, $p_{1j}$ satisfies
+$$\PP_{H_{01j}}\left(p_{1j} < \alpha \middle| M_{1j}, X_{\setminus\left\{1, j\right\}}, A_1\right) = \alpha.$$
+Taking expectation on both sides gives
+$$\PP_{H_{01j}}\left(p_{1j} < \alpha \middle| A_1\right) = \alpha.$$
+Therefore these $p_{1j}$ are indeed valid exact $p$-values.
+
 Without loss of generality, it is sufficient to show that $p_{12} \ge p_{13}$.
 In the computation of either $p$-values, $X_4, \ldots, X_n$ are all conditioned on.
-The first point in \Cref{lma:two_properties} says that we may assume $n = 3$ without affecting the Schur-concavity of $g$.
+The first point in \Cref{lma:twoprop} says that we may assume $n = 3$ without affecting the Schur-concavity of $g$.
 This allows us to clean up our notation and
@@
 
-Indeed from the second point \Cref{lma:two_properties} we have
+Indeed from the second point in \Cref{lma:twoprop} we have
 $$\left(X_1 + z, X_2 - z, X_3\right) \succeq \left(X_1 + z, X_2, X_3 - z\right)$$
@@
 
-For the alternative case where $X_2 \ge M_{13}$, it follows from a similar proof.
+For the alternative case where $X_2 \ge M_{13}$, the segment $C$ will reach the line $x_1 = x_2$ first before it reach $x_1 = x_3$, ending at $\left(X_2, X_2, X_1 - X_2 + X_3\right)$ instead.
+But we can still extend $A$ by $\tilde{A}$ to $\left(X_2, X_1, X_3\right)$.
+The rest of the proof follows.
 In either cases, $p_{12} \ge p_{13}$, or in generality, $p_{12} \ge p_{1j}$ for $j > 1$.
-A test based on only $X_1$ and $X_2$ is sufficient for the null hypothesis $H_{01}$, if the carrying measure $g$ is Schur-concave.
-Indeed, since the denominator of $p_{12}$ under the null hypothesis, this one-sided test comparing $X_1$ and $X_2$ is identical to a naive two-sided test comparing $X_1$ and $X_2$.
-By \Cref{thm:stoch}, rejecting this null hypothesis is equivalent to inferring that $X_1 \ge X_j$ for all $j>1$ stochastically.
+In other words, $p_{12} = p_{1*}$.
 
+Since the denominator of $p_{12}$ is half of the symmetric distribution before truncation, a one-sided test that rejects based on $p_{12}$ is identical to the naive unadjusted pairwise test comparing $X_1$ and $X_2$.
+The naive unadjusted pairwise test is indeed valid.
 \end{proof}
 
-As the construction of this test follows \cite{Fithian:2014ws}, it is also a uniformly most powerful unbiased selective level-$\alpha$ test.
-
-If the distribution is discrete, the proof above holds true.
-Instead of performing integrals, the atoms on the rays will be summed.
+The proof above holds true if the exponential family is defined on the counting measure.
 If ties are broken independently and randomly, as in \Cref{sec:multinomial_example}, the end points on the rays can be considered as ``half an atom''.
 
-\section{Selective confidence bound}
-\label{sec:selective_confidence_bound}
+As the construction of this test follows \citet{Fithian:2014ws}, it is also a UMPU selective level-$\alpha$ test.
 
-We can take the idea above further and construct confidence bound for $\theta_1 - \max_{j>1} \theta_j$.
-This can be achieved by considering a statistical test, to see if $\theta_1 - \max_{j>1} \theta_j \le \delta$, followed by the duality of confidence interval and statistical test.
+The selective type I error we opted to control for Procedure 1 offers the more conventional, marginal type I error rate.
+\begin{equation}
+\PP_{H_{01}}\left(\text{reject } H_{01}\right) = \PP_{H_{01}}\left(\text{Winner is } 1\right) \PP_{H_{01}}\left(\text{reject } H_{01} \middle| \text{Winner is } 1\right) \le \frac{n-1}{n} \alpha,
+\label{eqn:marginal}
+\end{equation}
+because, under the hypothesis $H_{01}$, the probability of $1$, which is not the best population, winning is at most $\frac{n-1}{n}$.
+Selective type I error rate control provides more than just marginal type I error rate control.
+\citet{Fithian:2015uj} has shown that it helps controlling familywise error rate, which we will utilize in \Cref{sec:stepdown}.
+
+Finally, comparing the parameters $\theta_j$ has an even more appealing interpretation:
 
 \begin{theorem}
-In the same setup as \Cref{thm:main_result}, there is a selective level-$\alpha$ lower confidence bound for $\theta_{j^*} - \max_{j \ne j^*} \theta_j$.
+\label{thm:stoch}
+$X_1 \ge X_2$ in stochastic order if and only if $\theta_1 > \theta_2$.
 \end{theorem}
@@
 \begin{proof}
+It suffices to prove the ``if'' part, as the ``only if'' part can be follows from swapping the role of $\theta_1$ and $\theta_2$.
+For any fixed $a$, and $X_1 \ge a$ and $X_2 < a$, we have $X_1 > X_2$ and
+$$\exp\left(\theta_1 X_1 + \theta_2 X_2 + \cdots + \theta_n X_n - \psi\left(\theta\right)\right) g\left(X\right) \ge \exp\left(\theta_1 X_2 + \theta_2 X_1 + \cdots + \theta_n X_n - \psi\left(\theta\right)\right) g\left(X\right).$$
+Integrating both sides over the region $\left\{X: X_1 \ge a, X_2 < a\right\}$ gives
+$$\PP\left(X_1 \ge a, X_2 < a\right) \ge \PP\left(X_1 < a, X_2 \ge a\right).$$
+Now adding $\PP\left(X_1 \ge a, X_2 \ge a\right)$ to both probabilities gives
+$$\PP\left(X_1 \ge a\right) \ge \PP\left(X_2 \ge a\right),$$
+meaning that $X_1$ is greater than $X_2$ in stochastic order.
+\end{proof}
 
-Again we start with assuming $X_1 \ge \cdots \ge X_n$.
-The null hypothesis $H_{01}^\delta$ can be thought of as $\bigcup_{j > 1} H_{01j}^\delta$, where $H_{01j}^\delta$ is $\theta_1 - \theta_j \le \delta$.
-In other words, we focus on the conditional law
+\subsection{Multinomial Case: Connection with the Subset Selection}
+\label{sec:subsetsel}
+
+Gupta and Nagel \cite{Gupta:1967wg} devised a rule to select a subset that includes the maximum $\pi_j$. In other words, if the selected subset is $J\left(X\right)$, they guaranteed
+$$\PP\left(\argmax_j \pi_j \in J\left(X\right)\right) \ge 1 - \alpha.$$
+This was achieved by finding an integer $D$, as a function on $m$, $n$ and $\alpha$, and select by
+$$J\left(X\right) = \left\{j: X_j \ge \max_k X_k - D\right\}.$$
+Gupta and Nagel also provided the method to choose $D$.
+The subset selection can be modified.
+Inherently, the event $\left\{J\left(X\right) = \left\{1\right\}\right\}$ is the same as inferring $\pi_1$ is the largest.
+We thus implemented their test for this purpose.
+
+\Cref{fig:power} gives the power curves for $\text{Multinomial}\left(m, \pi\right)$ and
+$$\pi \propto \left(e^\delta, 1, \ldots, 1\right),$$
+for various combinations of $m$ and $n$.
+For Gupta and Nagel, we use $\alpha = 0.05$; but in light of the extra factor of $\frac{n-1}{n}$ in \Cref{eqn:marginal}, we will apply the selective procedure with $\frac{n}{n-1} \alpha$ such that the marginal type I error rate of both procedures are controlled at $\alpha$.
+Gupta and Nagel coincides with our test at $n = 2$; however as $n$ grows, the selective test shoes significantly more power than Gupta and Nagel's test.
+
+\begin{figure}[htbp]
+\begin{center}
+\includegraphics[width = \textwidth]{plotMultinomialPower}
+\end{center}
+\caption{Power curves as a function of $\delta$.
+The plots in the first row all have $m = 50$ and the second row $m = 250$.
+The solid line and the dashed line are the power for the selective test and Gupta and Nagel's test, respectively.}
+\label{fig:power}
+\end{figure}
+
+\section{By How Much?}
+\label{sec:confbound}
+
+We can take the idea above further and construct confidence bound for $\theta_{[1]} - \max_{j \ne [1]} \theta_{j}$.
+This can be achieved by considering a statistical test, to see if $\theta_{[1]} - \max_{j \ne [1]} \theta_{j} \le \delta$, followed by the duality of confidence interval and statistical test.
+
+Here we provide a more powerful Procedure 2' first.
+The confidence lower bound can be taken as the smallest $\delta$ such that we can reject $H_{0[1]}^\delta: \theta_{[1]} - \max_{j \ne [1]} \theta_{[j]} > \delta$.
+Once again this can be written as a union of null hypothesis
+$$H_{0[1]}^\delta = \bigcup_{j \ne [1]} H_{0[1]j}: \theta_1 - \theta_j > \delta.$$
+By \Cref{lma:union}, we can construct selective exact one-tailed $p$-values $p_{[1]j}$ for each of these by conditioning on $A_{[1]}$, $M_{[1]j}$ and $X_{\setminus\left\{[1], j\right\}}$, giving us an exact test for $H_{0[1]}$ by rejecting whenever $\max_{j \ne [1]} p_{[1]j} < \alpha$.
+
+\begin{theorem}
+The $p$-values constructed above satisfies $p_{[1][2]} \ge p_{[1]j}$ for any $j \ne [1]$.
+\end{theorem}
+
+\begin{proof}
+Again we start with assuming $X_1 \ge \cdots \ge X_n$. The $p$-values in question are derived from the conditional law
 $$\mathcal{L}_{\theta_1 - \theta_j = \delta} \left(D_{1j} \middle| D_{1j}, X_2, \ldots, X_n, A\right),$$
@@
 
-As before in \Cref{sec:exponential_families}, without loss of generality we assume $n = 3$.
-Once again it is sufficient to show that $p_{12} \ge p_{13}$.
-We have the same two cases.
-If $X_2 < M_{13}$, then
+As before in \Cref{thm:seltest}, without loss of generality we assume $n = 3$. Once again it is sufficient to show that $p_{12} \ge p_{13}$. We have the same two cases. If $X_2 < M_{13}$, then
 \begin{align*}
 p_{12} & = \frac{\int_0^\infty \exp\left(\delta \left(z + D_{12}\right)\right) g\left(X_1 + z, X_2 - z, X_3\right) \,dz}{\int_{-D_{12}}^\infty \exp\left(\delta \left(z + D_{12}\right)\right) g\left(X_1 + z, X_2 - z, X_3\right) \,dz} \\
-& \ge \frac{\int_0^\infty \exp\left(\delta z\right) g\left(X_1 + z, X_2 - z, X_3\right) \,dz}{\int_{-D_{13}}^\infty \exp\left(\delta z\right) g\left(X_1 + z, X_2 - z, X_3\right) \,dz} \\
+& = \frac{\int_0^\infty \exp\left(\delta z\right) g\left(X_1 + z, X_2 - z, X_3\right) \,dz}{\int_{-D_{12}}^\infty \exp\left(\delta z\right) g\left(X_1 + z, X_2 - z, X_3\right) \,dz} \\
 p_{13} & = \frac{\int_0^\infty \exp\left(\delta \left(z + D_{13}\right)\right) g\left(X_1 + z, X_2, X_3 - z\right) \,dz}{\int_{-D_{13}}^\infty \exp\left(\delta \left(z + D_{13}\right)\right) g\left(X_1 + z, X_2, X_3 - z\right) \,dz} \\
@@
 
-The same argument in \Cref{fig:compare_rays} shows that $p_{12} \ge p_{13}$.
-This is again true for the case where $X_2 \ge M_{13}$ as well.
-This means that the bound can be constructed considering only $p_{12}$.
-
+The same argument in \Cref{fig:compare_rays} shows that $p_{12} \ge p_{13}$. This is again true for the case where $X_2 \ge M_{13}$ as well.
 \end{proof}
 
-\section{Step down procedure}
-\label{sec:step_down_procedure}
+In other words, Procedure 2' can be summarized as: Find the minimum $\delta$ such that $p_{12} \le \alpha$.
+And by construction, Procedure 2' gives exact $1-\alpha$ confidence bound for $\theta_{[1]} - \max_{j \ne [1]} \theta_j$.
 
-If one is interested in verifying more than just the ``winner'', this selective test can also be extended to a step-down procedure that verifies the ``first runner-up'' and ``second runner-up'' etc., while controlling the FWER and the FDR.
+\begin{corollary}
+Assume the model~\eqref{eqn:expfam} holds and $g\left(x\right)$ is a Schur-concave function.
+Procedure 2 (the lower bound of unadjusted pairwise confidence interval) gives a conservative $1-\alpha$ lower confidence bound for $\theta_{[1]} - \max_{j \ne [1]} \theta_j$.
+\end{corollary}
+
+\begin{proof}
+If the confidence bound $\delta^*$ is negative, we report $-\infty$ so it definitely is valid and conservative.
+On the other hand, if $\delta^* \ne 0$, then at $\delta^*$ the $p$-value $p_{12} = \alpha$.
+The denominator is the positive part of a positively skewed distribution, and thus bigger than half of the distribution.
+So the unadjusted pairwise test $p$-value from Procedure 2 comparing $X_{[1]}$ and $X_{[2]}$ is larger than $p_{12}$ from Procedure 2', rendering Procedure 2 conservative.
+\end{proof}
+
+Note that Procedure 2 reporting $-\infty$ in case of $\delta^*$ is rather extreme.
+In reality, we can always just adopt Procedure 2' in the case when Procedure 1 rejects.
+In fact, by Procedure 2', the multinomial example for polling in \Cref{sec:iowa} can give a stronger lower confidence bound, that $\log \pi_{\text{Trump}} - \max_{j \ne \text{Trump}} \log \pi_{j} \ge 0.103142$.
+
+\section{Is the Runner-Up Really the Second Best, etc.?}
+\label{sec:stepdown}
+
+If one is interested in verifying more than just the ``winner'', this selective test can also be extended to a step-down procedure that verifies the ``first runner-up'' and ``second runner-up'' etc., while controlling the FWER.
 
 Formally, we wish to find the biggest $j$ such that we can infer
-$$\theta_1 > \ldots > \theta_j > \max_{k>j} \theta_k.$$
-If $j_0$ is the true value of $j$, the two error rates we mentioned above refer to
-$$\text{FWER} = \PP\left(j \ne j_0\right) ~~~~ \text{ and } ~~~~ \text{FDR} = \EE\left[\frac{\left(j - j_0\right)_+}{j}\right],$$
-where $\left(j - j_0\right)_+ / j$ is taken to be $0$ if $j = 0$.
+$$\theta_{[1]} > \ldots > \theta_{[j]} > \max_{k>j} \theta_{[k]}.$$
+If $j_0$ is the true value of $j$, the FWER refers to $\PP\left(j \ne j_0\right)$.
 
 \begin{theorem}
-There is a step-down procedure that infers $j_0$ above with both the FWER and FDR controlled at $\alpha$.
+There is a step-down procedure, which we will denote as Procedure 3', that infers $j_0$ above with the FWER controlled at $\alpha$.
 \end{theorem}
@@
 
-Here we are only comparing $X_j$ to $X_{j+1}$ by \Cref{sec:exponential_families}.
-The upper truncation for $X_j$ can be represented by cropping \Cref{fig:compare_rays} along a vertical line, shown in \Cref{fig:crop_rays}, thus the proof of \Cref{thm:main_result} on sufficiency to compare $X_1$ and $X_2$ remains valid with appropriate conditioning.
+Here we are only comparing $X_j$ to $X_{j+1}$ by \Cref{sec:winnerbest}.
+The upper truncation for $X_j$ can be represented by cropping \Cref{fig:compare_rays} along a vertical line, shown in \Cref{fig:crop_rays}, thus the proof of \Cref{thm:seltest} on sufficiency to compare $X_1$ and $X_2$ remains valid with appropriate conditioning.
 Again we can construct the $p$-values as in \Cref{eqn:p1j} for $k>j$.
@@
 
-Hence similar to the proof of \Cref{thm:main_result}, Schur-concavity ensures $p_{j\left(j+1\right)} \ge p_{jk}$ for all $k>j$, meaning that it is sufficient to compare $X_j$ and $X_{j+1}$.
+Hence similar to the proof of \Cref{thm:seltest}, Schur-concavity ensures $p_{j\left(j+1\right)} \ge p_{jk}$ for all $k>j$, meaning that it is sufficient to compare $X_j$ and $X_{j+1}$.
 In fact, we can take $p_j = p_{j\left(j+1\right)}$.
@@
 Hence the nested sequence of model satisfies the subpath sufficiency principle, and the $p$-values sequence $p_j$ is independent on nulls, as defined in and shown in Theorem 4 of \cite{Fithian:2015uj}.
-Thus the step-down procedure where we keep rejecting $H_{0j}$ until the first time that $p_j > \alpha$ controls FWER and FDR.
-
+Thus the step-down procedure where we keep rejecting $H_{0j}$ until the first time that $p_j > \alpha$ controls FWER.
 \end{proof}
 
-\section{Applications}
-\label{sec:applications}
+\begin{corollary}
+Assume the model~\eqref{eqn:expfam} holds and $g\left(x\right)$ is a Schur-concave function. Procedure 3 is a conservative step-down procedure with FWER no larger than $\alpha$.
+\end{corollary}
 
-Our result above applies to a wide range of joint distributions. Note that since multiplying $-1$ preserves the majorization partial order, the following examples also work in verifying the minimum.
+\begin{proof}
+The $p$-values $p_{j\left(j+1\right)}$ obtained in Procedure 3' are always smaller than their counterpart in Procedure 3, as the upper truncation at $X_{j-1}$ is on the upper tail.
+Therefore Procedure 3 is more conservative and definitely valid.
+\end{proof}
 
-\begin{enumerate}
+\section{Conclusion}
+\label{sec:conclusion}
 
-\item Correlated Gaussian: Suppose $X \sim N\left(\mu, \Sigma\right)$, where
-\begin{align*}
-\mu & = \left(\mu_1, \ldots, \mu_n\right), \\
-\Sigma & = \begin{pmatrix}
-1 & p & \cdots & p \\
-p & 1 & \ddots & \vdots \\
-\vdots & \ddots & \ddots & p \\
-p & \cdots & p & 1
-\end{pmatrix}
-\end{align*}
-and $p$ is fixed. Then the natural parameter is ordered the same way as $\mu$. Our test can thus be used to verify the order of the mean.
-
-\item Multinomial distribution, e.g.\ the Iowa Republican poll example in \Cref{sec:introduction}.
-$$p\left(x\right) \propto \exp\left(x^T \left(\log \pi\right)\right) \frac{1_{\left\{x_1 + \cdots + x_n = m\right\}}}{x_1! \cdots x_n!}$$
-Comparing $\pi_i$ is the same as comparing $\log \pi_i$, the natural parameters.
-Note that the multinomial coefficient is naturally Schur-concave.
-The step-down procedure is applied to verify the position of the other candidates.
-Note that for a multinomial distribution, the conditioning \Cref{eqn:step_down_law} is equivalent to conditioning only on $M_{j\left(j+1\right)}$.
-We summarize the test in \Cref{tbl:poll_analysis}.
-
-\begin{table}[htbp]
-\begin{center}
-\begin{tabular}{c c c c c}
-\hline
-Rank ($j$) & $X_{j-1}$ & $X_j$ & $X_{j+1}$ & $p$-value \\
-\hline
-$1$ & $\infty$ & $276$ & $214$ & $0.0065$ \\
-$2$ & $276$ & $214$ & $151$ & $0.0015$ \\
-$3$ & $214$ & $151$ & $71$ & $1.1126 \times 10^{-7}$ \\
-$4$ & $151$ & $71$ & $36$ & $0.0014$ \\
-$5$ & $71$ & $36$ & $36$ & $1.0000$ \\
-\hline
-\end{tabular}
-\end{center}
-\caption{Applying the step-down procedure to the Iowa Republican caucus.
-Each $p$-value is constructed by considering the conditional law in \Cref{eqn:step_down_law}, a $\text{Binomial}\left(X_j + X_{j-1}, \frac{1}{2}\right)$ truncated at $X_{j-1}$.
-The result was also indicated in \Cref{tbl:poll}.}
-\label{tbl:poll_analysis}
-\end{table}
-
-We can also construct selective confidence bound for $\log \pi_1 - \max_{j>1} \log \pi_j$, i.e.\ find a $\delta^*$ such that
-$$\PP_{H_{01}^\delta} \left(\text{reject } H_{01}^\delta: \log \pi_1 - \max_{j>1} \log \pi_j \le \delta \middle| A_1\right) < 0.05,$$
-according to \Cref{sec:selective_confidence_bound}.
-
-Once again, for multinomial distribution, conditioning on $M_{12}, X_3, \ldots, X_n$ is the same as conditioning on $M_{12}$, which gives $X_1 \sim \text{Binomial}\left(X_1 + X_2, \frac{e^\delta}{e^\delta + 1}\right)$, truncated at $M_{12}$.
-There is a maximum $\delta^*$ for this truncated binomial distribution has a survival function of $0.05$ at $X_1$.
-
-This gives $\delta^* = 0.103142$.
-This translates to $\log \pi_1 - \max_{j>1} \log \pi_j \ge 0.103142$, or $\pi_1 / \max_{j>1} \pi_j \ge 1.10865$, with $0.95$-confidence.
-Or in terms of the Iowa Republican poll example, Trump has relatively around $11\%$ more support than any other candidates.
-This is smaller than the number deduced from raw vote count, $\left(276 - 214\right) / 214 \approx 29\%$, accounting for selection bias.
-
-\item Independent binomials
-$$p\left(x\right) \propto \exp\left(x^T \left(\log p\right)\right) \frac{1}{x_1! \left(m-x_1\right)! \cdots x_n! \left(m-p_x\right)!}$$
-
-\item Round robin tournaments with the Bradley--Terry model, where each player has a score $\theta_i$, and the probability of player $j$ winning against player $k$ is
-$$\frac{e^{\theta_j - \theta_k}}{1 + e^{\theta_j - \theta_k}} = \frac{e^{\left(\theta_j - \theta_k\right) / 2}}{e^{\left(\theta_j - \theta_k\right) / 2} + e^{\left(\theta_k - \theta_j\right) / 2}}.$$
-
-Suppose $Y_{jk} = 1$ if $j$ beats $k$ and $Y_{jk} = 0$ if $k$ beats $j$. We will also adopt the convention that $Y_{jk} + Y_{kj} = 1$. Thus the joint distribution of $\left(Y_{jk}\right)_{j, k}$ is
-$$p\left(\left(y_{jk}\right)_{j, k}\right) \propto \exp\left(\sum_j 2\theta_j \sum_{k \ne j} y_{jk}\right)  = \exp\left(\theta^T x\right),$$
-where $x_j = \sum_{k \ne j} y_{jk}$. In other words, $x_j$ is the number of wins by player $j$.
-
-If the individual results are masked and we only know about the net wins, then
-$$p\left(x\right) \propto \exp\left(2\theta^T x\right) g\left(x\right),$$
-where $g\left(x\right)$ is a function that count number of possible tournament results giving the net win vector $x$.
-A bijection proof shows that $x$ is indeed Schur-concave, allowing to apply the main result in comparing $2\theta$ and thus $\theta$.
-
-\end{enumerate}
-
-\bibliographystyle{plain}
+\bibliographystyle{plainnat}
 \bibliography{papers,additional}

### 2016-04-22 verifying-winner.tex
Discussion and psychology experiment added

@@
 \Cref{sec:confbound,sec:stepdown} prove Procedure 2 and 3 are valid.
-We will finally examine a published study with our methods in \Cref{sec:conclusion}.
+We will finally examine a published study with our methods in \Cref{sec:disc}.
 
@@
 
-\section{Conclusion}
-\label{sec:conclusion}
+\section{Discussion}
+\label{sec:disc}
+
+Our selective test procedure allows us to untangle multiple comparisons based on correlated observations easily, while avoiding the pitfalls of selective inference.
+To illustrate, we look at a past psychology study done by \citet{Uhls:2012gf}.
+
+\begin{table}[htbp]
+\begin{center}
+\begin{tabular}{c c}
+	\hline
+	Value & Count \\
+	\hline
+	Achievement & $3$ \\
+	Benevolence & $5$ \\
+	Fame & $8$ \\
+	Community feeling & $2$ \\
+	Financial success & $1$ \\
+	Self-acceptance & $0$ \\
+	Image & $0$ \\
+	Other & $1$ \\
+	\hline
+\end{tabular}
+\end{center}
+\caption{The number of study participants who chose each value as their top desired one. Since only one options can be chosen, these observations are inherently multinomial.}
+\label{tbl:fame}
+\end{table}
+
+A sample of $20$ students from elementary and middle schools were asked to choose a top ``value'' from 7 different options: achievement, benevolence, fame, community feeling, financial success, self-acceptance, image and other.
+The results are tabulated in \Cref{tbl:fame}.
+The study postulates that fame is significantly the top value of choice.
+It proceeds to perform a binomial test for the null hypothesis that the participants chose among the $7$ options uniformly and concluded with a $p$-value of $0.006$ that fame is indeed the top desired value.
+The analysis failed to address the ``winner's curse'', as well as the intricate dependence among the observations.
+Our paper addressed these two issues and provided a simple test --- perform a unadjusted (two-tailed) binomial test of the winner and the runner-up.
+In this case, we test if $8$ is a significant observation in $\text{Binomial}\left(8 + 5, 0.5\right)$.
+The two-tailed $p$-value is $0.580811$, suggesting that the study was inconclusive.
 

### 2016-04-22 verifying-winner.tex
Minor fixes

@@
 A Schur-concave function is symmetric by default since $a \succeq b$ and $b \succeq a$ if and only if $b$ is a permutation of the coordinates of $a$.
-Conversely a symmetric and log-concave function is Schur-concave \cite{Marshall:2010hb}, thus many common exponential family distributions lie in this class.
+Conversely a symmetric and log-concave function is Schur-concave \citep{Marshall:2010hb}, thus many common exponential family distributions lie in this class.
 Schur-concave functions indeed appear a lot, \Cref{sec:examples} includes both continuous and discrete examples.
@@
 
-\begin{proof}[Proof of \Cref{thm:seltest}]
+\begin{proof}
 Without loss of generality, otherwise by relabeling, we consider only the case where the winner is $1$ and the runner-up is $2$, etc., i.e.\ $X_1 \ge \cdots \ge X_n$.
@@
 The proof above holds true if the exponential family is defined on the counting measure.
-If ties are broken independently and randomly, as in \Cref{sec:multinomial_example}, the end points on the rays can be considered as ``half an atom''.
+If ties are broken independently and randomly, the end points on the rays can be considered as ``half an atom''.
 
@@
 
-Gupta and Nagel \cite{Gupta:1967wg} devised a rule to select a subset that includes the maximum $\pi_j$. In other words, if the selected subset is $J\left(X\right)$, they guaranteed
+\citet{Gupta:1967wg} devised a rule to select a subset that includes the maximum $\pi_j$. In other words, if the selected subset is $J\left(X\right)$, they guaranteed
 $$\PP\left(\argmax_j \pi_j \in J\left(X\right)\right) \ge 1 - \alpha.$$
@@
 $$J\left(X\right) = \left\{j: X_j \ge \max_k X_k - D\right\}.$$
-Gupta and Nagel also provided the method to choose $D$.
+They also provided the method to choose $D$.
 The subset selection can be modified.
@@
 for various combinations of $m$ and $n$.
-For Gupta and Nagel, we use $\alpha = 0.05$; but in light of the extra factor of $\frac{n-1}{n}$ in \Cref{eqn:marginal}, we will apply the selective procedure with $\frac{n}{n-1} \alpha$ such that the marginal type I error rate of both procedures are controlled at $\alpha$.
-Gupta and Nagel coincides with our test at $n = 2$; however as $n$ grows, the selective test shoes significantly more power than Gupta and Nagel's test.
+For their method, we use $\alpha = 0.05$; but in light of the extra factor of $\frac{n-1}{n}$ in \Cref{eqn:marginal}, we will apply the selective procedure with $\frac{n}{n-1} \alpha$ such that the marginal type I error rate of both procedures are controlled at $\alpha$.
+Their test coincides with our test at $n = 2$; however as $n$ grows, the selective test shows significantly more power than Gupta and Nagel's test.
 
@@
 D_{1j} & \sim \exp\left(\left(\theta_1 - \theta_j\right) D_{1j} + \theta_2 X_2 + \cdots + \left(\theta_1 + \theta_j\right) M_{1j} + \cdots + \theta_n X_n \right) \\
-& ~~~~~~~~ g\left(M_{ij} + D_{ij}, X_2, \ldots, M_{ij} - D_{ij}, \ldots X_n\right) 1_{A_1} \\
-& \sim \exp\left(\delta D_{ij}\right) g\left(M_{ij} + D_{ij}, X_2, \ldots, M_{ij} - D_{ij}, \ldots X_n\right) 1_{A_1}.
+& ~~~~~~~~ g\left(M_{1j} + D_{1j}, X_2, \ldots, M_{1j} - D_{1j}, \ldots X_n\right) 1_{A_1} \\
+& \sim \exp\left(\delta D_{1j}\right) g\left(M_{1j} + D_{1j}, X_2, \ldots, M_{1j} - D_{1j}, \ldots X_n\right) 1_{A_1}.
 \end{align*}
@@
 The denominator is the positive part of a positively skewed distribution, and thus bigger than half of the distribution.
-So the unadjusted pairwise test $p$-value from Procedure 2 comparing $X_{[1]}$ and $X_{[2]}$ is larger than $p_{12}$ from Procedure 2', rendering Procedure 2 conservative.
+So the unadjusted pairwise test $p$-value from Procedure 2 comparing $X_1$ and $X_2$ is larger than $p_{12}$ from Procedure 2', rendering Procedure 2 conservative.
 \end{proof}
@@
 
-This can be fitted into the selective sequential model selection framework proposed by Fithian, Taylor and Tibshirani \cite{Fithian:2015uj}.
+This can be fitted into the selective sequential model selection framework proposed by \citet{Fithian:2015uj}.
 Given the observations $X_1 \ge \cdots \ge X_n$, drawn from an unknown distribution $F$, we consider the sequence of null hypothesis of
@@
 In fact, we can take $p_j = p_{j\left(j+1\right)}$.
-These are valid selective $p$-value as required in Fithian, Taylor and Tibshirani, as
+These are valid selective $p$-value as required in \citet{Fithian:2015uj}, as
 $$\PP_F \left(p_j \le \alpha \middle| M_{j-1}\left(X\right)\right) \le \alpha \text{ a.s.}, ~~~~~~~~ F \in M_{j-1}\left(X\right)$$
@@
 
-The conditioning above indeed holds some significance. The sufficient filtration \cite{Fithian:2015uj} $\mathscr{F}_k$ is given as the $\sigma$-field
+The conditioning above indeed holds some significance. The sufficient filtration \citep{Fithian:2015uj} $\mathscr{F}_k$ is given as the $\sigma$-field
 \begin{align*}
@@
 which is the conditioning we used just now.
-Hence the nested sequence of model satisfies the subpath sufficiency principle, and the $p$-values sequence $p_j$ is independent on nulls, as defined in and shown in Theorem 4 of \cite{Fithian:2015uj}.
+Hence the nested sequence of model satisfies the subpath sufficiency principle, and the $p$-values sequence $p_j$ is independent on nulls, as defined in and shown in Theorem 4 of \citet{Fithian:2015uj}.
 Thus the step-down procedure where we keep rejecting $H_{0j}$ until the first time that $p_j > \alpha$ controls FWER.
@@
 The $p$-values $p_{j\left(j+1\right)}$ obtained in Procedure 3' are always smaller than their counterpart in Procedure 3, as the upper truncation at $X_{j-1}$ is on the upper tail.
-Therefore Procedure 3 is more conservative and definitely valid.
+Therefore Procedure 3 is conservative and definitely valid.
 \end{proof}

### 2016-06-10 verifying-winner.tex
fixed some style issues

@@
 To compute the last column (Votes), we make the simplifying assumption that the reported percentages in the third column (Result) correspond to raw vote shares among survey respondents.
-The asterisks indicate that the rank is verified through a step-down procedure.}
+The asterisks indicate that the rank is verified at $0.05$-level through a step-down procedure.}
 \label{tbl:poll}
@@
 Nevertheless, if we blithely ignore the selection issue, we might carry out the following analyses to answer the questions we posed before at significance level $\alpha = 0.05$.
-We assume for simplicity that the poll represents a simple random sample of Iowa Republicans, i.e., that the data are a multinomial sample of size $890$ and underlying probabilities $\left(\pi_{\text{Trump}}, \pi_{\text{Cruz}}, \ldots\right)$.\footnote{The reality is a bit more complicated: before releasing the data, Quinnipiac has processed it to make the reported result more representative of likely caucus-goers.}
+We assume for simplicity that the poll represents a simple random sample of Iowa Republicans; i.e., that the data are a multinomial sample of size $890$ and underlying probabilities $\left(\pi_{\text{Trump}}, \pi_{\text{Cruz}}, \ldots\right)$.\footnote{The reality is a bit more complicated: before releasing the data, Quinnipiac has processed it to make the reported result more representative of likely caucus-goers.}
 
@@
 X \sim \exp\left(\theta'x - \psi\left(\theta\right)\right) g\left(x\right),
-\tag{*}
 \label{eqn:expfam}
 \end{equation}
-with respect to either the Lebesgue on $\RR^n$ or counting measure on $\ZZ^n$.
-We assume further that $g\left(x\right)$ is symmetric.
+with respect to either the Lebesgue measure on $\RR^n$ or counting measure on $\ZZ^n$.
+We assume further that $g\left(x\right)$ is symmetric with respect to permutation, and Schur concave, a mild technical condition defined in \Cref{sec:maj}.
 In addition to the multinomial family, model~\eqref{eqn:expfam} also encompasses settings such as comparing independent binomial treatment outcomes in a clinical trial, competing sports teams under a Bradley--Terry model, entries of a Dirichlet distribution, and many more; see \Cref{sec:examples} for these and other examples.
@@
 Following the convention in the ranking and selection literature, we assume that if there are multiple largest $\theta_j$, then one is arbitrarily marked as the best.
-Note that in cases where it is more interesting to ask which is the smallest population --- for example, if $X_j$ is the number of patients on treatment $j$ who suffer a heart attack during a trial --- we can change variables to $-X$.
+Note that in cases where it is more interesting to ask which is the smallest population (for example, if $X_j$ is the number of patients on treatment $j$ who suffer a heart attack during a trial) we can change the variables to $-X$ and the parameters to $\theta$.
 
@@
 For the case of independent binomials we would apply Fisher's exact test, again conditioning on $X_j+X_k$.
-These are both examples of a generic UMPU pairwise test in which we condition on the other $n-2$ indices (notated $X_{\setminus \{j,k\}}$) and $X_j+X_k$, and reject the null if $X_j$ is outside the $\alpha/2$ and $1-\alpha/2$ quantiles of the known conditional law $\mathcal{L}_{\theta_j=\theta_k}(X_j \mid X_j+X_k, X_{\setminus\{j,k\}})$.
+These are both examples of a generic UMPU pairwise test in which we condition on the other $n-2$ indices (notated $X_{\setminus \{j,k\}}$) and $X_j+X_k$, and reject the null if $X_j$ is outside the $\alpha/2$ and $1-\alpha/2$ quantiles of the conditional law $\mathcal{L}_{\theta_j=\theta_k}(X_j \mid X_j+X_k, X_{\setminus\{j,k\}})$, which crucially does not depend on the value of $\theta_j$ or $\theta_k$.
 We call this test the (two-tailed) {\em unadjusted pairwise test} since it makes no explicit adjustment for selection.
@@
 If the test rejects at level $\alpha$, conclude that the winner is really the best.
-\item {\em By how much?} Construct the unadjusted pairwise confidence interval comparing the winner to the runner-up, and report the lower confidence bound obtained for $\theta_{[1]}-\theta_{[2]}$ if it were nonnegative, report $-\infty$ otherwise.
+\item {\em By how much?} Construct the unadjusted pairwise confidence interval comparing the winner to the runner-up, and report the lower confidence bound obtained for $\theta_{[1]}-\theta_{[2]}$ if it is nonnegative, report $-\infty$ otherwise.
 \item {\em Is the runner-up really the second best, etc.?} Continue by comparing the runner-up to the second-runner-up, again using the unadjusted pairwise test, and so on down the list comparing adjacent values.
@@
 \end{enumerate}
-Here Procedure $2$ is modified due to technicalities. A less extreme modification is provided in this paper later.
+Procedure $2$ is modified above due to some technicalities. If reporting $-\infty$ seems extreme, we included a gentler modification in this paper as well.
 
@@
 
-We define Schur-concave functions and discuss their properties in \Cref{sec:maj}.
+We define Schur-concavity and discuss its properties in \Cref{sec:maj}.
 Because any log-concave and symmetric function is Schur-concave, \Cref{thm:main} applies to all of the cases discussed above.
-The proof relies on the conditional selective-inference framework of \citet{Fithian:2014ws} combined with classical multiple-testing methods, as well as ideas involving majorization and Schur-concavity.
+The proof relies on the conditional selective-inference framework of \citet{Fithian:2014ws} combined with classical multiple-testing methods, as well as some properties of majorization and Schur-concavity.
 
@@
 If we instead based our tests on an independent realization $X^*$, then, for example, Procedure 1 could use a right-tailed version of the unadjusted pairwise test.
-In the case $n = 2$ Procedure 1 amounts to a simple two-tailed test of the null hypothesis $\theta_1 = \theta_2$, and it is intuitively clear that a one-tailed test would be anti-conservative.
+In the case $n = 2$, Procedure 1 amounts to a simple two-tailed test of the null hypothesis $\theta_1 = \theta_2$, and it is intuitively clear that a one-tailed test would be anti-conservative.
 More surprising is that, no matter how large $n$ is, Procedures 1--3 require no further adjustment beyond what is required when $n = 2$.
@@
 
-\citet{Gutmann:1987fk} have worked on a similar question where the observations are from a location family, and the location parameters are compared.
-In contrast, a related paper by \citet{Karnnan:2009iv} discussed a scale family instead, comparing the scale parameters.
-\citet{Bofinger:1991hv} gave a location-scale family generated by the exponential distribution as well.
-However, as location-scale families have limited overlap with exponential families, the counterpart question for exponential families have remained unaddressed.
-Location-scale families assumed independence between observations, while this is not required in exponential families.
-A follow-up paper by \citet{Maymin:1992fz} gave a slightly more general result, applicable to more than location-scale families, yet still under the constraints of independence.
+Previous works construct tests comparing parameters in various families of distributions, by comparing just the winner and the runner-up.
+\citet{Gutmann:1987fk} tackles the question where the observations are from a location family, and the location parameters are compared.
+In which case, the difference of the winner and the runner-up has to pass a predetermined threshold.
+In contrast, a related paper by \citet{Karnnan:2009iv} discusses a scale family, comparing the scale parameters instead.
+Specifically, to test for the smallest variance across multiple populations, it is sufficient to test the ratio of the smallest to the second-smallest variances.
+\citet{Bofinger:1991hv} gives a location-scale family generated by translating an exponential distribution as well.
+Similarly, test the difference between the winner and the runner-up is enough.
+A follow-up paper by \citet{Maymin:1992fz} gave an analogous result for location-scale families, yet still under the constraints of independence as well.
 
-In the vicinity of the polling problem above, \citet{Nettleton:2009ht} provided an asymptotic test for multinomial distribution, imposing the selection by considering intersection-union tests.
-\citet{Ng:2007cn} also analyzed the multinomial case for an exact test, but with an additional restriction that maximum observation is a known constant.
+However, as location-scale families have limited overlap with exponential families, the counterpart question for exponential families remains unaddressed.
+Location-scale families assumes independence between observations, while this is not required in exponential families.
+For instance, in the vicinity of the polling problem above, \citet{Nettleton:2009ht} provides an asymptotic test for multinomial distribution, imposing the selection by considering intersection-union tests.
+\citet{Ng:2007cn} also analyzes the multinomial case for an exact test, but with an additional restriction that maximum observation is a known constant $M$.
+In terms of the polling problem above, we poll until one candidate hits a goal $M$.
+While in either papers the observations $X$ are not independent, it still suffices to test the difference between the winner and the runner-up.
 
-The subset selection problem solved in \citet{Gupta:1967wg} can indeed be used to solve the multinomial case.
-They selected a subset that contains the largest, or ``tagged'', parameter with probability $1-\alpha$.
+One final result that our particular interest in the subset selection problem \citep{Gupta:1967wg}.
+It can indeed be used to solve the multinomial case.
+They select a subset that contains the largest, or ``tagged'', parameter with probability $1-\alpha$.
 Confirming the largest parameter is thus equivalent to asserting the selected subset has size $1$.
@@
 \subsection{Outline}
-\Cref{sec:maj} gives a formal definition of the condition we are imposing, as well as common examples satisfying the condition.
-\Cref{sec:winnerbest} proves that an unadjusted pairwise test comparing the winner to the runner-up is valid, as well as a demonstration of the power of this test.
-This section also explains the validity of level $\alpha$ conditional on the best population not winning.
-\Cref{sec:confbound,sec:stepdown} prove Procedure 2 and 3 are valid.
-We will finally examine a published study with our methods in \Cref{sec:disc}.
+\Cref{sec:maj} gives a formal definition of Schur-concavity, as well as common examples satisfying this condition.
+\Cref{sec:winnerbest} proves that an unadjusted pairwise test comparing the winner to the runner-up is valid, and demonstrates the power of this test.
+\Cref{sec:confbound,sec:stepdown} justify Procedures 2 and 3.
+We conclude by examining a published study with our methods in \Cref{sec:disc}.
 
@@
 \begin{definition}
-For two vectors $a$ and $b$ in $\RR^n$ (or $\ZZ^n$), suppose permuting the two vectors in descending order gives
+For two vectors $a$ and $b$ in $\RR^n$ (or $\ZZ^n$), suppose sorting the two vectors in descending order gives
 $a_{\left(1\right)} \ge \cdots \ge a_{\left(n\right)}$ and $b_{\left(1\right)} \ge \cdots \ge b_{\left(n\right)}$. We say that $a \succeq b$ ($a$ majorizes $b$) if for $1 \le i < n$,
@@
 \item Comparing the variances of different normal populations.
-Suppose there are $n$ normal population with laws $N\left(\mu_j, \sigma_j^2\right)$ and $m$ independent observations from each of them.
+Suppose there are $n$ normal populations with laws $N\left(\mu_j, \sigma_j^2\right)$ and $m$ independent observations from each of them.
 The sample variance for population $j$ can be denoted as $r_j$.
@@
 The proof above holds true if the exponential family is defined on the counting measure.
-If ties are broken independently and randomly, the end points on the rays can be considered as ``half an atom''.
+If ties are broken independently and randomly, the end points on the rays can be considered as ``half an atom'' if the coordinates are integers, and a ``full atom'' otherwise.
 
@@
 
-The selective type I error we opted to control for Procedure 1 offers the more conventional, marginal type I error rate.
+The selective type I error we opted to control for Procedure 1 offers the conventional, marginal type I error rate.
 \begin{equation}
@@
 
-\citet{Gupta:1967wg} devised a rule to select a subset that includes the maximum $\pi_j$. In other words, if the selected subset is $J\left(X\right)$, they guaranteed
+\citet{Gupta:1967wg} devises a rule to select a subset that includes the maximum $\pi_j$. In other words, if the selected subset is $J\left(X\right)$, it guarantees
 $$\PP\left(\argmax_j \pi_j \in J\left(X\right)\right) \ge 1 - \alpha.$$
-This was achieved by finding an integer $D$, as a function on $m$, $n$ and $\alpha$, and select by
+This is achieved by finding an integer $D$, as a function on $m$, $n$ and $\alpha$, and selecting by
 $$J\left(X\right) = \left\{j: X_j \ge \max_k X_k - D\right\}.$$
-They also provided the method to choose $D$.
+It also provides the method to choose $D$.
 The subset selection can be modified.

### 2016-06-16 verifying-winner.tex
added comments to verifying-winner.tex

@@
 \end{theorem}
+\WFcomment{You seem to restate each part of this theorem later in the paper, so that e.g. Theorem 4 is the same as part 1 of Theorem 1.}
 
@@
 \item (Principle of transfer) If $x_1 > x_2$ and $t \ge 0$, then
-$$\left(x_1 + t, x_2, x_3, \ldots\right) \succeq \left(x_1, x_2 + t, x_3\right).$$
+$$\left(x_1 + t, x_2, x_3, \ldots\right) \succeq \left(x_1, x_2 + t, x_3, \ldots\right).$$
 If the $t \le 0$, the majorization is reversed.
@@
 
-\item Competing sports under Bradley--Terry model.
-Suppose $n$ players held a round robin tournaments with the Bradley--Terry model, where player $j$ has a score $\theta_j$, and the probability of player $j$ winning against player $k$ is
+\item Competitive sports under the Bradley--Terry model.
+Suppose $n$ players compete in a round robin tournament, where player $j$ has ability $\theta_j$, and the probability of player $j$ winning against player $k$ is
 $$\frac{e^{\theta_j - \theta_k}}{1 + e^{\theta_j - \theta_k}} = \frac{e^{\left(\theta_j - \theta_k\right) / 2}}{e^{\left(\theta_j - \theta_k\right) / 2} + e^{\left(\theta_k - \theta_j\right) / 2}}.$$
@@
 For symmetry, we will also adopt the convention that $Y_{jk} + Y_{kj} = 1$.
-Thus the joint distribution of $\left(Y_{jk}\right)_{j, k}$ is
-$$p\left(\left(y_{jk}\right)_{j, k}\right) \propto \exp\left(\sum_j 2\theta_j \sum_{k \ne j} y_{jk}\right)  = \exp\left(2\theta' x\right),$$
-where $x_j = \sum_{k \ne j} y_{jk}$. In other words, $x_j$ is the number of wins by player $j$.
-
-If the individual results are masked and we only know about the net wins, then
-$$p\left(x\right) \propto \exp\left(2\theta' x\right) g\left(x\right),$$
-where $g\left(x\right)$ is a function that count number of possible tournament results giving the net win vector $x$. A bijection proof shows that $x$ is indeed Schur-concave.
+Thus the joint distribution of $Y=\left(Y_{jk}\right)_{j\neq k}$ is
+$$p\left(y\right) \propto \exp\left(\sum_j 2\theta_j \sum_{k \ne j} y_{jk}\right)  = \exp\left(2\theta' x\right),$$
+where $x_j = \sum_{k \ne j} y_{jk}$. In other words, if $X_j$ is the number of wins by player $j$, then $X=(X_1,\ldots,X_n)$ is a sufficient statistic with distribution
+$$p\left(x\right) = \exp\left(2\theta' x\right) g\left(x\right),$$
+where $g\left(x\right)$ is a function that counts the number of possible tournament results giving the net win vector $x$.
+A bijection proof shows that $x$ is indeed Schur-concave.
+\WFcomment{What is a bijection proof?} Therefore, we can use Procedures 1--3 to compare player qualities.
 
@@
 Suppose there are $n$ normal populations with laws $N\left(\mu_j, \sigma_j^2\right)$ and $m$ independent observations from each of them.
-The sample variance for population $j$ can be denoted as $r_j$.
-By Cochran's theorem, $\left(m-1\right) r_j \sim \sigma_j^2 \chi_{m-1}^2$, and thus the joint distribution of $r$ is
+The sample variance for population $j$ can be denoted as $R_j$.
+By Cochran's theorem, $\left(m-1\right) R_j \sim \sigma_j^2 \chi_{m-1}^2$, and thus the joint distribution of $R$ is
 \begin{align*}
@@
 The carrier measure is $\prod_{j=1}^n r_j^{\left(m-3\right) / 2} 1_{\left\{r > 0\right\}}$, which is Schur-concave.
+Thus, we can use Procedures 1--3 to find populations with the smallest or largest variances.
 \end{enumerate}
@@
 \begin{proof}
+\WFcomment{I don't think this is a new result. In particular, it's a special case of the partial conjunction null test, but it should also predate that paper.\\
+
+Careful on terminology: the term ``exact'' usually means ``non-asymptotic'' as opposed to ``exactly uniform.'' Also, I was thrown at first when you said ``since $p_j$ are all valid $p$-values.'' I know what you mean now but at first I thought you were saying all the null hypotheses were true.}
+
 Since $p_j$ are all valid $p$-values,
 $$\PP_{H_{0j}}\left(p_j < \alpha\right) \le \alpha.$$
-S for the union null hypothesis
+So for the union null hypothesis
 $$\PP_{H_0}\left(p_* < \alpha\right) = \max_j \PP_{H_{0j}}\left(p_* < \alpha\right) \le \max_j \PP_{H_{0j}}\left(p_j < \alpha\right) \le \alpha.$$
 And thus $p_*$ is a valid $p$-value for the union null hypothesis. Now if $p_j$ are all exact, then equality holds above and $p_*$ is exact as well.
+
+\WFcomment{What is $\PP_{H_{0j}}\left(p_* < \alpha\right)$?
+That is not a well-defined probability because it depends on the distribution of the other p-values (I suppose the same could be said for $\PP_{H_{0j}}(p_j < \alpha)$, but at least that won't confuse anyone).
+Anyway, the second claim in this Lemma isn't true: if all the p-values are uniform, then the max p-value is not uniform.}
 \end{proof}
@@
 \end{theorem}
+\WFcomment{This is just a restatement of conclusion 1 of Theorem 1, right?}
 
 \begin{proof}
-Without loss of generality, otherwise by relabeling, we consider only the case where the winner is $1$ and the runner-up is $2$, etc., i.e.\ $X_1 \ge \cdots \ge X_n$.
+\WFcomment{I've now read this proof carefully and it looks generally correct, but I wonder if we could organize it a little more clearly?}
+
+Without loss of generality, otherwise by relabeling, we consider only the case where the winner is $1$ and the runner-up is $2$, etc., i.e.\ $X_1 \ge \cdots \ge X_n$\WFcomment{and that ties are broken such that...
+need to figure out how to say this right.
+Also, we should be a little more careful how we say ``without loss of generality'' --- sounds like you're saying we can relabel indices after observing the data?}.
 In this case, we will test the null hypothesis $H_{01}: \theta_1 \le \max_{j > 1} \theta_j$, which is the union of the null hypotheses $H_{01j}: \theta_1 \le \theta_j$ for $j > 1$.
 For each of these we can construct an exact $p$-value $p_{1j}$.
-Hence by \Cref{lma:union}, a test based on $p_{1*} = \max_j p_{1j}$ would be exact for $H_{01}$.
-Procedure 1 will perform an unadjusted pairwise test comparing $X_1$ to $X_2$.
+Hence by \Cref{lma:union}, a test based on $p_{1*} = \max_j p_{1j}$ would be exact for $H_{01}$\WFcomment{No; see note.
+However, because $p_{1*}=p_{12}$ almost surely given $X_1>X_2>\cdots$, $p_{1*}$ actually is conditionally uniform.}.
+\WFcomment{As we will see, } Procedure 1 will perform an unadjusted pairwise test comparing $X_1$ to $X_2$.
 Hence it is sufficient to show that $p_{12} = p_{1*}$ and that the test based on $p_{12}$ coincides with the unadjusted pairwise test.
 
-Following the framework in \citet{Fithian:2014ws}, we consider the selection event where the winner is $1$: $$A_1 = \left\{X_1 \ge \max_{j > 1} X_j\right\}.$$
+Following the framework in \citet{Fithian:2014ws}, we consider the selection event where the winner is $1$: \WFcomment{Did we already condition on $X_1\ge X_2\ge\cdots\ge X_n$? See prev. comment.}
+$$A_1 = \left\{X_1 \ge \max_{j > 1} X_j\right\}.$$
 For convenience, we let
@@
 
-We start by re-parametrizing to replace $X_1$ and $X_j$ with $D_{1j}$ and $M_{1j}$ and consider
+We start by re-parametrizing to replace $X_1$ and $X_j$ with $D_{1j}$ and $M_{1j}$ \WFcomment{Worth pointing out we now have an exponential family in $D_{1j},M_{1j},\cdots$ with nat.
+param.s ...?} and consider
 \begin{equation}
@@
 \end{align*}
+\WFcomment{What happened to the other $\theta_j$ values? I think the first ``$\sim$'' above should be a ``$\propto$'' and you need to say where all the $\theta$'s went.}
 
@@
 $$\PP_{H_{01j}}\left(p_{1j} < \alpha \middle| M_{1j}, X_{\setminus\left\{1, j\right\}}, A_1\right) = \alpha.$$
-Taking expectation on both sides gives
+Taking expectation on both sides gives \WFcomment{``Marginalizing over $M_{1j},X_{\setminus{1,j}}$,'' maybe?}
 $$\PP_{H_{01j}}\left(p_{1j} < \alpha \middle| A_1\right) = \alpha.$$
@@
 Without loss of generality, it is sufficient to show that $p_{12} \ge p_{13}$.
-In the computation of either $p$-values, $X_4, \ldots, X_n$ are all conditioned on.
+In the computation of either $p$-value, $X_4, \ldots, X_n$ are all conditioned on.
 The first point in \Cref{lma:twoprop} says that we may assume $n = 3$ without affecting the Schur-concavity of $g$.
-This allows us to clean up our notation and
+\WFcomment{Again, exactly what are we doing here?
+I think we're not really assuming $n=3$; more like conditioning on the other variables to reduce to a case where $n=3$, but we need to be explicit about how this reduction works.} This allows us to clean up our notation and
 \begin{align*}
@@
 
-Suppose $X_2 < M_{13}$, then we can re-parametrize the integrals above to give
+Suppose $X_2 < M_{13}$. \WFcomment{Changing variables to $z + D_{12}$ and $z + D_{13}$ respectively}, we can re-parametrize the integrals above to give
 \begin{align*}
@@
 \end{align*}
-To help see the re-parametrization, each of these integrals can be thought of in terms integrals along segments and rays.
-For example $p_{12}$ can be represented in terms integrals $A$ and $B$ in \Cref{fig:p-value}.
+To help see the re-parametrization, each of these integrals can be thought of in terms of integrals along segments and rays.
+For example $p_{12}$ can be represented in terms of integrals $A$ and $B$ in \Cref{fig:p-value}.
 Specifically,
@@
 \caption{The $p$-value $p_{12}$ can be written in terms of integral $A$ along the segment and $B$ along the ray.
-The diagram is drawn a level set of $x_1 + x_2 + x_3$.
+The diagram is drawn a level set of $x_1 + x_2 + x_3$ \WFcomment{Problem: the point $(1,0,0)$ is not actually in that level set.}.
 The green region represents the selection event $A_1$.}
@@
 $A'$ would refer to the sum of $A$ with the dashed line portion labeled as $\tilde{A}$, formally explained in \Cref{eqn:int_extension}.
-The majorization relation is indicated by the dotted line.}
+The majorization relation is indicated by the dotted line.
+\WFcomment{The point $(X_1,X_2,X_3)$ is cut off a bit in the picture.}}
 \label{fig:compare_rays}
@@
 
-For the alternative case where $X_2 \ge M_{13}$, the segment $C$ will reach the line $x_1 = x_2$ first before it reach $x_1 = x_3$, ending at $\left(X_2, X_2, X_1 - X_2 + X_3\right)$ instead.
+For the alternative case where $X_2 \ge M_{13}$, the segment $C$ will reach the line $x_1 = x_2$ first before it reaches $x_1 = x_3$, ending at $\left(X_2, X_2, X_1 - X_2 + X_3\right)$ instead.
 But we can still extend $A$ by $\tilde{A}$ to $\left(X_2, X_1, X_3\right)$.
@@
 If ties are broken independently and randomly, the end points on the rays can be considered as ``half an atom'' if the coordinates are integers, and a ``full atom'' otherwise.
+\WFcomment{Should be part of the proof.}
 
@@
 \end{theorem}
+\WFcomment{Under what conditions? For a multivariate exponential family with a symmetric carrier distribution, right? Also, are we sure this is a new result?}
 
@@
 \label{sec:subsetsel}
+\WFcomment{Section title can be improved: this section is primarily about a power comparison with the most natural competing procedure.}
 
 \citet{Gupta:1967wg} devises a rule to select a subset that includes the maximum $\pi_j$. In other words, if the selected subset is $J\left(X\right)$, it guarantees
-$$\PP\left(\argmax_j \pi_j \in J\left(X\right)\right) \ge 1 - \alpha.$$
+\begin{equation}\label{eq:subsetsel}
+\PP\left(\argmax_j \pi_j \in J\left(X\right)\right) \ge 1 - \alpha.
+\end{equation}
 This is achieved by finding an integer $D$, as a function on $m$, $n$ and $\alpha$, and selecting by
 $$J\left(X\right) = \left\{j: X_j \ge \max_k X_k - D\right\}.$$
+
+\WFcomment{Why is $D$ capitalized?
+It's not a random variable, is it?
+Also, can you explain how $D$ is selected?
+e.g., ``Here, we take $d(m,n,\alpha)$ to be the smallest integer such that \eqref{eq:subsetsel} holds for any $\pi$.''}
 It also provides the method to choose $D$.
@@
 We thus implemented their test for this purpose.
+\WFcomment{The phrasing here is awkward because the relationship between successive sentences is not clear.
+Instead try something like: ``Subset selection is closely related to testing whether the winner is the best.
+In particular, we can define a test that declares $j$ the best whenever $\{J(X)=\{j\}\}$.
+If $J(X)$ satisfies \eqref{eq:subsetsel}, this test is valid at level $\alpha$.
+We next compare the power of the resulting test against the power of our Procedure 1 in a multinomial example with $pi \propto \left(e^\delta, 1, \ldots, 1\right)$, for several combinations of $m$ and $n$.''}
 
@@
 
+\WFcomment{Is there any way we can get an asymptotic expression for $d$ in terms of $n$, as $m\to\infty$, and compare it to our procedure's ``effective $d$''?
+I suspect there is a $\log n$ factor in there that we don't have.}
+
+\WFcomment{``To interpret, e.g., the lower left plot, suppose that in a poll of $m=250$ respondents, one candidate enjoys $20\%$ support and the other $n-1=9$ split the remainder ($\smash{\delta = \log\frac{0.2}{0.8 / 9} \approx 0.69}$).
+Then our procedure has power XXXX to detect the best candidate, while Gupta \& Nagel's procedure has power YYYY.''}
+
 \section{By How Much?}
 \label{sec:confbound}
+\WFcomment{I like that your section heading recalls the earlier discussion, but this feels a little informal for a section heading.}
 
@@
 
-Our selective test procedure allows us to untangle multiple comparisons based on correlated observations easily, while avoiding the pitfalls of selective inference.
+Our selective test procedure allows us to untangle multiple comparisons based on correlated observations easily, while avoiding the pitfalls of selective inference \WFcomment{This sentence is confusing}.
 To illustrate, we look at a past psychology study done by \citet{Uhls:2012gf}.
@@
 \end{center}
-\caption{The number of study participants who chose each value as their top desired one. Since only one options can be chosen, these observations are inherently multinomial.}
+\caption{The number of study participants who chose each value as their top desired one.
+Since only one option can be chosen, these observations are inherently multinomial \WFcomment{I think it goes without saying this is multinomial}.}
 \label{tbl:fame}
@@
 It proceeds to perform a binomial test for the null hypothesis that the participants chose among the $7$ options uniformly and concluded with a $p$-value of $0.006$ that fame is indeed the top desired value.
-The analysis failed to address the ``winner's curse'', as well as the intricate dependence among the observations.
+The analysis failed to address the ``winner's curse'', as well as the intricate dependence among the observations \WFcomment{Intricate dependence?}.
 Our paper addressed these two issues and provided a simple test --- perform a unadjusted (two-tailed) binomial test of the winner and the runner-up.
@@
 The two-tailed $p$-value is $0.580811$, suggesting that the study was inconclusive.
+
+\WFcomment{Ending is a bit abrupt.}
 

### 2016-06-28 verifying-winner.tex
minor edits on proofs

--- 2016-06-10 verifying-winner.tex
@@
 \DeclareMathOperator*{\argmax}{arg\,max}
+
 \newtheorem{corollary}{Corollary}
@@
 \setlist{listparindent=\parindent, parsep=0pt}
-
+\newtheoremstyle{custom}{}{}{\itshape}{}{\bfseries}{.}{.5em}{\thmnote{#3}}
+\theoremstyle{custom}
+\newtheorem*{customthm}{Theorem}
 \newcommand{\EE}{\mathbb{E}}
@@
 For symmetry, we will also adopt the convention that $Y_{jk} + Y_{kj} = 1$.
-Thus the joint distribution of $\left(Y_{jk}\right)_{j, k}$ is
-$$p\left(\left(y_{jk}\right)_{j, k}\right) \propto \exp\left(\sum_j 2\theta_j \sum_{k \ne j} y_{jk}\right)  = \exp\left(2\theta' x\right),$$
-where $x_j = \sum_{k \ne j} y_{jk}$. In other words, $x_j$ is the number of wins by player $j$.
-
-If the individual results are masked and we only know about the net wins, then
-$$p\left(x\right) \propto \exp\left(2\theta' x\right) g\left(x\right),$$
-where $g\left(x\right)$ is a function that count number of possible tournament results giving the net win vector $x$. A bijection proof shows that $x$ is indeed Schur-concave.
+Thus the joint distribution of $Y=\left(Y_{jk}\right)_{j\neq k}$ is
+$$p\left(y\right) \propto \exp\left(\sum_j 2\theta_j \sum_{k \ne j} y_{jk}\right)  = \exp\left(2\theta' x\right),$$
+where $x_j = \sum_{k \ne j} y_{jk}$. In other words, if $X_j$ is the number of wins by player $j$, then $X=(X_1,\ldots,X_n)$ is a sufficient statistic with distribution
+$$p\left(x\right) = \exp\left(2\theta' x\right) g\left(x\right),$$
+where $g\left(x\right)$ is a function that counts the number of possible tournament results giving the net win vector $x$.
+A bijection proof shows that $x$ is indeed Schur-concave.
+Therefore, we can use Procedures 1--3 to compare player qualities.
 
@@
 The carrier measure is $\prod_{j=1}^n r_j^{\left(m-3\right) / 2} 1_{\left\{r > 0\right\}}$, which is Schur-concave.
+Thus, we can use Procedures 1--3 to find populations with the smallest or largest variances.
 \end{enumerate}
 
-\section{Is the Winner Really the Best?}
+\section{Verifying the Winner: Is the Winner Really the Best?}
 \label{sec:winnerbest}
@@
 
-\begin{lemma}
-If $p_j$ are valid $p$-values for testing null hypothesis $H_{0j}$, then $p_* = \max_j p_j$ is a valid $p$-value for the union null hypothesis $H_0 = \bigcup_j H_{0j}$.
-If all the $p$-values are exact, then $p_*$ is also an exact $p$-value.
+\begin{lemma}[\citealp{Berger:1982hy}]
+If $p_j$ are valid $p$-values for testing null hypothesis $H_{0j}$, then $p_* = \max_j p_j$ is a valid $p$-value for the union null (i.e.\ disjunction null) hypothesis $H_0 = \bigcup_j H_{0j}$.
+If all the $p$-values are uniform, then $p_*$ is also a valid $p$-value.
 \label{lma:union}
@@
 \begin{proof}
-Since $p_j$ are all valid $p$-values,
-$$\PP_{H_{0j}}\left(p_j < \alpha\right) \le \alpha.$$
-S for the union null hypothesis
-$$\PP_{H_0}\left(p_* < \alpha\right) = \max_j \PP_{H_{0j}}\left(p_* < \alpha\right) \le \max_j \PP_{H_{0j}}\left(p_j < \alpha\right) \le \alpha.$$
-And thus $p_*$ is a valid $p$-value for the union null hypothesis. Now if $p_j$ are all exact, then equality holds above and $p_*$ is exact as well.
+
+Under $H_0$, one of the $H_{0j}$ is true. Suppose this is $H_{01}$. In this case,
+$$\PP\left(p_* \le \alpha\right) \le \PP\left(p_1 \le \alpha\right) \le \alpha.$$
+And thus $p_*$ is a valid $p$-value for the union null hypothesis.
+
 \end{proof}
@@
 
-\begin{theorem}
+\begin{customthm}[Part 1 of \Cref{thm:main}]
 Assume the model~\eqref{eqn:expfam} holds and $g\left(x\right)$ is a Schur-concave function.
 Procedure 1 (the unadjusted pairwise test) has level $\alpha$ conditional on the best population not winning.
-\label{thm:seltest}
-\end{theorem}
+\end{customthm}
 
 \begin{proof}
-Without loss of generality, otherwise by relabeling, we consider only the case where the winner is $1$ and the runner-up is $2$, etc., i.e.\ $X_1 \ge \cdots \ge X_n$.
+
+We start by assuming that we are working with the Lebesgue measure rather than the counting measure.
+The necessary modification of the proof for the counting measure case is provided at the end of this proof.
+
+Here, we consider only the case where the winner is $1$ and the runner-up is $2$, etc., i.e.\ $X_1 \ge \cdots \ge X_n$ and that ties are broken uniformly.
+For other cases, the following proof remains valid under relabeling.
 In this case, we will test the null hypothesis $H_{01}: \theta_1 \le \max_{j > 1} \theta_j$, which is the union of the null hypotheses $H_{01j}: \theta_1 \le \theta_j$ for $j > 1$.
 For each of these we can construct an exact $p$-value $p_{1j}$.
-Hence by \Cref{lma:union}, a test based on $p_{1*} = \max_j p_{1j}$ would be exact for $H_{01}$.
-Procedure 1 will perform an unadjusted pairwise test comparing $X_1$ to $X_2$.
+Hence by \Cref{lma:union}, a test based on $p_{1*} = \max_j p_{1j}$ would be valid for $H_{01}$.
+Procedure 1 performs an unadjusted pairwise test comparing $X_1$ to $X_2$.
 Hence it is sufficient to show that $p_{12} = p_{1*}$ and that the test based on $p_{12}$ coincides with the unadjusted pairwise test.
 
-Following the framework in \citet{Fithian:2014ws}, we consider the selection event where the winner is $1$: $$A_1 = \left\{X_1 \ge \max_{j > 1} X_j\right\}.$$
+Following the framework in \citet{Fithian:2014ws}, we consider the selection event where the winner is $1$: 
+$$A_1 = \left\{X_1 \ge \max_{j > 1} X_j\right\}.$$
 For convenience, we let
@@
 
-We start by re-parametrizing to replace $X_1$ and $X_j$ with $D_{1j}$ and $M_{1j}$ and consider
+We start by re-parametrizing to replace $X_1$ and $X_j$ with $D_{1j}$ and $M_{1j}$.
+The distribution is now an exponential family with sufficient statistics $D_{1j}, M_{1j}, X_{\setminus\left\{1, j\right\}}$ and corresponding natural parameters $\theta_1 - \theta_j, \theta_1 + \theta_j, \theta_{\setminus\left\{1, j\right\}}$.
+We now consider
 \begin{equation}
@@
 \begin{align*}
-D_{1j} & \sim \exp\left(\left(\theta_1 - \theta_j\right) D_{1j} + \theta_2 X_2 + \cdots + \left(\theta_1 + \theta_j\right) M_{1j} + \cdots + \theta_n X_n \right) \\
+p\left(D_{1j}\right) & \propto \exp\left(\left(\theta_1 - \theta_j\right) D_{1j} + \theta_2 X_2 + \cdots + \left(\theta_1 + \theta_j\right) M_{1j} + \cdots + \theta_n X_n \right) \\
 & ~~~~~~~~ g\left(M_{ij} + D_{ij}, X_2, \ldots, M_{ij} - D_{ij}, \ldots X_n\right) 1_{A_1} \\
-& \sim g\left(M_{ij} + D_{ij}, X_2, \ldots, M_{ij} - D_{ij}, \ldots X_n\right) 1_{A_1}.
+& \stackrel{\text{(a)}}{\propto} g\left(M_{ij} + D_{ij}, X_2, \ldots, M_{ij} - D_{ij}, \ldots X_n\right) 1_{A_1},
 \end{align*}
+where at step (a), conditioning on $X_{\setminus\left\{1, j\right\}}$ and $M_{1j}$ removes dependence on $\theta_{\setminus\left\{1, j\right\}}$ and $\theta_1 + \theta_j$ respectively, while $\theta_1 - \theta_j$ is taken to be $0$ under our null hypothesis.
 
@@
 $$\PP_{H_{01j}}\left(p_{1j} < \alpha \middle| M_{1j}, X_{\setminus\left\{1, j\right\}}, A_1\right) = \alpha.$$
-Taking expectation on both sides gives
+Marginalizing over $M_{1j}, X_{\setminus\left\{1, j\right\}}$,
 $$\PP_{H_{01j}}\left(p_{1j} < \alpha \middle| A_1\right) = \alpha.$$
@@
 Without loss of generality, it is sufficient to show that $p_{12} \ge p_{13}$.
-In the computation of either $p$-values, $X_4, \ldots, X_n$ are all conditioned on.
-The first point in \Cref{lma:twoprop} says that we may assume $n = 3$ without affecting the Schur-concavity of $g$.
-This allows us to clean up our notation and
+In the computation of either $p$-value, $X_4, \ldots, X_n$ are all conditioned on.
+Fixing these variables that are conditioned on, $g$ has only thee variables: $X_1$, $X_2$ and $X_3$.
+We can write this as $g_{X_4, \ldots, X_n}\left(X_1, X_2, X_3\right)$.
+The first point in \Cref{lma:twoprop} says that the function $g_{X_4, \ldots, X_n}$ is Schur-concave as well.
+This allows us to clean up our notation and just rename $g_{X_4, \ldots, X_n}$ as $g$.
+The p-values thus are
 \begin{align*}
@@
 
-Suppose $X_2 < M_{13}$, then we can re-parametrize the integrals above to give
+The maximum in the denominator of $p_{13}$ prompts us to consider two separate cases.
+First, we suppose $X_2 < M_{13}$.
+Changing variables such that the lower limits of both integrals in the numerator is $0$, we can re-parametrize the integrals above to give
 \begin{align*}
@@
 	\fill (B) circle(2pt) node[above right] {$\left(X_1, X_2, X_3\right)$};
-	\draw[thick, ->] (0, 0) -- (1, 0) node[right] {\tiny $\left(1, 0, 0\right)$};
-	\draw[thick, ->] (0, 0) -- (120:1) node[above] {\tiny $\left(0, 1, 0\right)$};
-	\draw[thick, ->] (0, 0) -- (240:1) node[below] {\tiny $\left(0, 0, 1\right)$};
+	\fill (0, 0) circle(2pt) node[left] {$\left(\overline{X} = \frac{X_1 + X_2 + X_3}{3}, \overline{X}, \overline{X}\right)$};
+	\draw[thick, ->] (0, 0) -- (1, 0) node[right] {\tiny $+ \left(1, 0, 0\right)$};
+	\draw[thick, ->] (0, 0) -- (120:1) node[above] {\tiny $+ \left(0, 1, 0\right)$};
+	\draw[thick, ->] (0, 0) -- (240:1) node[below] {\tiny $+ \left(0, 0, 1\right)$};
 \end{tikzpicture}
@@
 
-For the alternative case where $X_2 \ge M_{13}$, the segment $C$ will reach the line $x_1 = x_2$ first before it reach $x_1 = x_3$, ending at $\left(X_2, X_2, X_1 - X_2 + X_3\right)$ instead.
+For the second case where $X_2 \ge M_{13}$, the segment $C$ will reach the line $x_1 = x_2$ first before it reaches $x_1 = x_3$, ending at $\left(X_2, X_2, X_1 - X_2 + X_3\right)$ instead.
 But we can still extend $A$ by $\tilde{A}$ to $\left(X_2, X_1, X_3\right)$.
@@
 The naive unadjusted pairwise test is indeed valid.
+
+Now suppose the exponential family is defined on the counting measure instead.
+If ties are broken independently and randomly, the end points on the rays can be considered as ``half an atom'' if the coordinates are integers, and a ``full atom'' otherwise.
+
 \end{proof}
-
-The proof above holds true if the exponential family is defined on the counting measure.
-If ties are broken independently and randomly, the end points on the rays can be considered as ``half an atom'' if the coordinates are integers, and a ``full atom'' otherwise.
 
@@
 \label{thm:stoch}
-$X_1 \ge X_2$ in stochastic order if and only if $\theta_1 > \theta_2$.
+For a multivariate exponential family with a symmetric carrier distribution, $X_1 \ge X_2$ in stochastic order if and only if $\theta_1 > \theta_2$.
 \end{theorem}
+\WFcomment{Are we sure this is a new result?} \KHcomment{Nothing found when I looked up a text for stochastic order, and on Google with ``stochastic order exponential family''}
 
@@
 
-\subsection{Multinomial Case: Connection with the Subset Selection}
+\subsection{Power Comparison in the Multinomial Case}
 \label{sec:subsetsel}
@@
 \citet{Gupta:1967wg} devises a rule to select a subset that includes the maximum $\pi_j$. In other words, if the selected subset is $J\left(X\right)$, it guarantees
-$$\PP\left(\argmax_j \pi_j \in J\left(X\right)\right) \ge 1 - \alpha.$$
-This is achieved by finding an integer $D$, as a function on $m$, $n$ and $\alpha$, and selecting by
-$$J\left(X\right) = \left\{j: X_j \ge \max_k X_k - D\right\}.$$
-It also provides the method to choose $D$.
-The subset selection can be modified.
-Inherently, the event $\left\{J\left(X\right) = \left\{1\right\}\right\}$ is the same as inferring $\pi_1$ is the largest.
-We thus implemented their test for this purpose.
+\begin{equation}\label{eq:subsetsel}
+\PP\left(\argmax_j \pi_j \in J\left(X\right)\right) \ge 1 - \alpha.
+\end{equation}
+This is achieved by finding an integer $d$, as a function on $m$, $n$ and $\alpha$, and selecting the subset
+$$J\left(X\right) = \left\{j: X_j \ge \max_k X_k - d\right\}.$$
+Here, we take $d(m, n, \alpha)$ to be the smallest integer such that \eqref{eq:subsetsel} holds for any $\pi$.
+
+It also provides the algorithm computing $d$.
+Subset selection is closely related to testing whether the winner is the best.
+In particular, we can define a test that declares $j$ the best whenever $J\left(X\right) = \left\{j\right\}$.
+If $J\left(X\right)$ satisfies \eqref{eq:subsetsel}, this test is valid at level $\alpha$.
+We next compare the power of the resulting test against the power of our Procedure 1 in a multinomial example with $\pi \propto \left(e^\delta, 1, \ldots, 1\right)$, for several combinations of $m$ and $n$.
 
@@
 For their method, we use $\alpha = 0.05$; but in light of the extra factor of $\frac{n-1}{n}$ in \Cref{eqn:marginal}, we will apply the selective procedure with $\frac{n}{n-1} \alpha$ such that the marginal type I error rate of both procedures are controlled at $\alpha$.
-Their test coincides with our test at $n = 2$; however as $n$ grows, the selective test shows significantly more power than Gupta and Nagel's test.
+Their test coincides with our test at $n = 2$; however as $n$ grows, the selective test shows significantly more power than \citeauthor{Gupta:1967wg}'s test.
 
@@
 
-\section{By How Much?}
+To interpret, e.g., the lower left plot, suppose that in a poll of $m = 50$ respondents, one candidate enjoys $30\%$ support and the other $n - 1 = 9$ split the remainder ($\delta = \log\frac{0.3}{0.7 / 9} \approx 1.35$).
+Then our procedure has power approximately $0.3$ to detect the best candidate, while \citeauthor{Gupta:1967wg}'s procedure has power around $0.1$.
+
+A fundamental difference between the two methods is the definition of the threshold.
+The threshold from \citet{Gupta:1967wg} depends solely on the setup of the model: $m$ and $n$.
+Our threshold, however, depends on the data itself.
+Such difference is amplified when $n$ is large.
+The threshold from \citeauthor{Gupta:1967wg} increases with $n$ even if the added observations are all $0$.
+In such case, our threshold does not change at all, suggesting more potential test power.
+
+\WFcomment{Is there any way we can get an asymptotic expression for $d$ in terms of $n$, as $m\to\infty$, and compare it to our procedure's ``effective $d$''?
+I suspect there is a $\log n$ factor in there that we don't have.} \KHcomment{We will need to get into details about $r^*$ to explain so, which seems like excessive details.
+I added some intuition on why our test it better.
+Not sure if it suffices.}
+
+\section{Confidence Bounds on Differences: By How Much?}
 \label{sec:confbound}
@@
 \begin{align*}
-D_{1j} & \sim \exp\left(\left(\theta_1 - \theta_j\right) D_{1j} + \theta_2 X_2 + \cdots + \left(\theta_1 + \theta_j\right) M_{1j} + \cdots + \theta_n X_n \right) \\
+p\left(D_{1j}\right) & \propto \exp\left(\left(\theta_1 - \theta_j\right) D_{1j} + \theta_2 X_2 + \cdots + \left(\theta_1 + \theta_j\right) M_{1j} + \cdots + \theta_n X_n \right) \\
 & ~~~~~~~~ g\left(M_{1j} + D_{1j}, X_2, \ldots, M_{1j} - D_{1j}, \ldots X_n\right) 1_{A_1} \\
-& \sim \exp\left(\delta D_{1j}\right) g\left(M_{1j} + D_{1j}, X_2, \ldots, M_{1j} - D_{1j}, \ldots X_n\right) 1_{A_1}.
+& \propto \exp\left(\delta D_{1j}\right) g\left(M_{1j} + D_{1j}, X_2, \ldots, M_{1j} - D_{1j}, \ldots X_n\right) 1_{A_1}.
 \end{align*}
@@
 
-As before in \Cref{thm:seltest}, without loss of generality we assume $n = 3$. Once again it is sufficient to show that $p_{12} \ge p_{13}$. We have the same two cases. If $X_2 < M_{13}$, then
+As before in Part 1 of \Cref{thm:main}, the conditioning reduces to the case where $n = 3$.
+Once again it is sufficient to show that $p_{12} \ge p_{13}$.
+We have the same two cases.
+If $X_2 < M_{13}$, then
 \begin{align*}
@@
 
-\begin{corollary}
+\begin{customthm}[Part 2 of \Cref{thm:main}]
 Assume the model~\eqref{eqn:expfam} holds and $g\left(x\right)$ is a Schur-concave function.
 Procedure 2 (the lower bound of unadjusted pairwise confidence interval) gives a conservative $1-\alpha$ lower confidence bound for $\theta_{[1]} - \max_{j \ne [1]} \theta_j$.
-\end{corollary}
+\end{customthm}
 
@@
 
-\section{Is the Runner-Up Really the Second Best, etc.?}
+\section{Verifying Other Ranks: Is the Runner-Up Really the Second Best, etc.?}
 \label{sec:stepdown}
@@
 Here we are only comparing $X_j$ to $X_{j+1}$ by \Cref{sec:winnerbest}.
-The upper truncation for $X_j$ can be represented by cropping \Cref{fig:compare_rays} along a vertical line, shown in \Cref{fig:crop_rays}, thus the proof of \Cref{thm:seltest} on sufficiency to compare $X_1$ and $X_2$ remains valid with appropriate conditioning.
+The upper truncation for $X_j$ can be represented by cropping \Cref{fig:compare_rays} along a vertical line, shown in \Cref{fig:crop_rays}, thus the proof of Part 1 of \Cref{thm:main} on sufficiency to compare $X_1$ and $X_2$ remains valid with appropriate conditioning.
 Again we can construct the $p$-values as in \Cref{eqn:p1j} for $k>j$.
@@
 
-Hence similar to the proof of \Cref{thm:seltest}, Schur-concavity ensures $p_{j\left(j+1\right)} \ge p_{jk}$ for all $k>j$, meaning that it is sufficient to compare $X_j$ and $X_{j+1}$.
+Hence similar to the proof of Part 1 of \Cref{thm:main}, Schur-concavity ensures $p_{j\left(j+1\right)} \ge p_{jk}$ for all $k>j$, meaning that it is sufficient to compare $X_j$ and $X_{j+1}$.
 In fact, we can take $p_j = p_{j\left(j+1\right)}$.
@@
 
-\begin{corollary}
+\begin{customthm}[Part 3 of \Cref{thm:main}]
 Assume the model~\eqref{eqn:expfam} holds and $g\left(x\right)$ is a Schur-concave function. Procedure 3 is a conservative step-down procedure with FWER no larger than $\alpha$.
-\end{corollary}
+\end{customthm}
 
@@
 
-Our selective test procedure allows us to untangle multiple comparisons based on correlated observations easily, while avoiding the pitfalls of selective inference.
+Our selective test procedure allows us to untangle multiple comparisons based on correlated observations easily, while avoiding the pitfalls of selection.
 To illustrate, we look at a past psychology study done by \citet{Uhls:2012gf}.
@@
 \end{center}
-\caption{The number of study participants who chose each value as their top desired one. Since only one options can be chosen, these observations are inherently multinomial.}
+\caption{The number of study participants who chose each value as their top desired one. Since only one option can be chosen, these observations are inherently multinomial.}
 \label{tbl:fame}
@@
 It proceeds to perform a binomial test for the null hypothesis that the participants chose among the $7$ options uniformly and concluded with a $p$-value of $0.006$ that fame is indeed the top desired value.
-The analysis failed to address the ``winner's curse'', as well as the intricate dependence among the observations.
+The analysis failed to address the ``winner's curse'', as well as the dependence among the observations.
 Our paper addressed these two issues and provided a simple test --- perform a unadjusted (two-tailed) binomial test of the winner and the runner-up.
@@
 The two-tailed $p$-value is $0.580811$, suggesting that the study was inconclusive.
+
+This paper has provided a straightforward yet powerful method for verifying that the winner is the best, for joint distributions in the exponential family with mild condition.
+Such a test allows us to ``ignore'' the issues of selection and multiple-testing, which are often overlooked or mishandled.
 

### 2016-06-30 verifying-winner.tex
more comments / small edits

@@
 \usepackage{mathrsfs}
+\usepackage{verbatim}
 \usepackage{tikz}
@@
 
+Our proof has three main parts: (1) deriving $p_{1j}$ for each $j\geq 2$, (2) showing that $p_{12} \geq p_{1j}$ for each $j\geq 2$, and 
+(3) showing that $p_{12}$ is an unadjusted pairwise $p$-value.
+
+\paragraph{Derivation of $p_{1j}$}
 Following the framework in \citet{Fithian:2014ws}, we consider the selection event where the winner is $1$: 
@@
 
+\paragraph{Demonstration that $p_{1*}=p_{12}$}
+
+We now proceed to show that $p_{12}$, the $p$-value comparing the winner to the runner-up, is the largest of all $p_{1j}$.
 Without loss of generality, it is sufficient to show that $p_{12} \ge p_{13}$.
-In the computation of either $p$-value, $X_4, \ldots, X_n$ are all conditioned on.
-Fixing these variables that are conditioned on, $g$ has only thee variables: $X_1$, $X_2$ and $X_3$.
 We can write this as $g_{X_4, \ldots, X_n}\left(X_1, X_2, X_3\right)$.
@@
 
+\paragraph{3. $p_{12}$ is an unadjusted pairwise $p$-value}
+
 Since the denominator of $p_{12}$ is half of the symmetric distribution before truncation, a one-sided test that rejects based on $p_{12}$ is identical to the naive unadjusted pairwise test comparing $X_1$ and $X_2$.
@@
 The threshold from \citeauthor{Gupta:1967wg} increases with $n$ even if the added observations are all $0$.
-In such case, our threshold does not change at all, suggesting more potential test power.
+In such case, our threshold does not change at all, suggesting more potential test power.\WFcomment{Actually this isn't really why ours is more powerful.}
 
@@
 
-We can take the idea above further and construct confidence bound for $\theta_{[1]} - \max_{j \ne [1]} \theta_{j}$.
-This can be achieved by considering a statistical test, to see if $\theta_{[1]} - \max_{j \ne [1]} \theta_{j} \le \delta$, followed by the duality of confidence interval and statistical test.
-
+By generalizing the above, we can construct a lower confidence bound for $\theta_{[1]} - \max_{j \ne [1]} \theta_{j}$.
 Here we provide a more powerful Procedure 2' first.
-The confidence lower bound can be taken as the smallest $\delta$ such that we can reject $H_{0[1]}^\delta: \theta_{[1]} - \max_{j \ne [1]} \theta_{[j]} > \delta$.
-Once again this can be written as a union of null hypothesis
-$$H_{0[1]}^\delta = \bigcup_{j \ne [1]} H_{0[1]j}: \theta_1 - \theta_j > \delta.$$
-By \Cref{lma:union}, we can construct selective exact one-tailed $p$-values $p_{[1]j}$ for each of these by conditioning on $A_{[1]}$, $M_{[1]j}$ and $X_{\setminus\left\{[1], j\right\}}$, giving us an exact test for $H_{0[1]}$ by rejecting whenever $\max_{j \ne [1]} p_{[1]j} < \alpha$.
+We will proceed by inverting a statistical test of the hypothesis $H_{0[1]}^\delta:\; \theta_{[1]} - \max_{j \ne [1]} \theta_{j} \le \delta$, which can be written as a union of null hypotheses:
+$$H_{0[1]}^\delta = \bigcup_{j \ne [1]} H_{0[1]j}: \theta_{[1]} - \theta_j \le \delta.$$
+By \Cref{lma:union}, we can construct selective exact one-tailed $p$-values $p_{[1]j}^{(\delta)}$ \WFcomment{What do you think of attaching something like a superscript here to make it clear there are different $p$-values for every $\delta$?} for each of these by conditioning on $A_{[1]}$, $M_{[1]j}$ and $X_{\setminus\left\{[1], j\right\}}$, giving us an exact test for $H_{0[1]}$ by rejecting whenever $\max_{j \ne [1]} p_{[1]j}^{(\delta)} < \alpha$.
 
 \begin{theorem}
-The $p$-values constructed above satisfies $p_{[1][2]} \ge p_{[1]j}$ for any $j \ne [1]$.
+The $p$-values constructed above satisfy $p_{[1][2]}^{(\delta)} \ge p_{[1]j}^{(\delta)}$ for any $j \ne [1]$.
 \end{theorem}
@@
 Again we start with assuming $X_1 \ge \cdots \ge X_n$. The $p$-values in question are derived from the conditional law
-$$\mathcal{L}_{\theta_1 - \theta_j = \delta} \left(D_{1j} \middle| D_{1j}, X_2, \ldots, X_n, A\right),$$
+$$\mathcal{L}_{\theta_1 - \theta_j = \delta} \left(D_{1j} \middle| M_{1j}, X_2, \ldots, X_n, A\right),$$
 which is the truncated distribution
@@
 
-In other words, Procedure 2' can be summarized as: Find the minimum $\delta$ such that $p_{12} \le \alpha$.
+In other words, Procedure 2' can be summarized as: Find the minimum $\delta$ such that $p_{[1][2]}^{(\delta)} \le \alpha$.
 And by construction, Procedure 2' gives exact $1-\alpha$ confidence bound for $\theta_{[1]} - \max_{j \ne [1]} \theta_j$.
@@
 So the unadjusted pairwise test $p$-value from Procedure 2 comparing $X_1$ and $X_2$ is larger than $p_{12}$ from Procedure 2', rendering Procedure 2 conservative.
+
+\WFcomment{I found this proof confusing.}
 \end{proof}
@@
 In reality, we can always just adopt Procedure 2' in the case when Procedure 1 rejects.
-In fact, by Procedure 2', the multinomial example for polling in \Cref{sec:iowa} can give a stronger lower confidence bound, that $\log \pi_{\text{Trump}} - \max_{j \ne \text{Trump}} \log \pi_{j} \ge 0.103142$.
+In fact, by Procedure 2', the multinomial example for polling in \Cref{sec:iowa} can give a stronger lower confidence bound, that $\log \pi_{\text{Trump}} - \max_{j \ne \text{Trump}} \log \pi_{j} \ge 0.103$.\WFcomment{0.103142 is a lot of sig.
+digits.}%142$.
 
@@
 \end{theorem}
+\WFcomment{Probably better to define Procedure 3' outside the theorem?}
 
@@
 This can be fitted into the selective sequential model selection framework proposed by \citet{Fithian:2015uj}.
-Given the observations $X_1 \ge \cdots \ge X_n$, drawn from an unknown distribution $F$, we consider the sequence of null hypothesis of
+Given the observations $X_1 \ge \cdots \ge X_n$, drawn from an unknown distribution $F$, we consider the following sequence of null hypotheses:
 $$H_{0j}: \theta_j \le \max_{k > j} \theta_k.$$
@@
 $$M_0\left(X\right) \subseteq M_1\left(X\right) \subseteq \cdots \subseteq M_n\left(X\right), ~~~~~~~~ M_j\left(X\right)^c = \left\{\theta_1 > \cdots > \theta_j > \max_{k > j} \theta_k\right\},$$
-and the each $M_j$ depends on $X$ through the order of $X$. The step-down procedure for rejecting $H_{0j}$ is equivalent to selecting the smallest $j$ for which $F \in M_j\left(X\right)$.
+\WFcomment{You're overloading the variable name $M$ here}
+
+and the each $M_j$ depends on $X$ through the order of $X$.
+The step-down procedure for rejecting $H_{0j}$ is equivalent to selecting the smallest $j$ for which $F \in M_j\left(X\right)$.
+\WFcomment{More like the smallest $j$ for which we cannot reject...}
 
@@
 Here we are only comparing $X_j$ to $X_{j+1}$ by \Cref{sec:winnerbest}.
-The upper truncation for $X_j$ can be represented by cropping \Cref{fig:compare_rays} along a vertical line, shown in \Cref{fig:crop_rays}, thus the proof of Part 1 of \Cref{thm:main} on sufficiency to compare $X_1$ and $X_2$ remains valid with appropriate conditioning.
+The upper truncation for $X_j$ can be represented by cropping \Cref{fig:compare_rays} along a vertical line, shown in \Cref{fig:crop_rays}, thus the proof of Part 1 of \Cref{thm:main} on sufficiency\WFcomment{Careful about the word ``sufficiency'', it's a bit of a loaded term in stats} to compare $X_1$ and $X_2$ remains valid with appropriate conditioning.
 Again we can construct the $p$-values as in \Cref{eqn:p1j} for $k>j$.
@@
 These are valid selective $p$-value as required in \citet{Fithian:2015uj}, as
+$$\PP_\theta \left(p_j \le \alpha \mid \theta_{[i]} \text{ is not the } i\text{th largest, some } i\leq j\right) \le \alpha \text{ a.s.}, \quad \forall \; \theta$$
 $$\PP_F \left(p_j \le \alpha \middle| M_{j-1}\left(X\right)\right) \le \alpha \text{ a.s.}, ~~~~~~~~ F \in M_{j-1}\left(X\right)$$
-by tower property.
+by tower property. \WFcomment{Careful on notation again for ``$F\in M_{j-1}$,'' the right hand side is random.}
 
@@
 Our selective test procedure allows us to untangle multiple comparisons based on correlated observations easily, while avoiding the pitfalls of selection.
-To illustrate, we look at a past psychology study done by \citet{Uhls:2012gf}.
+Claims reporting the ``winner'' are commonly made in the scientific literature, usually with no significance level reported or an incorrect method applied.
+For example, \citet{Uhls:2012gf} asked $n=20$ elementary and middle school students which of seven personal values they most hoped to embody as adults: ``Fame'' (8 selected), ``Benevolence'' (5), ``Achievement'' (3), and several others (4 total including one response of ``Other'').
+The authors' main finding --- which appeared in the abstract, the first paragraph of the article, and later a CNN.com headline --- was that ``Fame'' was the most common response.
+This claim was accompanied by a signficance level of $0.006$, which the authors computed by testing whether the probability of selecting ``Fame'' was larger than 1/7.
 
+\begin{comment}
 \begin{table}[htbp]
@@
 The analysis failed to address the ``winner's curse'', as well as the dependence among the observations.
-Our paper addressed these two issues and provided a simple test --- perform a unadjusted (two-tailed) binomial test of the winner and the runner-up.
+
+We have provided a simple, powerful and straightforward test based on comparing the winner to the runner-up.
+
+comparing the number of ``Fame'' responses to the distribution
+
+ --- perform a unadjusted (two-tailed) binomial test of the winner and the runner-up.
 In this case, we test if $8$ is a significant observation in $\text{Binomial}\left(8 + 5, 0.5\right)$.
 The two-tailed $p$-value is $0.580811$, suggesting that the study was inconclusive.
+\end{comment}
 
-This paper has provided a straightforward yet powerful method for verifying that the winner is the best, for joint distributions in the exponential family with mild condition.
-Such a test allows us to ``ignore'' the issues of selection and multiple-testing, which are often overlooked or mishandled.
+The obvious error in the authors' reasoning is perhaps understandable since there is, presently, no agreed-upon statistical solution for this commonplace problem.
+Using our approach, they could have performed a two-tailed binomial test of the winner (``Fame'') vs.
+the runner-up (``Benevolence'').
+This test returns a $p$-value of
+\[
+p = 2\PP\left[\text{Binomial}\left(8 + 5, 0.5\right) \geq 8\right] = 0.58,
+\]
+indicating that their data did not support their major finding.
+
+This paper has provided a straightforward yet powerful method for verifying that the winner is the best, for joint distributions in the exponential family with a mild technical condition.
+Such a test allows us to ``ignore'' the issues of selection and multiple-testing, which are often overlooked or mishandled.\WFcomment{This last sentence might give the wrong impression.}
 

### 2016-07-02 verifying-winner.tex
proofs enhanced; comments added; conclusion fixing attempted

@@
 \usepackage{enumitem}
+\newlist{inlinelist}{enumerate*}{1}
+\setlist*[inlinelist,1]{label=(\arabic*)}
+\usepackage[totalwidth=480pt, totalheight=680pt]{geometry}
 \usepackage{graphicx}
-\usepackage[totalwidth=480pt, totalheight=680pt]{geometry}
 \usepackage{mathrsfs}
-\usepackage{verbatim}
+\usepackage[round]{natbib}
 \usepackage{tikz}
 \usetikzlibrary{calc}
+\usepackage{verbatim}
 \usepackage{xcolor}
-\usepackage[round]{natbib}
 \definecolor{mid_green}{HTML}{99d8c9}
@@
 
-We will generically use the term {\em population} to refer to the treatment group, sports team, political candidate, etc.
-represented by a given random variable $X_j$.
+We will generically use the term {\em population} to refer to the treatment group, sports team, political candidate, etc.\ represented by a given random variable $X_j$.
 As we will see, $\theta_j \ge \theta_k$ if and only if $X_j$ is stochastically larger than $X_k$; thus, there is a well-defined stochastic ordering of the populations that matches the ordering of the entries of $\theta$.
@@
 \begin{align*}
-a_{\left(1\right)} + \cdots + a_{\left(i\right)} & \ge b_{\left(1\right)} + \cdots + b_{\left(i\right)} \\
+a_{\left(1\right)} + \cdots + a_{\left(i\right)} & \ge b_{\left(1\right)} + \cdots + b_{\left(i\right)}, \\
 a_{\left(1\right)} + \cdots + a_{\left(n\right)} & = b_{\left(1\right)} + \cdots + b_{\left(n\right)}
@@
 \begin{proof}
-
 Under $H_0$, one of the $H_{0j}$ is true. Suppose this is $H_{01}$. In this case,
@@
 \begin{proof}
-
 We start by assuming that we are working with the Lebesgue measure rather than the counting measure.
@@
 
-Our proof has three main parts: (1) deriving $p_{1j}$ for each $j\geq 2$, (2) showing that $p_{12} \geq p_{1j}$ for each $j\geq 2$, and 
-(3) showing that $p_{12}$ is an unadjusted pairwise $p$-value.
+Our proof has three main parts:
+\begin{inlinelist}
+\item deriving $p_{1j}$ for each $j\ge 2$,
+\item showing that $p_{12} \ge p_{1j}$ for each $j\ge 2$, and
+\item showing that $p_{12}$ is an unadjusted pairwise $p$-value.
+\end{inlinelist}
 
 \paragraph{Derivation of $p_{1j}$}
-Following the framework in \citet{Fithian:2014ws}, we consider the selection event where the winner is $1$: 
+
+Following the framework in \citet{Fithian:2014ws}, we first construct the p-values by conditioning on the selection event where the winner is $1$: 
 $$A_1 = \left\{X_1 \ge \max_{j > 1} X_j\right\}.$$
@@
 
-We start by re-parametrizing to replace $X_1$ and $X_j$ with $D_{1j}$ and $M_{1j}$.
+We then re-parametrize to replace $X_1$ and $X_j$ with $D_{1j}$ and $M_{1j}$.
 The distribution is now an exponential family with sufficient statistics $D_{1j}, M_{1j}, X_{\setminus\left\{1, j\right\}}$ and corresponding natural parameters $\theta_1 - \theta_j, \theta_1 + \theta_j, \theta_{\setminus\left\{1, j\right\}}$.
@@
 \begin{equation}
-\mathcal{L}_{\theta_1 - \theta_j = 0} \left(D_{1j} \middle| M_{1j}, X_{\setminus\left\{1, j\right\}}, A_1\right), \text{ where } A_1 = \left\{D_{1j} \ge \max_{k \ne 1, j} X_k - M_{1j}\right\} \cap \left\{D_{1j} \ge 0\right\}.
+\mathcal{L}_{\theta_1 - \theta_j = 0} \left(D_{1j} \;\middle|\; M_{1j}, X_{\setminus\left\{1, j\right\}}, A_1\right), \text{ where } A_1 = \left\{D_{1j} \ge \max_{k \ne 1, j} X_k - M_{1j}\right\} \cap \left\{D_{1j} \ge 0\right\}.
 \label{eqn:condlaw}
@@
 
-By construction, $p_{1j}$ satisfies
-$$\PP_{H_{01j}}\left(p_{1j} < \alpha \middle| M_{1j}, X_{\setminus\left\{1, j\right\}}, A_1\right) = \alpha.$$
+Finally, by construction, $p_{1j}$ satisfies
+$$\PP_{H_{01j}}\left(p_{1j} < \alpha \;\middle|\; M_{1j}, X_{\setminus\left\{1, j\right\}}, A_1\right) = \alpha.$$
 Marginalizing over $M_{1j}, X_{\setminus\left\{1, j\right\}}$,
-$$\PP_{H_{01j}}\left(p_{1j} < \alpha \middle| A_1\right) = \alpha.$$
-Therefore these $p_{1j}$ are indeed valid exact $p$-values.
+$$\PP_{H_{01j}}\left(p_{1j} < \alpha \;\middle|\; A_1\right) = \alpha.$$
+Therefore these $p_{1j}$ are indeed valid $p$-values.
 
@@
 Without loss of generality, it is sufficient to show that $p_{12} \ge p_{13}$.
-We can write this as $g_{X_4, \ldots, X_n}\left(X_1, X_2, X_3\right)$.
+
+From the first part of this proof, both p-values are constructed by conditioning on $X_4, \ldots, X_n$.
+Upon conditioning these, $\left(X_1, X_2, X_3\right)$ follows an exponential family distribution, with carrier distribution
+$$g_{X_4, \ldots, X_n}\left(X_1, X_2, X_3\right) = g\left(X_1, \ldots, X_n\right).$$
 The first point in \Cref{lma:twoprop} says that the function $g_{X_4, \ldots, X_n}$ is Schur-concave as well.
-This allows us to clean up our notation and just rename $g_{X_4, \ldots, X_n}$ as $g$.
-The p-values thus are
+We have reduced the problem to the case when $n = 3$: we can apply the result for $n = 3$ to $g_{X_4, \ldots, X_n}$ to yield $p_{12} \ge p_{13}$ for $n > 3$.
+
+We shall henceforth focus on the case when $n = 3$. The p-values thus are
 \begin{align*}
-p_{12} & = \frac{\int_{D_{12}}^\infty g\left(M_{12} + z, M_{12} - z, X_3\right) \,dz}{\int_0^\infty g\left(M_{12} + z, M_{12} - z, X_3\right) \,dz} \\
+p_{12} & = \frac{\int_{D_{12}}^\infty g\left(M_{12} + z, M_{12} - z, X_3\right) \,dz}{\int_0^\infty g\left(M_{12} + z, M_{12} - z, X_3\right) \,dz}, \\
 p_{13} & = \frac{\int_{D_{13}}^\infty g\left(M_{13} + z, X_2, M_{13} - z\right) \,dz}{\int_{\max\left\{X_2 - M_{13}, 0\right\}}^\infty g\left(M_{13} + z, X_2, M_{13} - z\right) \,dz}
@@
 p_{12} & = \frac{\int_0^\infty g\left(X_1 + z, X_2 - z, X_3\right) \,dz}{\int_0^\infty g\left(M_{12} + z, M_{12} - z, X_3\right) \,dz} \\
-& = \frac{\int_0^\infty g\left(X_1 + z, X_2 - z, X_3\right) \,dz}{\int_{-D_{12}}^\infty g\left(X_1 + z, X_2 - z, X_3\right) \,dz} \\
+& = \frac{\int_0^\infty g\left(X_1 + z, X_2 - z, X_3\right) \,dz}{\int_{-D_{12}}^\infty g\left(X_1 + z, X_2 - z, X_3\right) \,dz}, \\
 p_{13} & = \frac{\int_0^\infty g\left(X_1 + z, X_2, X_3 - z\right) \,dz}{\int_0^\infty g\left(M_{13} + z, X_2, M_{13} - z\right) \,dz} \\
-& = \frac{\int_0^\infty g\left(X_1 + z, X_2, X_3 - z\right) \,dz}{\int_{-D_{13}}^\infty g\left(X_1 + z, X_2, X_3 - z\right) \,dz}
+& = \frac{\int_0^\infty g\left(X_1 + z, X_2, X_3 - z\right) \,dz}{\int_{-D_{13}}^\infty g\left(X_1 + z, X_2, X_3 - z\right) \,dz}.
 \end{align*}
@@
 
-\paragraph{3. $p_{12}$ is an unadjusted pairwise $p$-value}
+\paragraph{$p_{12}$ is an unadjusted pairwise $p$-value}
 
@@
 
+\paragraph{Modification for counting measure}
+
 Now suppose the exponential family is defined on the counting measure instead.
 If ties are broken independently and randomly, the end points on the rays can be considered as ``half an atom'' if the coordinates are integers, and a ``full atom'' otherwise.
-
 \end{proof}
@@
 \begin{equation}
-\PP_{H_{01}}\left(\text{reject } H_{01}\right) = \PP_{H_{01}}\left(\text{Winner is } 1\right) \PP_{H_{01}}\left(\text{reject } H_{01} \middle| \text{Winner is } 1\right) \le \frac{n-1}{n} \alpha,
+\PP_{H_{01}}\left(\text{reject } H_{01}\right) = \PP_{H_{01}}\left(\text{Winner is } 1\right) \PP_{H_{01}}\left(\text{reject } H_{01} \;\middle|\; \text{Winner is } 1\right) \le \frac{n-1}{n} \alpha,
 \label{eqn:marginal}
@@
 \end{theorem}
-\WFcomment{Are we sure this is a new result?} \KHcomment{Nothing found when I looked up a text for stochastic order, and on Google with ``stochastic order exponential family''}
 
@@
 Such difference is amplified when $n$ is large.
-The threshold from \citeauthor{Gupta:1967wg} increases with $n$ even if the added observations are all $0$.
-In such case, our threshold does not change at all, suggesting more potential test power.\WFcomment{Actually this isn't really why ours is more powerful.}
-
-\WFcomment{Is there any way we can get an asymptotic expression for $d$ in terms of $n$, as $m\to\infty$, and compare it to our procedure's ``effective $d$''?
-I suspect there is a $\log n$ factor in there that we don't have.} \KHcomment{We will need to get into details about $r^*$ to explain so, which seems like excessive details.
-I added some intuition on why our test it better.
-Not sure if it suffices.}
+When $n$ is large, $d$ from \citeauthor{Gupta:1967wg} is computed by considering the often-worst case scenario where $\pi = \left(\frac{1}{2}, \frac{1}{2}, 0, \ldots, 0\right)$.
+Hence $d$ is the $1-\alpha$ quantile of
+$$X_1 - X_2 \sim m - 2 \cdot \text{Binomial}\left(m, \frac{1}{2}\right) \approx \text{Normal}\left(0, m\right)$$
+and $d \approx \sqrt{m} z_\alpha$. On the other hand, our method defines a threshold based on the $1 - \frac{n}{n-1} \cdot \frac{\alpha}{2}$ quantile of
+$$X_1 - X_2 \mid X_1 + X_2 \sim X_1 + X_2 - 2 \cdot \text{Binomial}\left(X_1 + X_2, \frac{1}{2}\right),$$
+which is approximately $\sqrt{X_1 + X_2} z_{\alpha / 2}$.
+The smaller $\left(X_1 + X_2\right) / m$ is (e.g.\ if $\pi_1 + \pi_2$ is smaller), the more different the two thresholds are, suggesting that our test is more powerful.
 
@@
 $$H_{0[1]}^\delta = \bigcup_{j \ne [1]} H_{0[1]j}: \theta_{[1]} - \theta_j \le \delta.$$
-By \Cref{lma:union}, we can construct selective exact one-tailed $p$-values $p_{[1]j}^{(\delta)}$ \WFcomment{What do you think of attaching something like a superscript here to make it clear there are different $p$-values for every $\delta$?} for each of these by conditioning on $A_{[1]}$, $M_{[1]j}$ and $X_{\setminus\left\{[1], j\right\}}$, giving us an exact test for $H_{0[1]}$ by rejecting whenever $\max_{j \ne [1]} p_{[1]j}^{(\delta)} < \alpha$.
+By \Cref{lma:union}, we can construct selective exact one-tailed $p$-values $p_{[1]j}^\delta$ for each of these by conditioning on $A_{[1]}$, $M_{[1]j}$ and $X_{\setminus\left\{[1], j\right\}}$, giving us an exact test for $H_{0[1]}$ by rejecting whenever $\max_{j \ne [1]} p_{[1]j}^\delta < \alpha$.
 
 \begin{theorem}
-The $p$-values constructed above satisfy $p_{[1][2]}^{(\delta)} \ge p_{[1]j}^{(\delta)}$ for any $j \ne [1]$.
+The $p$-values constructed above satisfy $p_{[1][2]}^\delta \ge p_{[1]j}^\delta$ for any $j \ne [1]$.
 \end{theorem}
@@
 Again we start with assuming $X_1 \ge \cdots \ge X_n$. The $p$-values in question are derived from the conditional law
-$$\mathcal{L}_{\theta_1 - \theta_j = \delta} \left(D_{1j} \middle| M_{1j}, X_2, \ldots, X_n, A\right),$$
+$$\mathcal{L}_{\theta_1 - \theta_j = \delta} \left(D_{1j} \;\middle|\; M_{1j}, X_2, \ldots, X_n, A\right),$$
 which is the truncated distribution
@@
 The $p$-values thus are
-$$p_{1j} = \frac{\int_{D_{1j}}^\infty \exp\left(\delta z\right) g\left(M_{1j} + z, X_2, \ldots, M_{1j} - z, \ldots, X_n\right) \,dz}{\int_{\max\left\{X_2 - M_{1j}, 0\right\}}^\infty \exp\left(\delta z\right) g\left(M_{1j} + z, X_2, \ldots, M_{1j} - z, \ldots, X_n\right) \,dz}.$$
+$$p_{1j}^\delta = \frac{\int_{D_{1j}}^\infty \exp\left(\delta z\right) g\left(M_{1j} + z, X_2, \ldots, M_{1j} - z, \ldots, X_n\right) \,dz}{\int_{\max\left\{X_2 - M_{1j}, 0\right\}}^\infty \exp\left(\delta z\right) g\left(M_{1j} + z, X_2, \ldots, M_{1j} - z, \ldots, X_n\right) \,dz}.$$
 
@@
 \begin{align*}
-p_{12} & = \frac{\int_0^\infty \exp\left(\delta \left(z + D_{12}\right)\right) g\left(X_1 + z, X_2 - z, X_3\right) \,dz}{\int_{-D_{12}}^\infty \exp\left(\delta \left(z + D_{12}\right)\right) g\left(X_1 + z, X_2 - z, X_3\right) \,dz} \\
+p_{12}^\delta & = \frac{\int_0^\infty \exp\left(\delta \left(z + D_{12}\right)\right) g\left(X_1 + z, X_2 - z, X_3\right) \,dz}{\int_{-D_{12}}^\infty \exp\left(\delta \left(z + D_{12}\right)\right) g\left(X_1 + z, X_2 - z, X_3\right) \,dz} \\
 & = \frac{\int_0^\infty \exp\left(\delta z\right) g\left(X_1 + z, X_2 - z, X_3\right) \,dz}{\int_{-D_{12}}^\infty \exp\left(\delta z\right) g\left(X_1 + z, X_2 - z, X_3\right) \,dz} \\
-p_{13} & = \frac{\int_0^\infty \exp\left(\delta \left(z + D_{13}\right)\right) g\left(X_1 + z, X_2, X_3 - z\right) \,dz}{\int_{-D_{13}}^\infty \exp\left(\delta \left(z + D_{13}\right)\right) g\left(X_1 + z, X_2, X_3 - z\right) \,dz} \\
-& = \frac{\int_0^\infty \exp\left(\delta z\right) g\left(X_1 + z, X_2, X_3 - z\right) \,dz}{\int_{-D_{13}}^\infty \exp\left(\delta z\right) g\left(X_1 + z, X_2, X_3 - z\right) \,dz}
+p_{13}^\delta & = \frac{\int_0^\infty \exp\left(\delta \left(z + D_{13}\right)\right) g\left(X_1 + z, X_2, X_3 - z\right) \,dz}{\int_{-D_{13}}^\infty \exp\left(\delta \left(z + D_{13}\right)\right) g\left(X_1 + z, X_2, X_3 - z\right) \,dz} \\
+& = \frac{\int_0^\infty \exp\left(\delta z\right) g\left(X_1 + z, X_2, X_3 - z\right) \,dz}{\int_{-D_{13}}^\infty \exp\left(\delta z\right) g\left(X_1 + z, X_2, X_3 - z\right) \,dz}.
 \end{align*}
 
-The same argument in \Cref{fig:compare_rays} shows that $p_{12} \ge p_{13}$. This is again true for the case where $X_2 \ge M_{13}$ as well.
+The same argument in \Cref{fig:compare_rays} shows that $p_{12}^\delta \ge p_{13}^\delta$. This is again true for the case where $X_2 \ge M_{13}$ as well.
 \end{proof}
 
-In other words, Procedure 2' can be summarized as: Find the minimum $\delta$ such that $p_{[1][2]}^{(\delta)} \le \alpha$.
+In other words, Procedure 2' can be summarized as: Find the minimum $\delta$ such that $p_{[1][2]}^\delta \le \alpha$.
 And by construction, Procedure 2' gives exact $1-\alpha$ confidence bound for $\theta_{[1]} - \max_{j \ne [1]} \theta_j$.
@@
 \begin{proof}
-If the confidence bound $\delta^*$ is negative, we report $-\infty$ so it definitely is valid and conservative.
-On the other hand, if $\delta^* \ne 0$, then at $\delta^*$ the $p$-value $p_{12} = \alpha$.
-The denominator is the positive part of a positively skewed distribution, and thus bigger than half of the distribution.
-So the unadjusted pairwise test $p$-value from Procedure 2 comparing $X_1$ and $X_2$ is larger than $p_{12}$ from Procedure 2', rendering Procedure 2 conservative.
+When Procedure 2 reports $-\infty$ as a confidence lower bound, it is definitely valid and conservative.
+It remains to show that when Procedure 2 reports a finite confidence lower bound, it is smaller than the confidence lower bound reported by Procedure 2'.
 
-\WFcomment{I found this proof confusing.}
+If Procedure 2 reports a finite confidence lower bound $\delta^*$, then $\delta^* \ge 0$. Also
+\begin{equation}
+\frac{\alpha}{2} = \frac{\int_{D_{12}}^\infty \exp\left(\delta^* z\right) g\left(M_{12} + z, X_2, \ldots, M_{12} - z, \ldots, X_n\right) \,dz}{\int_{-\infty}^\infty \exp\left(\delta^* z\right) g\left(M_{12} + z, X_2, \ldots, M_{12} - z, \ldots, X_n\right) \,dz}
+\label{eq:naivelo}
+\end{equation}
+as Procedure 2 is constructed from an unadjusted two-tail pairwise confidence interval. However, as $\delta^* \ge 0$, we have
+\begin{align*}
+\frac{\int_{-\infty}^0 \exp\left(\delta^* z\right) g\left(M_{12} + z, X_2, \ldots, M_{12} - z, \ldots, X_n\right) \,dz}{\int_0^\infty \exp\left(\delta^* z\right) g\left(M_{12} + z, X_2, \ldots, M_{12} - z, \ldots, X_n\right) \,dz} & \le 1 \\
+\frac{\int_{-\infty}^\infty \exp\left(\delta^* z\right) g\left(M_{12} + z, X_2, \ldots, M_{12} - z, \ldots, X_n\right) \,dz}{\int_0^\infty \exp\left(\delta^* z\right) g\left(M_{12} + z, X_2, \ldots, M_{12} - z, \ldots, X_n\right) \,dz} & \le 2.
+\end{align*}
+Multiplying this to \eqref{eq:naivelo}, we have
+$$\alpha \ge \frac{\int_{D_{12}}^\infty \exp\left(\delta^* z\right) g\left(M_{12} + z, X_2, \ldots, M_{12} - z, \ldots, X_n\right) \,dz}{\int_0^\infty \exp\left(\delta^* z\right) g\left(M_{12} + z, X_2, \ldots, M_{12} - z, \ldots, X_n\right) \,dz},$$
+indicating that $\delta^*$ is smaller than the confidence bound that Procedure 2' would report. Hence $\delta^*$ is a valid and conservative.
 \end{proof}
@@
 In reality, we can always just adopt Procedure 2' in the case when Procedure 1 rejects.
-In fact, by Procedure 2', the multinomial example for polling in \Cref{sec:iowa} can give a stronger lower confidence bound, that $\log \pi_{\text{Trump}} - \max_{j \ne \text{Trump}} \log \pi_{j} \ge 0.103$.\WFcomment{0.103142 is a lot of sig.
-digits.}%142$.
+In fact, by Procedure 2', the multinomial example for polling in \Cref{sec:iowa} can give a stronger lower confidence bound, that $\log \pi_{\text{Trump}} - \max_{j \ne \text{Trump}} \log \pi_{j} \ge 0.103$.
 
@@
 
+We will first show that a less conservative Procedure 3' performs the above inference: Repeat while we can reject, a one-tail test for $\theta_{\left[j\right]} - \theta_{\left[j+1\right]} > 0$ based on comparing $X_{\left[j\right]}$ and $X_{\left[j+1\right]}$ conditioned on $\left\{X_{\left[j-1\right]} \ge X_{\left[j\right]} \ge \max_{k>j} X_{\left[k\right]}\right\}$ as well as $X_{\left[1\right]}, \ldots, X_{\left[j-1\right]}$.
+
 \begin{theorem}
-There is a step-down procedure, which we will denote as Procedure 3', that infers $j_0$ above with the FWER controlled at $\alpha$.
+Procedure 3' is a step-down procedure that infers $j_0$ above with the FWER controlled at $\alpha$.
 \end{theorem}
-\WFcomment{Probably better to define Procedure 3' outside the theorem?}
 
 \begin{proof}
-
 This can be fitted into the selective sequential model selection framework proposed by \citet{Fithian:2015uj}.
@@
 Alternatively, we can think of them as a sequence of nested model
-$$M_0\left(X\right) \subseteq M_1\left(X\right) \subseteq \cdots \subseteq M_n\left(X\right), ~~~~~~~~ M_j\left(X\right)^c = \left\{\theta_1 > \cdots > \theta_j > \max_{k > j} \theta_k\right\},$$
-\WFcomment{You're overloading the variable name $M$ here}
+$$\mathcal{M}_0\left(X\right) \subseteq \mathcal{M}_1\left(X\right) \subseteq \cdots \subseteq \mathcal{M}_n\left(X\right), ~~~~~~~~ \mathcal{M}_j\left(X\right)^c = \left\{\theta_1 > \cdots > \theta_j > \max_{k > j} \theta_k\right\},$$
+and the each $\mathcal{M}_j$ depends on $X$ through the order of $X$.
+The step-down procedure for rejecting $H_{0j}$ is equivalent to selecting the smallest $j$ for which we cannot reject $F \in \mathcal{M}_j\left(X\right)$.
 
-and the each $M_j$ depends on $X$ through the order of $X$.
-The step-down procedure for rejecting $H_{0j}$ is equivalent to selecting the smallest $j$ for which $F \in M_j\left(X\right)$.
-\WFcomment{More like the smallest $j$ for which we cannot reject...}
-
-We can construct selective $p$-values by conditioning on $M_j\left(X\right)$, as well as other nuisance parameters.
-Specifically, we are conditioning on the selection of the model $M_j\left(X\right)$.
+We can construct selective $p$-values by conditioning on $\mathcal{M}_j\left(X\right)$, as well as other nuisance parameters.
+Specifically, we are conditioning on the selection of the model $\mathcal{M}_j\left(X\right)$.
 We can take $p_j$ to be the survival function of the conditional law
 \begin{align}
-&~ \mathcal{L}_{\theta_j = \theta_{j+1}} \left(D_{j\left(j+1\right)} \middle| M_j\left(X\right), X_1, \ldots, X_{j-1}, M_{j\left(j+1\right)}, X_{j+2}, \ldots, X_n\right) \nonumber \\
-= &~ \mathcal{L}_{\theta_j = \theta_{j+1}} \left(D_{j\left(j+1\right)} \middle| \left\{X_1 > \ldots > X_j > \max_{k > j} X_k\right\}, X_1, \ldots, X_{j-1}, M_{j\left(j+1\right)}, X_{j+2}, \ldots, X_n\right) \nonumber \\
-= &~ \mathcal{L}_{\theta_j = \theta_{j+1}} \left(D_{j\left(j+1\right)} \middle| \left\{X_{j-1} > X_j > M_{j\left(j+1\right)}\right\}, X_1, \ldots, X_{j-1}, M_{j\left(j+1\right)}, X_{j+2}, \ldots, X_n\right).
+&~ \mathcal{L}_{\theta_j = \theta_{j+1}} \left(D_{j\left(j+1\right)} \;\middle|\; \mathcal{M}_j\left(X\right), X_1, \ldots, X_{j-1}, M_{j\left(j+1\right)}, X_{j+2}, \ldots, X_n\right) \nonumber \\
+= &~ \mathcal{L}_{\theta_j = \theta_{j+1}} \left(D_{j\left(j+1\right)} \;\middle|\; \left\{X_1 \ge \ldots \ge X_j \ge \max_{k > j} X_k\right\}, X_1, \ldots, X_{j-1}, M_{j\left(j+1\right)}, X_{j+2}, \ldots, X_n\right) \nonumber \\
+= &~ \mathcal{L}_{\theta_j = \theta_{j+1}} \left(D_{j\left(j+1\right)} \;\middle|\; \left\{X_{j-1} \ge X_j \ge M_{j\left(j+1\right)}\right\}, X_1, \ldots, X_{j-1}, M_{j\left(j+1\right)}, X_{j+2}, \ldots, X_n\right).
 \label{eqn:step_down_law}
@@
 	\draw[dashed] (0, 0) -- (C2);
-	\draw[dashed] (C5) -- (C6) node[midway, above, rotate = -90] {Truncation for $X_j < X_{j-1}$};
+	\draw[dashed] (C5) -- (C6) node[midway, above, rotate = -90] {Truncation for $X_j \le X_{j-1}$};
 	\fill[mid_green] (0, 0) -- (C1) -- (C5) -- (C6) -- (C2) -- cycle;
@@
 Here we are only comparing $X_j$ to $X_{j+1}$ by \Cref{sec:winnerbest}.
-The upper truncation for $X_j$ can be represented by cropping \Cref{fig:compare_rays} along a vertical line, shown in \Cref{fig:crop_rays}, thus the proof of Part 1 of \Cref{thm:main} on sufficiency\WFcomment{Careful about the word ``sufficiency'', it's a bit of a loaded term in stats} to compare $X_1$ and $X_2$ remains valid with appropriate conditioning.
+The upper truncation for $X_j$ can be represented by cropping \Cref{fig:compare_rays} along a vertical line, shown in \Cref{fig:crop_rays}, thus the proof of Part 1 of \Cref{thm:main} that it suffices to compare $X_1$ and $X_2$ remains valid with appropriate conditioning.
 Again we can construct the $p$-values as in \Cref{eqn:p1j} for $k>j$.
@@
 These are valid selective $p$-value as required in \citet{Fithian:2015uj}, as
-$$\PP_\theta \left(p_j \le \alpha \mid \theta_{[i]} \text{ is not the } i\text{th largest, some } i\leq j\right) \le \alpha \text{ a.s.}, \quad \forall \; \theta$$
-$$\PP_F \left(p_j \le \alpha \middle| M_{j-1}\left(X\right)\right) \le \alpha \text{ a.s.}, ~~~~~~~~ F \in M_{j-1}\left(X\right)$$
-by tower property. \WFcomment{Careful on notation again for ``$F\in M_{j-1}$,'' the right hand side is random.}
+$$\PP_\theta \left(p_j \le \alpha \mid \theta_{[k]} \text{ is not the } k\text{-th largest, for some } k \le j\right) \le \alpha \text{ a.s.}, ~~~~~~~~ \text{for all } \theta,$$
+by tower property.
+Note that the conditioning is indeed a random event as the order of $\theta$ depends on $X$ (emphasized with the square brackets here).
+\KHcomment{I should probably add a line transitioning from using $\mathcal{M}$ to suddenly mentioning $\theta$ here, shouldn't I?}
 
@@
 \begin{align*}
-\mathscr{F}_k & = \sigma\left(M_0\left(X\right), \ldots, M_j\left(X\right), X_1, \ldots, X_{j-1}, \frac{X_j + X_{j+1}}{2}, X_{j+2}, \ldots, X_n\right) \\
+\mathscr{F}_k & = \sigma\left(\mathcal{M}_0\left(X\right), \ldots, \mathcal{M}_j\left(X\right), X_1, \ldots, X_{j-1}, \frac{X_j + X_{j+1}}{2}, X_{j+2}, \ldots, X_n\right) \\
 & = \sigma\left(\left\{X_1 > \ldots > X_j > \max_{k>j} X_k\right\}, X_1, \ldots, X_{j-1}, \frac{X_j + X_{j+1}}{2}, X_{j+2}, \ldots, X_n\right) \\
-& = \sigma\left(M_j\left(X\right), X_1, \ldots, X_{j-1}, \frac{X_j + X_{j+1}}{2}, X_{j+2}, \ldots, X_n\right),
+& = \sigma\left(\mathcal{M}_j\left(X\right), X_1, \ldots, X_{j-1}, \frac{X_j + X_{j+1}}{2}, X_{j+2}, \ldots, X_n\right),
 \end{align*}
@@
 The authors' main finding --- which appeared in the abstract, the first paragraph of the article, and later a CNN.com headline --- was that ``Fame'' was the most common response.
-This claim was accompanied by a signficance level of $0.006$, which the authors computed by testing whether the probability of selecting ``Fame'' was larger than 1/7.
-
-\begin{comment}
-\begin{table}[htbp]
-\begin{center}
-\begin{tabular}{c c}
-	\hline
-	Value & Count \\
-	\hline
-	Achievement & $3$ \\
-	Benevolence & $5$ \\
-	Fame & $8$ \\
-	Community feeling & $2$ \\
-	Financial success & $1$ \\
-	Self-acceptance & $0$ \\
-	Image & $0$ \\
-	Other & $1$ \\
-	\hline
-\end{tabular}
-\end{center}
-\caption{The number of study participants who chose each value as their top desired one. Since only one option can be chosen, these observations are inherently multinomial.}
-\label{tbl:fame}
-\end{table}
-
-A sample of $20$ students from elementary and middle schools were asked to choose a top ``value'' from 7 different options: achievement, benevolence, fame, community feeling, financial success, self-acceptance, image and other.
-The results are tabulated in \Cref{tbl:fame}.
-The study postulates that fame is significantly the top value of choice.
-It proceeds to perform a binomial test for the null hypothesis that the participants chose among the $7$ options uniformly and concluded with a $p$-value of $0.006$ that fame is indeed the top desired value.
-The analysis failed to address the ``winner's curse'', as well as the dependence among the observations.
-
-We have provided a simple, powerful and straightforward test based on comparing the winner to the runner-up.
-
-comparing the number of ``Fame'' responses to the distribution
-
- --- perform a unadjusted (two-tailed) binomial test of the winner and the runner-up.
-In this case, we test if $8$ is a significant observation in $\text{Binomial}\left(8 + 5, 0.5\right)$.
-The two-tailed $p$-value is $0.580811$, suggesting that the study was inconclusive.
-\end{comment}
+This claim was accompanied by a significance level of $0.006$, which the authors computed by testing whether the probability of selecting ``Fame'' was larger than 1/7.
 
@@
 This test returns a $p$-value of
-\[
-p = 2\PP\left[\text{Binomial}\left(8 + 5, 0.5\right) \geq 8\right] = 0.58,
-\]
+$$p = 2\PP\left[\text{Binomial}\left(8 + 5, 0.5\right) \ge 8\right] = 0.58,$$
 indicating that their data did not support their major finding.
@@
 This paper has provided a straightforward yet powerful method for verifying that the winner is the best, for joint distributions in the exponential family with a mild technical condition.
-Such a test allows us to ``ignore'' the issues of selection and multiple-testing, which are often overlooked or mishandled.\WFcomment{This last sentence might give the wrong impression.}
+Such a test allows us to ``ignore'' the issues of selection and multiple-testing with relative ease and power.
+\WFcomment{This last sentence might give the wrong impression.}
 

### 2016-07-08 verifying-winner.tex
some minor edits and comments on paper

@@
 \begin{proof}
+The type I error --- the probability of incorrectly declaring anyone other than the best to be the best --- is
+\[
+\PP\left[\bigcup_{j \text{ not best}} \text{declare } j \text{ best}\right] \leq \sum_j \PP\left[ \text{declare } j \text{ best} \mid j \text{ wins}\right] \PP[j \text{ wins}].
+\]
+Because only one candidate can win (recall that ties are broken randomly), it is sufficient to show for each $j$ that 
+$\PP_{H_{0j}}\left[ \text{reject } H_{0j} \mid j \text{ wins}\right] \leq \alpha$.
+
 We start by assuming that we are working with the Lebesgue measure rather than the counting measure.
@@
 
-Here, we consider only the case where the winner is $1$ and the runner-up is $2$, etc., i.e.\ $X_1 \ge \cdots \ge X_n$ and that ties are broken uniformly.
+To avoid notational clutter, we consider only the case where the winner is $1$ and the runner-up is $2$, etc., i.e.\ $X_1 \ge \cdots \ge X_n$.
 For other cases, the following proof remains valid under relabeling.
-In this case, we will test the null hypothesis $H_{01}: \theta_1 \le \max_{j > 1} \theta_j$, which is the union of the null hypotheses $H_{01j}: \theta_1 \le \theta_j$ for $j > 1$.
-For each of these we can construct an exact $p$-value $p_{1j}$.
-Hence by \Cref{lma:union}, a test based on $p_{1*} = \max_j p_{1j}$ would be valid for $H_{01}$.
+In this case, we will test the null hypothesis $H_{01}: \theta_1 \le \max_{j > 1} \theta_j$, which is the union of the null hypotheses $H_{01j}: \theta_1 \le \theta_j$ for $j \ge 2$.
+For each of these we can construct an exact $p$-value $p_{1j}$, which is valid under $H_{01j}$ conditional on $A_1$, the event that $X_1$ is the winner.
+Hence by \Cref{lma:union}, a test based on $p_{1*} = \max_j p_{1j}$ would be valid for $H_{01}$ conditional on $A_1$.
 Procedure 1 performs an unadjusted pairwise test comparing $X_1$ to $X_2$.
@@
 \begin{equation}
-\mathcal{L}_{\theta_1 - \theta_j = 0} \left(D_{1j} \;\middle|\; M_{1j}, X_{\setminus\left\{1, j\right\}}, A_1\right), \text{ where } A_1 = \left\{D_{1j} \ge \max_{k \ne 1, j} X_k - M_{1j}\right\} \cap \left\{D_{1j} \ge 0\right\}.
+\mathcal{L}_{\theta_1 - \theta_j = 0} \left(D_{1j} \;\middle|\; M_{1j}, X_{\setminus\left\{1, j\right\}}, A_1\right).
 \label{eqn:condlaw}
 \end{equation}
+We can rewrite the selection event in terms of our new parameterization as
+\begin{align*}
+A_1 &= \left\{X_1 \ge X_j\right\} \cap \left\{X_1 \ge \max_{k \neq 1,j} X_k\right\}\\
+&= \left\{D_{1j} \ge 0\right\} \cap \left\{D_{1j} \ge \max_{k \ne 1, j} X_k - M_{1j}\right\}.
+\end{align*}
 The conditional law in \Cref{eqn:condlaw}, in particular, is a truncated distribution
 \begin{align*}
-p\left(D_{1j}\right) & \propto \exp\left(\left(\theta_1 - \theta_j\right) D_{1j} + \theta_2 X_2 + \cdots + \left(\theta_1 + \theta_j\right) M_{1j} + \cdots + \theta_n X_n \right) \\
+p\left(D_{1j} \mid \cdots\right) & \propto \exp\left(\left(\theta_1 - \theta_j\right) D_{1j} + \theta_2 X_2 + \cdots + \left(\theta_1 + \theta_j\right) M_{1j} + \cdots + \theta_n X_n \right) \\
 & ~~~~~~~~ g\left(M_{ij} + D_{ij}, X_2, \ldots, M_{ij} - D_{ij}, \ldots X_n\right) 1_{A_1} \\
@@
 If ties are broken independently and randomly, the end points on the rays can be considered as ``half an atom'' if the coordinates are integers, and a ``full atom'' otherwise.
+\WFcomment{It also relies on the atoms on the two rays ``matching up,'' right?}
 \end{proof}
@@
 When $n$ is large, $d$ from \citeauthor{Gupta:1967wg} is computed by considering the often-worst case scenario where $\pi = \left(\frac{1}{2}, \frac{1}{2}, 0, \ldots, 0\right)$.
-Hence $d$ is the $1-\alpha$ quantile of
+Hence $d$ is the $1-\alpha$ \WFcomment{$1-\alpha/2$?} quantile of
 $$X_1 - X_2 \sim m - 2 \cdot \text{Binomial}\left(m, \frac{1}{2}\right) \approx \text{Normal}\left(0, m\right)$$
-and $d \approx \sqrt{m} z_\alpha$. On the other hand, our method defines a threshold based on the $1 - \frac{n}{n-1} \cdot \frac{\alpha}{2}$ quantile of
+and $d \approx \sqrt{m} z_\alpha$ \WFcomment{where $z_\alpha$ is BLAH}. On the other hand, our method defines a threshold based on the $1 - \frac{n}{n-1} \cdot \frac{\alpha}{2}$ quantile of
 $$X_1 - X_2 \mid X_1 + X_2 \sim X_1 + X_2 - 2 \cdot \text{Binomial}\left(X_1 + X_2, \frac{1}{2}\right),$$

### 2016-07-08 verifying-winner.tex
minor fixes

@@
 Under $H_0$, one of the $H_{0j}$ is true. Suppose this is $H_{01}$. In this case,
-$$\PP\left(p_* \le \alpha\right) \le \PP\left(p_1 \le \alpha\right) \le \alpha.$$
+$$\PP\left[p_* \le \alpha\right] \le \PP\left[p_1 \le \alpha\right] \le \alpha.$$
 And thus $p_*$ is a valid $p$-value for the union null hypothesis.
-
 \end{proof}
@@
 \begin{proof}
-The type I error --- the probability of incorrectly declaring anyone other than the best to be the best --- is
-\[
-\PP\left[\bigcup_{j \text{ not best}} \text{declare } j \text{ best}\right] \leq \sum_j \PP\left[ \text{declare } j \text{ best} \mid j \text{ wins}\right] \PP[j \text{ wins}].
-\]
-Because only one candidate can win (recall that ties are broken randomly), it is sufficient to show for each $j$ that 
-$\PP_{H_{0j}}\left[ \text{reject } H_{0j} \mid j \text{ wins}\right] \leq \alpha$.
+The type I error --- the probability of incorrectly declaring any non-best to be the best --- is
+\begin{equation}
+\PP\left[\bigcup_{j \ne j^*} \text{declare } j \text{ best}\right] \le \sum_{j \ne j^*} \PP\left[\text{declare } j \text{ best} \;\middle|\; j \text{ wins}\right] \PP\left[j \text{ wins}\right],
+\label{eq:marginal}
+\end{equation}
+where $j^*$ is the best (fixed when the distribution is determined).
+The probability above is taken over all distributions where $j^*$ is the best.
+However, since there is exactly one winner at all times (recall that ties are broken at all times), it is sufficient to bound $\PP_{j^* \text{ is the best}}\left[ \text{declare } j \text{ best} \;\middle|\; j \text{ wins}\right]$, for each $j \ne j^*$.
+Since $j^*$ being the best implies that $j$ is not the best, it is, in turn, sufficient to show that
+$$\PP_{j \text{ is not the best}}\left[ \text{declare } j \text{ best} \;\middle|\; j \text{ wins}\right].$$
 
@@
 Finally, by construction, $p_{1j}$ satisfies
-$$\PP_{H_{01j}}\left(p_{1j} < \alpha \;\middle|\; M_{1j}, X_{\setminus\left\{1, j\right\}}, A_1\right) = \alpha.$$
+$$\PP_{H_{01j}}\left[p_{1j} < \alpha \;\middle|\; M_{1j}, X_{\setminus\left\{1, j\right\}}, A_1\right] = \alpha.$$
 Marginalizing over $M_{1j}, X_{\setminus\left\{1, j\right\}}$,
-$$\PP_{H_{01j}}\left(p_{1j} < \alpha \;\middle|\; A_1\right) = \alpha.$$
+$$\PP_{H_{01j}}\left[p_{1j} < \alpha \;\middle|\; A_1\right] = \alpha.$$
 Therefore these $p_{1j}$ are indeed valid $p$-values.
@@
 If ties are broken independently and randomly, the end points on the rays can be considered as ``half an atom'' if the coordinates are integers, and a ``full atom'' otherwise.
-\WFcomment{It also relies on the atoms on the two rays ``matching up,'' right?}
+The number of atoms on each ray is the same (after the extension $\tilde{A}$) and thus the atoms on each ray can be paired up.
+The inequalities above still hold for each pair of the atoms.
 \end{proof}
@@
 
-The selective type I error we opted to control for Procedure 1 offers the conventional, marginal type I error rate.
+The selective type I error we opted to control for Procedure 1 offers the conventional, marginal type I error rate, as shown in \eqref{eq:marginal}. More precisely with our notation in the proof,
 \begin{equation}
-\PP_{H_{01}}\left(\text{reject } H_{01}\right) = \PP_{H_{01}}\left(\text{Winner is } 1\right) \PP_{H_{01}}\left(\text{reject } H_{01} \;\middle|\; \text{Winner is } 1\right) \le \frac{n-1}{n} \alpha,
+\PP_{H_{01}}\left[\text{reject } H_{01}\right] = \PP_{H_{01}}\left[\text{Winner is } 1\right] \PP_{H_{01}}\left[\text{reject } H_{01} \;\middle|\; \text{Winner is } 1\right] \le \frac{n-1}{n} \alpha,
 \label{eqn:marginal}
@@
 Integrating both sides over the region $\left\{X: X_1 \ge a, X_2 < a\right\}$ gives
-$$\PP\left(X_1 \ge a, X_2 < a\right) \ge \PP\left(X_1 < a, X_2 \ge a\right).$$
-Now adding $\PP\left(X_1 \ge a, X_2 \ge a\right)$ to both probabilities gives
-$$\PP\left(X_1 \ge a\right) \ge \PP\left(X_2 \ge a\right),$$
+$$\PP\left[X_1 \ge a, X_2 < a\right] \ge \PP\left[X_1 < a, X_2 \ge a\right].$$
+Now adding $\PP\left[X_1 \ge a, X_2 \ge a\right]$ to both probabilities gives
+$$\PP\left[X_1 \ge a\right] \ge \PP\left[X_2 \ge a\right],$$
 meaning that $X_1$ is greater than $X_2$ in stochastic order.
@@
 \begin{equation}\label{eq:subsetsel}
-\PP\left(\argmax_j \pi_j \in J\left(X\right)\right) \ge 1 - \alpha.
+\PP\left[\argmax_j \pi_j \in J\left(X\right)\right] \ge 1 - \alpha.
 \end{equation}
@@
 When $n$ is large, $d$ from \citeauthor{Gupta:1967wg} is computed by considering the often-worst case scenario where $\pi = \left(\frac{1}{2}, \frac{1}{2}, 0, \ldots, 0\right)$.
-Hence $d$ is the $1-\alpha$ \WFcomment{$1-\alpha/2$?} quantile of
+Hence $d$ is the upper $\alpha$ quantile of
 $$X_1 - X_2 \sim m - 2 \cdot \text{Binomial}\left(m, \frac{1}{2}\right) \approx \text{Normal}\left(0, m\right)$$
-and $d \approx \sqrt{m} z_\alpha$ \WFcomment{where $z_\alpha$ is BLAH}. On the other hand, our method defines a threshold based on the $1 - \frac{n}{n-1} \cdot \frac{\alpha}{2}$ quantile of
+and $d \approx \sqrt{m} z_\alpha$, where $z_\alpha$ is the upper $\alpha$ quantile of a standard Gaussian.
+On the other hand, our method defines a threshold based on the upper $\frac{n}{n-1} \cdot \frac{\alpha}{2}$ quantile of
 $$X_1 - X_2 \mid X_1 + X_2 \sim X_1 + X_2 - 2 \cdot \text{Binomial}\left(X_1 + X_2, \frac{1}{2}\right),$$
@@
 $$\theta_{[1]} > \ldots > \theta_{[j]} > \max_{k>j} \theta_{[k]}.$$
-If $j_0$ is the true value of $j$, the FWER refers to $\PP\left(j \ne j_0\right)$.
+If $j_0$ is the true value of $j$, the FWER refers to $\PP\left[j \ne j_0\right]$.
 
@@
 These are valid selective $p$-value as required in \citet{Fithian:2015uj}, as
-$$\PP_\theta \left(p_j \le \alpha \mid \theta_{[k]} \text{ is not the } k\text{-th largest, for some } k \le j\right) \le \alpha \text{ a.s.}, ~~~~~~~~ \text{for all } \theta,$$
+$$\PP_\theta \left[p_j \le \alpha \mid \theta_{[k]} \text{ is not the } k\text{-th largest, for some } k \le j\right] \le \alpha \text{ a.s.}, ~~~~~~~~ \text{for all } \theta,$$
 by tower property.
@@
 This test returns a $p$-value of
-$$p = 2\PP\left[\text{Binomial}\left(8 + 5, 0.5\right) \ge 8\right] = 0.58,$$
+$$p = 2 \cdot \PP\left[\text{Binomial}\left(8 + 5, 0.5\right) \ge 8\right] = 0.58,$$
 indicating that their data did not support their major finding.

### 2016-07-08 verifying-winner.tex
minor fixes #2

@@
 The type I error --- the probability of incorrectly declaring any non-best to be the best --- is
-\begin{equation}
-\PP\left[\bigcup_{j \ne j^*} \text{declare } j \text{ best}\right] \le \sum_{j \ne j^*} \PP\left[\text{declare } j \text{ best} \;\middle|\; j \text{ wins}\right] \PP\left[j \text{ wins}\right],
-\label{eq:marginal}
-\end{equation}
+$$\PP\left[\bigcup_{j \ne j^*} \text{declare } j \text{ best}\right] \le \sum_{j \ne j^*} \PP\left[\text{declare } j \text{ best} \;\middle|\; j \text{ wins}\right] \PP\left[j \text{ wins}\right],$$
 where $j^*$ is the best (fixed when the distribution is determined).
@@
 Since $j^*$ being the best implies that $j$ is not the best, it is, in turn, sufficient to show that
-$$\PP_{j \text{ is not the best}}\left[ \text{declare } j \text{ best} \;\middle|\; j \text{ wins}\right].$$
+$$\PP_{j \text{ is not the best}}\left[ \text{declare } j \text{ best} \;\middle|\; j \text{ wins}\right] \le \alpha,$$
+giving us
+\begin{equation}
+\PP\left[\bigcup_{j \ne j^*} \text{declare } j \text{ best}\right] \le \sum_{j \ne j^*} \alpha \cdot \PP\left[j \text{ wins}\right] \le \frac{n-1}{n} \alpha.
+\label{eq:marginal}
+\end{equation}
 
@@
 As the construction of this test follows \citet{Fithian:2014ws}, it is also a UMPU selective level-$\alpha$ test.
-
-The selective type I error we opted to control for Procedure 1 offers the conventional, marginal type I error rate, as shown in \eqref{eq:marginal}. More precisely with our notation in the proof,
-\begin{equation}
-\PP_{H_{01}}\left[\text{reject } H_{01}\right] = \PP_{H_{01}}\left[\text{Winner is } 1\right] \PP_{H_{01}}\left[\text{reject } H_{01} \;\middle|\; \text{Winner is } 1\right] \le \frac{n-1}{n} \alpha,
-\label{eqn:marginal}
-\end{equation}
-because, under the hypothesis $H_{01}$, the probability of $1$, which is not the best population, winning is at most $\frac{n-1}{n}$.
-Selective type I error rate control provides more than just marginal type I error rate control.
+The selective type I error we opted to control for Procedure 1 offers more than just marginal type I error rate control.
 \citet{Fithian:2015uj} has shown that it helps controlling familywise error rate, which we will utilize in \Cref{sec:stepdown}.
@@
 for various combinations of $m$ and $n$.
-For their method, we use $\alpha = 0.05$; but in light of the extra factor of $\frac{n-1}{n}$ in \Cref{eqn:marginal}, we will apply the selective procedure with $\frac{n}{n-1} \alpha$ such that the marginal type I error rate of both procedures are controlled at $\alpha$.
+For their method, we use $\alpha = 0.05$; but in light of the extra factor of $\frac{n-1}{n}$ in \eqref{eq:marginal}, we will apply the selective procedure with $\frac{n}{n-1} \alpha$ such that the marginal type I error rate of both procedures are controlled at $\alpha$.
 Their test coincides with our test at $n = 2$; however as $n$ grows, the selective test shows significantly more power than \citeauthor{Gupta:1967wg}'s test.

### 2016-08-05 verifying-winner.tex
broken sentences fixed; unified notations

@@
 \begin{enumerate}
-\item {\em Is Trump really winning?} If Trump and Cruz were in fact tied, then Trump's share of their combined 490 votes would be distributed as $\text{Binom}\left(490, 0.5\right)$.
+\item {\em Is Trump really winning?} If Trump and Cruz were in fact tied, then Trump's share of their combined 490 votes would be distributed as $\text{Binomial}\left(490, 0.5\right)$.
 Because the (two-tailed) $p$-value for this pairwise test is $p = 0.006$, we reject the null and conclude that Trump is really winning.
@@
 Similarly, test the difference between the winner and the runner-up is enough.
-A follow-up paper by \citet{Maymin:1992fz} gave an analogous result for location-scale families, yet still under the constraints of independence as well.
+A follow-up paper by \citet{Maymin:1992fz} gave an analogous result for location-scale families, yet still under the constraints of independence.
 
 However, as location-scale families have limited overlap with exponential families, the counterpart question for exponential families remains unaddressed.
-Location-scale families assumes independence between observations, while this is not required in exponential families.
+Location-scale families assumes independence between observations, while this is not necessarily the case in exponential families.
 For instance, in the vicinity of the polling problem above, \citet{Nettleton:2009ht} provides an asymptotic test for multinomial distribution, imposing the selection by considering intersection-union tests.
@@
 
-One final result that our particular interest in the subset selection problem \citep{Gupta:1967wg}.
-It can indeed be used to solve the multinomial case.
-They select a subset that contains the largest, or ``tagged'', parameter with probability $1-\alpha$.
+One final result that has our attention is the subset selection problem \citep{Gupta:1967wg}.
+The procedure provided in the paper can indeed be used to solve the multinomial case.
+It selects a subset that contains the largest, or ``tagged'', parameter with probability $1-\alpha$.
 Confirming the largest parameter is thus equivalent to asserting the selected subset has size $1$.
@@
 To avoid notational clutter, we consider only the case where the winner is $1$ and the runner-up is $2$, etc., i.e.\ $X_1 \ge \cdots \ge X_n$.
-For other cases, the following proof remains valid under relabeling.
+For other cases, the following proof remains valid under relabeling and can thus be applied.
 In this case, we will test the null hypothesis $H_{01}: \theta_1 \le \max_{j > 1} \theta_j$, which is the union of the null hypotheses $H_{01j}: \theta_1 \le \theta_j$ for $j \ge 2$.
@@
 The inequalities above still hold for each pair of the atoms.
+Summing these inequalities yields our desired result.
 \end{proof}
@@
 Alternatively, we can think of them as a sequence of nested model
-$$\mathcal{M}_0\left(X\right) \subseteq \mathcal{M}_1\left(X\right) \subseteq \cdots \subseteq \mathcal{M}_n\left(X\right), ~~~~~~~~ \mathcal{M}_j\left(X\right)^c = \left\{\theta_1 > \cdots > \theta_j > \max_{k > j} \theta_k\right\},$$
+$$\mathcal{M}_0\left(X\right) \subseteq \mathcal{M}_1\left(X\right) \subseteq \cdots \subseteq \mathcal{M}_n\left(X\right), ~~~~~~~~ \mathcal{M}_j\left(X\right)^c = \left\{\theta_{[1]} > \cdots > \theta_{[j]} > \max_{k > j} \theta_{[k]}\right\},$$
 and the each $\mathcal{M}_j$ depends on $X$ through the order of $X$.
@@
 These are valid selective $p$-value as required in \citet{Fithian:2015uj}, as
-$$\PP_\theta \left[p_j \le \alpha \mid \theta_{[k]} \text{ is not the } k\text{-th largest, for some } k \le j\right] \le \alpha \text{ a.s.}, ~~~~~~~~ \text{for all } \theta,$$
-by tower property.
+\begin{align*}
+\PP_\theta \left[p_j \le \alpha \mid \theta_{[k]} \text{ is not the } k\text{-th largest, for some } k \le j\right] = \PP_\theta \left[p_j \le \alpha \mid \mathcal{M}_j\left(X\right)^c = M\right] \le \alpha \text{ a.s.},
+\end{align*}
+for all $\theta \in M$, where $M$ is the selected model, by tower property.
 Note that the conditioning is indeed a random event as the order of $\theta$ depends on $X$ (emphasized with the square brackets here).
-\KHcomment{I should probably add a line transitioning from using $\mathcal{M}$ to suddenly mentioning $\theta$ here, shouldn't I?}
 

### 2016-08-16 verifying-winner.tex
made some edits, added some comments

@@
 \setlist*[inlinelist,1]{label=(\arabic*)}
-\usepackage[totalwidth=480pt, totalheight=680pt]{geometry}
+\usepackage[totalwidth=450pt, totalheight=630pt]{geometry}
 \usepackage{graphicx}
@@
 \newtheorem{theorem}[corollary]{Theorem}
+
+\theoremstyle{definition}
+\newtheorem{example}{Example}
+
 \setlength{\tabcolsep}{1em}
@@
 
-Surprisingly, all of the three procedures described above are statistically valid despite ignoring the implicit multiple-comparisons issue.
+Surprisingly, all of the three procedures described above are statistically valid despite their ostensibly ignoring the implicit multiple-comparisons issue.
 The remainder of this article is dedicated to justifying these procedures for the multinomial family and analogous procedures in other settings.
@@
 We assume further that $g\left(x\right)$ is symmetric with respect to permutation, and Schur concave, a mild technical condition defined in \Cref{sec:maj}.
-In addition to the multinomial family, model~\eqref{eqn:expfam} also encompasses settings such as comparing independent binomial treatment outcomes in a clinical trial, competing sports teams under a Bradley--Terry model, entries of a Dirichlet distribution, and many more; see \Cref{sec:examples} for these and other examples.
+In addition to the multinomial family, model~\eqref{eqn:expfam} also encompasses settings such as comparing independent binomial treatment outcomes in a clinical trial, competing sports teams under a Bradley--Terry model, entries of a Dirichlet distribution, and many more; see \Cref{sec:maj} for these and other examples.
 
@@
 \end{enumerate}
-Procedure $2$ is modified above due to some technicalities. If reporting $-\infty$ seems extreme, we included a gentler modification in this paper as well.
+Procedure $2$ is modified above due to some technicalities; as we will see, reporting $-\infty$ is not really necessary because the bound can be improved with only a little more work.
 
@@
 \subsection{Related work}
+
+\WFcomment{Merge this discussion with my discussion from NSF.}
 
@@
 \subsection{Outline}
+
+\WFcomment{Rewrite for motivation}
+
 \Cref{sec:maj} gives a formal definition of Schur-concavity, as well as common examples satisfying this condition.
@@
 \begin{align*}
-a_{\left(1\right)} + \cdots + a_{\left(i\right)} & \ge b_{\left(1\right)} + \cdots + b_{\left(i\right)}, \\
-a_{\left(1\right)} + \cdots + a_{\left(n\right)} & = b_{\left(1\right)} + \cdots + b_{\left(n\right)}
+a_{\left(1\right)} + \cdots + a_{\left(i\right)} & \ge b_{\left(1\right)} + \cdots + b_{\left(i\right)}, \quad \text{and}\\
+a_{\left(1\right)} + \cdots + a_{\left(n\right)} & = b_{\left(1\right)} + \cdots + b_{\left(n\right)}.
 \end{align*}
@@
 
-\begin{lemma}
+\begin{lemma}~\\
 \begin{enumerate}
-\item Suppose $\left(x_1, x_2, x_3, \ldots\right)$ and $\left(x_1, x_2', x_3' \ldots\right)$ are two vectors in $\RR^n$. Then
-$$\left(x_1, x_2, x_3, \ldots\right) \succeq \left(x_1, x_2', x_3', \ldots\right) \text{ if and only if } \left(x_2, x_3, \ldots\right) \succeq \left(x_2', x_3', \ldots\right).$$
+\item Suppose $\left(x_1, x_2, x_3, \ldots\right)$ and $\left(x_1, y_2, y_3, \ldots\right)$ are two vectors in $\RR^n$. Then
+$$\left(x_1, x_2, x_3, \ldots\right) \succeq \left(x_1, y_2, y_3, \ldots\right) \text{ if and only if } \left(x_2, x_3, \ldots\right) \succeq \left(y_2, y_3, \ldots\right).$$
 \item (Principle of transfer) If $x_1 > x_2$ and $t \ge 0$, then
 $$\left(x_1 + t, x_2, x_3, \ldots\right) \succeq \left(x_1, x_2 + t, x_3, \ldots\right).$$
-If the $t \le 0$, the majorization is reversed.
+If $t \le 0$, the majorization is reversed.
 \end{enumerate}
@@
 
-\begin{proof}
+\begin{proof}~\\
 \begin{enumerate}
@@
 Conversely a symmetric and log-concave function is Schur-concave \citep{Marshall:2010hb}, thus many common exponential family distributions lie in this class.
-Schur-concave functions indeed appear a lot, \Cref{sec:examples} includes both continuous and discrete examples.
-
-\Cref{thm:main} requires that $g\left(x\right)$ in model~\eqref{eqn:expfam} to be Schur-concave.
-It was stated in the ensuing discussion that this condition is mild, and that the examples are abundant.
 To name a few:
 
-\subsection{Examples}
-\label{sec:examples}
-
-\begin{enumerate}
-\item Independent binomial treatment outcome in a clinical trial.
-If each of the $n$ different treatments are applied $m$ patients independently, the number of positive outcomes $X_j$ for treatment $j$ can be modeled by $\text{Binomial}\left(m, p_j\right)$.
+\begin{example}[Independent binomial treatment outcomes in a clinical trial]
+ If each of $n$ different treatments are applied to $m$ patients independently, the number of positive outcomes $X_j$ for treatment $j$ is $\text{Binomial}\left(m, p_j\right)$.
 The best treatment would be the treatment with the highest success probability $p_j$.
 The joint distribution of $X$ is given by
-$$p\left(x\right) \propto \exp\left(x' \left(\log p\right)\right) \frac{1}{x_1! \left(m-x_1\right)! \cdots x_n! \left(m-p_x\right)!}$$
+$$p\left(x\right) \propto \exp\left(x' \left(\log p\right)\right) \frac{1}{x_1! \left(m-x_1\right)! \cdots x_n! \left(m-p_n\right)!}$$
 The carrier measure above is Schur-concave.
+\end{example}
 
-\item Competitive sports under the Bradley--Terry model.
+\begin{example}[Competitive sports under the Bradley--Terry model]
   Suppose $n$ players compete in a round robin tournament, where player $j$ has ability $\theta_j$, and the probability of player $j$ winning against player $k$ is
@@
 Therefore, we can use Procedures 1--3 to compare player qualities.
+\end{example}
 
-\item Comparing the variances of different normal populations.
-Suppose there are $n$ normal populations with laws $N\left(\mu_j, \sigma_j^2\right)$ and $m$ independent observations from each of them.
+\begin{example}[Comparing the variances of different normal populations] Suppose there are $n$ normal populations with laws $N\left(\mu_j, \sigma_j^2\right)$ and $m$ independent observations from each of them.
 The sample variance for population $j$ can be denoted as $R_j$.
@@
 Thus, we can use Procedures 1--3 to find populations with the smallest or largest variances.
-\end{enumerate}
+\end{example}
 
@@
 
-The following lemma should clarify the key idea in the proof of the theorem.
+First, we justify the notion that the population with largest $\theta_j$ is also the largest population in stochastic order:
+\begin{theorem}
+\label{thm:stoch}
+For a multivariate exponential family with a symmetric carrier distribution, $X_1 \ge X_2$ in stochastic order if and only if $\theta_1 > \theta_2$.
+\end{theorem}
+
+\begin{proof}
+It suffices to prove the ``if'' part, as the ``only if'' part can be follows from swapping the role of $\theta_1$ and $\theta_2$.
+For any fixed $a$, and $X_1 \ge a$ and $X_2 < a$, we have $X_1 > X_2$ and
+$$\exp\left(\theta_1 X_1 + \theta_2 X_2 + \cdots + \theta_n X_n - \psi\left(\theta\right)\right) g\left(X\right) \ge \exp\left(\theta_1 X_2 + \theta_2 X_1 + \cdots + \theta_n X_n - \psi\left(\theta\right)\right) g\left(X\right).$$
+Integrating both sides over the region $\left\{X: X_1 \ge a, X_2 < a\right\}$ gives
+$$\PP\left[X_1 \ge a, X_2 < a\right] \ge \PP\left[X_1 < a, X_2 \ge a\right].$$
+Now adding $\PP\left[X_1 \ge a, X_2 \ge a\right]$ to both probabilities gives
+$$\PP\left[X_1 \ge a\right] \ge \PP\left[X_2 \ge a\right],$$
+meaning that $X_1$ is greater than $X_2$ in stochastic order.
+\end{proof}
+
+Before proving our main result for Procedure 1, we give the following lemma, which clarifies a key idea in the proof.
 
@@
 \begin{proof}
-Under $H_0$, one of the $H_{0j}$ is true. Suppose this is $H_{01}$. In this case,
+Under $H_0$, one of the $H_{0j}$ is true; without loss of generality assume it is $H_{01}$. Then,
 $$\PP\left[p_* \le \alpha\right] \le \PP\left[p_1 \le \alpha\right] \le \alpha.$$
-And thus $p_*$ is a valid $p$-value for the union null hypothesis.
+Therefore $p_*$ is a valid $p$-value for the union null hypothesis.
 \end{proof}
 
-We are now ready to prove our result for Procedure 1.
+We are now ready to prove our result for Procedure 1, restated here for reference.
 
@@
 \begin{proof}
-The type I error --- the probability of incorrectly declaring any non-best to be the best --- is
+Let $j^*$ denote the (fixed) index of the best population, so $\theta_{j^*} \geq \max_{j\neq j^*} \theta_j$.
+The type I error --- the probability of incorrectly declaring any other $j$ to be the best --- is
 $$\PP\left[\bigcup_{j \ne j^*} \text{declare } j \text{ best}\right] \le \sum_{j \ne j^*} \PP\left[\text{declare } j \text{ best} \;\middle|\; j \text{ wins}\right] \PP\left[j \text{ wins}\right],$$
-where $j^*$ is the best (fixed when the distribution is determined).
-The probability above is taken over all distributions where $j^*$ is the best.
-However, since there is exactly one winner at all times (recall that ties are broken at all times), it is sufficient to bound $\PP_{j^* \text{ is the best}}\left[ \text{declare } j \text{ best} \;\middle|\; j \text{ wins}\right]$, for each $j \ne j^*$.
-Since $j^*$ being the best implies that $j$ is not the best, it is, in turn, sufficient to show that
-$$\PP_{j \text{ is not the best}}\left[ \text{declare } j \text{ best} \;\middle|\; j \text{ wins}\right] \le \alpha,$$
-giving us
+recalling that ties are broken randomly, so there is only one winner in any realization.
+Thus, it is enough to bound $\PP_{\theta}\left[ \text{declare } j \text{ best} \;\middle|\; j \text{ wins}\right] \leq \alpha$, for each $j \ne j^*$, and for all $\theta$ with $j^* \in \argmax_j \theta_j$.
+Then we will have
 \begin{equation}
-\PP\left[\bigcup_{j \ne j^*} \text{declare } j \text{ best}\right] \le \sum_{j \ne j^*} \alpha \cdot \PP\left[j \text{ wins}\right] \le \frac{n-1}{n} \alpha.
+\PP\left[\bigcup_{j \ne j^*} \text{declare } j \text{ best}\right] \le \sum_{j \ne j^*} \alpha \cdot \PP\left[j \text{ wins}\right] \le \frac{n-1}{n} \alpha,
 \label{eq:marginal}
 \end{equation}
+where the second inequality uses the stochastic ordering on $X_j$. \WFcomment{Should we put that Prop. first? Also I'm not sure it quite justifies the second inequality.}
 
-We start by assuming that we are working with the Lebesgue measure rather than the counting measure.
+We start by assuming that we are working with the Lebesgue measure rather than the counting measure (eliminating the possibility of ties).
 The necessary modification of the proof for the counting measure case is provided at the end of this proof.
 
-To avoid notational clutter, we consider only the case where the winner is $1$ and the runner-up is $2$, etc., i.e.\ $X_1 \ge \cdots \ge X_n$.
+To minimize notational clutter, we consider only the case where the winner is $1$ and the runner-up is $2$, etc., i.e.\ $X_1 \ge \cdots \ge X_n$.
 For other cases, the following proof remains valid under relabeling and can thus be applied.
@@
 For each of these we can construct an exact $p$-value $p_{1j}$, which is valid under $H_{01j}$ conditional on $A_1$, the event that $X_1$ is the winner.
-Hence by \Cref{lma:union}, a test based on $p_{1*} = \max_j p_{1j}$ would be valid for $H_{01}$ conditional on $A_1$.
+Hence by \Cref{lma:union}, a test that rejects when $p_{1*} = \max_j p_{1j} \leq \alpha$ is valid for $H_{01}$ conditional on $A_1$.
 Procedure 1 performs an unadjusted pairwise test comparing $X_1$ to $X_2$.
-Hence it is sufficient to show that $p_{12} = p_{1*}$ and that the test based on $p_{12}$ coincides with the unadjusted pairwise test.
+Hence it is sufficient to show that $p_{12} = p_{1*}$ and that rejecting when $p_{12}\leq \alpha$ coincides with the unadjusted pairwise test.
 
@@
 \end{align*}
+\WFcomment{This notation is confusing because there should also be another indicator that $M_{ij}=m_{ij}$ where $m_{ij}$ is the realized value this time, also for $X_{\setminus\left\{1,j\right\}}=x_{\cdots}$.}
 where at step (a), conditioning on $X_{\setminus\left\{1, j\right\}}$ and $M_{1j}$ removes dependence on $\theta_{\setminus\left\{1, j\right\}}$ and $\theta_1 + \theta_j$ respectively, while $\theta_1 - \theta_j$ is taken to be $0$ under our null hypothesis.
@@
 Finally, by construction, $p_{1j}$ satisfies
-$$\PP_{H_{01j}}\left[p_{1j} < \alpha \;\middle|\; M_{1j}, X_{\setminus\left\{1, j\right\}}, A_1\right] = \alpha.$$
-Marginalizing over $M_{1j}, X_{\setminus\left\{1, j\right\}}$,
-$$\PP_{H_{01j}}\left[p_{1j} < \alpha \;\middle|\; A_1\right] = \alpha.$$
+$$\PP_{H_{01j}}\left[p_{1j} < \alpha \;\middle|\; M_{1j}, X_{\setminus\left\{1, j\right\}}, A_1\right] \le \alpha,$$
+almost surely. Marginalizing over $M_{1j}, X_{\setminus\left\{1, j\right\}}$,
+$$\PP_{H_{01j}}\left[p_{1j} < \alpha \;\middle|\; A_1\right] \le \alpha.$$
 Therefore these $p_{1j}$ are indeed valid $p$-values.
@@
 $$g_{X_4, \ldots, X_n}\left(X_1, X_2, X_3\right) = g\left(X_1, \ldots, X_n\right).$$
+\WFcomment{What does the subscripting mean?}
 The first point in \Cref{lma:twoprop} says that the function $g_{X_4, \ldots, X_n}$ is Schur-concave as well.
@@
 
-We shall henceforth focus on the case when $n = 3$. The p-values thus are
+We have reduced to the case when $n = 3$. The p-values thus are
 \begin{align*}
@@
 First, we suppose $X_2 < M_{13}$.
-Changing variables such that the lower limits of both integrals in the numerator is $0$, we can re-parametrize the integrals above to give
+Changing variables such that the lower limits of both integrals in the numerator are $0$, we can re-parametrize the integrals above to give
 \begin{align*}
@@
 
-Since the denominator of $p_{12}$ is half of the symmetric distribution before truncation, a one-sided test that rejects based on $p_{12}$ is identical to the naive unadjusted pairwise test comparing $X_1$ and $X_2$.
-The naive unadjusted pairwise test is indeed valid.
+Before conditioning on $A_1$, the distribution in \label{eqn:condlaw} is symmetric around 0 under $\theta_1=\theta_j$.
+Since the denominator of $p_{12}$ integrates over half of this symmetric distribution, it is always equal to $1/2$.
+Thus, the one-sided conditional test at level $\alpha$ is equivalent to the one-sided unadjusted test at level $\alpha/2$, or equivalently the two-sided unadjusted pairwise test at level $\alpha$.
 
@@
 Now suppose the exponential family is defined on the counting measure instead.
-If ties are broken independently and randomly, the end points on the rays can be considered as ``half an atom'' if the coordinates are integers, and a ``full atom'' otherwise.
-The number of atoms on each ray is the same (after the extension $\tilde{A}$) and thus the atoms on each ray can be paired up.
-The inequalities above still hold for each pair of the atoms.
+If ties are broken independently and randomly, the end points on the rays can be considered as ``half an atom'' if the coordinates are integers (or a smaller fraction of an atom in case of a multi-way tie).
+The number of atoms on each ray is the same (after the extension $\tilde{A}$) and the atoms on each ray can be paired up in exactly the same way as illustrated in Figure~\ref{fig:compare_rays}, with the inequalities above still holding for each pair of the atoms.
 Summing these inequalities yields our desired result.
-\end{proof}
-
-As the construction of this test follows \citet{Fithian:2014ws}, it is also a UMPU selective level-$\alpha$ test.
-The selective type I error we opted to control for Procedure 1 offers more than just marginal type I error rate control.
-\citet{Fithian:2015uj} has shown that it helps controlling familywise error rate, which we will utilize in \Cref{sec:stepdown}.
-
-Finally, comparing the parameters $\theta_j$ has an even more appealing interpretation:
-
-\begin{theorem}
-\label{thm:stoch}
-For a multivariate exponential family with a symmetric carrier distribution, $X_1 \ge X_2$ in stochastic order if and only if $\theta_1 > \theta_2$.
-\end{theorem}
-
-\begin{proof}
-It suffices to prove the ``if'' part, as the ``only if'' part can be follows from swapping the role of $\theta_1$ and $\theta_2$.
-For any fixed $a$, and $X_1 \ge a$ and $X_2 < a$, we have $X_1 > X_2$ and
-$$\exp\left(\theta_1 X_1 + \theta_2 X_2 + \cdots + \theta_n X_n - \psi\left(\theta\right)\right) g\left(X\right) \ge \exp\left(\theta_1 X_2 + \theta_2 X_1 + \cdots + \theta_n X_n - \psi\left(\theta\right)\right) g\left(X\right).$$
-Integrating both sides over the region $\left\{X: X_1 \ge a, X_2 < a\right\}$ gives
-$$\PP\left[X_1 \ge a, X_2 < a\right] \ge \PP\left[X_1 < a, X_2 \ge a\right].$$
-Now adding $\PP\left[X_1 \ge a, X_2 \ge a\right]$ to both probabilities gives
-$$\PP\left[X_1 \ge a\right] \ge \PP\left[X_2 \ge a\right],$$
-meaning that $X_1$ is greater than $X_2$ in stochastic order.
 \end{proof}
@@
 
-\citet{Gupta:1967wg} devises a rule to select a subset that includes the maximum $\pi_j$. In other words, if the selected subset is $J\left(X\right)$, it guarantees
+As the construction of this test follows \citet{Fithian:2014ws}, it uses UMPU selective level-$\alpha$ tests for the pairwise $p$-values.
+This section compares the power of our procedure to the best previously known method for verifying multinomial ranks, by \citet{Gupta:1967wg}.
+They devise a rule to select a subset that includes the maximum $\pi_j$.
+In other words, if the selected subset is $J\left(X\right)$, it guarantees
 \begin{equation}\label{eq:subsetsel}
@@
 $$J\left(X\right) = \left\{j: X_j \ge \max_k X_k - d\right\}.$$
-Here, we take $d(m, n, \alpha)$ to be the smallest integer such that \eqref{eq:subsetsel} holds for any $\pi$.
+We take $d(m, n, \alpha)$ to be the smallest integer such that \eqref{eq:subsetsel} holds for any $\pi$; \citet{Gupta:1967wg} provide an algorithm for determining $d$.
 
-It also provides the algorithm computing $d$.
 Subset selection is closely related to testing whether the winner is the best.
@@
 
-To interpret, e.g., the lower left plot, suppose that in a poll of $m = 50$ respondents, one candidate enjoys $30\%$ support and the other $n - 1 = 9$ split the remainder ($\delta = \log\frac{0.3}{0.7 / 9} \approx 1.35$).
+To interpret, e.g., the upper right panel of Figure~\ref{fig:power}, suppose that in a poll of $m = 50$ respondents, one candidate enjoys $30\%$ support and the other $n - 1 = 9$ split the remainder ($\delta = \log\frac{0.3}{0.7 / 9} \approx 1.35$).
 Then our procedure has power approximately $0.3$ to detect the best candidate, while \citeauthor{Gupta:1967wg}'s procedure has power around $0.1$.
 
-A fundamental difference between the two methods is the definition of the threshold.
-The threshold from \citet{Gupta:1967wg} depends solely on the setup of the model: $m$ and $n$.
-Our threshold, however, depends on the data itself.
-Such difference is amplified when $n$ is large.
-When $n$ is large, $d$ from \citeauthor{Gupta:1967wg} is computed by considering the often-worst case scenario where $\pi = \left(\frac{1}{2}, \frac{1}{2}, 0, \ldots, 0\right)$.
-Hence $d$ is the upper $\alpha$ quantile of
-$$X_1 - X_2 \sim m - 2 \cdot \text{Binomial}\left(m, \frac{1}{2}\right) \approx \text{Normal}\left(0, m\right)$$
-and $d \approx \sqrt{m} z_\alpha$, where $z_\alpha$ is the upper $\alpha$ quantile of a standard Gaussian.
+To understand why our method is more powerful, note that both procedures operate by comparing $X_{[1]}-X_{[2]}$ to some threshold, but the two methods differ in how that threshold is determined.
+The threshold from \citet{Gupta:1967wg} is fixed and depends on $m$ and $n$ alone, whereas in our procedure the threshold depends on $X_{[1]}+X_{[2]}$, a data-adaptive choice.
+
+The difference between the two methods is amplified when $n$ is large and $\pi_{[1]} \ll 1/2$.
+In that case, $d$ from \citeauthor{Gupta:1967wg} is usually computed based on the worst-case scenario $\pi = \left(\frac{1}{2}, \frac{1}{2}, 0, \ldots, 0\right)$; i.e.
+$d$ is the upper $\alpha$ quantile of
+$$X_1 - X_2 \sim m - 2 \cdot \text{Binomial}\left(m, \frac{1}{2}\right) \approx \text{Normal}\left(0, m\right).$$
+Thus $d \approx \sqrt{m} z_\alpha$, where $z_\alpha$ is the upper $\alpha$ quantile of a standard Gaussian.
 On the other hand, our method defines a threshold based on the upper $\frac{n}{n-1} \cdot \frac{\alpha}{2}$ quantile of
 $$X_1 - X_2 \mid X_1 + X_2 \sim X_1 + X_2 - 2 \cdot \text{Binomial}\left(X_1 + X_2, \frac{1}{2}\right),$$
-which is approximately $\sqrt{X_1 + X_2} z_{\alpha / 2}$.
-The smaller $\left(X_1 + X_2\right) / m$ is (e.g.\ if $\pi_1 + \pi_2$ is smaller), the more different the two thresholds are, suggesting that our test is more powerful.
+which is approximately $\sqrt{X_1 + X_2} z_{\alpha / 2}$. If $\pi_{[1]} \ll 1/2$ then with high probability $X_1 + X_2 \ll  m$, making our test much more liberal.
 
@@
 
-Note that Procedure 2 reporting $-\infty$ in case of $\delta^*$ is rather extreme.
+Note that Procedure 2 reporting $-\infty$ in case of $\delta^*\leq 0$ is rather extreme.
 In reality, we can always just adopt Procedure 2' in the case when Procedure 1 rejects.
-In fact, by Procedure 2', the multinomial example for polling in \Cref{sec:iowa} can give a stronger lower confidence bound, that $\log \pi_{\text{Trump}} - \max_{j \ne \text{Trump}} \log \pi_{j} \ge 0.103$.
+In fact, by Procedure 2', the multinomial example for polling in \Cref{sec:iowa} can give a stronger lower confidence bound, that $\pi_{\text{Trump}} \geq \max_{j \ne \text{Trump}} \pi_{j} \geq 1.108$ (Trump leads the field by at least $10.8\%$).
 
@@
 \label{sec:stepdown}
+\WFcomment{This whole section is too vague.
+The procedure, and even the decision problem, are not that familiar to most readers so they need to be set out very explicitly.
+I tried to improve this a bit but parts still need more work.}
 
-If one is interested in verifying more than just the ``winner'', this selective test can also be extended to a step-down procedure that verifies the ``first runner-up'' and ``second runner-up'' etc., while controlling the FWER.
+Often we will be interested in verifying ranks beyond the winner. More generally, we could imagine declaring that the first $j$ candidates are all in the correct order, that is
+\begin{equation}\label{eq:jrankscorrect}
+\theta_{[1]} > \ldots > \theta_{[j]} > \max_{k>j} \theta_{[k]}.
+\end{equation}
+Let $j_0$ denote the largest $j$ for which~\eqref{eq:jrankscorrect} is true.
+Note that $j_0$ is both random and unknown, because it depends on both the data and population ranks.
+Procedure 3 declares that $j_0 \geq j$ if the unadjusted pairwise tests between $X_{[k]}$ and $X_{[k+1]}$, reject at level $\alpha$ for {\em all} of $k=1,\ldots,j$.
 
-Formally, we wish to find the biggest $j$ such that we can infer
-$$\theta_{[1]} > \ldots > \theta_{[j]} > \max_{k>j} \theta_{[k]}.$$
-If $j_0$ is the true value of $j$, the FWER refers to $\PP\left[j \ne j_0\right]$.
+Let $\hat{j}$ denote the number of ranks validated by a procedure (the number of rejections).
+Then the FWER of $\hat{j}$ is the probability that too many rejections are made; i.e.
+$\PP\left[\hat{j} > j_0\right]$.
+For example, suppose that the top three data ranks and population ranks coincide, but not the fourth ($j_0=3$).
+Then we will have made a Type I error if we declare that the top five ranks are correct ($\hat{j}=5$), but not if we declare that the top two are correct ($\hat{j}=2$).
 
-We will first show that a less conservative Procedure 3' performs the above inference: Repeat while we can reject, a one-tail test for $\theta_{\left[j\right]} - \theta_{\left[j+1\right]} > 0$ based on comparing $X_{\left[j\right]}$ and $X_{\left[j+1\right]}$ conditioned on $\left\{X_{\left[j-1\right]} \ge X_{\left[j\right]} \ge \max_{k>j} X_{\left[k\right]}\right\}$ as well as $X_{\left[1\right]}, \ldots, X_{\left[j-1\right]}$.
+To show that Procedure 3 is valid, we will prove the validity of a more liberal Procedure 3', described below.
+
+\WFcomment{Need to describe this procedure more explicitly. Try using the algorithm2e package.}
+Repeat while we can reject, a one-tail test for $\theta_{\left[j\right]} - \theta_{\left[j+1\right]} > 0$ based on comparing $X_{\left[j\right]}$ and $X_{\left[j+1\right]}$ conditioned on $\left\{X_{\left[j-1\right]} \ge X_{\left[j\right]} \ge \max_{k>j} X_{\left[k\right]}\right\}$ as well as $X_{\left[1\right]}, \ldots, X_{\left[j-1\right]}$.
 
@@
 Procedure 3' is a step-down procedure that infers $j_0$ above with the FWER controlled at $\alpha$.
+\WFcomment{``Infers'' is too vague. We need to say exactly what is true of the procedure, in rigorous mathematical terms.}
 \end{theorem}
@@
 \begin{proof}
-This can be fitted into the selective sequential model selection framework proposed by \citet{Fithian:2015uj}.
-Given the observations $X_1 \ge \cdots \ge X_n$, drawn from an unknown distribution $F$, we consider the following sequence of null hypotheses:
-$$H_{0j}: \theta_j \le \max_{k > j} \theta_k.$$
-Alternatively, we can think of them as a sequence of nested model
-$$\mathcal{M}_0\left(X\right) \subseteq \mathcal{M}_1\left(X\right) \subseteq \cdots \subseteq \mathcal{M}_n\left(X\right), ~~~~~~~~ \mathcal{M}_j\left(X\right)^c = \left\{\theta_{[1]} > \cdots > \theta_{[j]} > \max_{k > j} \theta_{[k]}\right\},$$
-and the each $\mathcal{M}_j$ depends on $X$ through the order of $X$.
-The step-down procedure for rejecting $H_{0j}$ is equivalent to selecting the smallest $j$ for which we cannot reject $F \in \mathcal{M}_j\left(X\right)$.
+This problem falls into the sequential goodness-of-fit testing framework proposed by \citet{Fithian:2015uj}.
+Given the observations $X_{[1]} \ge \cdots \ge X_{[n]}$, define the $j$th null hypothesis as
+$$\widetilde{H}_{0j}: \theta_{[j]} \le \max_{k > j} \theta_{[k]}.$$
 
-We can construct selective $p$-values by conditioning on $\mathcal{M}_j\left(X\right)$, as well as other nuisance parameters.
-Specifically, we are conditioning on the selection of the model $\mathcal{M}_j\left(X\right)$.
+$\widetilde{H}_{01},\ldots,\widetilde{H}_{0j}$ are all false if and only if $\theta\notin \mathcal{M}_j(X)$, where the $\mathcal{M}_j$ represent a sequence of nested models:
+$$\mathcal{M}_1\left(X\right) \subseteq \cdots \subseteq \mathcal{M}_n\left(X\right), \quad\text{ where }~~ \mathcal{M}_j\left(X\right)^c = \left\{\theta:\; \theta_{[1]} > \cdots > \theta_{[j]} > \max_{k > j} \theta_{[k]}\right\}.$$
+Thus, returning $\hat{j}=j$ amounts to rejecting $\widetilde{H}_{01},\ldots,\widetilde{H}_{0j}$, or equivalently determining that the models $\mathcal{M}_1(X),\ldots,\mathcal{M}_j(X)$ do {\em not} fit the data.
+
+\WFcomment{The rest of this proof seems correct but is hard to follow. Can you try to go through and clean it up a bit?}
+
+We can construct selective $p$-values by conditioning on $\mathcal{M}_j\left(X\right)$, as well as other nuisance parameters \WFcomment{We condition on data, not parameters}.
+Specifically, we are conditioning on the selection of the model $\mathcal{M}_j\left(X\right)$ \WFcomment{Why?
+Also, we are conditioning on more things as well.}.
 We can take $p_j$ to be the survival function of the conditional law
@@
 \end{align}
+\WFcomment{Why does all this work? Maybe cite a specific theorem in Fithian et al. (2015)?}
 
@@
 which is the conditioning we used just now.
-Hence the nested sequence of model satisfies the subpath sufficiency principle, and the $p$-values sequence $p_j$ is independent on nulls, as defined in and shown in Theorem 4 of \citet{Fithian:2015uj}.
+Hence the nested sequence of model satisfies the subpath sufficiency principle , and the $p$-values sequence $p_j$ is independent on nulls, as defined in and shown in Theorem 4 of \citet{Fithian:2015uj}.
 Thus the step-down procedure where we keep rejecting $H_{0j}$ until the first time that $p_j > \alpha$ controls FWER.
+
+\WFcomment{Should the reference to SSP be earlier if you are going to say it?
+Also, is it actually necessary to bring up the SSP?
+You've already said directly that we are conditioning on $X_{[1]}$ through $X_{[j-1]}$.
+More generally, if we can sidestep the more generic langauge of that paper and substitute more specific language for our specific problem, I think that will make this a lot more readable.}
 \end{proof}
@@
 \label{sec:disc}
+
+\WFcomment{Discussion still needs fleshing out.}
 

### 2016-08-22 verifying-winner.tex
Easy fixes

@@
 \usepackage{amsthm}
+\usepackage[linesnumbered, ruled]{algorithm2e}
 \usepackage{caption}
@@
 \newlist{inlinelist}{enumerate*}{1}
-\setlist*[inlinelist,1]{label=(\arabic*)}
+\setlist*[inlinelist]{label=(\arabic*)}
 \usepackage[totalwidth=450pt, totalheight=630pt]{geometry}
@@
 If we instead based our tests on an independent realization $X^*$, then, for example, Procedure 1 could use a right-tailed version of the unadjusted pairwise test.
-In the case $n = 2$, Procedure 1 amounts to a simple two-tailed test of the null hypothesis $\theta_1 = \theta_2$, and it is intuitively clear that a one-tailed test would be anti-conservative.
+In the case $n = 2$, Procedure 1 amounts to a simple two-tailed test of the null hypothesis $\theta_1 = \theta_2$, and it is intuitively clear that a one-tailed test would be more liberal.
 More surprising is that, no matter how large $n$ is, Procedures 1--3 require no further adjustment beyond what is required when $n = 2$.
@@
 \item The property follows from an equivalent formulation of majorization listed in \citet{Marshall:2010hb}, where $x \succeq y$ if and only if
-$$\sum_{j=1}^n x_n = \sum_{j=1}^n y_n ~~~~ \text{ and } ~~~~ \sum_{j=1}^n \left(x_j - a\right)_+ \ge \sum_{j=1}^n \left(y_j - a\right)_+ \text{ for all } a \in \RR.$$
+$$\sum_{j=1}^n x_n = \sum_{j=1}^n y_n \quad \text{ and } \quad \sum_{j=1}^n \left(x_j - a\right)_+ \ge \sum_{j=1}^n \left(y_j - a\right)_+ \text{ for all } a \in \RR.$$
 
@@
 \begin{theorem}
+For a multivariate exponential family with a symmetric carrier distribution, $X_1 \ge X_2$ in stochastic order if and only if $\theta_1 > \theta_2$.
 \label{thm:stoch}
-For a multivariate exponential family with a symmetric carrier distribution, $X_1 \ge X_2$ in stochastic order if and only if $\theta_1 > \theta_2$.
 \end{theorem}
@@
 
-Before proving our main result for Procedure 1, we give the following lemma, which clarifies a key idea in the proof.
+Before proving our main result for Procedure 1, we give the following lemmas, the first of which clarifies a key idea in the proof, and the second is needed for a sharper bound in \eqref{eq:marginal}.
 
@@
 Therefore $p_*$ is a valid $p$-value for the union null hypothesis.
+\end{proof}
+
+\begin{lemma}
+If $\theta_1 \ge \max_{j \ne 1} \theta_j$, then $\PP\left[1 \text{ wins}\right] \ge \frac{1}{n}$.
+\label{lma:margsharp}
+\end{lemma}
+
+\begin{proof}
+We can prove so with a coupling argument: for any sequence $X_1, X_2, \ldots, X_n$, define $Y_1, Y_2, \ldots, Y_n$, obtained by swapping $X_1$ with the largest value in the sequence $X$. Hence
+$$\exp\left(\theta_1 Y_1 + \theta_2 Y_2 + \cdots + \theta_n Y_n - \psi\left(\theta\right)\right) g\left(X\right) \ge \exp\left(\theta_1 X_1 + \theta_2 X_2 + \cdots + \theta_n X_n - \psi\left(\theta\right)\right) g\left(X\right).$$
+Integrating both sides over $\mathbb{R}^n$ (or $\mathbb{Z}^n$ in the case of counting measure) gives
+$$n \PP\left[1 \text{ wins}\right] \ge 1$$
+as desired.
 \end{proof}
@@
 \begin{equation}
-\PP\left[\bigcup_{j \ne j^*} \text{declare } j \text{ best}\right] \le \sum_{j \ne j^*} \alpha \cdot \PP\left[j \text{ wins}\right] \le \frac{n-1}{n} \alpha,
+\PP\left[\bigcup_{j \ne j^*} \text{declare } j \text{ best}\right] \le \sum_{j \ne j^*} \alpha \cdot \PP\left[j \text{ wins}\right] = \alpha \PP\left[j^* \text{ does not win}\right] \le \frac{n-1}{n} \alpha,
 \label{eq:marginal}
 \end{equation}
-where the second inequality uses the stochastic ordering on $X_j$. \WFcomment{Should we put that Prop. first? Also I'm not sure it quite justifies the second inequality.}
+where the last inequality follows from \Cref{lma:margsharp}.
 
@@
 For convenience, we let
-$$D_{jk} = \frac{X_j - X_k}{2} ~~~~ \text{ and } ~~~~ M_{jk} = \frac{X_j + X_k}{2}.$$
+$$D_{jk} = \frac{X_j - X_k}{2} \quad \text{ and } \quad M_{jk} = \frac{X_j + X_k}{2}.$$
 
@@
 \begin{align*}
-p\left(D_{1j} \mid \cdots\right) & \propto \exp\left(\left(\theta_1 - \theta_j\right) D_{1j} + \theta_2 X_2 + \cdots + \left(\theta_1 + \theta_j\right) M_{1j} + \cdots + \theta_n X_n \right) \\
-& ~~~~~~~~ g\left(M_{ij} + D_{ij}, X_2, \ldots, M_{ij} - D_{ij}, \ldots X_n\right) 1_{A_1} \\
+p\left(D_{1j} \mid M_{1j}, X_{\setminus\left\{1, j\right\}}, A_1\right) & \propto \exp\left(\left(\theta_1 - \theta_j\right) D_{1j} + \theta_2 X_2 + \cdots + \left(\theta_1 + \theta_j\right) M_{1j} + \cdots + \theta_n X_n \right) \\
+& \quad\quad g\left(M_{ij} + D_{ij}, X_2, \ldots, M_{ij} - D_{ij}, \ldots X_n\right) 1_{A_1} \\
 & \stackrel{\text{(a)}}{\propto} g\left(M_{ij} + D_{ij}, X_2, \ldots, M_{ij} - D_{ij}, \ldots X_n\right) 1_{A_1},
@@
 \WFcomment{This notation is confusing because there should also be another indicator that $M_{ij}=m_{ij}$ where $m_{ij}$ is the realized value this time, also for $X_{\setminus\left\{1,j\right\}}=x_{\cdots}$.}
+\KHcomment{It seems appropriate as conditioning should give a density in terms of the variables being conditioned. Clarified the variables conditioned on nonetheless.}
 where at step (a), conditioning on $X_{\setminus\left\{1, j\right\}}$ and $M_{1j}$ removes dependence on $\theta_{\setminus\left\{1, j\right\}}$ and $\theta_1 + \theta_j$ respectively, while $\theta_1 - \theta_j$ is taken to be $0$ under our null hypothesis.
@@
 Finally, by construction, $p_{1j}$ satisfies
-$$\PP_{H_{01j}}\left[p_{1j} < \alpha \;\middle|\; M_{1j}, X_{\setminus\left\{1, j\right\}}, A_1\right] \le \alpha,$$
-almost surely. Marginalizing over $M_{1j}, X_{\setminus\left\{1, j\right\}}$,
+$$\PP_{H_{01j}}\left[p_{1j} < \alpha \;\middle|\; M_{1j}, X_{\setminus\left\{1, j\right\}}, A_1\right] \le \alpha \quad \text{a.s.},$$
+Marginalizing over $M_{1j}, X_{\setminus\left\{1, j\right\}}$,
 $$\PP_{H_{01j}}\left[p_{1j} < \alpha \;\middle|\; A_1\right] \le \alpha.$$
@@
 Upon conditioning these, $\left(X_1, X_2, X_3\right)$ follows an exponential family distribution, with carrier distribution
-$$g_{X_4, \ldots, X_n}\left(X_1, X_2, X_3\right) = g\left(X_1, \ldots, X_n\right).$$
-\WFcomment{What does the subscripting mean?}
+$$g_{X_4, \ldots, X_n}\left(X_1, X_2, X_3\right) = g\left(X_1, \ldots, X_n\right),$$
+here $X_4, \ldots, X_n$ are used in the subscript as they are conditioned on and no longer considered as variables.
 The first point in \Cref{lma:twoprop} says that the function $g_{X_4, \ldots, X_n}$ is Schur-concave as well.
@@
 \Cref{fig:compare_rays} has both the $p$-values shown on the same diagram. Proving $p_{12} \ge p_{13}$ is the same as proving
-$$\frac{B}{A+B} \ge \frac{D}{C+D} ~~~~ \Longleftrightarrow ~~~~ \frac{B}{A} \ge \frac{D}{C}.$$
+$$\frac{B}{A+B} \ge \frac{D}{C+D} \quad \Longleftrightarrow \quad \frac{B}{A} \ge \frac{D}{C}.$$
 We will prove so by extending $A$ to include $\tilde{A}$ on the diagram. We denote the sum $A + \tilde{A}$ as $A'$. Formally,
@@
 p\left(D_{1j}\right) & \propto \exp\left(\left(\theta_1 - \theta_j\right) D_{1j} + \theta_2 X_2 + \cdots + \left(\theta_1 + \theta_j\right) M_{1j} + \cdots + \theta_n X_n \right) \\
-& ~~~~~~~~ g\left(M_{1j} + D_{1j}, X_2, \ldots, M_{1j} - D_{1j}, \ldots X_n\right) 1_{A_1} \\
+& \quad\quad g\left(M_{1j} + D_{1j}, X_2, \ldots, M_{1j} - D_{1j}, \ldots X_n\right) 1_{A_1} \\
 & \propto \exp\left(\delta D_{1j}\right) g\left(M_{1j} + D_{1j}, X_2, \ldots, M_{1j} - D_{1j}, \ldots X_n\right) 1_{A_1}.
@@
 
-Let $\hat{j}$ denote the number of ranks validated by a procedure (the number of rejections).
-Then the FWER of $\hat{j}$ is the probability that too many rejections are made; i.e.
-$\PP\left[\hat{j} > j_0\right]$.
+Let $\hat{j}_0$ denote the number of ranks validated by a procedure (the number of rejections).
+Then the FWER of $\hat{j}_0$ is the probability that too many rejections are made; i.e.
+$\PP\left[\hat{j}_0 > j_0\right]$.
 For example, suppose that the top three data ranks and population ranks coincide, but not the fourth ($j_0=3$).
-Then we will have made a Type I error if we declare that the top five ranks are correct ($\hat{j}=5$), but not if we declare that the top two are correct ($\hat{j}=2$).
+Then we will have made a Type I error if we declare that the top five ranks are correct ($\hat{j}_0=5$), but not if we declare that the top two are correct ($\hat{j}_0=2$).
 
@@
 
-\WFcomment{Need to describe this procedure more explicitly. Try using the algorithm2e package.}
-Repeat while we can reject, a one-tail test for $\theta_{\left[j\right]} - \theta_{\left[j+1\right]} > 0$ based on comparing $X_{\left[j\right]}$ and $X_{\left[j+1\right]}$ conditioned on $\left\{X_{\left[j-1\right]} \ge X_{\left[j\right]} \ge \max_{k>j} X_{\left[k\right]}\right\}$ as well as $X_{\left[1\right]}, \ldots, X_{\left[j-1\right]}$.
+\begin{algorithm}[htbp]
+	\SetKwInOut{Input}{input}
+	\SetKwInOut{Output}{output}
+	\SetKwData{Rejected}{rejected}
+	\SetKwComment{Comment}{\# }{}
+	\SetKw{Test}{test}
+	\SetKw{True}{true}
+	\Input{$X_1, \ldots, X_n$}
+	\Output{$\hat{j}_0$, an estimate for $j_0$}
+	\Comment{Initialization}
+	$X_{[0]} \leftarrow \infty$\;
+	$j \leftarrow 0$\;
+	\Rejected $\leftarrow$ \True\;
+	\While{\Rejected}{
+		$j \leftarrow j+1$\;
+		$D_{[j][j+1]} \leftarrow X_{[j]} - X_{[j+1]}$\;
+		Set up the distribution of $D_{[j][j+1]}$, conditioned on
+		\begin{itemize}
+		\item the variables $X_{[1]}, \ldots, X_{[j-1]}, X_{[j+2]}, \ldots, X_{[n]}$, and
+		\item the event $\left\{X_{[j-1]} \ge X_{[j]} \ge \max_{k>j} X_{[k]}\right\}$\; \label{lne:event}
+		\end{itemize}
+		\Comment{The distribution of $D_{[j][j+1]}$ depends only on $\theta_{[j]} - \theta_{[j+1]}$ now}
+		\Test $H_0: \theta_{[j]} - \theta_{[j+1]} \le 0$ against $H_1: \theta_{[j]} - \theta_{[j+1]} > 0$ according to the distribution of $D_{[j][j+1]}$\;
+		Set \Rejected as the output of the test\;
+	}
+	$\hat{j}_0 \leftarrow j-1$\;
+	\caption{Procedure 3', a more liberal version of Procedure 3}
+\end{algorithm}
+
+Later we will see that Procedure 3 is mostly the same as Procedure 3', except that Procedure 3 conditions on a larger event $\left\{X_{[j]} \ge \max_{k>j} X_{[k]}\right\}$ in \Cref{lne:event}.
 
@@
 $$\mathcal{M}_1\left(X\right) \subseteq \cdots \subseteq \mathcal{M}_n\left(X\right), \quad\text{ where }~~ \mathcal{M}_j\left(X\right)^c = \left\{\theta:\; \theta_{[1]} > \cdots > \theta_{[j]} > \max_{k > j} \theta_{[k]}\right\}.$$
-Thus, returning $\hat{j}=j$ amounts to rejecting $\widetilde{H}_{01},\ldots,\widetilde{H}_{0j}$, or equivalently determining that the models $\mathcal{M}_1(X),\ldots,\mathcal{M}_j(X)$ do {\em not} fit the data.
+Thus, returning $\hat{j}_0=j$ amounts to rejecting $\widetilde{H}_{01},\ldots,\widetilde{H}_{0j}$, or equivalently determining that the models $\mathcal{M}_1(X),\ldots,\mathcal{M}_j(X)$ do {\em not} fit the data.
 
@@
 
-We can construct selective $p$-values by conditioning on $\mathcal{M}_j\left(X\right)$, as well as other nuisance parameters \WFcomment{We condition on data, not parameters}.
+We can construct selective $p$-values by conditioning on $\mathcal{M}_j\left(X\right)$, as well as other variables corresponding to the nuisance parameters.
 Specifically, we are conditioning on the selection of the model $\mathcal{M}_j\left(X\right)$ \WFcomment{Why?

### 2016-08-25 verifying-winner.tex
Minor fixes

@@
 \begin{proof}
-Let $j^*$ denote the (fixed) index of the best population, so $\theta_{j^*} \geq \max_{j\neq j^*} \theta_j$.
+Let $j^*$ denote the (fixed) index of the best population, so $\theta_{j^*} \ge \max_{j\neq j^*} \theta_j$.
 The type I error --- the probability of incorrectly declaring any other $j$ to be the best --- is
@@
 recalling that ties are broken randomly, so there is only one winner in any realization.
-Thus, it is enough to bound $\PP_{\theta}\left[ \text{declare } j \text{ best} \;\middle|\; j \text{ wins}\right] \leq \alpha$, for each $j \ne j^*$, and for all $\theta$ with $j^* \in \argmax_j \theta_j$.
+Thus, it is enough to bound $\PP_{\theta}\left[ \text{declare } j \text{ best} \;\middle|\; j \text{ wins}\right] \le \alpha$, for each $j \ne j^*$, and for all $\theta$ with $j^* \in \argmax_j \theta_j$.
 Then we will have
@@
 For each of these we can construct an exact $p$-value $p_{1j}$, which is valid under $H_{01j}$ conditional on $A_1$, the event that $X_1$ is the winner.
-Hence by \Cref{lma:union}, a test that rejects when $p_{1*} = \max_j p_{1j} \leq \alpha$ is valid for $H_{01}$ conditional on $A_1$.
+Hence by \Cref{lma:union}, a test that rejects when $p_{1*} = \max_j p_{1j} \le \alpha$ is valid for $H_{01}$ conditional on $A_1$.
 Procedure 1 performs an unadjusted pairwise test comparing $X_1$ to $X_2$.
-Hence it is sufficient to show that $p_{12} = p_{1*}$ and that rejecting when $p_{12}\leq \alpha$ coincides with the unadjusted pairwise test.
+Hence it is sufficient to show that $p_{12} = p_{1*}$ and that rejecting when $p_{12}\le \alpha$ coincides with the unadjusted pairwise test.
 
@@
 
-Note that Procedure 2 reporting $-\infty$ in case of $\delta^*\leq 0$ is rather extreme.
+Note that Procedure 2 reporting $-\infty$ in case of $\delta^* \le 0$ is rather extreme.
 In reality, we can always just adopt Procedure 2' in the case when Procedure 1 rejects.
-In fact, by Procedure 2', the multinomial example for polling in \Cref{sec:iowa} can give a stronger lower confidence bound, that $\pi_{\text{Trump}} \geq \max_{j \ne \text{Trump}} \pi_{j} \geq 1.108$ (Trump leads the field by at least $10.8\%$).
+In fact, by Procedure 2', the multinomial example for polling in \Cref{sec:iowa} can give a stronger lower confidence bound, that $\pi_{\text{Trump}} \ge \max_{j \ne \text{Trump}} \pi_{j} \ge 1.108$ (Trump leads the field by at least $10.8\%$).
 
@@
 Often we will be interested in verifying ranks beyond the winner. More generally, we could imagine declaring that the first $j$ candidates are all in the correct order, that is
-\begin{equation}\label{eq:jrankscorrect}
-\theta_{[1]} > \ldots > \theta_{[j]} > \max_{k>j} \theta_{[k]}.
+\begin{equation}
+\theta_{[1]} > \cdots > \theta_{[j]} > \max_{k>j} \theta_{[k]}.
+\label{eq:jrankscorrect}
 \end{equation}
-Let $j_0$ denote the largest $j$ for which~\eqref{eq:jrankscorrect} is true.
+
+Let $j_0$ denote the largest $j$ for which \eqref{eq:jrankscorrect} is true.
 Note that $j_0$ is both random and unknown, because it depends on both the data and population ranks.
-Procedure 3 declares that $j_0 \geq j$ if the unadjusted pairwise tests between $X_{[k]}$ and $X_{[k+1]}$, reject at level $\alpha$ for {\em all} of $k=1,\ldots,j$.
+Procedure 3 declares that $j_0 \ge j$ if the unadjusted pairwise tests between $X_{[k]}$ and $X_{[k+1]}$, reject at level $\alpha$ for {\em all} of $k = 1, \ldots, j$.
 
-Let $\hat{j}_0$ denote the number of ranks validated by a procedure (the number of rejections).
+Using the example in \Cref{sec:intro} regarding the polls, we would like to produce a statement of ``Trump is the best, Cruz is the runner-up and Rubio is the second runner-up''.
+Procedure 3 performs unadjusted pairwise tests to ask if Cruz is really the runner-up upon verifying that Trump is the best, and if Rubio is really the second runner-up upon verifying that Cruz is the runner-up, etc., until we can no longer infer that a certain candidate really holds its rank.
+
+While we aim to declare more candidates to be in the correct order, declaring too many candidates, i.e.\ out-of-place candidates, to be in the right order is undesirable.
+While it is possible to consider false discovery rate (the expected portion of out-of-place candidates declared) here, we restrict our derivation to FWER (the probability of having out-of-place candidates declared).
+
+Formally, let $\hat{j}_0$ denote the number of ranks validated by a procedure (the number of rejections).
 Then the FWER of $\hat{j}_0$ is the probability that too many rejections are made; i.e.
@@
 
-Later we will see that Procedure 3 is mostly the same as Procedure 3', except that Procedure 3 conditions on a larger event $\left\{X_{[j]} \ge \max_{k>j} X_{[k]}\right\}$ in \Cref{lne:event}.
+Later we will see that Procedure 3 is equivalent to Procedure 3' for the most part, except that Procedure 3 conditions on a larger event $\left\{X_{[j]} \ge \max_{k>j} X_{[k]}\right\}$ in \Cref{lne:event}.
 
 \begin{theorem}
-Procedure 3' is a step-down procedure that infers $j_0$ above with the FWER controlled at $\alpha$.
-\WFcomment{``Infers'' is too vague. We need to say exactly what is true of the procedure, in rigorous mathematical terms.}
+Procedure 3' is a step-down procedure that an estimate $\hat{j}_0$ of $j_0$ at the FWER controlled at $\alpha$, where $j_0$ is given by
+$$j_0 = \max_j \left\{\theta_{[1]} > \cdots > \theta_{[j]} > \max_{k>j} \theta_{[k]}\right\}.$$
 \end{theorem}
@@
 \begin{proof}
-This problem falls into the sequential goodness-of-fit testing framework proposed by \citet{Fithian:2015uj}.
-Given the observations $X_{[1]} \ge \cdots \ge X_{[n]}$, define the $j$th null hypothesis as
-$$\widetilde{H}_{0j}: \theta_{[j]} \le \max_{k > j} \theta_{[k]}.$$
+We will first show that Procedure 3' falls into the sequential goodness-of-fit testing framework proposed by \citet{Fithian:2015uj}.
+Then we will show that it satisfies the subpath sufficiency principle (SSP) and construct the $p$-values.
+These constructions suffice to show that FWER is controlled by Theorem 4 in \citet{Fithian:2015uj}.
 
-$\widetilde{H}_{01},\ldots,\widetilde{H}_{0j}$ are all false if and only if $\theta\notin \mathcal{M}_j(X)$, where the $\mathcal{M}_j$ represent a sequence of nested models:
-$$\mathcal{M}_1\left(X\right) \subseteq \cdots \subseteq \mathcal{M}_n\left(X\right), \quad\text{ where }~~ \mathcal{M}_j\left(X\right)^c = \left\{\theta:\; \theta_{[1]} > \cdots > \theta_{[j]} > \max_{k > j} \theta_{[k]}\right\}.$$
-Thus, returning $\hat{j}_0=j$ amounts to rejecting $\widetilde{H}_{01},\ldots,\widetilde{H}_{0j}$, or equivalently determining that the models $\mathcal{M}_1(X),\ldots,\mathcal{M}_j(X)$ do {\em not} fit the data.
+\paragraph{Application of the sequential goodness-of-fit testing framework}
 
-\WFcomment{The rest of this proof seems correct but is hard to follow. Can you try to go through and clean it up a bit?}
+Upon observing $X_{[1]} \ge \cdots \ge X_{[n]}$, we can set up a sequence of nested model
+$$\mathcal{M}_1\left(X\right) \subseteq \cdots \subseteq \mathcal{M}_n\left(X\right), \quad\text{ where } \mathcal{M}_j\left(X\right)^c = \left\{\theta:\; \theta_{[1]} > \cdots > \theta_{[j]} > \max_{k > j} \theta_{[k]}\right\}.$$
+If we define the $j$-th null hypothesis as
+$$\widetilde{H}_{0j}: \theta_{[j]} \le \max_{k > j} \theta_{[k]},$$
+then $\widetilde{H}_{01},\ldots,\widetilde{H}_{0j}$ are all false if and only if $\theta\notin \mathcal{M}_j(X)$.
 
-We can construct selective $p$-values by conditioning on $\mathcal{M}_j\left(X\right)$, as well as other variables corresponding to the nuisance parameters.
-Specifically, we are conditioning on the selection of the model $\mathcal{M}_j\left(X\right)$ \WFcomment{Why?
-Also, we are conditioning on more things as well.}.
+In other words, $\mathcal{M}_j\left(X\right)$ is a family of distributions that does not have all first $j$ ranks correct.
+As we will see later, each step in Procedure 3' corresponds to testing $\widetilde{H}_{0j}$, stating that without the first $j$ ranks correct, it is hard to explain the observations.
+Thus, returning $\hat{j}_0 = j$ amounts to rejecting $\widetilde{H}_{01},\ldots,\widetilde{H}_{0j}$, or equivalently determining that the models $\mathcal{M}_1(X), \ldots, \mathcal{M}_j(X)$ do {\em not} fit the data.
+
+\paragraph{Demonstration of the SSP} As in the proof of Parts 1 and 2 of \Cref{thm:main} before, we drop the square brackets subscripts for convenience here, while maintaining that the sample ranks are random.
+Under the model $\mathcal{M}_j\left(X\right)$, the minimal sufficient statistic is simply $X$.
+The sufficient filtration \citep{Fithian:2015uj} is thus
+$$\mathscr{F}_j = \sigma\left(\mathcal{M}_0\left(X\right), \ldots, \mathcal{M}_j\left(X\right), X\right) = \sigma\left(X\right),$$
+where $\mathcal{M}_k\left(X\right)$ above refers to the choice of the model as a random variable, and thus measurable in $\sigma\left(X\right)$.
+This is the same as $\sigma\left(\mathcal{M}_j\left(X\right), X\right) = \sigma\left(X\right)$ for all $j$.
+Thus the random sequence of model satisfies SSP.
+
+Now if we construct valid selective $p$-values, the $p$-values sequence will be independent on nulls, as defined and shown in Theorem 4 of \citet{Fithian:2015uj} and FWER will be controlled.
+
+\KHcomment{It occured to me that the minimal sufficient statistic should be the entire $X$, as the sequence of model does not assert $\theta_j = \theta_{j+1}$.}
+
+\paragraph{Construction of the selective $p$-values}
+
+As defined in \citet{Fithian:2015uj}, a selective $p$-value $p_j$, for testing $H_{0j}: \theta \in \mathcal{M}_j\left(X\right)$ is valid if and only if
+$$\PP_\theta\left(p_j \le \alpha \;\middle|\; \mathcal{M}_j\right) \le \alpha \text{ a.s.\ on } \left\{\theta \in \mathcal{M}_j\left(X\right)\right\}.$$
+
+\KHcomment{Testing $H_{0j}$ is not the same $\widetilde{H}_{0j}$, need fixes.}
+
+By smoothing, we can construct selective $p$-values by conditioning on $\mathcal{M}_j\left(X\right)$, as well as other variables corresponding to the nuisance parameters.
+Specifically, we are conditioning on the choice of the model $\mathcal{M}_j\left(X\right)$ and the variables $X_1, \ldots, X_{j-1}, X_{j+1}, \ldots, X_n$ and $M_{j\left(j+1\right)}$ as defined in earlier in the proof of Part 1 of \Cref{thm:main}.
 We can take $p_j$ to be the survival function of the conditional law
@@
 \end{align}
-\WFcomment{Why does all this work? Maybe cite a specific theorem in Fithian et al. (2015)?}
 
@@
 	\fill (C3) circle(2pt);
-	\fill (A) circle(2pt) node[above right] {$\left(M_{12}, M_{12}, X_3\right)$};
-	\fill (B) circle(2pt) node[right] {$\left(X_1, X_2, X_3\right)$};
+	\fill (A) circle(2pt) node[above right] {$\left(M_{j\left(j+1\right)}, M_{j\left(j+1\right)}, X_k\right)$};
+	\fill (B) circle(2pt) node[right] {$\left(X_j, X_{j+1}, X_k\right)$};
 	\draw[thick] (C) -- (B) node[midway, below right] {$C$};
-	\node[below] at (C) {$\left(M_{13}, X_2, M_{13}\right)$};
+	\node[below] at (C) {$\left(M_{jk}, X_{j+1}, M_{jk}\right)$};
 	\draw[thick] (B) -- (C4) node[midway, above left] {$D$};
@@
 	\draw[thick, dashed] (A) -- (D) node[midway, below left] {$\tilde{A}$};
-	\fill (D) circle(2pt) node[above] {$\left(M_{13}, X_2 + D_{13}, X_3\right)$};
+	\fill (D) circle(2pt) node[above] {$\left(M_{jk}, X_{j+1} + D_{jk}, X_k\right)$};
 	\draw[thick, dotted] (C) -- (D) node[midway, below, rotate=-90] {$\succeq$};
@@
 \caption{The two $p$-values constructed corresponds to taking integrals of $g$ along these segments, that lie on a level set of $x_j + x_{j+1} + x_k$.
-The dashed line corresponds to extension in \Cref{eqn:int_extension}.
+The dashed line corresponds to extension in \eqref{eqn:int_extension}.
 The dotted line on the far right is the truncation that enforces $X_j < X_{j-1}$.}
@@
 Here we are only comparing $X_j$ to $X_{j+1}$ by \Cref{sec:winnerbest}.
-The upper truncation for $X_j$ can be represented by cropping \Cref{fig:compare_rays} along a vertical line, shown in \Cref{fig:crop_rays}, thus the proof of Part 1 of \Cref{thm:main} that it suffices to compare $X_1$ and $X_2$ remains valid with appropriate conditioning.
+The upper truncation for $X_j$ can be represented by cropping \Cref{fig:compare_rays} along a vertical line, shown in \Cref{fig:crop_rays}.
+Thus the proof of Part 1 of \Cref{thm:main} that it suffices to compare $X_1$ and $X_2$ remains valid.
 Again we can construct the $p$-values as in \Cref{eqn:p1j} for $k>j$.
@@
 
-The conditioning above indeed holds some significance. The sufficient filtration \citep{Fithian:2015uj} $\mathscr{F}_k$ is given as the $\sigma$-field
-\begin{align*}
-\mathscr{F}_k & = \sigma\left(\mathcal{M}_0\left(X\right), \ldots, \mathcal{M}_j\left(X\right), X_1, \ldots, X_{j-1}, \frac{X_j + X_{j+1}}{2}, X_{j+2}, \ldots, X_n\right) \\
-& = \sigma\left(\left\{X_1 > \ldots > X_j > \max_{k>j} X_k\right\}, X_1, \ldots, X_{j-1}, \frac{X_j + X_{j+1}}{2}, X_{j+2}, \ldots, X_n\right) \\
-& = \sigma\left(\mathcal{M}_j\left(X\right), X_1, \ldots, X_{j-1}, \frac{X_j + X_{j+1}}{2}, X_{j+2}, \ldots, X_n\right),
-\end{align*}
-which is the conditioning we used just now.
-Hence the nested sequence of model satisfies the subpath sufficiency principle , and the $p$-values sequence $p_j$ is independent on nulls, as defined in and shown in Theorem 4 of \citet{Fithian:2015uj}.
-Thus the step-down procedure where we keep rejecting $H_{0j}$ until the first time that $p_j > \alpha$ controls FWER.
+\paragraph{FWER is controlled}
 
-\WFcomment{Should the reference to SSP be earlier if you are going to say it?
-Also, is it actually necessary to bring up the SSP?
-You've already said directly that we are conditioning on $X_{[1]}$ through $X_{[j-1]}$.
-More generally, if we can sidestep the more generic langauge of that paper and substitute more specific language for our specific problem, I think that will make this a lot more readable.}
+\WFcomment{You've already said directly that we are conditioning on $X_{[1]}$ through $X_{[j-1]}$.
+More generally, if we can sidestep the more generic language of that paper and substitute more specific language for our specific problem, I think that will make this a lot more readable.}
 \end{proof}

### 2016-08-26 verifying-winner.tex
Major fixes for Procedure 3

@@
 X \sim \exp\left(\theta'x - \psi\left(\theta\right)\right) g\left(x\right),
-\label{eqn:expfam}
+\label{eq:expfam}
 \end{equation}
@@
 We assume further that $g\left(x\right)$ is symmetric with respect to permutation, and Schur concave, a mild technical condition defined in \Cref{sec:maj}.
-In addition to the multinomial family, model~\eqref{eqn:expfam} also encompasses settings such as comparing independent binomial treatment outcomes in a clinical trial, competing sports teams under a Bradley--Terry model, entries of a Dirichlet distribution, and many more; see \Cref{sec:maj} for these and other examples.
+In addition to the multinomial family, model~\eqref{eq:expfam} also encompasses settings such as comparing independent binomial treatment outcomes in a clinical trial, competing sports teams under a Bradley--Terry model, entries of a Dirichlet distribution, and many more; see \Cref{sec:maj} for these and other examples.
 
@@
 \begin{theorem}
-Assume the model~\eqref{eqn:expfam} holds and $g\left(x\right)$ is a Schur-concave function. Then:
+Assume the model~\eqref{eq:expfam} holds and $g\left(x\right)$ is a Schur-concave function. Then:
 \begin{enumerate}
@@
 \begin{customthm}[Part 1 of \Cref{thm:main}]
-Assume the model~\eqref{eqn:expfam} holds and $g\left(x\right)$ is a Schur-concave function.
+Assume the model~\eqref{eq:expfam} holds and $g\left(x\right)$ is a Schur-concave function.
 Procedure 1 (the unadjusted pairwise test) has level $\alpha$ conditional on the best population not winning.
@@
 \mathcal{L}_{\theta_1 - \theta_j = 0} \left(D_{1j} \;\middle|\; M_{1j}, X_{\setminus\left\{1, j\right\}}, A_1\right).
-\label{eqn:condlaw}
+\label{eq:condlaw}
 \end{equation}
@@
 \end{align*}
-The conditional law in \Cref{eqn:condlaw}, in particular, is a truncated distribution
+The conditional law in \Cref{eq:condlaw}, in particular, is a truncated distribution
 \begin{align*}
@@
 p_{1j} = \frac{\int_{D_{1j}}^\infty g\left(M_{1j} + z, X_2, \ldots, M_{1j} - z, \ldots, X_n\right) \,dz}{\int_{\max\left\{X_2 - M_{1j}, 0\right\}}^\infty g\left(M_{1j} + z, X_2, \ldots, M_{1j} - z, \ldots, X_n\right) \,dz}.
-\label{eqn:p1j}
+\label{eq:p1j}
 \end{equation}
@@
 
-\Cref{fig:compare_rays} has both the $p$-values shown on the same diagram. Proving $p_{12} \ge p_{13}$ is the same as proving
+\Cref{fig:comparerays} has both the $p$-values shown on the same diagram. Proving $p_{12} \ge p_{13}$ is the same as proving
 $$\frac{B}{A+B} \ge \frac{D}{C+D} \quad \Longleftrightarrow \quad \frac{B}{A} \ge \frac{D}{C}.$$
@@
 A' = \int_{-D_{13}}^0 g\left(X_1 + z, X_2 - z, X_3\right) \,dz \ge \int_{-D_{12}}^0 g\left(X_1 + z, X_2 - z, X_3\right) \,dz = A.
-\label{eqn:int_extension}
+\label{eq:int_extension}
 \end{equation}
@@
 \caption{The $p$-value $p_{12}$ can be written in terms of integral $A$ along the segment and $B$ along the ray; and $p_{13}$ in terms of $C$ and $D$.
-$A'$ would refer to the sum of $A$ with the dashed line portion labeled as $\tilde{A}$, formally explained in \Cref{eqn:int_extension}.
+$A'$ would refer to the sum of $A$ with the dashed line portion labeled as $\tilde{A}$, formally explained in \Cref{eq:int_extension}.
 The majorization relation is indicated by the dotted line.}
-\label{fig:compare_rays}
+\label{fig:comparerays}
 \end{figure}
@@
 $$\left(X_1 + z, X_2 - z, X_3\right) \succeq \left(X_1 + z, X_2, X_3 - z\right)$$
-for $z \le 0$ and the majorization reversed for $z \ge 0$. This majorization relation is indicated as the dotted line in \Cref{fig:compare_rays}. So Schur-concavity shows that
+for $z \le 0$ and the majorization reversed for $z \ge 0$. This majorization relation is indicated as the dotted line in \Cref{fig:comparerays}. So Schur-concavity shows that
 $$g\left(X_1 + z, X_2 - z, X_3\right) \le g\left(X_1 + z, X_2, X_3 - z\right)$$
@@
 
-Before conditioning on $A_1$, the distribution in \label{eqn:condlaw} is symmetric around 0 under $\theta_1=\theta_j$.
+Before conditioning on $A_1$, the distribution in \label{eq:condlaw} is symmetric around 0 under $\theta_1=\theta_j$.
 Since the denominator of $p_{12}$ integrates over half of this symmetric distribution, it is always equal to $1/2$.
@@
 If ties are broken independently and randomly, the end points on the rays can be considered as ``half an atom'' if the coordinates are integers (or a smaller fraction of an atom in case of a multi-way tie).
-The number of atoms on each ray is the same (after the extension $\tilde{A}$) and the atoms on each ray can be paired up in exactly the same way as illustrated in Figure~\ref{fig:compare_rays}, with the inequalities above still holding for each pair of the atoms.
+The number of atoms on each ray is the same (after the extension $\tilde{A}$) and the atoms on each ray can be paired up in exactly the same way as illustrated in Figure~\ref{fig:comparerays}, with the inequalities above still holding for each pair of the atoms.
 Summing these inequalities yields our desired result.
@@
 
-The same argument in \Cref{fig:compare_rays} shows that $p_{12}^\delta \ge p_{13}^\delta$. This is again true for the case where $X_2 \ge M_{13}$ as well.
+The same argument in \Cref{fig:comparerays} shows that $p_{12}^\delta \ge p_{13}^\delta$. This is again true for the case where $X_2 \ge M_{13}$ as well.
 \end{proof}
@@
 \begin{customthm}[Part 2 of \Cref{thm:main}]
-Assume the model~\eqref{eqn:expfam} holds and $g\left(x\right)$ is a Schur-concave function.
+Assume the model~\eqref{eq:expfam} holds and $g\left(x\right)$ is a Schur-concave function.
 Procedure 2 (the lower bound of unadjusted pairwise confidence interval) gives a conservative $1-\alpha$ lower confidence bound for $\theta_{[1]} - \max_{j \ne [1]} \theta_j$.
@@
 \label{sec:stepdown}
-\WFcomment{This whole section is too vague.
-The procedure, and even the decision problem, are not that familiar to most readers so they need to be set out very explicitly.
-I tried to improve this a bit but parts still need more work.}
 
@@
 $\PP\left[\hat{j}_0 > j_0\right]$.
-For example, suppose that the top three data ranks and population ranks coincide, but not the fourth ($j_0=3$).
-Then we will have made a Type I error if we declare that the top five ranks are correct ($\hat{j}_0=5$), but not if we declare that the top two are correct ($\hat{j}_0=2$).
+For example, suppose that the top three data ranks and population ranks coincide, but not the fourth ($j_0 = 3$).
+Then we will have made a Type I error if we declare that the top five ranks are correct ($\hat{j}_0 = 5$), but not if we declare that the top two are correct ($\hat{j}_0 = 2$).
 
-To show that Procedure 3 is valid, we will prove the validity of a more liberal Procedure 3', described below.
+To show that Procedure 3 is valid, we will prove the validity of a more liberal Procedure 3', described in \Cref{alg:proc3}.
 
@@
 	\Comment{Initialization}
-	$X_{[0]} \leftarrow \infty$\;
+	$\tau_j \leftarrow [j]$\;
+	\Comment{Consider $\tau_j$ as part of the observation and the fixed realization of the random index $[j]$}
+	$X_{\tau_0} \leftarrow \infty$\;
 	$j \leftarrow 0$\;
@@
 		$j \leftarrow j+1$\;
-		$D_{[j][j+1]} \leftarrow X_{[j]} - X_{[j+1]}$\;
-		Set up the distribution of $D_{[j][j+1]}$, conditioned on
+		$D_{\tau_j} \leftarrow X_{\tau_j} - X_{\tau_{j+1}}$\;
+		Set up the distribution of $D_{\tau_j \tau_{j+1}}$, conditioned on
 		\begin{itemize}
-		\item the variables $X_{[1]}, \ldots, X_{[j-1]}, X_{[j+2]}, \ldots, X_{[n]}$, and
-		\item the event $\left\{X_{[j-1]} \ge X_{[j]} \ge \max_{k>j} X_{[k]}\right\}$\; \label{lne:event}
+		\item the variables $X_{\tau_1}, \ldots, X_{\tau_{j-1}}, X_{\tau_{j+2}}, \ldots, X_{\tau_n]}$, and
+		\item the event $\left\{X_{\tau_{j-1}} \ge X_{\tau_j} \ge \max_{k>j} X_{\tau_k)}\right\}$\; \label{lne:event}
 		\end{itemize}
-		\Comment{The distribution of $D_{[j][j+1]}$ depends only on $\theta_{[j]} - \theta_{[j+1]}$ now}
-		\Test $H_0: \theta_{[j]} - \theta_{[j+1]} \le 0$ against $H_1: \theta_{[j]} - \theta_{[j+1]} > 0$ according to the distribution of $D_{[j][j+1]}$\;
+		\Comment{The distribution of $D_{\tau_j \tau_{j+1}}$ depends only on $\theta_{\tau_j} - \theta_{\tau_{j+1}}$ now}
+		\Test $H_0: \theta_{\tau_j} - \theta_{\tau_{j+1}} \le 0$ against $H_1: \theta_{\tau_j} - \theta_{\tau_{j+1}} > 0$ according to the distribution of $D_{\tau_j \tau_{j+1}}$\;
 		Set \Rejected as the output of the test\;
@@
 	\caption{Procedure 3', a more liberal version of Procedure 3}
+	\label{alg:proc3}
 \end{algorithm}
@@
 We will first show that Procedure 3' falls into the sequential goodness-of-fit testing framework proposed by \citet{Fithian:2015uj}.
-Then we will show that it satisfies the subpath sufficiency principle (SSP) and construct the $p$-values.
-These constructions suffice to show that FWER is controlled by Theorem 4 in \citet{Fithian:2015uj}.
+We thus analyze Procedure 3' as a special case of the BasicStop procedure on random hypothesis, described in the same paper.
+This enables us to construct valid selective $p$-values and derives Procedure 3'.
 
@@
 
-Upon observing $X_{[1]} \ge \cdots \ge X_{[n]}$, we can set up a sequence of nested model
+Upon observing $X_{[1]} \ge \cdots \ge X_{[n]}$, we can set up a sequence of nested models
 $$\mathcal{M}_1\left(X\right) \subseteq \cdots \subseteq \mathcal{M}_n\left(X\right), \quad\text{ where } \mathcal{M}_j\left(X\right)^c = \left\{\theta:\; \theta_{[1]} > \cdots > \theta_{[j]} > \max_{k > j} \theta_{[k]}\right\}.$$
@@
 In other words, $\mathcal{M}_j\left(X\right)$ is a family of distributions that does not have all first $j$ ranks correct.
-As we will see later, each step in Procedure 3' corresponds to testing $\widetilde{H}_{0j}$, stating that without the first $j$ ranks correct, it is hard to explain the observations.
+As we will see later, each step in Procedure 3' is similar to testing $\widetilde{H}_{0j}$, stating that without the first $j$ ranks correct, it is hard to explain the observations.
 Thus, returning $\hat{j}_0 = j$ amounts to rejecting $\widetilde{H}_{01},\ldots,\widetilde{H}_{0j}$, or equivalently determining that the models $\mathcal{M}_1(X), \ldots, \mathcal{M}_j(X)$ do {\em not} fit the data.
 
-\paragraph{Demonstration of the SSP} As in the proof of Parts 1 and 2 of \Cref{thm:main} before, we drop the square brackets subscripts for convenience here, while maintaining that the sample ranks are random.
-Under the model $\mathcal{M}_j\left(X\right)$, the minimal sufficient statistic is simply $X$.
-The sufficient filtration \citep{Fithian:2015uj} is thus
-$$\mathscr{F}_j = \sigma\left(\mathcal{M}_0\left(X\right), \ldots, \mathcal{M}_j\left(X\right), X\right) = \sigma\left(X\right),$$
-where $\mathcal{M}_k\left(X\right)$ above refers to the choice of the model as a random variable, and thus measurable in $\sigma\left(X\right)$.
-This is the same as $\sigma\left(\mathcal{M}_j\left(X\right), X\right) = \sigma\left(X\right)$ for all $j$.
-Thus the random sequence of model satisfies SSP.
+While the null hypotheses $\widetilde{H}_{0j}$ provided intuition in the setting up the nested models, they are rather cumbersome to work with.
+Inspired by \citet{Fithian:2015uj}, we will instead consider another sequence of random hypothesis that are more closely related to the nest models,
+$$H_{0j}: \theta \in \mathcal{M}_j\left(X\right),$$
+or equivalently, that $\theta_{[1]}, \ldots, \theta_{[j]}$ are not the best $j$ parameters in order.
 
-Now if we construct valid selective $p$-values, the $p$-values sequence will be independent on nulls, as defined and shown in Theorem 4 of \citet{Fithian:2015uj} and FWER will be controlled.
+Adapting this notation, the FWER can be viewed as $\PP\left[\text{reject } H_{0 {j_0+1}}\right]$.
 
-\KHcomment{It occured to me that the minimal sufficient statistic should be the entire $X$, as the sequence of model does not assert $\theta_j = \theta_{j+1}$.}
+\paragraph{Special case of the BasicStop procedure}
 
-\paragraph{Construction of the selective $p$-values}
+While impractical, Procedure 3' can be thought of as performing all $n$ tests first, producing a sequence of $p$-values $p_j$, returning
+\begin{equation}
+\hat{j}_0 = \min\left\{j: p_j > \alpha\right\} - 1.
+\label{eq:basicstop}
+\end{equation}
+This is a special case of the BasicStop procedure.
+Instead simply checking that Procedure 3' fits all the requirement for FWER control in BasicStop, we will give the construction of Procedure 3', assuming that we are to estimate $j_0$ with BasicStop.
 
-As defined in \citet{Fithian:2015uj}, a selective $p$-value $p_j$, for testing $H_{0j}: \theta \in \mathcal{M}_j\left(X\right)$ is valid if and only if
-$$\PP_\theta\left(p_j \le \alpha \;\middle|\; \mathcal{M}_j\right) \le \alpha \text{ a.s.\ on } \left\{\theta \in \mathcal{M}_j\left(X\right)\right\}.$$
+In general, the FWER for BasicStop can be rewritten as $\PP\left[p_{j_0+1} \le \alpha\right]$.
+This is however difficult to analyze, as $j_0$ itself is random and dependent on $X$, thus we break the FWER down as follows:
+\begin{align*}
+\PP\left[p_{j_0+1} \le \alpha\right] & = \sum_j \PP\left[p_{j_0+1} \le \alpha \;\middle|\; j_0 = j\right] \PP\left[j_0 = j\right] \\
+& = \sum_j \PP\left[p_{j+1} \le \alpha \;\middle|\; j_0 = j\right] \PP\left[j_0 = j\right] \\
+& = \sum_j \PP\left[p_{j+1} \le \alpha \;\middle|\; \theta \in \mathcal{M}_{j+1}\left(X\right) \setminus \mathcal{M}_j\left(X\right)\right] \PP\left[j_0 = j\right].
+\end{align*}
 
-\KHcomment{Testing $H_{0j}$ is not the same $\widetilde{H}_{0j}$, need fixes.}
+Thus it suffices to construct the $p$-values such that
+\begin{equation}
+\PP\left[p_j \le \alpha \;\middle|\; \theta \in \mathcal{M}_j\left(X\right) \setminus \mathcal{M}_{j-1}\left(X\right)\right] \le \alpha \quad \text{for all } j.
+\label{eq:basicstopreq}
+\end{equation}
 
-By smoothing, we can construct selective $p$-values by conditioning on $\mathcal{M}_j\left(X\right)$, as well as other variables corresponding to the nuisance parameters.
-Specifically, we are conditioning on the choice of the model $\mathcal{M}_j\left(X\right)$ and the variables $X_1, \ldots, X_{j-1}, X_{j+1}, \ldots, X_n$ and $M_{j\left(j+1\right)}$ as defined in earlier in the proof of Part 1 of \Cref{thm:main}.
-We can take $p_j$ to be the survival function of the conditional law
-\begin{align}
-&~ \mathcal{L}_{\theta_j = \theta_{j+1}} \left(D_{j\left(j+1\right)} \;\middle|\; \mathcal{M}_j\left(X\right), X_1, \ldots, X_{j-1}, M_{j\left(j+1\right)}, X_{j+2}, \ldots, X_n\right) \nonumber \\
-= &~ \mathcal{L}_{\theta_j = \theta_{j+1}} \left(D_{j\left(j+1\right)} \;\middle|\; \left\{X_1 \ge \ldots \ge X_j \ge \max_{k > j} X_k\right\}, X_1, \ldots, X_{j-1}, M_{j\left(j+1\right)}, X_{j+2}, \ldots, X_n\right) \nonumber \\
-= &~ \mathcal{L}_{\theta_j = \theta_{j+1}} \left(D_{j\left(j+1\right)} \;\middle|\; \left\{X_{j-1} \ge X_j \ge M_{j\left(j+1\right)}\right\}, X_1, \ldots, X_{j-1}, M_{j\left(j+1\right)}, X_{j+2}, \ldots, X_n\right).
-\label{eqn:step_down_law}
-\end{align}
+\paragraph{Construction of $p$-values}
+
+By smoothing, we are free to condition on additional variables in \eqref{eq:basicstopreq}.
+A logical choice that simplified \eqref{eq:basicstopreq} is conditioning on the variables $\mathcal{M}_{j-1}\left(X\right)$ and $\mathcal{M}_j\left(X\right)$.
+Note that the choice of the model $\mathcal{M}_j\left(X\right)$, once again, based solely on the random indices $[1], \ldots, [j]$, so conditioning on both $\mathcal{M}_{j-1}\left(X\right)$ and $\mathcal{M}_j\left(X\right)$ is equivalent to conditioning on the random indices $[1], \ldots, [j]$, which in turns is equivalent to conditioning on the $\sigma$-field generated by the partition of the observation space $X$
+$$\left\{\left\{X_{\tau_1} \ge \cdots \ge X_{\tau_j} \ge \max_{k>j} X_{\tau_k}\right\}: \tau \text{ is any permutation of } \left(1, \ldots, n\right)\right\},$$
+or colloquially, the set of all possible choices of $[1], \ldots, [j]$.
+Within each set in this partition, the event $\left\{\theta \in \mathcal{M}_j\left(X\right) \setminus \mathcal{M}_{j-1}\left(X\right)\right\}$ is simply $\left\{\theta_{\tau_1} > \cdots > \theta_{\tau_j} \text { and } \theta_{\tau_j} \le \max_{k>j} \theta_{\tau_k}\right\}$, a trivial event.
+
+As a brief summary, we want to construct $p$-values $p_j$ such that
+$$\PP_{\substack{\theta_{\tau_1} > \cdots > \theta_{\tau_j} \\ \theta_{\tau_j} \le \max_{k>j} \theta_{\tau_k}}} \left[p_j \le \alpha \;\middle|\; X_{\tau_1} \ge \cdots \ge X_{\tau_j} \ge \max_{k>j} X_{\tau_k}\right].$$
+To avoid the clutter in the subscript notation, we will drop the $\tau$ in the subscript. Hence our goal is now
+$$\PP_{\substack{\theta_1 > \cdots > \theta_j \\ \theta_j \le \max_{k>j} \theta_k}} \left[p_j \le \alpha \;\middle|\; X_1 \ge \cdots \ge X_j \ge \max_{k>j} X_k\right]$$
+Construction of $p_j$ for other permutations $\tau$ can be obtained similarly.
+
+There are many valid options for $p_j$ (such as constant $\alpha$).
+We will follow the idea in the proof of Part 1 of \Cref{thm:main} here.
+$p_j$ is intended to test $H_{0j}: \theta \in \mathcal{M}_j\left(X\right)$, which is equivalent to the union of the null hypotheses:
+\begin{enumerate}
+\item $\theta_k \le \theta_{k+1}$ for $k = 1, \ldots, j-1$, and
+\item $\theta_j \le \theta_k$ for $k = j+1, \ldots, n$.\footnote{The union of these null hypotheses is $\widetilde{H}_{0j}$.}
+\end{enumerate}
+
+Since the joint distribution of $X$, restricted to $\left\{X_1 \ge \cdots \ge X_j \ge \max_{k>j} X_k\right\}$, remains in the exponential family, we can construct the $p$-values for each of the hypotheses above by conditioning on the variables corresponding to the nuisance parameters here, similar to the proof of Part 1 of \Cref{thm:main}.
+Then we can take $p_j$ as the maximum of such $p$-values.
+
+For the hypothesis $H_{0jk}: \theta_j \le \theta_k$, we can construct $p_{jk}$, by considering the survival function of the conditional law
+\begin{align*}
+&~ \mathcal{L}_{\theta_j = \theta_k} \left(D_{jk} \;\middle|\; \left\{X_1 \ge \cdots \ge X_j \ge \max_{\ell>j} X_\ell\right\}, X_{\setminus\left\{j, k\right\}}, M_{jk}\right) \\
+= &~ \mathcal{L}_{\theta_j = \theta_k} \left(D_{jk} \;\middle|\; \left\{X_{j-1} \ge X_j \ge \max_{\substack{\ell>j \\ \ell \ne k}} X_\ell \text{ and } X_j \ge M_{jk}\right\}, X_{\setminus\left\{j, k\right\}}, M_{jk}\right)
+\end{align*}
+
+It is not necessarily true that $X_{j+1} = \max_{\ell > j} X_\ell$, but we will use so as a shorthand and simplify our notation. Now the $p$-values are similar to the ones in \Cref{eq:p1j} for $k>j$.
+
+$$p_{jk} = \frac{\int_{D_{jk}}^{X_{j-1}} g\left(X_1, \ldots, M_{jk} + z, \ldots, M_{jk} - z, \ldots, X_n\right) \,dz}{\int_{\max\left\{X_{j+1} - M_{jk}, 0\right\}}^{X_{j-1}} g\left(X_1, \ldots, M_{jk} + z, \ldots, M_{jk} - z, \ldots, X_n\right) \,dz}.$$
+
+We can graphically represent this in a diagram (\Cref{fig:croprays}) similar to \Cref{fig:comparerays}.
 
@@
 \caption{The two $p$-values constructed corresponds to taking integrals of $g$ along these segments, that lie on a level set of $x_j + x_{j+1} + x_k$.
-The dashed line corresponds to extension in \eqref{eqn:int_extension}.
+The dashed line corresponds to extension in \eqref{eq:int_extension}.
 The dotted line on the far right is the truncation that enforces $X_j < X_{j-1}$.}
-\label{fig:crop_rays}
+\label{fig:croprays}
 \end{figure}
 
-Here we are only comparing $X_j$ to $X_{j+1}$ by \Cref{sec:winnerbest}.
-The upper truncation for $X_j$ can be represented by cropping \Cref{fig:compare_rays} along a vertical line, shown in \Cref{fig:crop_rays}.
-Thus the proof of Part 1 of \Cref{thm:main} that it suffices to compare $X_1$ and $X_2$ remains valid.
-Again we can construct the $p$-values as in \Cref{eqn:p1j} for $k>j$.
+We have $p_{j(j+1)} \ge \max_{k>j} p_{jk}$ by \Cref{sec:winnerbest}: the upper truncation for $X_j$ can be represented by cropping \Cref{fig:comparerays} along a vertical line, shown in \Cref{fig:croprays}.
+Considering $p_{j(j+1)}$ is sufficient in rejecting all the $H_{0jk}$.
+We will take $p_j' = p_{j(j+1)}$, noting that this is the $p$-value that Procedure 3' would produce.
+In fact, $p_j'$ is also the $p$-value we would have constructed if we were to reject only $\widetilde{H}_{0j}$.
 
-$$p_{jk} = \frac{\int_{D_{jk}}^{X_{j-1}} g\left(X_1, \ldots, M_{jk} + z, \ldots, M_{jk} - z, \ldots, X_n\right) \,dz}{\int_{\max\left\{X_{j+1} - M_{jk}, 0\right\}}^{X_{j-1}} g\left(X_1, \ldots, M_{jk} + z, \ldots, M_{jk} - z, \ldots, X_n\right) \,dz}.$$
-
-Hence similar to the proof of Part 1 of \Cref{thm:main}, Schur-concavity ensures $p_{j\left(j+1\right)} \ge p_{jk}$ for all $k>j$, meaning that it is sufficient to compare $X_j$ and $X_{j+1}$.
-In fact, we can take $p_j = p_{j\left(j+1\right)}$.
-These are valid selective $p$-value as required in \citet{Fithian:2015uj}, as
-\begin{align*}
-\PP_\theta \left[p_j \le \alpha \mid \theta_{[k]} \text{ is not the } k\text{-th largest, for some } k \le j\right] = \PP_\theta \left[p_j \le \alpha \mid \mathcal{M}_j\left(X\right)^c = M\right] \le \alpha \text{ a.s.},
-\end{align*}
-for all $\theta \in M$, where $M$ is the selected model, by tower property.
-Note that the conditioning is indeed a random event as the order of $\theta$ depends on $X$ (emphasized with the square brackets here).
-
-\paragraph{FWER is controlled}
-
-\WFcomment{You've already said directly that we are conditioning on $X_{[1]}$ through $X_{[j-1]}$.
-More generally, if we can sidestep the more generic language of that paper and substitute more specific language for our specific problem, I think that will make this a lot more readable.}
-\end{proof}
+Upon constructing $p_j$, one should realize that the $p$-values for testing $\theta_k \le \theta_{k+1}$ would have been constructed in earlier iterations of BasicStop.
+In other words, $p_j = \max_{k \le j} p_k'$ is the sequence of $p$-values that works with BasicStop.
+However, from \eqref{eq:basicstop},
+$$\hat{j}_0 = \min\left\{j: \max_{k \le j} p_k' > \alpha\right\} - 1 = \min\left\{j: p_j' > \alpha\right\} - 1,$$
+so it is safe to apply BasicStop to $p_j'$ directly, yielding Procedure 3'.
 
 \begin{customthm}[Part 3 of \Cref{thm:main}]
-Assume the model~\eqref{eqn:expfam} holds and $g\left(x\right)$ is a Schur-concave function. Procedure 3 is a conservative step-down procedure with FWER no larger than $\alpha$.
+Assume the model~\eqref{eq:expfam} holds and $g\left(x\right)$ is a Schur-concave function. Procedure 3 is a conservative step-down procedure with FWER no larger than $\alpha$.
 \end{customthm}

### 2016-08-26 verifying-winner.tex
Typos from major fix fixed

@@
 While we aim to declare more candidates to be in the correct order, declaring too many candidates, i.e.\ out-of-place candidates, to be in the right order is undesirable.
-While it is possible to consider false discovery rate (the expected portion of out-of-place candidates declared) here, we restrict our derivation to FWER (the probability of having out-of-place candidates declared).
+It is possible to consider false discovery rate (the expected portion of out-of-place candidates declared) here, but we restrict our derivation to FWER (the probability of having any out-of-place candidates declared).
 
@@
 
-Later we will see that Procedure 3 is equivalent to Procedure 3' for the most part, except that Procedure 3 conditions on a larger event $\left\{X_{[j]} \ge \max_{k>j} X_{[k]}\right\}$ in \Cref{lne:event}.
+Procedure 3 is equivalent to Procedure 3' for the most part, except that Procedure 3 conditions on a larger event $\left\{X_{[j]} \ge \max_{k>j} X_{[k]}\right\}$ in \Cref{lne:event}.
 
@@
 We thus analyze Procedure 3' as a special case of the BasicStop procedure on random hypothesis, described in the same paper.
-This enables us to construct valid selective $p$-values and derives Procedure 3'.
+This enables us to construct valid selective $p$-values and derive Procedure 3'.
 
@@
 
-While impractical, Procedure 3' can be thought of as performing all $n$ tests first, producing a sequence of $p$-values $p_j$, returning
+While impractical, Procedure 3' can be thought of as performing all $n$ tests first, producing a sequence of $p$-values $p_j$, and returning
 \begin{equation}
@@
 This is a special case of the BasicStop procedure.
-Instead simply checking that Procedure 3' fits all the requirement for FWER control in BasicStop, we will give the construction of Procedure 3', assuming that we are to estimate $j_0$ with BasicStop.
+Instead of simply checking that Procedure 3' fits all the requirement for FWER control in BasicStop, we will give the construction of Procedure 3', assuming that we are to estimate $j_0$ with BasicStop.
 
@@
 
-\paragraph{Construction of $p$-values}
+\paragraph{Considerations for conditioning}
 
@@
 $$\PP_{\substack{\theta_{\tau_1} > \cdots > \theta_{\tau_j} \\ \theta_{\tau_j} \le \max_{k>j} \theta_{\tau_k}}} \left[p_j \le \alpha \;\middle|\; X_{\tau_1} \ge \cdots \ge X_{\tau_j} \ge \max_{k>j} X_{\tau_k}\right].$$
+
+\paragraph{Construction of the $p$-values}
+
 To avoid the clutter in the subscript notation, we will drop the $\tau$ in the subscript. Hence our goal is now
@@
 
-It is not necessarily true that $X_{j+1} = \max_{\ell > j} X_\ell$, but we will use so as a shorthand and simplify our notation. Now the $p$-values are similar to the ones in \Cref{eq:p1j} for $k>j$.
+It is not necessarily true that $X_{j+1} = \max_{\ell > j} X_\ell$, but we will use so as a shorthand and simplify our notation. Now the $p$-values are similar to the ones in \Cref{eq:p1j}, for $k>j$:
 
@@
 
-We can graphically represent this in a diagram (\Cref{fig:croprays}) similar to \Cref{fig:comparerays}.
+We can graphically represent $p_{jk}$ in \Cref{fig:croprays}, a diagram analogous to \Cref{fig:comparerays}.
 
@@
 
-Upon constructing $p_j$, one should realize that the $p$-values for testing $\theta_k \le \theta_{k+1}$ would have been constructed in earlier iterations of BasicStop.
+Upon constructing $p_j$, one should realize that the $p$-values for testing $\theta_k \le \theta_{k+1}$ would have been constructed in earlier iterations of BasicStop, as $p_k'$.
 In other words, $p_j = \max_{k \le j} p_k'$ is the sequence of $p$-values that works with BasicStop.
@@
 so it is safe to apply BasicStop to $p_j'$ directly, yielding Procedure 3'.
+\end{proof}
 

### 2016-08-31 verifying-winner.tex
some edits to abstract and intro

@@
 Many statistical experiments involve comparing multiple population groups.
-For example, a public opinion poll may ask which of several political candidates commands the most support, or a clinical trial may compare patient outcomes to determine the best of several treatment conditions.
-This article concerns the problem of {\em rank verification} --- post hoc tests of whether the ordering discovered in the data is in fact statistically significant.
-For exponential family models, we show under mild conditions that an unadjusted two-tailed pairwise test comparing the ``winning'' population to the ``runner-up'' is a valid test of whether the winner is truly the best.
-We also propose comparably simple procedures to give lower confidence bounds on the gap between the winning population and the others, and to verify ranks beyond the first.
+For example, a public opinion poll may ask which of several political candidates commands the most support; a social scientific survey may report the most common of several responses to a question; or, a clinical trial may compare binary patient outcomes under several treatment conditions to determine the most effective treatment.
+Having observed the ``winner'' (largest observed response) in a noisy experiment, it is natural to ask whether that candidate, survey response, or treatment is actually the ``best'' (stochastically largest response).
+This article concerns the problem of {\em rank verification} --- post hoc significance tests of whether the orderings discovered in the data reflect the population ranks.
+For exponential family models, we show under mild conditions that an unadjusted two-tailed pairwise test comparing the top two observations (i.e., comparing the ``winner'' to the ``runner-up'') is a valid test of whether the winner is truly the best.
+We extend our analysis to provide equally simple procedures to obtain lower confidence bounds on the gap between the winning population and the others, and to verify ranks beyond the first.
 \end{abstract}
@@
 \caption{Results from a February 1, 2016 Quinnipiac University poll of $890$ Iowa Republicans.
-To compute the last column (Votes), we make the simplifying assumption that the reported percentages in the third column (Result) correspond to raw vote shares among survey respondents.
-The asterisks indicate that the rank is verified at $0.05$-level through a step-down procedure.}
+To compute the last column (Votes), we make the simplifying assumption that the reported percentages in the third column (Result) are raw vote shares among survey respondents.
+The asterisks indicate that the rank is verified at level $0.05$ by a step-down procedure.}
 \label{tbl:poll}
@@
 Nevertheless, if we blithely ignore the selection issue, we might carry out the following analyses to answer the questions we posed before at significance level $\alpha = 0.05$.
-We assume for simplicity that the poll represents a simple random sample of Iowa Republicans; i.e., that the data are a multinomial sample of size $890$ and underlying probabilities $\left(\pi_{\text{Trump}}, \pi_{\text{Cruz}}, \ldots\right)$.\footnote{The reality is a bit more complicated: before releasing the data, Quinnipiac has processed it to make the reported result more representative of likely caucus-goers.}
+We assume for simplicity that the poll represents a simple random sample of Iowa Republicans; i.e., that the data are a multinomial sample of size $890$ and underlying probabilities $\left(\pi_{\text{Trump}}, \pi_{\text{Cruz}}, \ldots\right)$.\footnote{The reality is a bit more complicated: before releasing the data, Quinnipiac has post-processed it to make the reported result more representative of likely caucus-goers.
+The raw data is proprietary.}
 
@@
 Surprisingly, all of the three procedures described above are statistically valid despite their ostensibly ignoring the implicit multiple-comparisons issue.
-The remainder of this article is dedicated to justifying these procedures for the multinomial family and analogous procedures in other settings.
+The remainder of this article is dedicated to justifying these procedures for the multinomial family, and analogous procedures in other settings.
 
@@
 Following the convention in the ranking and selection literature, we assume that if there are multiple largest $\theta_j$, then one is arbitrarily marked as the best.
-Note that in cases where it is more interesting to ask which is the smallest population (for example, if $X_j$ is the number of patients on treatment $j$ who suffer a heart attack during a trial) we can change the variables to $-X$ and the parameters to $\theta$.
+Note that in cases where it is more interesting to ask which is the smallest population (for example, if $X_j$ is the number of patients on treatment $j$ who suffer a heart attack during a trial) we can change the variables to $-X$ and the parameters to $-\theta$; this does not affect the Schur concavity assumption.
 
@@
 For the case of independent binomials we would apply Fisher's exact test, again conditioning on $X_j+X_k$.
-These are both examples of a generic UMPU pairwise test in which we condition on the other $n-2$ indices (notated $X_{\setminus \{j,k\}}$) and $X_j+X_k$, and reject the null if $X_j$ is outside the $\alpha/2$ and $1-\alpha/2$ quantiles of the conditional law $\mathcal{L}_{\theta_j=\theta_k}(X_j \mid X_j+X_k, X_{\setminus\{j,k\}})$, which crucially does not depend on the value of $\theta_j$ or $\theta_k$.
+These are both examples of a generic UMPU pairwise test in which we condition on the other $n-2$ indices (notated $X_{\setminus \{j,k\}}$) and $X_j+X_k$, and reject the null if $X_j$ is outside the $\alpha/2$ and $1-\alpha/2$ quantiles of the conditional law $\mathcal{L}_{\theta_j=\theta_k}(X_j \mid X_j+X_k, X_{\setminus\{j,k\}})$.
+Crucially, this null distribution does not depend on the value of $\theta$ provided that $\theta_j=\theta_k$.
 We call this test the (two-tailed) {\em unadjusted pairwise test} since it makes no explicit adjustment for selection.
-Similarly, inverting this test for all values of $\theta_j-\theta_k$ yields an {\em unadjusted pairwise confidence interval}.\footnote{To avoid trivialities in the discrete case, we assume these procedures are appropriately randomized at the rejection thresholds to give exact level-$\alpha$ control.}
+Similarly, inverting this test for other values of $\theta_j-\theta_k$ yields an {\em unadjusted pairwise confidence interval}.\footnote{To avoid trivialities in the discrete case, we assume these procedures are appropriately randomized at the rejection thresholds to give exact level-$\alpha$ control.}
 
@@
 \end{enumerate}
-Procedure $2$ is modified above due to some technicalities; as we will see, reporting $-\infty$ is not really necessary because the bound can be improved with only a little more work.
+Procedures 2 and 3 are conservative stand-ins for exact, but slightly more involved, procedures.
+In particular, as we will see, reporting $-\infty$ in Procedure 2 is not really necessary because the confidence bound can be improved with an exact conditional procedure.
 
@@
 
-\WFcomment{Merge this discussion with my discussion from NSF.}
+Rank verification, especially for the first rank, has been studied extensively in the ranking and selection literature.
+In particular, \citet{Gutmann:1987fk} prove a result analogous to our main result: that a two-tailed test comparing the winner to the runner-up is valid for log-concave location families.
+\citet{Bofinger:1991hv, Maymin:1992fz, Karnnan:2009iv} give similar results for other models including scale and location-scale families.
+These results use very different technical tools than the ones we use here, require independence between the different groups (ruling out, for example, the multinomial fmaily), and do not address the exponential family case.
+Because most exponential families are not location-scale families (the Gaussian being an exception), both our proof techniques and our technical results are complementary to the techniques and results in the above works.
 
-Previous works construct tests comparing parameters in various families of distributions, by comparing just the winner and the runner-up.
-\citet{Gutmann:1987fk} tackles the question where the observations are from a location family, and the location parameters are compared.
-In which case, the difference of the winner and the runner-up has to pass a predetermined threshold.
-In contrast, a related paper by \citet{Karnnan:2009iv} discusses a scale family, comparing the scale parameters instead.
-Specifically, to test for the smallest variance across multiple populations, it is sufficient to test the ratio of the smallest to the second-smallest variances.
-\citet{Bofinger:1991hv} gives a location-scale family generated by translating an exponential distribution as well.
-Similarly, test the difference between the winner and the runner-up is enough.
-A follow-up paper by \citet{Maymin:1992fz} gave an analogous result for location-scale families, yet still under the constraints of independence.
-
-However, as location-scale families have limited overlap with exponential families, the counterpart question for exponential families remains unaddressed.
-Location-scale families assumes independence between observations, while this is not necessarily the case in exponential families.
-For instance, in the vicinity of the polling problem above, \citet{Nettleton:2009ht} provides an asymptotic test for multinomial distribution, imposing the selection by considering intersection-union tests.
-\citet{Ng:2007cn} also analyzes the multinomial case for an exact test, but with an additional restriction that maximum observation is a known constant $M$.
-In terms of the polling problem above, we poll until one candidate hits a goal $M$.
-While in either papers the observations $X$ are not independent, it still suffices to test the difference between the winner and the runner-up.
-
-One final result that has our attention is the subset selection problem \citep{Gupta:1967wg}.
-The procedure provided in the paper can indeed be used to solve the multinomial case.
-It selects a subset that contains the largest, or ``tagged'', parameter with probability $1-\alpha$.
-Confirming the largest parameter is thus equivalent to asserting the selected subset has size $1$.
-\Cref{sec:subsetsel} includes a comparison of our proposed test and their test.
+For the multinomial case, \citet{Gupta:1967wg}, discussed in Section~\ref{sec:subsetsel} remains the state of the art in finite-sample tests.
+\citet{Nettleton:2009ht} proves validity for an asymptotic version of the winner-versus-runner-up test and \citet{Ng:2007cn} discusses an exact test for a modified problem in which the maximum count is fixed instead of the total count (i.e., we sample until the leading candidate has at least $m$ votes).
+As Section~\ref{sec:subsetsel} shows, our test can be much more powerful than the one in \citet{Gupta:1967wg}, especially if there are many candidates, because of the way our critical rejection threshold for $X_{[1]}-X_{[2]}$ adapts to the data.
+Thus, our paper will close a major gap in the ranking and selection literature, extending the result of \citet{Gutmann:1987fk} and others to new families like the multinomial, $n$ independent binomials, and many others.
 
@@
 
-\WFcomment{Rewrite for motivation}
-
-\Cref{sec:maj} gives a formal definition of Schur-concavity, as well as common examples satisfying this condition.
-\Cref{sec:winnerbest} proves that an unadjusted pairwise test comparing the winner to the runner-up is valid, and demonstrates the power of this test.
-\Cref{sec:confbound,sec:stepdown} justify Procedures 2 and 3.
-We conclude by examining a published study with our methods in \Cref{sec:disc}.
+\Cref{sec:maj} defines Schur concavity, and gives several examples satisfying this condition.
+\Cref{sec:winnerbest} justifies Procedure 1 and compares its power to that of \citet{Gupta:1967wg}.
+\Cref{sec:confbound,sec:stepdown} justify Procedures 2 and 3 and \Cref{sec:disc} concludes.
 
@@
 
-Using the example in \Cref{sec:intro} regarding the polls, we would like to produce a statement of ``Trump is the best, Cruz is the runner-up and Rubio is the second runner-up''.
-Procedure 3 performs unadjusted pairwise tests to ask if Cruz is really the runner-up upon verifying that Trump is the best, and if Rubio is really the second runner-up upon verifying that Cruz is the runner-up, etc., until we can no longer infer that a certain candidate really holds its rank.
+In terms of the Iowa polling example of \Cref{sec:intro}, we would like to produce a statement of the form ``Trump has the most support, Cruz has the second-most, and Rubio has the third-most.'' Procedure 3 performs unadjusted pairwise tests to ask if Cruz is really the runner-up upon verifying that Trump is the best, and if Rubio is really the second runner-up upon verifying that Cruz is the runner-up, etc., until we can no longer infer that a certain candidate really holds its rank.
 
@@
 Then we will have made a Type I error if we declare that the top five ranks are correct ($\hat{j}_0 = 5$), but not if we declare that the top two are correct ($\hat{j}_0 = 2$).
+In other words, $\hat{j}_0$ is a lower confidence bound for $j_0$.
 
@@
 \end{align*}
-
-Thus it suffices to construct the $p$-values such that
+We emphasize here that $\theta$ is {\em not} random, but $\mathcal{M}_{j+1}$ is. Thus it suffices to construct the $p$-values such that
 \begin{equation}

### 2016-09-01 verifying-winner.tex
typo fixed, minor spacing fixed

@@
 The joint distribution of $X$ is given by
-$$p\left(x\right) \propto \exp\left(x' \left(\log p\right)\right) \frac{1}{x_1! \left(m-x_1\right)! \cdots x_n! \left(m-p_n\right)!}$$
+$$p\left(x\right) \propto \exp\left(x' \left(\log p\right)\right) \frac{1}{x_1! \left(m-x_1\right)! \cdots x_n! \left(m-x_n\right)!}$$
 The carrier measure above is Schur-concave.
@@
 
-\begin{example}[Comparing the variances of different normal populations] Suppose there are $n$ normal populations with laws $N\left(\mu_j, \sigma_j^2\right)$ and $m$ independent observations from each of them.
+\begin{example}[Comparing the variances of different normal populations] Suppose there are $n$ normal populations with laws $N(\mu_j, \sigma_j^2)$ and $m$ independent observations from each of them.
 The sample variance for population $j$ can be denoted as $R_j$.
@@
 It suffices to prove the ``if'' part, as the ``only if'' part can be follows from swapping the role of $\theta_1$ and $\theta_2$.
-For any fixed $a$, and $X_1 \ge a$ and $X_2 < a$, we have $X_1 > X_2$ and
-$$\exp\left(\theta_1 X_1 + \theta_2 X_2 + \cdots + \theta_n X_n - \psi\left(\theta\right)\right) g\left(X\right) \ge \exp\left(\theta_1 X_2 + \theta_2 X_1 + \cdots + \theta_n X_n - \psi\left(\theta\right)\right) g\left(X\right).$$
-Integrating both sides over the region $\left\{X: X_1 \ge a, X_2 < a\right\}$ gives
+For any fixed $a$, and $x_1 \ge a$ and $x_2 < a$, we have $x_1 > x_2$ and
+$$\exp\left(\theta_1 x_1 + \theta_2 x_2 + \cdots + \theta_n x_n - \psi\left(\theta\right)\right) g\left(x\right) \ge \exp\left(\theta_1 x_2 + \theta_2 x_1 + \cdots + \theta_n x_n - \psi\left(\theta\right)\right) g\left(x\right).$$
+Integrating both sides over the region $\left\{x: x_1 \ge a, x_2 < a\right\}$ gives
 $$\PP\left[X_1 \ge a, X_2 < a\right] \ge \PP\left[X_1 < a, X_2 \ge a\right].$$
@@
 \begin{proof}
-We can prove so with a coupling argument: for any sequence $X_1, X_2, \ldots, X_n$, define $Y_1, Y_2, \ldots, Y_n$, obtained by swapping $X_1$ with the largest value in the sequence $X$. Hence
-$$\exp\left(\theta_1 Y_1 + \theta_2 Y_2 + \cdots + \theta_n Y_n - \psi\left(\theta\right)\right) g\left(X\right) \ge \exp\left(\theta_1 X_1 + \theta_2 X_2 + \cdots + \theta_n X_n - \psi\left(\theta\right)\right) g\left(X\right).$$
+We can prove so with a coupling argument: for any sequence $x_1, x_2, \ldots, x_n$, define $y_1, y_2, \ldots, y_n$, obtained by swapping $x_1$ with the largest value in the sequence $x$. Hence
+$$\exp\left(\theta_1 y_1 + \theta_2 y_2 + \cdots + \theta_n y_n - \psi\left(\theta\right)\right) g\left(X\right) \ge \exp\left(\theta_1 x_1 + \theta_2 x_2 + \cdots + \theta_n x_n - \psi\left(\theta\right)\right) g\left(X\right).$$
 Integrating both sides over $\mathbb{R}^n$ (or $\mathbb{Z}^n$ in the case of counting measure) gives
@@
 
-To minimize notational clutter, we consider only the case where the winner is $1$ and the runner-up is $2$, etc., i.e.\ $X_1 \ge \cdots \ge X_n$.
+To minimize notational clutter, we consider only the case where the winner is $1$, i.e.\ $X_1 \ge \max_{j > 1} X_j$.
+Furthermore, we will denote the runner-up with $2$.
+This is not necessarily true, but we will use it as a shorthand to simplify our notation.
 For other cases, the following proof remains valid under relabeling and can thus be applied.
@@
 \end{align*}
-The conditional law in \Cref{eq:condlaw}, in particular, is a truncated distribution
+The conditional law of $D_{1j}$ in \eqref{eq:condlaw}, in particular, is a truncated distribution\footnote{Here consider this as a one-dimensional distribution of $D_{1j}$ on $\RR$, where $M_{1j}$ and $X_{\setminus\left\{1, j\right\}}$ are treated as fixed.}
 \begin{align*}
-p\left(D_{1j} \mid M_{1j}, X_{\setminus\left\{1, j\right\}}, A_1\right) & \propto \exp\left(\left(\theta_1 - \theta_j\right) D_{1j} + \theta_2 X_2 + \cdots + \left(\theta_1 + \theta_j\right) M_{1j} + \cdots + \theta_n X_n \right) \\
-& \quad\quad g\left(M_{ij} + D_{ij}, X_2, \ldots, M_{ij} - D_{ij}, \ldots X_n\right) 1_{A_1} \\
-& \stackrel{\text{(a)}}{\propto} g\left(M_{ij} + D_{ij}, X_2, \ldots, M_{ij} - D_{ij}, \ldots X_n\right) 1_{A_1},
+p\left(d_{1j} \mid M_{1j}, X_{\setminus\left\{1, j\right\}}, A_1\right) & \propto \exp\left(\left(\theta_1 - \theta_j\right) d_{1j} + \theta_2 X_2 + \cdots + \left(\theta_1 + \theta_j\right) M_{1j} + \cdots + \theta_n X_n \right) \\
+& \quad\quad g\left(M_{1j} + d_{ij}, X_2, \ldots, M_{ij} - d_{ij}, \ldots X_n\right) 1_{A_1} \\
+& \stackrel{\text{(a)}}{\propto} g\left(M_{1j} + d_{1j}, X_2, \ldots, M_{1j} - d_{1j}, \ldots X_n\right) 1_{A_1},
 \end{align*}
-\WFcomment{This notation is confusing because there should also be another indicator that $M_{ij}=m_{ij}$ where $m_{ij}$ is the realized value this time, also for $X_{\setminus\left\{1,j\right\}}=x_{\cdots}$.}
-\KHcomment{It seems appropriate as conditioning should give a density in terms of the variables being conditioned. Clarified the variables conditioned on nonetheless.}
 where at step (a), conditioning on $X_{\setminus\left\{1, j\right\}}$ and $M_{1j}$ removes dependence on $\theta_{\setminus\left\{1, j\right\}}$ and $\theta_1 + \theta_j$ respectively, while $\theta_1 - \theta_j$ is taken to be $0$ under our null hypothesis.
@@
 \begin{center}
-\includegraphics[width = \textwidth]{plotMultinomialPower}
+\includegraphics[width = \textwidth, clip, trim = {4cm 2cm 4cm 2cm}]{plotMultinomialPower}
 \end{center}
@@
 
-To interpret, e.g., the upper right panel of Figure~\ref{fig:power}, suppose that in a poll of $m = 50$ respondents, one candidate enjoys $30\%$ support and the other $n - 1 = 9$ split the remainder ($\delta = \log\frac{0.3}{0.7 / 9} \approx 1.35$).
+To interpret, e.g., the upper right panel of \Cref{fig:power}, suppose that in a poll of $m = 50$ respondents, one candidate enjoys $30\%$ support and the other $n - 1 = 9$ split the remainder ($\delta = \log\frac{0.3}{0.7 / 9} \approx 1.35$).
 Then our procedure has power approximately $0.3$ to detect the best candidate, while \citeauthor{Gupta:1967wg}'s procedure has power around $0.1$.
@@
 
-The difference between the two methods is amplified when $n$ is large and $\pi_{[1]} \ll 1/2$.
-In that case, $d$ from \citeauthor{Gupta:1967wg} is usually computed based on the worst-case scenario $\pi = \left(\frac{1}{2}, \frac{1}{2}, 0, \ldots, 0\right)$; i.e.
-$d$ is the upper $\alpha$ quantile of
+The difference between the two methods is amplified when $n$ is large and $\pi_{(1)} \ll 1/2$.
+In that case, $d$ from \citeauthor{Gupta:1967wg} is usually computed based on the worst-case scenario $\pi = \left(\frac{1}{2}, \frac{1}{2}, 0, \ldots, 0\right)$; i.e.\ $d$ is the upper $\alpha$ quantile of
 $$X_1 - X_2 \sim m - 2 \cdot \text{Binomial}\left(m, \frac{1}{2}\right) \approx \text{Normal}\left(0, m\right).$$
@@
 $$X_1 - X_2 \mid X_1 + X_2 \sim X_1 + X_2 - 2 \cdot \text{Binomial}\left(X_1 + X_2, \frac{1}{2}\right),$$
-which is approximately $\sqrt{X_1 + X_2} z_{\alpha / 2}$. If $\pi_{[1]} \ll 1/2$ then with high probability $X_1 + X_2 \ll  m$, making our test much more liberal.
+which is approximately $\sqrt{X_1 + X_2} z_{\alpha / 2}$. If $\pi_{(1)} \ll 1/2$ then with high probability $X_1 + X_2 \ll  m$, making our test much more liberal.
 
@@
 \begin{proof}
-Again we start with assuming $X_1 \ge \cdots \ge X_n$. The $p$-values in question are derived from the conditional law
+Again we start with assuming $X_1 \ge X_2 \ge \max_{j > 2} X_j$ for convenience. The $p$-values in question are derived from the conditional law
 $$\mathcal{L}_{\theta_1 - \theta_j = \delta} \left(D_{1j} \;\middle|\; M_{1j}, X_2, \ldots, X_n, A\right),$$
@@
 \begin{align*}
-p\left(D_{1j}\right) & \propto \exp\left(\left(\theta_1 - \theta_j\right) D_{1j} + \theta_2 X_2 + \cdots + \left(\theta_1 + \theta_j\right) M_{1j} + \cdots + \theta_n X_n \right) \\
-& \quad\quad g\left(M_{1j} + D_{1j}, X_2, \ldots, M_{1j} - D_{1j}, \ldots X_n\right) 1_{A_1} \\
-& \propto \exp\left(\delta D_{1j}\right) g\left(M_{1j} + D_{1j}, X_2, \ldots, M_{1j} - D_{1j}, \ldots X_n\right) 1_{A_1}.
+p\left(d_{1j}\right) & \propto \exp\left(\left(\theta_1 - \theta_j\right) d_{1j} + \theta_2 X_2 + \cdots + \left(\theta_1 + \theta_j\right) M_{1j} + \cdots + \theta_n X_n \right) \\
+& \quad\quad g\left(M_{1j} + d_{1j}, X_2, \ldots, M_{1j} - d_{1j}, \ldots X_n\right) 1_{A_1} \\
+& \propto \exp\left(\delta d_{1j}\right) g\left(M_{1j} + d_{1j}, X_2, \ldots, M_{1j} - d_{1j}, \ldots X_n\right) 1_{A_1}.
 \end{align*}
@@
 
-Often we will be interested in verifying ranks beyond the winner. More generally, we could imagine declaring that the first $j$ candidates are all in the correct order, that is
+Often we will be interested in verifying ranks beyond the winner. More generally, we could imagine declaring that the first $j$ populations are all in the correct order, that is
 \begin{equation}
@@
 
-In terms of the Iowa polling example of \Cref{sec:intro}, we would like to produce a statement of the form ``Trump has the most support, Cruz has the second-most, and Rubio has the third-most.'' Procedure 3 performs unadjusted pairwise tests to ask if Cruz is really the runner-up upon verifying that Trump is the best, and if Rubio is really the second runner-up upon verifying that Cruz is the runner-up, etc., until we can no longer infer that a certain candidate really holds its rank.
+In terms of the Iowa polling example of \Cref{sec:intro}, we would like to produce a statement of the form ``Trump has the most support, Cruz has the second-most, and Rubio has the third-most.'' Procedure 3 performs unadjusted pairwise tests to ask if Cruz is really the runner-up upon verifying that Trump is the best, and if Rubio is really the second runner-up upon verifying that Cruz is the runner-up, etc., until we can no longer infer that a certain population really holds its rank.
 
-While we aim to declare more candidates to be in the correct order, declaring too many candidates, i.e.\ out-of-place candidates, to be in the right order is undesirable.
-It is possible to consider false discovery rate (the expected portion of out-of-place candidates declared) here, but we restrict our derivation to FWER (the probability of having any out-of-place candidates declared).
+While we aim to declare more populations to be in the correct order, declaring too many populations, i.e.\ out-of-place populations, to be in the right order is undesirable.
+It is possible to consider false discovery rate (the expected portion of out-of-place populations declared) here, but we restrict our derivation to FWER (the probability of having any out-of-place populations declared).
 
 Formally, let $\hat{j}_0$ denote the number of ranks validated by a procedure (the number of rejections).
-Then the FWER of $\hat{j}_0$ is the probability that too many rejections are made; i.e.
-$\PP\left[\hat{j}_0 > j_0\right]$.
+Then the FWER of $\hat{j}_0$ is the probability that too many rejections are made; i.e.\ $\PP\left[\hat{j}_0 > j_0\right]$.
 For example, suppose that the top three data ranks and population ranks coincide, but not the fourth ($j_0 = 3$).
@@
 To show that Procedure 3 is valid, we will prove the validity of a more liberal Procedure 3', described in \Cref{alg:proc3}.
+Procedure 3 is equivalent to Procedure 3' for the most part, except that Procedure 3 conditions on a larger event $\left\{X_{[j]} \ge \max_{k>j} X_{[k]}\right\}$ in \Cref{lne:event}.
 
@@
 
-Procedure 3 is equivalent to Procedure 3' for the most part, except that Procedure 3 conditions on a larger event $\left\{X_{[j]} \ge \max_{k>j} X_{[k]}\right\}$ in \Cref{lne:event}.
-
 \begin{theorem}
@@
 
-Adapting this notation, the FWER can be viewed as $\PP\left[\text{reject } H_{0 {j_0+1}}\right]$.
+Adapting this notation, the FWER can be viewed as $\PP\left[\text{reject } H_{0(j_0+1)}\right]$.
 
@@
 
-To avoid the clutter in the subscript notation, we will drop the $\tau$ in the subscript. Hence our goal is now
+To avoid the clutter in the subscripts, we will drop the $\tau$ in the subscript. Hence our goal is now
 $$\PP_{\substack{\theta_1 > \cdots > \theta_j \\ \theta_j \le \max_{k>j} \theta_k}} \left[p_j \le \alpha \;\middle|\; X_1 \ge \cdots \ge X_j \ge \max_{k>j} X_k\right]$$
@@
 
-It is not necessarily true that $X_{j+1} = \max_{\ell > j} X_\ell$, but we will use so as a shorthand and simplify our notation. Now the $p$-values are similar to the ones in \Cref{eq:p1j}, for $k>j$:
+Once again, $X_{j+1} = \max_{\ell > j} X_\ell$ is simply shorthand for simplifying our notation. Now the $p$-values are similar to the ones in \Cref{eq:p1j}, for $k>j$:
 
@@
 Considering $p_{j(j+1)}$ is sufficient in rejecting all the $H_{0jk}$.
-We will take $p_j' = p_{j(j+1)}$, noting that this is the $p$-value that Procedure 3' would produce.
-In fact, $p_j'$ is also the $p$-value we would have constructed if we were to reject only $\widetilde{H}_{0j}$.
+We will take $p_{j*} = p_{j(j+1)}$, noting that this is the $p$-value that Procedure 3' would produce.
+In fact, $p_{j*}$ is also the $p$-value we would have constructed if we were to reject only $\widetilde{H}_{0j}$.
 
-Upon constructing $p_j$, one should realize that the $p$-values for testing $\theta_k \le \theta_{k+1}$ would have been constructed in earlier iterations of BasicStop, as $p_k'$.
-In other words, $p_j = \max_{k \le j} p_k'$ is the sequence of $p$-values that works with BasicStop.
+Upon constructing $p_j$, one should realize that the $p$-values for testing $\theta_k \le \theta_{k+1}$ would have been constructed in earlier iterations of BasicStop, as $p_{k*}$.
+In other words, $p_j = \max_{k \le j} p_{k*}$ is the sequence of $p$-values that works with BasicStop.
 However, from \eqref{eq:basicstop},
-$$\hat{j}_0 = \min\left\{j: \max_{k \le j} p_k' > \alpha\right\} - 1 = \min\left\{j: p_j' > \alpha\right\} - 1,$$
-so it is safe to apply BasicStop to $p_j'$ directly, yielding Procedure 3'.
+$$\hat{j}_0 = \min\left\{j: \max_{k \le j} p_{k*} > \alpha\right\} - 1 = \min\left\{j: p_{j*} > \alpha\right\} - 1,$$
+so it is safe to apply BasicStop to $p_{j*}$ directly, yielding Procedure 3'.
 \end{proof}

### 2016-09-28 verifying-winner.tex
added discussion, made some other minor edits

@@
 Seeing that Trump leads this poll, several salient questions may occur to us: Is Trump really winning, and if so by how much?
-And analogously, is Cruz really in second, is Rubio really in third, and so on?
+Furthermore, is Cruz really in second, is Rubio really in third, and so on?
 Note that there is implicitly a problem of multiple comparisons here, because if Cruz had led the poll instead, we would be asking a different set of questions.
@@
 As we will see, $\theta_j \ge \theta_k$ if and only if $X_j$ is stochastically larger than $X_k$; thus, there is a well-defined stochastic ordering of the populations that matches the ordering of the entries of $\theta$.
-We will refer to the population with maximal $\theta_j$ as the {\em best}, the one with maximal $X_j$ as the {\em winner}, and the one with maximal $X_j$ other than the winner as the {\em runner-up}.
+We will refer to the population with maximal $\theta_j$ as the {\em best}, the one with maximal $X_j$ as the {\em winner}, and the one with the second-largest $X_j$ as the {\em runner-up}, where ties between observations are broken randomly to obtain a full ordering.
 Following the convention in the ranking and selection literature, we assume that if there are multiple largest $\theta_j$, then one is arbitrarily marked as the best.
@@
 where $[j]$ will denote the random index for the $j$-th order statistic.
-Define $\theta_{[j]}$ as the entry of $\theta$ corresponding to the $j$-th order statistic of $X$ (so $\theta_{[1]}$ might {\em not} equal $\max_j \theta_j$, for example).
-We assume any ties between entries of $X$ are broken randomly.
+Thus, $\theta_{[j]}$ is the entry of $\theta$ corresponding to the $j$-th order statistic of $X$ (so $\theta_{[1]}$ might {\em not} equal $\max_j \theta_j$, for example).
 
@@
 \end{enumerate}
-Procedures 2 and 3 are conservative stand-ins for exact, but slightly more involved, procedures.
-In particular, as we will see, reporting $-\infty$ in Procedure 2 is not really necessary because the confidence bound can be improved with an exact conditional procedure.
+Procedures 2 and 3 are conservative stand-ins for exact, but slightly more involved, conditional inference procedures.
+In particular, as we will see, reporting $-\infty$ in Procedure 2 is typically much more conservative than is necessary.
 
@@
 \begin{enumerate}
-\item Procedure 1 has level $\alpha$ conditional on the best population not winning (otherwise an error is impossible).
+\item Procedure 1 has level $\alpha$ conditional on the best population not winning (otherwise a Type I error is impossible).
 \item Procedure 2 gives a conservative $1-\alpha$ lower confidence bound for $\theta_{[1]} - \max_{j \ne [1]} \theta_{j}$.
@@
 Because any log-concave and symmetric function is Schur-concave, \Cref{thm:main} applies to all of the cases discussed above.
-The proof relies on the conditional selective-inference framework of \citet{Fithian:2014ws} combined with classical multiple-testing methods, as well as some properties of majorization and Schur-concavity.
+The proof combines the conditional selective-inference framework of \citet{Fithian:2014ws} with classical multiple-testing methods, as well as new technical tools involving majorization and Schur-concavity.
 
-Note that these procedures make an implicit adjustment for selection because they use two-tailed unadjusted tests.
-If we instead based our tests on an independent realization $X^*$, then, for example, Procedure 1 could use a right-tailed version of the unadjusted pairwise test.
-In the case $n = 2$, Procedure 1 amounts to a simple two-tailed test of the null hypothesis $\theta_1 = \theta_2$, and it is intuitively clear that a one-tailed test would be more liberal.
+Note that these procedures make an implicit adjustment for selection because they use two-tailed, rather than one-tailed, unadjusted tests.
+If we instead based our tests on an independent realization $X^*= (X_1^*,\ldots,X_n^*)$ then, for example, Procedure 1 could use a right-tailed version of the unadjusted pairwise test.
+In the case $n = 2$, Procedure 1 amounts to a simple two-tailed test of the null hypothesis $\theta_1 = \theta_2$, and it is intuitively clear that a one-tailed test would be too liberal.
 More surprising is that, no matter how large $n$ is, Procedures 1--3 require no further adjustment beyond what is required when $n = 2$.
@@
 
-Rank verification, especially for the first rank, has been studied extensively in the ranking and selection literature.
-In particular, \citet{Gutmann:1987fk} prove a result analogous to our main result: that a two-tailed test comparing the winner to the runner-up is valid for log-concave location families.
+Rank verification, especially for the first rank, has been studied extensively in the ranking and selection literature; see~\citet{Gupta:1971wk} and \citet{hsu1996multiple} for surveys.
+In particular, \citet{Gutmann:1987fk} prove a result analogous to our main result in a different setting: that a two-tailed test comparing the winner to the runner-up is valid for log-concave location families.
 \citet{Bofinger:1991hv, Maymin:1992fz, Karnnan:2009iv} give similar results for other models including scale and location-scale families.
-These results use very different technical tools than the ones we use here, require independence between the different groups (ruling out, for example, the multinomial fmaily), and do not address the exponential family case.
-Because most exponential families are not location-scale families (the Gaussian being an exception), both our proof techniques and our technical results are complementary to the techniques and results in the above works.
+These results use very different technical tools than the ones we use here, require independence between the different groups (ruling out, for example, the multinomial family), and do not address the exponential family case.
+Because most exponential families are not location-scale families (the Gaussian being a notable exception), and because our results involve more general dependence structures, both our proof techniques and our technical results are complementary to the techniques and results in the above works.
 
 For the multinomial case, \citet{Gupta:1967wg}, discussed in Section~\ref{sec:subsetsel} remains the state of the art in finite-sample tests.
-\citet{Nettleton:2009ht} proves validity for an asymptotic version of the winner-versus-runner-up test and \citet{Ng:2007cn} discusses an exact test for a modified problem in which the maximum count is fixed instead of the total count (i.e., we sample until the leading candidate has at least $m$ votes).
+\citet{Nettleton:2009ht} proves validity for an asymptotic version of the winner-versus-runner-up test.
+\citet{Ng:2007cn} discuss an exact test for a modified problem in which the maximum count is fixed instead of the total count; that is, we sample until the leading candidate has at least $m$ votes.
 As Section~\ref{sec:subsetsel} shows, our test can be much more powerful than the one in \citet{Gupta:1967wg}, especially if there are many candidates, because of the way our critical rejection threshold for $X_{[1]}-X_{[2]}$ adapts to the data.
-Thus, our paper will close a major gap in the ranking and selection literature, extending the result of \citet{Gutmann:1987fk} and others to new families like the multinomial, $n$ independent binomials, and many others.
+Thus, our paper will close a major gap in the ranking and selection literature, extending the result of \citet{Gutmann:1987fk} and others to new families like the multinomial, independent binomials, and many others.
 
@@
 \Cref{sec:winnerbest} justifies Procedure 1 and compares its power to that of \citet{Gupta:1967wg}.
-\Cref{sec:confbound,sec:stepdown} justify Procedures 2 and 3 and \Cref{sec:disc} concludes.
+\Cref{sec:confbound,sec:stepdown} justify Procedures 2 and 3 respectively, and \Cref{sec:disc} concludes.
 
-\section{Majorization and Schur-concavity}
+\section{Majorization and Schur concavity}
 \label{sec:maj}
@@
 The joint distribution of $X$ is given by
-$$p\left(x\right) \propto \exp\left(x' \left(\log p\right)\right) \frac{1}{x_1! \left(m-x_1\right)! \cdots x_n! \left(m-x_n\right)!}$$
+$$p\left(x\right) \propto \exp\left(\sum_j x_j \log\frac{p_j}{1-p_j}\right) \frac{1}{x_1! \left(m-x_1\right)! \cdots x_n! \left(m-x_n\right)!}$$
 The carrier measure above is Schur-concave.
@@
 \begin{theorem}
-For a multivariate exponential family with a symmetric carrier distribution, $X_1 \ge X_2$ in stochastic order if and only if $\theta_1 > \theta_2$.
+For a multivariate exponential family with a symmetric carrier distribution, $X_1 \ge X_2$ in stochastic order if and only if $\theta_1 \geq \theta_2$.
 \label{thm:stoch}
@@
 If $p_j$ are valid $p$-values for testing null hypothesis $H_{0j}$, then $p_* = \max_j p_j$ is a valid $p$-value for the union null (i.e.\ disjunction null) hypothesis $H_0 = \bigcup_j H_{0j}$.
-If all the $p$-values are uniform, then $p_*$ is also a valid $p$-value.
 \label{lma:union}
@@
 $$n \PP\left[1 \text{ wins}\right] \ge 1$$
-as desired.
+as desired. \WFcomment{can you make this argument a bit more explicit? And how does it work for discrete data?}
 \end{proof}
@@
 
-\WFcomment{Discussion still needs fleshing out.}
+Combining ideas from conditional inference and multiple testing, we have proven the validity of several very simple and seemingly ``naive'' procedures for significance testing of sample ranks.
+In particular, we have shown that an unadjusted pairwise test comparing the winner with the runner-up is a valid significance test for the first rank.
+Our result complements and extends pre-exisiting analogous results for location and location-scale families with independence between observations.
+Our approach is considerably more powerful than previously known solutions.
+We provide similarly straightforward conservative methods for producing a lower confidence bound for the difference between the winner and runner up, and for verifying ranks beyond the first.
 
-Our selective test procedure allows us to untangle multiple comparisons based on correlated observations easily, while avoiding the pitfalls of selection.
 Claims reporting the ``winner'' are commonly made in the scientific literature, usually with no significance level reported or an incorrect method applied.
-For example, \citet{Uhls:2012gf} asked $n=20$ elementary and middle school students which of seven personal values they most hoped to embody as adults: ``Fame'' (8 selected), ``Benevolence'' (5), ``Achievement'' (3), and several others (4 total including one response of ``Other'').
-The authors' main finding --- which appeared in the abstract, the first paragraph of the article, and later a CNN.com headline --- was that ``Fame'' was the most common response.
-This claim was accompanied by a significance level of $0.006$, which the authors computed by testing whether the probability of selecting ``Fame'' was larger than 1/7.
-
-The obvious error in the authors' reasoning is perhaps understandable since there is, presently, no agreed-upon statistical solution for this commonplace problem.
-Using our approach, they could have performed a two-tailed binomial test of the winner (``Fame'') vs.
-the runner-up (``Benevolence'').
-This test returns a $p$-value of
-$$p = 2 \cdot \PP\left[\text{Binomial}\left(8 + 5, 0.5\right) \ge 8\right] = 0.58,$$
-indicating that their data did not support their major finding.
-
-This paper has provided a straightforward yet powerful method for verifying that the winner is the best, for joint distributions in the exponential family with a mild technical condition.
-Such a test allows us to ``ignore'' the issues of selection and multiple-testing with relative ease and power.
-\WFcomment{This last sentence might give the wrong impression.}
+For example, \citet{Uhls:2012gf} asked $n=20$ elementary and middle school students which of seven personal values they most hoped to embody as adults, with ``Fame'' (8 responses) being the most commonly selected, with ``Benevolence'' (5 responses) second.
+The authors' main finding --- which appeared in the abstract, the first paragraph of the article, and later a CNN.com headline \citep{alikhani} --- was that ``Fame'' was the most likely response, accompanied by a significance level of $0.006$, which the authors computed by testing whether the probability of selecting ``Fame'' was larger than 1/7.
+The obvious error in the authors' reasoning could have been avoided if they had performed an equally straightforward two-tailed binomial test of ``Fame'' vs.
+``Benevolence,'' which would have produced a $p$-value of $0.58$.
 

### 2016-09-28 verifying-winner.tex
two bibs combined, elaborated on lemma

@@
 \begin{proof}
-We can prove so with a coupling argument: for any sequence $x_1, x_2, \ldots, x_n$, define $y_1, y_2, \ldots, y_n$, obtained by swapping $x_1$ with the largest value in the sequence $x$. Hence
-$$\exp\left(\theta_1 y_1 + \theta_2 y_2 + \cdots + \theta_n y_n - \psi\left(\theta\right)\right) g\left(X\right) \ge \exp\left(\theta_1 x_1 + \theta_2 x_2 + \cdots + \theta_n x_n - \psi\left(\theta\right)\right) g\left(X\right).$$
-Integrating both sides over $\mathbb{R}^n$ (or $\mathbb{Z}^n$ in the case of counting measure) gives
+We can prove so with a coupling argument: for any sequence $x_1, x_2, \ldots, x_n$, define $\tau\left(x\right) = \left\{\tau\left(x_j\right)\right\}_{j = 1, \ldots, n}$, obtained by swapping $x_1$ with the largest value in the sequence $x$.
+Hence
+$$\exp\left(\theta_1 \tau\left(x_1\right) + \cdots + \theta_n \tau\left(x_n\right) - \psi\left(\theta\right)\right) g\left(X\right) \ge \exp\left(\theta_1 x_1 + \cdots + \theta_n x_n - \psi\left(\theta\right)\right) g\left(X\right).$$
+If we integrating both sides over $\mathbb{R}^n$ (or $\mathbb{Z}^n$ in the case of counting measure), the right hand side gives $1$.
+Since $\tau$ is an $n$-to-$1$ mapping, the left hand side is $n$ times the integral over $\left\{x_1 \ge \max_{j > 1} x_j\right\}$.
+In other words
 $$n \PP\left[1 \text{ wins}\right] \ge 1$$
-as desired. \WFcomment{can you make this argument a bit more explicit? And how does it work for discrete data?}
+as desired.
+
+In the case of counting measure, the above argument follows if a subscript is attached to identical observations uniformly to ensure strict ordering.
 \end{proof}
@@
 \bibliographystyle{plainnat}
-\bibliography{papers,additional}
+\bibliography{papers}
 

### 2016-09-29 verifying-winner.tex
underfull hbox fixed

@@
 
-\begin{lemma}~\\
+\begin{lemma}\leavevmode
 \begin{enumerate}
@@
 
-\begin{proof}~\\
+\begin{proof}\leavevmode
 \begin{enumerate}
@@
 
-Following the framework in \citet{Fithian:2014ws}, we first construct the p-values by conditioning on the selection event where the winner is $1$: 
+Following the framework in \citet{Fithian:2014ws}, we first construct the $p$-values by conditioning on the selection event where the winner is $1$: 
 $$A_1 = \left\{X_1 \ge \max_{j > 1} X_j\right\}.$$
@@
 
-Before conditioning on $A_1$, the distribution in \label{eq:condlaw} is symmetric around 0 under $\theta_1=\theta_j$.
+Before conditioning on $A_1$, the distribution in \eqref{eq:condlaw} is symmetric around $0$ under $\theta_1=\theta_j$.
 Since the denominator of $p_{12}$ integrates over half of this symmetric distribution, it is always equal to $1/2$.

### 2016-10-04 verifying-winner.tex
added detail to examples section, included a few more references.

@@
 
-Rank verification, especially for the first rank, has been studied extensively in the ranking and selection literature; see~\citet{Gupta:1971wk} and \citet{hsu1996multiple} for surveys.
+Rank verification, especially for the first rank, has been studied extensively in the ranking and selection literature; see~\citet{Gupta:1971wk}, \citet{gupta1985subset}, and \citet{hsu1996multiple} for surveys.
 In particular, \citet{Gutmann:1987fk} prove a result analogous to our main result in a different setting: that a two-tailed test comparing the winner to the runner-up is valid for log-concave location families.
@@
 
-For the multinomial case, \citet{Gupta:1967wg}, discussed in Section~\ref{sec:subsetsel} remains the state of the art in finite-sample tests.
-\citet{Nettleton:2009ht} proves validity for an asymptotic version of the winner-versus-runner-up test.
+For the multinomial case, \citet{Gupta:1967wg}, discussed in Section~\ref{sec:subsetsel} remains the state of the art in finite-sample tests; \citet{gupta1978subset} discusses related approaches for Poisson models.
+\citet{Nettleton:2009ht} proves validity for an asymptotic version of the winner-versus-runner-up test, and \citet{gupta1989selecting} consider an empirical Bayes approach for selecting the best binomial population wherein a parametric prior distribution is assumed for the success probabilities for the different populations.
 \citet{Ng:2007cn} discuss an exact test for a modified problem in which the maximum count is fixed instead of the total count; that is, we sample until the leading candidate has at least $m$ votes.
 As Section~\ref{sec:subsetsel} shows, our test can be much more powerful than the one in \citet{Gupta:1967wg}, especially if there are many candidates, because of the way our critical rejection threshold for $X_{[1]}-X_{[2]}$ adapts to the data.
-Thus, our paper will close a major gap in the ranking and selection literature, extending the result of \citet{Gutmann:1987fk} and others to new families like the multinomial, independent binomials, and many others.
+Thus, our work closes a significant gap in the ranking and selection literature, extending the result of \citet{Gutmann:1987fk} and others to new families like the multinomial, independent binomials, and many others.
 
@@
 \label{sec:maj}
+
+\subsection{Definitions and basic properties}
 
@@
 A Schur-concave function is symmetric by default since $a \succeq b$ and $b \succeq a$ if and only if $b$ is a permutation of the coordinates of $a$.
-Conversely a symmetric and log-concave function is Schur-concave \citep{Marshall:2010hb}, thus many common exponential family distributions lie in this class.
-To name a few:
+Conversely a symmetric and log-concave function is Schur-concave \citep{Marshall:2010hb}.
+Interestingly, \citet{bjornstad1981class} also show that, in the context of independent location families, Schur concavity is equivalent to monotone likelihood ratio.
+
+\subsection{Examples}
+
+Many common exponential family models have Schur-concave carrier densities. Below we give a few examples:
 
@@
 $$p\left(x\right) \propto \exp\left(\sum_j x_j \log\frac{p_j}{1-p_j}\right) \frac{1}{x_1! \left(m-x_1\right)! \cdots x_n! \left(m-x_n\right)!}$$
-The carrier measure above is Schur-concave.
+The carrier measure above is Schur-concave. The unadjusted pairwise test in this family is Fisher's exact test.
 \end{example}
@@
 Therefore, we can use Procedures 1--3 to compare player qualities.
+
+After conditioning on $U(X)=(X_1+X_2, X_3,\ldots,X_n)$, and under the assumption $\theta_1=\theta_2$, every feasible configuration of $Y$ is equally likely.
+If $n$ is not too large (say, no more than 40 players), we can find the conditional distribution of $X_1$ by enumerating over the configurations; for larger $n$, computation might pose a more serious problem, requiring us for example to compute the $p$-value using Markov Chain Monte Carlo techniques~\citep{besag1989generalized}.
 \end{example}
@@
 Thus, we can use Procedures 1--3 to find populations with the smallest or largest variances.
+In this example, the distribution of $X_1/(X_1+X_2)$ conditional on $(X_1+X_2,X_3,\ldots,X_4)$ is distributed as $text{Beta}(m/2,m/2)$ under the null, or equivalently $X_1/X_2$ is conditionally distributed as $F_{m,m}$; hence a (two-tailed) $F$-test is valid for comparing the top two populations.
 \end{example}

### 2016-10-04 verifying-winner.tex
duplicates in bib cleaned up, solved some badbox

--- 2016-09-29 verifying-winner.tex
@@
 \usetikzlibrary{calc}
+\usepackage[hyphens]{url}
 \usepackage{verbatim}
@@
 If the test rejects at level $\alpha$, conclude that the winner is really the best.
-\item {\em By how much?} Construct the unadjusted pairwise confidence interval comparing the winner to the runner-up, and report the lower confidence bound obtained for $\theta_{[1]}-\theta_{[2]}$ if it is nonnegative, report $-\infty$ otherwise.
+\item {\em By how much?} Construct the unadjusted pairwise confidence interval comparing the winner to the runner-up, and report the lower confidence bound obtained for $\theta_{[1]} - \theta_{[2]}$ if it is nonnegative, report $-\infty$ otherwise.
 \item {\em Is the runner-up really the second best, etc.?} Continue by comparing the runner-up to the second-runner-up, again using the unadjusted pairwise test, and so on down the list comparing adjacent values.
@@
 Note that these procedures make an implicit adjustment for selection because they use two-tailed, rather than one-tailed, unadjusted tests.
-If we instead based our tests on an independent realization $X^*= (X_1^*,\ldots,X_n^*)$ then, for example, Procedure 1 could use a right-tailed version of the unadjusted pairwise test.
+If we instead based our tests on an independent realization $X^* = (X_1^*, \ldots, X_n^*)$ then, for example, Procedure 1 could use a right-tailed version of the unadjusted pairwise test.
 In the case $n = 2$, Procedure 1 amounts to a simple two-tailed test of the null hypothesis $\theta_1 = \theta_2$, and it is intuitively clear that a one-tailed test would be too liberal.
@@
 
-Rank verification, especially for the first rank, has been studied extensively in the ranking and selection literature; see~\citet{Gupta:1971wk} and \citet{hsu1996multiple} for surveys.
+Rank verification, especially for the first rank, has been studied extensively in the ranking and selection literature; see \citet{Gupta:1971wk, Gupta:1985bj}, and \citet{Hsu:1996} for surveys.
 In particular, \citet{Gutmann:1987fk} prove a result analogous to our main result in a different setting: that a two-tailed test comparing the winner to the runner-up is valid for log-concave location families.
@@
 
-For the multinomial case, \citet{Gupta:1967wg}, discussed in Section~\ref{sec:subsetsel} remains the state of the art in finite-sample tests.
-\citet{Nettleton:2009ht} proves validity for an asymptotic version of the winner-versus-runner-up test.
+For the multinomial case, \citet{Gupta:1967wg}, discussed in \Cref{sec:subsetsel}, remain the state of the art in finite-sample tests; \citet{Gupta:1976vd} discuss related approaches for Poisson models.
+\citet{Nettleton:2009ht} proves validity for an asymptotic version of the winner-versus-runner-up test, and \citet{Gupta:1989fe} consider an empirical Bayes approach for selecting the best binomial population wherein a parametric prior distribution is assumed for the success probabilities for the different populations.
 \citet{Ng:2007cn} discuss an exact test for a modified problem in which the maximum count is fixed instead of the total count; that is, we sample until the leading candidate has at least $m$ votes.
-As Section~\ref{sec:subsetsel} shows, our test can be much more powerful than the one in \citet{Gupta:1967wg}, especially if there are many candidates, because of the way our critical rejection threshold for $X_{[1]}-X_{[2]}$ adapts to the data.
-Thus, our paper will close a major gap in the ranking and selection literature, extending the result of \citet{Gutmann:1987fk} and others to new families like the multinomial, independent binomials, and many others.
+As \Cref{sec:subsetsel} shows, our test can be much more powerful than the one in \citet{Gupta:1967wg}, especially if there are many candidates, because of the way our critical rejection threshold for $X_{[1]} - X_{[2]}$ adapts to the data.
+Thus, our work closes a significant gap in the ranking and selection literature, extending the result of \citet{Gutmann:1987fk} and others to new families like the multinomial, independent binomials, and many others.
 
@@
 A Schur-concave function is symmetric by default since $a \succeq b$ and $b \succeq a$ if and only if $b$ is a permutation of the coordinates of $a$.
-Conversely a symmetric and log-concave function is Schur-concave \citep{Marshall:2010hb}, thus many common exponential family distributions lie in this class.
-To name a few:
+Conversely a symmetric and log-concave function is Schur-concave \citep{Marshall:2010hb}.
+Interestingly, \citet{Gupta:1984fw} also show that, in the context of independent location families, Schur concavity of the probability density is equivalent to monotone likelihood ratio.
+
+\subsection{Examples}
+
+Many common exponential family models have Schur-concave carrier densities. Below we give a few examples:
 
@@
 Therefore, we can use Procedures 1--3 to compare player qualities.
+
+After conditioning on $U(X) = (X_1 + X_2, X_3, \ldots, X_n)$, and under the assumption $\theta_1 = \theta_2$, every feasible configuration of $Y$ is equally likely.
+If $n$ is not too large (say, no more than $40$ players), we can find the conditional distribution of $X_1$ by enumerating over the configurations; for larger $n$, computation might pose a more serious problem, requiring us for example to compute the $p$-value using Markov Chain Monte Carlo techniques \citep{Besag:1989}.
 \end{example}
@@
 Thus, we can use Procedures 1--3 to find populations with the smallest or largest variances.
+In this example, the distribution of $X_1 / (X_1 + X_2)$ conditional on $(X_1 + X_2, X_3, \ldots, X_4)$ is distributed as $\text{Beta}(m/2, m/2)$ under the null, or equivalently $X_1 / X_2$ is conditionally distributed as $F_{m, m}$; hence a (two-tailed) $F$-test is valid for comparing the top two populations.
 \end{example}
@@
 $$\exp\left(\theta_1 x_1 + \theta_2 x_2 + \cdots + \theta_n x_n - \psi\left(\theta\right)\right) g\left(x\right) \ge \exp\left(\theta_1 x_2 + \theta_2 x_1 + \cdots + \theta_n x_n - \psi\left(\theta\right)\right) g\left(x\right).$$
-Integrating both sides over the region $\left\{x: x_1 \ge a, x_2 < a\right\}$ gives
+Integrating both sides over the region $\left\{x:\; x_1 \ge a, x_2 < a\right\}$ gives
 $$\PP\left[X_1 \ge a, X_2 < a\right] \ge \PP\left[X_1 < a, X_2 \ge a\right].$$
@@
 For other cases, the following proof remains valid under relabeling and can thus be applied.
-In this case, we will test the null hypothesis $H_{01}: \theta_1 \le \max_{j > 1} \theta_j$, which is the union of the null hypotheses $H_{01j}: \theta_1 \le \theta_j$ for $j \ge 2$.
+In this case, we will test the null hypothesis $H_{01}:\; \theta_1 \le \max_{j > 1} \theta_j$, which is the union of the null hypotheses $H_{01j}:\; \theta_1 \le \theta_j$ for $j \ge 2$.
 For each of these we can construct an exact $p$-value $p_{1j}$, which is valid under $H_{01j}$ conditional on $A_1$, the event that $X_1$ is the winner.
@@
 
-From the first part of this proof, both p-values are constructed by conditioning on $X_4, \ldots, X_n$.
+From the first part of this proof, both $p$-values are constructed by conditioning on $X_4, \ldots, X_n$.
 Upon conditioning these, $\left(X_1, X_2, X_3\right)$ follows an exponential family distribution, with carrier distribution
@@
 If ties are broken independently and randomly, the end points on the rays can be considered as ``half an atom'' if the coordinates are integers (or a smaller fraction of an atom in case of a multi-way tie).
-The number of atoms on each ray is the same (after the extension $\tilde{A}$) and the atoms on each ray can be paired up in exactly the same way as illustrated in Figure~\ref{fig:comparerays}, with the inequalities above still holding for each pair of the atoms.
+The number of atoms on each ray is the same (after the extension $\tilde{A}$) and the atoms on each ray can be paired up in exactly the same way as illustrated in \Cref{fig:comparerays}, with the inequalities above still holding for each pair of the atoms.
 Summing these inequalities yields our desired result.
@@
 If we define the $j$-th null hypothesis as
-$$\widetilde{H}_{0j}: \theta_{[j]} \le \max_{k > j} \theta_{[k]},$$
+$$\widetilde{H}_{0j}: \theta_{[j]} \le \max_{k>j} \theta_{[k]},$$
 then $\widetilde{H}_{01},\ldots,\widetilde{H}_{0j}$ are all false if and only if $\theta\notin \mathcal{M}_j(X)$.
@@
 As we will see later, each step in Procedure 3' is similar to testing $\widetilde{H}_{0j}$, stating that without the first $j$ ranks correct, it is hard to explain the observations.
-Thus, returning $\hat{j}_0 = j$ amounts to rejecting $\widetilde{H}_{01},\ldots,\widetilde{H}_{0j}$, or equivalently determining that the models $\mathcal{M}_1(X), \ldots, \mathcal{M}_j(X)$ do {\em not} fit the data.
+Thus, returning $\hat{j}_0 = j$ amounts to rejecting $\widetilde{H}_{01}, \ldots, \widetilde{H}_{0j}$, or equivalently determining that the models $\mathcal{M}_1(X), \ldots, \mathcal{M}_j(X)$ do {\em not} fit the data.
 
@@
 Note that the choice of the model $\mathcal{M}_j\left(X\right)$, once again, based solely on the random indices $[1], \ldots, [j]$, so conditioning on both $\mathcal{M}_{j-1}\left(X\right)$ and $\mathcal{M}_j\left(X\right)$ is equivalent to conditioning on the random indices $[1], \ldots, [j]$, which in turns is equivalent to conditioning on the $\sigma$-field generated by the partition of the observation space $X$
-$$\left\{\left\{X_{\tau_1} \ge \cdots \ge X_{\tau_j} \ge \max_{k>j} X_{\tau_k}\right\}: \tau \text{ is any permutation of } \left(1, \ldots, n\right)\right\},$$
+$$\left\{\left\{X_{\tau_1} \ge \cdots \ge X_{\tau_j} \ge \max_{k>j} X_{\tau_k}\right\}:\; \tau \text{ is any permutation of } \left(1, \ldots, n\right)\right\},$$
 or colloquially, the set of all possible choices of $[1], \ldots, [j]$.
@@
 However, from \eqref{eq:basicstop},
-$$\hat{j}_0 = \min\left\{j: \max_{k \le j} p_{k*} > \alpha\right\} - 1 = \min\left\{j: p_{j*} > \alpha\right\} - 1,$$
+$$\hat{j}_0 = \min\left\{j:\; \max_{k \le j} p_{k*} > \alpha\right\} - 1 = \min\left\{j:\; p_{j*} > \alpha\right\} - 1,$$
 so it is safe to apply BasicStop to $p_{j*}$ directly, yielding Procedure 3'.
@@
 Claims reporting the ``winner'' are commonly made in the scientific literature, usually with no significance level reported or an incorrect method applied.
-For example, \citet{Uhls:2012gf} asked $n=20$ elementary and middle school students which of seven personal values they most hoped to embody as adults, with ``Fame'' (8 responses) being the most commonly selected, with ``Benevolence'' (5 responses) second.
-The authors' main finding --- which appeared in the abstract, the first paragraph of the article, and later a CNN.com headline \citep{alikhani} --- was that ``Fame'' was the most likely response, accompanied by a significance level of $0.006$, which the authors computed by testing whether the probability of selecting ``Fame'' was larger than 1/7.
-The obvious error in the authors' reasoning could have been avoided if they had performed an equally straightforward two-tailed binomial test of ``Fame'' vs.
-``Benevolence,'' which would have produced a $p$-value of $0.58$.
+For example, \citet{Uhls:2012gf} asked $n = 20$ elementary and middle school students which of seven personal values they most hoped to embody as adults, with ``Fame'' (8 responses) being the most commonly selected, with ``Benevolence'' (5 responses) second.
+The authors' main finding --- which appeared in the abstract, the first paragraph of the article, and later a CNN.com headline \citep{Alikhani:2011} --- was that ``Fame'' was the most likely response, accompanied by a significance level of $0.006$, which the authors computed by testing whether the probability of selecting ``Fame'' was larger than 1/7.
+The obvious error in the authors' reasoning could have been avoided if they had performed an equally straightforward two-tailed binomial test of ``Fame'' vs.\ ``Benevolence,'' which would have produced a $p$-value of $0.58$.
 
+\Urlmuskip=0mu plus 1mu\relax
 \bibliographystyle{plainnat}

### 2016-10-05 verifying-winner.tex
code converted to r, minor fixes

@@
 \item Suppose $\left(x_1, x_2, x_3, \ldots\right)$ and $\left(x_1, y_2, y_3, \ldots\right)$ are two vectors in $\RR^n$. Then
-$$\left(x_1, x_2, x_3, \ldots\right) \succeq \left(x_1, y_2, y_3, \ldots\right) \text{ if and only if } \left(x_2, x_3, \ldots\right) \succeq \left(y_2, y_3, \ldots\right).$$
+\[\left(x_1, x_2, x_3, \ldots\right) \succeq \left(x_1, y_2, y_3, \ldots\right) \text{ if and only if } \left(x_2, x_3, \ldots\right) \succeq \left(y_2, y_3, \ldots\right).\]
 \item (Principle of transfer) If $x_1 > x_2$ and $t \ge 0$, then
-$$\left(x_1 + t, x_2, x_3, \ldots\right) \succeq \left(x_1, x_2 + t, x_3, \ldots\right).$$
+\[\left(x_1 + t, x_2, x_3, \ldots\right) \succeq \left(x_1, x_2 + t, x_3, \ldots\right).\]
 If $t \le 0$, the majorization is reversed.
@@
 \item The property follows from an equivalent formulation of majorization listed in \citet{Marshall:2010hb}, where $x \succeq y$ if and only if
-$$\sum_{j=1}^n x_n = \sum_{j=1}^n y_n \quad \text{ and } \quad \sum_{j=1}^n \left(x_j - a\right)_+ \ge \sum_{j=1}^n \left(y_j - a\right)_+ \text{ for all } a \in \RR.$$
+\[\sum_{j=1}^n x_n = \sum_{j=1}^n y_n \quad \text{ and } \quad \sum_{j=1}^n \left(x_j - a\right)_+ \ge \sum_{j=1}^n \left(y_j - a\right)_+ \text{ for all } a \in \RR.\]
 
@@
 The joint distribution of $X$ is given by
-$$p\left(x\right) \propto \exp\left(\sum_j x_j \log\frac{p_j}{1-p_j}\right) \frac{1}{x_1! \left(m-x_1\right)! \cdots x_n! \left(m-x_n\right)!}$$
+\[p\left(x\right) \propto \exp\left(\sum_j x_j \log\frac{p_j}{1-p_j}\right) \frac{1}{x_1! \left(m-x_1\right)! \cdots x_n! \left(m-x_n\right)!}\]
 The carrier measure above is Schur-concave. The unadjusted pairwise test in this family is Fisher's exact test.
@@
 Suppose $n$ players compete in a round robin tournament, where player $j$ has ability $\theta_j$, and the probability of player $j$ winning against player $k$ is
-$$\frac{e^{\theta_j - \theta_k}}{1 + e^{\theta_j - \theta_k}} = \frac{e^{\left(\theta_j - \theta_k\right) / 2}}{e^{\left(\theta_j - \theta_k\right) / 2} + e^{\left(\theta_k - \theta_j\right) / 2}}.$$
+\[\frac{e^{\theta_j - \theta_k}}{1 + e^{\theta_j - \theta_k}} = \frac{e^{\left(\theta_j - \theta_k\right) / 2}}{e^{\left(\theta_j - \theta_k\right) / 2} + e^{\left(\theta_k - \theta_j\right) / 2}}.\]
 
@@
 Thus the joint distribution of $Y=\left(Y_{jk}\right)_{j\neq k}$ is
-$$p\left(y\right) \propto \exp\left(\sum_j 2\theta_j \sum_{k \ne j} y_{jk}\right)  = \exp\left(2\theta' x\right),$$
+\[p\left(y\right) \propto \exp\left(\sum_j 2\theta_j \sum_{k \ne j} y_{jk}\right)  = \exp\left(2\theta' x\right),\]
 where $x_j = \sum_{k \ne j} y_{jk}$. In other words, if $X_j$ is the number of wins by player $j$, then $X=(X_1,\ldots,X_n)$ is a sufficient statistic with distribution
-$$p\left(x\right) = \exp\left(2\theta' x\right) g\left(x\right),$$
+\[p\left(x\right) = \exp\left(2\theta' x\right) g\left(x\right),\]
 where $g\left(x\right)$ is a function that counts the number of possible tournament results giving the net win vector $x$.
@@
 For any fixed $a$, and $x_1 \ge a$ and $x_2 < a$, we have $x_1 > x_2$ and
-$$\exp\left(\theta_1 x_1 + \theta_2 x_2 + \cdots + \theta_n x_n - \psi\left(\theta\right)\right) g\left(x\right) \ge \exp\left(\theta_1 x_2 + \theta_2 x_1 + \cdots + \theta_n x_n - \psi\left(\theta\right)\right) g\left(x\right).$$
+\[\exp\left(\theta_1 x_1 + \theta_2 x_2 + \cdots + \theta_n x_n - \psi\left(\theta\right)\right) g\left(x\right) \ge \exp\left(\theta_1 x_2 + \theta_2 x_1 + \cdots + \theta_n x_n - \psi\left(\theta\right)\right) g\left(x\right).\]
 Integrating both sides over the region $\left\{x:\; x_1 \ge a, x_2 < a\right\}$ gives
-$$\PP\left[X_1 \ge a, X_2 < a\right] \ge \PP\left[X_1 < a, X_2 \ge a\right].$$
+\[\PP\left[X_1 \ge a, X_2 < a\right] \ge \PP\left[X_1 < a, X_2 \ge a\right].$$
 Now adding $\PP\left[X_1 \ge a, X_2 \ge a\right]$ to both probabilities gives
-$$\PP\left[X_1 \ge a\right] \ge \PP\left[X_2 \ge a\right],$$
+$$\PP\left[X_1 \ge a\right] \ge \PP\left[X_2 \ge a\right],\]
 meaning that $X_1$ is greater than $X_2$ in stochastic order.
@@
 Under $H_0$, one of the $H_{0j}$ is true; without loss of generality assume it is $H_{01}$. Then,
-$$\PP\left[p_* \le \alpha\right] \le \PP\left[p_1 \le \alpha\right] \le \alpha.$$
+\[\PP\left[p_* \le \alpha\right] \le \PP\left[p_1 \le \alpha\right] \le \alpha.\]
 Therefore $p_*$ is a valid $p$-value for the union null hypothesis.
@@
 Hence
-$$\exp\left(\theta_1 \tau\left(x_1\right) + \cdots + \theta_n \tau\left(x_n\right) - \psi\left(\theta\right)\right) g\left(X\right) \ge \exp\left(\theta_1 x_1 + \cdots + \theta_n x_n - \psi\left(\theta\right)\right) g\left(X\right).$$
+\[\exp\left(\theta_1 \tau\left(x_1\right) + \cdots + \theta_n \tau\left(x_n\right) - \psi\left(\theta\right)\right) g\left(X\right) \ge \exp\left(\theta_1 x_1 + \cdots + \theta_n x_n - \psi\left(\theta\right)\right) g\left(X\right).\]
 If we integrating both sides over $\mathbb{R}^n$ (or $\mathbb{Z}^n$ in the case of counting measure), the right hand side gives $1$.
 Since $\tau$ is an $n$-to-$1$ mapping, the left hand side is $n$ times the integral over $\left\{x_1 \ge \max_{j > 1} x_j\right\}$.
-In other words
-$$n \PP\left[1 \text{ wins}\right] \ge 1$$
+In other words,
+\[n \PP\left[1 \text{ wins}\right] \ge 1\]
 as desired.
@@
 The type I error --- the probability of incorrectly declaring any other $j$ to be the best --- is
-$$\PP\left[\bigcup_{j \ne j^*} \text{declare } j \text{ best}\right] \le \sum_{j \ne j^*} \PP\left[\text{declare } j \text{ best} \;\middle|\; j \text{ wins}\right] \PP\left[j \text{ wins}\right],$$
+\[\PP\left[\bigcup_{j \ne j^*} \text{declare } j \text{ best}\right] \le \sum_{j \ne j^*} \PP\left[\text{declare } j \text{ best} \;\middle|\; j \text{ wins}\right] \PP\left[j \text{ wins}\right],\]
 recalling that ties are broken randomly, so there is only one winner in any realization.
-Thus, it is enough to bound $\PP_{\theta}\left[ \text{declare } j \text{ best} \;\middle|\; j \text{ wins}\right] \le \alpha$, for each $j \ne j^*$, and for all $\theta$ with $j^* \in \argmax_j \theta_j$.
+Thus, it is enough to bound $\PP_{\theta}\left[\text{declare } j \text{ best} \;\middle|\; j \text{ wins}\right] \le \alpha$, for each $j \ne j^*$, and for all $\theta$ with $j^* \in \argmax_j \theta_j$.
 Then we will have
@@
 Following the framework in \citet{Fithian:2014ws}, we first construct the $p$-values by conditioning on the selection event where the winner is $1$: 
-$$A_1 = \left\{X_1 \ge \max_{j > 1} X_j\right\}.$$
+\[A_1 = \left\{X_1 \ge \max_{j > 1} X_j\right\}.\]
 For convenience, we let
-$$D_{jk} = \frac{X_j - X_k}{2} \quad \text{ and } \quad M_{jk} = \frac{X_j + X_k}{2}.$$
+\[D_{jk} = \frac{X_j - X_k}{2} \quad \text{ and } \quad M_{jk} = \frac{X_j + X_k}{2}.\]
 
@@
 Finally, by construction, $p_{1j}$ satisfies
-$$\PP_{H_{01j}}\left[p_{1j} < \alpha \;\middle|\; M_{1j}, X_{\setminus\left\{1, j\right\}}, A_1\right] \le \alpha \quad \text{a.s.},$$
+\[\PP_{H_{01j}}\left[p_{1j} < \alpha \;\middle|\; M_{1j}, X_{\setminus\left\{1, j\right\}}, A_1\right] \le \alpha \quad \text{a.s.},\]
 Marginalizing over $M_{1j}, X_{\setminus\left\{1, j\right\}}$,
-$$\PP_{H_{01j}}\left[p_{1j} < \alpha \;\middle|\; A_1\right] \le \alpha.$$
+\[\PP_{H_{01j}}\left[p_{1j} < \alpha \;\middle|\; A_1\right] \le \alpha.\]
 Therefore these $p_{1j}$ are indeed valid $p$-values.
@@
 Upon conditioning these, $\left(X_1, X_2, X_3\right)$ follows an exponential family distribution, with carrier distribution
-$$g_{X_4, \ldots, X_n}\left(X_1, X_2, X_3\right) = g\left(X_1, \ldots, X_n\right),$$
+\[g_{X_4, \ldots, X_n}\left(X_1, X_2, X_3\right) = g\left(X_1, \ldots, X_n\right),\]
 here $X_4, \ldots, X_n$ are used in the subscript as they are conditioned on and no longer considered as variables.
@@
 Specifically,
-$$p_{12} = \frac{B}{A + B}$$
+\[p_{12} = \frac{B}{A+B}\]
 
@@
 \Cref{fig:comparerays} has both the $p$-values shown on the same diagram. Proving $p_{12} \ge p_{13}$ is the same as proving
-$$\frac{B}{A+B} \ge \frac{D}{C+D} \quad \Longleftrightarrow \quad \frac{B}{A} \ge \frac{D}{C}.$$
+\[\frac{B}{A+B} \ge \frac{D}{C+D} \quad \Longleftrightarrow \quad \frac{B}{A} \ge \frac{D}{C}.\]
 We will prove so by extending $A$ to include $\tilde{A}$ on the diagram. We denote the sum $A + \tilde{A}$ as $A'$. Formally,
@@
 Indeed from the second point in \Cref{lma:twoprop} we have
-$$\left(X_1 + z, X_2 - z, X_3\right) \succeq \left(X_1 + z, X_2, X_3 - z\right)$$
+\[\left(X_1 + z, X_2 - z, X_3\right) \succeq \left(X_1 + z, X_2, X_3 - z\right)\]
 for $z \le 0$ and the majorization reversed for $z \ge 0$. This majorization relation is indicated as the dotted line in \Cref{fig:comparerays}. So Schur-concavity shows that
-$$g\left(X_1 + z, X_2 - z, X_3\right) \le g\left(X_1 + z, X_2, X_3 - z\right)$$
+\[g\left(X_1 + z, X_2 - z, X_3\right) \le g\left(X_1 + z, X_2, X_3 - z\right)\]
 for $z \le 0$, and the inequality reversed for $z \ge 0$. Taking integrals on both sides yields the desired inequality.
@@
 This is achieved by finding an integer $d$, as a function on $m$, $n$ and $\alpha$, and selecting the subset
-$$J\left(X\right) = \left\{j: X_j \ge \max_k X_k - d\right\}.$$
+\[J\left(X\right) = \left\{j: X_j \ge \max_k X_k - d\right\}.\]
 We take $d(m, n, \alpha)$ to be the smallest integer such that \eqref{eq:subsetsel} holds for any $\pi$; \citet{Gupta:1967wg} provide an algorithm for determining $d$.
@@
 \Cref{fig:power} gives the power curves for $\text{Multinomial}\left(m, \pi\right)$ and
-$$\pi \propto \left(e^\delta, 1, \ldots, 1\right),$$
+\[\pi \propto \left(e^\delta, 1, \ldots, 1\right),\]
 for various combinations of $m$ and $n$.
@@
 \begin{center}
-\includegraphics[width = \textwidth, clip, trim = {4cm 2cm 4cm 2cm}]{plotMultinomialPower}
+\includegraphics[width = \textwidth]{multinomial-power}
 \end{center}
@@
 In that case, $d$ from \citeauthor{Gupta:1967wg} is usually computed based on the worst-case scenario $\pi = \left(\frac{1}{2}, \frac{1}{2}, 0, \ldots, 0\right)$; i.e.\ $d$ is the upper $\alpha$ quantile of
-$$X_1 - X_2 \sim m - 2 \cdot \text{Binomial}\left(m, \frac{1}{2}\right) \approx \text{Normal}\left(0, m\right).$$
+\[X_1 - X_2 \sim m - 2 \cdot \text{Binomial}\left(m, \frac{1}{2}\right) \approx \text{Normal}\left(0, m\right).\]
 Thus $d \approx \sqrt{m} z_\alpha$, where $z_\alpha$ is the upper $\alpha$ quantile of a standard Gaussian.
 On the other hand, our method defines a threshold based on the upper $\frac{n}{n-1} \cdot \frac{\alpha}{2}$ quantile of
-$$X_1 - X_2 \mid X_1 + X_2 \sim X_1 + X_2 - 2 \cdot \text{Binomial}\left(X_1 + X_2, \frac{1}{2}\right),$$
+\[X_1 - X_2 \mid X_1 + X_2 \sim X_1 + X_2 - 2 \cdot \text{Binomial}\left(X_1 + X_2, \frac{1}{2}\right),\]
 which is approximately $\sqrt{X_1 + X_2} z_{\alpha / 2}$. If $\pi_{(1)} \ll 1/2$ then with high probability $X_1 + X_2 \ll  m$, making our test much more liberal.
@@
 We will proceed by inverting a statistical test of the hypothesis $H_{0[1]}^\delta:\; \theta_{[1]} - \max_{j \ne [1]} \theta_{j} \le \delta$, which can be written as a union of null hypotheses:
-$$H_{0[1]}^\delta = \bigcup_{j \ne [1]} H_{0[1]j}: \theta_{[1]} - \theta_j \le \delta.$$
+\[H_{0[1]}^\delta = \bigcup_{j \ne [1]} H_{0[1]j}: \theta_{[1]} - \theta_j \le \delta.\]
 By \Cref{lma:union}, we can construct selective exact one-tailed $p$-values $p_{[1]j}^\delta$ for each of these by conditioning on $A_{[1]}$, $M_{[1]j}$ and $X_{\setminus\left\{[1], j\right\}}$, giving us an exact test for $H_{0[1]}$ by rejecting whenever $\max_{j \ne [1]} p_{[1]j}^\delta < \alpha$.
@@
 Again we start with assuming $X_1 \ge X_2 \ge \max_{j > 2} X_j$ for convenience. The $p$-values in question are derived from the conditional law
-$$\mathcal{L}_{\theta_1 - \theta_j = \delta} \left(D_{1j} \;\middle|\; M_{1j}, X_2, \ldots, X_n, A\right),$$
+\[\mathcal{L}_{\theta_1 - \theta_j = \delta} \left(D_{1j} \;\middle|\; M_{1j}, X_2, \ldots, X_n, A\right),\]
 which is the truncated distribution
@@
 The $p$-values thus are
-$$p_{1j}^\delta = \frac{\int_{D_{1j}}^\infty \exp\left(\delta z\right) g\left(M_{1j} + z, X_2, \ldots, M_{1j} - z, \ldots, X_n\right) \,dz}{\int_{\max\left\{X_2 - M_{1j}, 0\right\}}^\infty \exp\left(\delta z\right) g\left(M_{1j} + z, X_2, \ldots, M_{1j} - z, \ldots, X_n\right) \,dz}.$$
+\[p_{1j}^\delta = \frac{\int_{D_{1j}}^\infty \exp\left(\delta z\right) g\left(M_{1j} + z, X_2, \ldots, M_{1j} - z, \ldots, X_n\right) \,dz}{\int_{\max\left\{X_2 - M_{1j}, 0\right\}}^\infty \exp\left(\delta z\right) g\left(M_{1j} + z, X_2, \ldots, M_{1j} - z, \ldots, X_n\right) \,dz}.\]
 
@@
 Multiplying this to \eqref{eq:naivelo}, we have
-$$\alpha \ge \frac{\int_{D_{12}}^\infty \exp\left(\delta^* z\right) g\left(M_{12} + z, X_2, \ldots, M_{12} - z, \ldots, X_n\right) \,dz}{\int_0^\infty \exp\left(\delta^* z\right) g\left(M_{12} + z, X_2, \ldots, M_{12} - z, \ldots, X_n\right) \,dz},$$
+\[\alpha \ge \frac{\int_{D_{12}}^\infty \exp\left(\delta^* z\right) g\left(M_{12} + z, X_2, \ldots, M_{12} - z, \ldots, X_n\right) \,dz}{\int_0^\infty \exp\left(\delta^* z\right) g\left(M_{12} + z, X_2, \ldots, M_{12} - z, \ldots, X_n\right) \,dz},\]
 indicating that $\delta^*$ is smaller than the confidence bound that Procedure 2' would report. Hence $\delta^*$ is a valid and conservative.
@@
 Procedure 3' is a step-down procedure that an estimate $\hat{j}_0$ of $j_0$ at the FWER controlled at $\alpha$, where $j_0$ is given by
-$$j_0 = \max_j \left\{\theta_{[1]} > \cdots > \theta_{[j]} > \max_{k>j} \theta_{[k]}\right\}.$$
+\[j_0 = \max_j \left\{\theta_{[1]} > \cdots > \theta_{[j]} > \max_{k>j} \theta_{[k]}\right\}.\]
 \end{theorem}
@@
 Upon observing $X_{[1]} \ge \cdots \ge X_{[n]}$, we can set up a sequence of nested models
-$$\mathcal{M}_1\left(X\right) \subseteq \cdots \subseteq \mathcal{M}_n\left(X\right), \quad\text{ where } \mathcal{M}_j\left(X\right)^c = \left\{\theta:\; \theta_{[1]} > \cdots > \theta_{[j]} > \max_{k > j} \theta_{[k]}\right\}.$$
+\[\mathcal{M}_1\left(X\right) \subseteq \cdots \subseteq \mathcal{M}_n\left(X\right), \quad\text{ where } \mathcal{M}_j\left(X\right)^c = \left\{\theta:\; \theta_{[1]} > \cdots > \theta_{[j]} > \max_{k > j} \theta_{[k]}\right\}.\]
 If we define the $j$-th null hypothesis as
-$$\widetilde{H}_{0j}: \theta_{[j]} \le \max_{k>j} \theta_{[k]},$$
+\[\widetilde{H}_{0j}: \theta_{[j]} \le \max_{k>j} \theta_{[k]},\]
 then $\widetilde{H}_{01},\ldots,\widetilde{H}_{0j}$ are all false if and only if $\theta\notin \mathcal{M}_j(X)$.
@@
 Inspired by \citet{Fithian:2015uj}, we will instead consider another sequence of random hypothesis that are more closely related to the nest models,
-$$H_{0j}: \theta \in \mathcal{M}_j\left(X\right),$$
+\[H_{0j}: \theta \in \mathcal{M}_j\left(X\right),\]
 or equivalently, that $\theta_{[1]}, \ldots, \theta_{[j]}$ are not the best $j$ parameters in order.
@@
 Note that the choice of the model $\mathcal{M}_j\left(X\right)$, once again, based solely on the random indices $[1], \ldots, [j]$, so conditioning on both $\mathcal{M}_{j-1}\left(X\right)$ and $\mathcal{M}_j\left(X\right)$ is equivalent to conditioning on the random indices $[1], \ldots, [j]$, which in turns is equivalent to conditioning on the $\sigma$-field generated by the partition of the observation space $X$
-$$\left\{\left\{X_{\tau_1} \ge \cdots \ge X_{\tau_j} \ge \max_{k>j} X_{\tau_k}\right\}:\; \tau \text{ is any permutation of } \left(1, \ldots, n\right)\right\},$$
+\[\left\{\left\{X_{\tau_1} \ge \cdots \ge X_{\tau_j} \ge \max_{k>j} X_{\tau_k}\right\}:\; \tau \text{ is any permutation of } \left(1, \ldots, n\right)\right\},\]
 or colloquially, the set of all possible choices of $[1], \ldots, [j]$.
@@
 As a brief summary, we want to construct $p$-values $p_j$ such that
-$$\PP_{\substack{\theta_{\tau_1} > \cdots > \theta_{\tau_j} \\ \theta_{\tau_j} \le \max_{k>j} \theta_{\tau_k}}} \left[p_j \le \alpha \;\middle|\; X_{\tau_1} \ge \cdots \ge X_{\tau_j} \ge \max_{k>j} X_{\tau_k}\right].$$
+\[\PP_{\substack{\theta_{\tau_1} > \cdots > \theta_{\tau_j} \\ \theta_{\tau_j} \le \max_{k>j} \theta_{\tau_k}}} \left[p_j \le \alpha \;\middle|\; X_{\tau_1} \ge \cdots \ge X_{\tau_j} \ge \max_{k>j} X_{\tau_k}\right].\]
 
@@
 To avoid the clutter in the subscripts, we will drop the $\tau$ in the subscript. Hence our goal is now
-$$\PP_{\substack{\theta_1 > \cdots > \theta_j \\ \theta_j \le \max_{k>j} \theta_k}} \left[p_j \le \alpha \;\middle|\; X_1 \ge \cdots \ge X_j \ge \max_{k>j} X_k\right]$$
+\[\PP_{\substack{\theta_1 > \cdots > \theta_j \\ \theta_j \le \max_{k>j} \theta_k}} \left[p_j \le \alpha \;\middle|\; X_1 \ge \cdots \ge X_j \ge \max_{k>j} X_k\right]\]
 Construction of $p_j$ for other permutations $\tau$ can be obtained similarly.
@@
 
-$$p_{jk} = \frac{\int_{D_{jk}}^{X_{j-1}} g\left(X_1, \ldots, M_{jk} + z, \ldots, M_{jk} - z, \ldots, X_n\right) \,dz}{\int_{\max\left\{X_{j+1} - M_{jk}, 0\right\}}^{X_{j-1}} g\left(X_1, \ldots, M_{jk} + z, \ldots, M_{jk} - z, \ldots, X_n\right) \,dz}.$$
+\[p_{jk} = \frac{\int_{D_{jk}}^{X_{j-1}} g\left(X_1, \ldots, M_{jk} + z, \ldots, M_{jk} - z, \ldots, X_n\right) \,dz}{\int_{\max\left\{X_{j+1} - M_{jk}, 0\right\}}^{X_{j-1}} g\left(X_1, \ldots, M_{jk} + z, \ldots, M_{jk} - z, \ldots, X_n\right) \,dz}.\]
 
@@
 However, from \eqref{eq:basicstop},
-$$\hat{j}_0 = \min\left\{j:\; \max_{k \le j} p_{k*} > \alpha\right\} - 1 = \min\left\{j:\; p_{j*} > \alpha\right\} - 1,$$
+\[\hat{j}_0 = \min\left\{j:\; \max_{k \le j} p_{k*} > \alpha\right\} - 1 = \min\left\{j:\; p_{j*} > \alpha\right\} - 1,\]
 so it is safe to apply BasicStop to $p_{j*}$ directly, yielding Procedure 3'.

### 2016-10-05 multinomial-power.r

@@ -1,0 +1,116 @@
+library(ggplot2)
+library(grid)
+library(gridExtra)
+library(reshape2)
+
+# Returns a probability vector proportional to (exp(delta, 1, ..., 1))
+Pr <- function(n, delta) {
+    pi <- rep(1, n)
+    pi[1] <- exp(delta)
+    pi <- pi / sum(pi)
+}
+
+# Find the selective test power for multinomial distribution
+# m = number of votes
+# n = number of candidates
+# distribution is proportional to (exp(delta), 1, ..., 1)
+# alpha = level of the test
+# num.sample = number of samples to take for simulation purposes
+SelectivePower <- function(m, n, delta, alpha, num.sample) {
+    # Probability vector of multinomial distribution
+    pi <- Pr(n, delta)
+    # Generates the samples
+    x <- rmultinom(num.sample, m, pi)
+    # sec.x is max(Xj; j>1), i.e. X2
+    if (n == 2) {
+        sec.x <- x[2, ]
+    } else {
+        sec.x <- apply(x[2:n, ], 2, max)
+    }
+    # n.x is X1 + X2
+    n.x <- sec.x + x[1, ]
+    rejected <- length(which(pbinom(sec.x, n.x, 0.5) * 2 <= alpha))
+    return(rejected / num.sample)
+}
+
+# Find the test power of Gupta & Nagel for multinomial distribution
+# m = number of votes
+# n = number of candidates
+# delta is a vector listing all the deltas we want to plot
+# alpha = level of the test
+# num.sample = number of sampels to take for simulation purposes
+GnPower <- function(m, n, delta, alpha, num.sample) {
+    # Initialization; d.star is the biggest d
+    d.star <- -Inf
+    for (r in 2:n) {
+        # Probability vector (1/r, ..., 1/r)
+        pi <- rep(1 / r, r)
+        # Generates the sample
+        x <- rmultinom(num.sample, m, pi)
+        # Takes the maximum of each column
+        max.x <- apply(x, 2, max)
+        # d for a given r is the upper alpha quantile, rounded up
+        d <- quantile(max.x - x[1, ], probs=(1 - alpha), type=1, names=FALSE)
+        if (d.star < d) {
+            d.star <- d
+        }
+    }
+    
+    # Initialization; power is a vector of powers corresponding to the deltas
+    power <- rep(0, length(delta))
+    for (i in 1:length(delta)) {
+        # Probability vector
+        pi <- Pr(n, delta[i])
[…]

### 2016-10-05 multinomialPower.m

@@ -1,80 +1,0 @@
-% Plots the power of the selective test vs. Gupta & Nagel for multinomial
-% distribution
-% m = number of votes, i.e. X1 + ... + Xn
-% n = number of candidates
-% alpha = level of the test
-% numSample = number of samples to take for simulation purposes
-function [] = multinomialPower (m, n, alpha, numSample)
-    % delta ranges from 0 to 2
-    delta = 0:0.01:2;
-    sel = arrayfun(@(x) selectivePower(m, n, x, alpha / (n-1) * n, numSample), delta);
-    gn = gnPower(m, n, delta, alpha, numSample);
-    plot(delta, sel, delta, gn, '--');
-    % legend('Selective', 'Gupta and Nagel', 'Location', 'southeast');
-    xlabel('\delta');
-    ylabel('Power');
-end
-
-% Finds the selective test power for multinomial distribution
-% m = number of votes
-% n = number of candidates
-% distribution is proportional to (exp(delta), 1, ..., 1)
-% alpha = level of the test
-% numSample = number of samples to take for simulation purposes
-function [power] = selectivePower(m, n, delta, alpha, numSample)
-    % Probability vector of multinomial distribution
-    pi = pr(n, delta);
-    % Generates the sample
-    X = mnrnd(m, pi, numSample);
-    % secX is max(Xj; j>1), i.e. X2
-    secX = max(X(:, 2:end), [], 2);
-    % nX is X1 + X2
-    nX = secX + X(:, 1);
-    rejected = nnz(cdf('Binomial', secX, nX, 1/2) * 2 <= alpha);
-    power = rejected / numSample;
-end
-
-% Find the test power of Gutpa and Nagel for multinomial distribution
-% m = number of votes
-% n = number of candidates
-% delta is a vector listing all the deltas we want to plot
-% alpha = level of the test
-% numSample = number of samples to take for simulation purposes
-function [power] = gnPower(m, n, delta, alpha, numSample)
-    % Initialization; dStar is the biggest d
-    dStar = -Inf;
-    for r = 2:n
-        % Probability vector (1/r, ..., 1/r)
-        pi = ones([1, r]) ./ r;
-        % Generates the sample
-        X = mnrnd(m, pi, numSample);
-        % Takes the maximum of each row
-        maxX = max(X, [], 2);
-        % d for a given r is the upper alpha quantile, rounded up
[…]

### 2016-10-05 plotMultinomialPower.m

@@ -1,32 +1,0 @@
-numSample = 10000;
-alpha = 0.05;
-
-subplot(2, 3, 1);
-multinomialPower(50, 2, alpha, numSample);
-grid on;
-title('m = 50, n = 2');
-
-subplot(2, 3, 2);
-multinomialPower(50, 5, alpha, numSample);
-grid on;
-title('m = 50, n = 5');
-
-subplot(2, 3, 3);
-multinomialPower(50, 10, alpha, numSample);
-grid on;
-title('m = 50, n = 10');
-
-subplot(2, 3, 4);
-multinomialPower(500, 20, alpha, numSample);
-grid on;
-title('m = 250, n = 10');
-
-subplot(2, 3, 5);
-multinomialPower(500, 50, alpha, numSample);
-grid on;
-title('m = 250, n = 25');
-
-subplot(2, 3, 6);
-multinomialPower(500, 100, alpha, numSample);
-grid on;
-title('m = 250, n = 50');

### 2016-10-13 verifying-winner.tex
Berger mentioned in Related Work
pre-arXiv clean up

@@
 \captionsetup{width=0.8\textwidth}
-\DeclareMathOperator*{\argmax}{arg\,max}
 
@@
 
-\setlength{\tabcolsep}{1em}
-\setlist{listparindent=\parindent, parsep=0pt}
 \newtheoremstyle{custom}{}{}{\itshape}{}{\bfseries}{.}{.5em}{\thmnote{#3}}
@@
 \newtheorem*{customthm}{Theorem}
+
+\setlength{\tabcolsep}{1em}
+\setlist{listparindent=\parindent, parsep=0pt}
+
 \newcommand{\EE}{\mathbb{E}}
@@
 \newcommand{\ZZ}{\mathbb{Z}}
-
-% Commands for inline commenting that shows up on pdf
-\newcommand{\WFcomment}[1]{{\color{red}{(WF: \bf \sc #1) }}}
-\newcommand{\KHcomment}[1]{{\color{green!60!black}{(KH: \bf \sc #1) }}}
+\DeclareMathOperator*{\argmax}{arg\,max}
 
@@
 \begin{table}[htbp]
-\begin{center}
+\centering
 \begin{tabular}{c c c c}
@@
 \end{tabular}
-\end{center}
 \caption{Results from a February 1, 2016 Quinnipiac University poll of $890$ Iowa Republicans.
@@
 For the multinomial case, \citet{Gupta:1967wg}, discussed in \Cref{sec:subsetsel}, remain the state of the art in finite-sample tests; \citet{Gupta:1976vd} discuss related approaches for Poisson models.
+\citet{Berger:1980ev} mentions an alternative, simpler rule which performs a binomial test on each population, but its power does not necessarily as the size $m$ of observations increases in cases like $\text{Multinomial}(m; 2/3, 1/3, 0, \ldots, 0)$.
 \citet{Nettleton:2009ht} proves validity for an asymptotic version of the winner-versus-runner-up test, and \citet{Gupta:1989fe} consider an empirical Bayes approach for selecting the best binomial population wherein a parametric prior distribution is assumed for the success probabilities for the different populations.
@@
 
-From the first part of this proof, both $p$-values are constructed by conditioning on $X_4, \ldots, X_n$.
+From the first part of this proof, both $p$-values are constructed by conditioning on $X_{\setminus\left\{1, 2, 3\right\}}$.
 Upon conditioning these, $\left(X_1, X_2, X_3\right)$ follows an exponential family distribution, with carrier distribution
@@
 \begin{figure}[htbp]
-\begin{center}
+\centering
 \begin{tikzpicture}
@@
 \end{tikzpicture}
-\end{center}
 \caption{The $p$-value $p_{12}$ can be written in terms of integral $A$ along the segment and $B$ along the ray.
@@
 \end{tikzpicture}
-\end{center}
 \caption{The $p$-value $p_{12}$ can be written in terms of integral $A$ along the segment and $B$ along the ray; and $p_{13}$ in terms of $C$ and $D$.
@@
 \begin{figure}[htbp]
-\begin{center}
+\centering
 \includegraphics[width = \textwidth]{multinomial-power}
-\end{center}
 \caption{Power curves as a function of $\delta$.
@@
 \end{tikzpicture}
-\end{center}
 \caption{The two $p$-values constructed corresponds to taking integrals of $g$ along these segments, that lie on a level set of $x_j + x_{j+1} + x_k$.
@@
 Claims reporting the ``winner'' are commonly made in the scientific literature, usually with no significance level reported or an incorrect method applied.
-For example, \citet{Uhls:2012gf} asked $n = 20$ elementary and middle school students which of seven personal values they most hoped to embody as adults, with ``Fame'' (8 responses) being the most commonly selected, with ``Benevolence'' (5 responses) second.
-The authors' main finding --- which appeared in the abstract, the first paragraph of the article, and later a CNN.com headline \citep{Alikhani:2011} --- was that ``Fame'' was the most likely response, accompanied by a significance level of $0.006$, which the authors computed by testing whether the probability of selecting ``Fame'' was larger than 1/7.
+For example, \citet{Uhls:2012gf} asked $n = 20$ elementary and middle school students which of seven personal values they most hoped to embody as adults, with ``Fame'' ($8$ responses) being the most commonly selected, with ``Benevolence'' ($5$ responses) second.
+The authors' main finding --- which appeared in the abstract, the first paragraph of the article, and later a CNN.com headline \citep{Alikhani:2011} --- was that ``Fame'' was the most likely response, accompanied by a significance level of $0.006$, which the authors computed by testing whether the probability of selecting ``Fame'' was larger than $1 / 7$.
 The obvious error in the authors' reasoning could have been avoided if they had performed an equally straightforward two-tailed binomial test of ``Fame'' vs.\ ``Benevolence,'' which would have produced a $p$-value of $0.58$.
+
+\section*{Reproducibility}
+A git repository containing with the code generating the image in this paper is available at \url{https://bitbucket.org/wfithian/verifying-winner}.
 

### 2016-10-13 multinomial-power.r

@@ -98,7 +98,8 @@ PlotMultinomialPower <- function(m, n, alpha, num.sample) {
                theme(axis.title.x = element_blank(),
                      axis.title.y = element_blank(),
                      legend.title = element_blank(),
-                     legend.position = "none") +
+                     legend.position = "none",
+                     plot.title = element_text(size = 10, face = "bold")) +
                ggtitle(sprintf("m = %d, n = %d", m, n)))
 }
 
@@ -111,6 +112,10 @@ p3 <- PlotMultinomialPower(50, 10, alpha, num.sample)
 p4 <- PlotMultinomialPower(250, 10, alpha, num.sample)
 p5 <- PlotMultinomialPower(250, 25, alpha, num.sample)
 p6 <- PlotMultinomialPower(250, 50, alpha, num.sample)
+
+# Saving the plot
+png("multinomial-power.png", width = 7, height = 5, units = 'in', res = 300)
 grid.arrange(arrangeGrob(p1, p2, p3, p4, p5, p6, ncol = 3,
                          left = textGrob("Power", rot = 90, vjust = 1),
                          bottom = textGrob(expression(delta))))
+dev.off()

### 2016-10-13 verifying-winner.tex
git address updated, arXiv ready

@@
 \section*{Reproducibility}
-A git repository containing with the code generating the image in this paper is available at \url{https://bitbucket.org/wfithian/verifying-winner}.
+A git repository containing with the code generating the image in this paper is available at \url{https://github.com/kenhungkk/verifying-winner}.
 

### 2016-10-13 verifying-winner.tex
arXiv fixes round 1
lesson learned on cleveref + algorithm2e + natbib, bad LaTeX style fixed

@@
 \usepackage{amsthm}
-\usepackage[linesnumbered, ruled]{algorithm2e}
 \usepackage{caption}
-\usepackage{cleveref}
 \usepackage{enumitem}
@@
 \usepackage{graphicx}
+\usepackage{hyperref} % hyperref must be loaded before cleveref
 \usepackage{mathrsfs}
-\usepackage[round]{natbib}
+\usepackage[round]{natbib} % natbib must be loaded before algorithm2e
+\usepackage[linesnumbered, ruled]{algorithm2e} % algorithm2e must be loaded before cleveref
+\usepackage{cleveref}
 \usepackage{tikz}
 \usetikzlibrary{calc}
-\usepackage[hyphens]{url}
 \usepackage{verbatim}
@@
 \begin{equation}
+\label{eq:expfam}
 X \sim \exp\left(\theta'x - \psi\left(\theta\right)\right) g\left(x\right),
-\label{eq:expfam}
 \end{equation}
@@
 \begin{theorem}
+\label{thm:main}
 Assume the model~\eqref{eq:expfam} holds and $g\left(x\right)$ is a Schur-concave function. Then:
@@
 \end{enumerate}
-\label{thm:main}
 \end{theorem}
@@
 \begin{lemma}\leavevmode
+\label{lma:twoprop}
 \begin{enumerate}
@@
 \end{enumerate}
-\label{lma:twoprop}
 \end{lemma}
@@
 \begin{theorem}
+\label{thm:stoch}
 For a multivariate exponential family with a symmetric carrier distribution, $X_1 \ge X_2$ in stochastic order if and only if $\theta_1 \geq \theta_2$.
-\label{thm:stoch}
 \end{theorem}
@@
 \begin{lemma}[\citealp{Berger:1982hy}]
+\label{lma:union}
 If $p_j$ are valid $p$-values for testing null hypothesis $H_{0j}$, then $p_* = \max_j p_j$ is a valid $p$-value for the union null (i.e.\ disjunction null) hypothesis $H_0 = \bigcup_j H_{0j}$.
-\label{lma:union}
 \end{lemma}
@@
 \begin{lemma}
+\label{lma:margsharp}
 If $\theta_1 \ge \max_{j \ne 1} \theta_j$, then $\PP\left[1 \text{ wins}\right] \ge \frac{1}{n}$.
-\label{lma:margsharp}
 \end{lemma}
@@
 \begin{equation}
+\label{eq:marginal}
 \PP\left[\bigcup_{j \ne j^*} \text{declare } j \text{ best}\right] \le \sum_{j \ne j^*} \alpha \cdot \PP\left[j \text{ wins}\right] = \alpha \PP\left[j^* \text{ does not win}\right] \le \frac{n-1}{n} \alpha,
-\label{eq:marginal}
 \end{equation}
@@
 \begin{equation}
+\label{eq:condlaw}
 \mathcal{L}_{\theta_1 - \theta_j = 0} \left(D_{1j} \;\middle|\; M_{1j}, X_{\setminus\left\{1, j\right\}}, A_1\right).
-\label{eq:condlaw}
 \end{equation}
@@
 \begin{equation}
+\label{eq:p1j}
 p_{1j} = \frac{\int_{D_{1j}}^\infty g\left(M_{1j} + z, X_2, \ldots, M_{1j} - z, \ldots, X_n\right) \,dz}{\int_{\max\left\{X_2 - M_{1j}, 0\right\}}^\infty g\left(M_{1j} + z, X_2, \ldots, M_{1j} - z, \ldots, X_n\right) \,dz}.
-\label{eq:p1j}
 \end{equation}
@@
 \begin{equation}
+\label{eq:int_extension}
 A' = \int_{-D_{13}}^0 g\left(X_1 + z, X_2 - z, X_3\right) \,dz \ge \int_{-D_{12}}^0 g\left(X_1 + z, X_2 - z, X_3\right) \,dz = A.
-\label{eq:int_extension}
 \end{equation}
@@
 In other words, if the selected subset is $J\left(X\right)$, it guarantees
-\begin{equation}\label{eq:subsetsel}
+\begin{equation}
+\label{eq:subsetsel}
 \PP\left[\argmax_j \pi_j \in J\left(X\right)\right] \ge 1 - \alpha.
@@
 \centering
-\includegraphics[width = \textwidth]{multinomial-power}
+\includegraphics[width = \textwidth]{multinomial-power.png}
 \caption{Power curves as a function of $\delta$.
@@
 \begin{equation}
+\label{eq:naivelo}
 \frac{\alpha}{2} = \frac{\int_{D_{12}}^\infty \exp\left(\delta^* z\right) g\left(M_{12} + z, X_2, \ldots, M_{12} - z, \ldots, X_n\right) \,dz}{\int_{-\infty}^\infty \exp\left(\delta^* z\right) g\left(M_{12} + z, X_2, \ldots, M_{12} - z, \ldots, X_n\right) \,dz}
-\label{eq:naivelo}
 \end{equation}
@@
 \begin{equation}
+\label{eq:jrankscorrect}
 \theta_{[1]} > \cdots > \theta_{[j]} > \max_{k>j} \theta_{[k]}.
-\label{eq:jrankscorrect}
 \end{equation}
@@
 		$D_{\tau_j} \leftarrow X_{\tau_j} - X_{\tau_{j+1}}$\;
-		Set up the distribution of $D_{\tau_j \tau_{j+1}}$, conditioned on
+		\label{lne:event} Set up the distribution of $D_{\tau_j \tau_{j+1}}$, conditioned on
 		\begin{itemize}
 		\item the variables $X_{\tau_1}, \ldots, X_{\tau_{j-1}}, X_{\tau_{j+2}}, \ldots, X_{\tau_n]}$, and
-		\item the event $\left\{X_{\tau_{j-1}} \ge X_{\tau_j} \ge \max_{k>j} X_{\tau_k)}\right\}$\; \label{lne:event}
+		\item the event $\left\{X_{\tau_{j-1}} \ge X_{\tau_j} \ge \max_{k>j} X_{\tau_k)}\right\}$\;
 		\end{itemize}
@@
 \begin{equation}
+\label{eq:basicstop}
 \hat{j}_0 = \min\left\{j: p_j > \alpha\right\} - 1.
-\label{eq:basicstop}
 \end{equation}
@@
 \begin{equation}
+\label{eq:basicstopreq}
 \PP\left[p_j \le \alpha \;\middle|\; \theta \in \mathcal{M}_j\left(X\right) \setminus \mathcal{M}_{j-1}\left(X\right)\right] \le \alpha \quad \text{for all } j.
-\label{eq:basicstopreq}
 \end{equation}

### 2017-06-23 slides.tex
readied for submission to aos; bib updated to include stefansson

% LAST UPDATED FOR MCP2017

\documentclass{beamer}
\usecolortheme[RGB={112,41,99}]{structure}
\usetheme{Berkeley}
\setbeamercovered{invisible}

\setbeamertemplate{frametitle continuation}{}

\usepackage{graphicx}
\usepackage{booktabs}
\usepackage{natbib}
\usepackage{lmodern}
\usepackage{tikz}
\usetikzlibrary{calc}
\usepackage{xcolor}
\definecolor{mid_purple}{HTML}{B894B1}

\title[Verifying Winner]{Rank Verification in Exponential Families}

\author[Kenneth Hung]{Kenneth Hung}
\institute[UC Berkeley]{
University of California, Berkeley \\
\medskip
\textit{kenhung@berkeley.edu}
}
\date{June 23, 2017 @ MCP2017}

\begin{document}

\begin{frame}
\titlepage
\end{frame}

\section{Introduction \& Motivation}

\begin{frame}{Introduction}
\begin{itemize}
\item Joint work with my advisor, Will Fithian
\item Paper available on arXiv:1610.03944
\end{itemize}
\end{frame}

\begin{frame}{A polling problem}
\begin{table}[htbp]
\centering
\begin{tabular}{c c c c}
	\hline
	Rank & Candidate & Result & Votes \\
	\hline
	$1$ & Trump & $31\%$ & $276$ \\
	$2$ & Cruz & $24\%$ & $214$ \\
	$3$ & Rubio & $17\%$ & $151$ \\
	$4$ & Carson & $8\%$ & $71$ \\
	$5$ & Paul & $4\%$ & $36$ \\
	$6$ & Bush & $4\%$ & $36$ \\
	$7$ & Huckabee & $3\%$ & $27$ \\
	$\vdots$ & $\vdots$ & $\vdots $ & $\vdots$ \\
	\hline
\end{tabular}
\caption{Simplified results from a February 1, 2016 Quinnipiac University poll of $890$ Iowa Republicans.}
\label{tbl:poll}
\end{table}
\end{frame}

\begin{frame}{A polling problem}
Questions that one might ask, {\it post hoc}:
\begin{itemize}
\item Verifying winner as best: Does Trump have the largest support?
\begin{itemize}
\item a.k.a.\ multiple comparison with sample best (CSB) in \citet{Stefansson:1988wj}
\end{itemize}
\item By how much: How much larger is Trump's support compared to other candidates?
\item Verifying other ranks: Does Cruz (Rubio, etc.) have the second (third, etc.) largest support? 
\end{itemize}
\end{frame}

\begin{frame}{A polling problem}
Two fundamental problems here:
\begin{enumerate}
	\item Only asking ``Is Trump the best?'' when Trump is winning --- selective inference
	\item Testing all pairwise hypotheses that Trump is better than Cruz, Rubio, Carson, etc. --- multiple comparison
\end{enumerate}
\end{frame}

\begin{frame}{Related work}
\begin{itemize}
\item Ranking and selection: \citet{Gupta:1971wk,Gupta:1985bj,Gutmann:1987fk}
\item Location-scale families: \citet{Gutmann:1987fk,Bofinger:1991hv,Maymin:1992fz,Karnnan:2009iv}
\item CSB for location family using partition: \citet{Stefansson:1988wj}
\item Multinomial families: \citet{Gupta:1967wg,Gupta:1976vd,Berger:1980ev,Nettleton:2009ht,Gupta:1989fe,Ng:2007cn,Gupta:1967wg}

\item Conditional selective inference: \citet{Fithian:2014ws}
\end{itemize}
\end{frame}

\section{Procedure}

\begin{frame}{A na\"ive approach}
\begin{itemize}
\item Verifying winner as best: One-tailed level-$\alpha$ test comparing Trump to Cruz
\item By how much: Invert the test above
\item Verifying other ranks: One-tailed level-$\alpha$ test comparing first runner-up to second runner-up, etc., using a step-down procedure.
\end{itemize}
\end{frame}

\begin{frame}{A valid, yet simple, approach}
\begin{itemize}
\item Verifying winner as best: {\bf Two}-tailed level-$\alpha$ test comparing Trump to Cruz
\item By how much: Invert the test above
\item Verifying other ranks: {\bf Two}-tailed level-$\alpha$ test comparing first runner-up to second runner-up, etc., using a step-down procedure
\end{itemize}
\end{frame}

\section{Technicalities}

\begin{frame}{Exponential families}
\begin{align*}
&~ p(x_1, \ldots, x_n; \theta_1, \ldots, \theta_n) \\
= &~ \exp(\theta_1 x_1 + \cdots + \theta_n x_n - \log A(\theta_1, \ldots, \theta_n)) h(x_1, \ldots, x_n)
\end{align*}
\begin{itemize}
\item $x_i$ are the observations
\item $\theta_i$ are the natural parameter being ranked and tested
\item $h(\cdot)$ is the carrier distribution
\item $A(\cdot)$ is the normalizing constant
\end{itemize}
\end{frame}

\begin{frame}{Schur-concave exponential families}
\begin{itemize}
\item Schur-concave exponential families require $h$ to be Schur-concave
\item Generalization and relaxation of log-concave exponential family to potentially multivariate, discrete distributions
\item If $x \succeq y$ is the majorization order, then
\[
h(x) \le h(y).
\]
\end{itemize}
\end{frame}

\begin{frame}{Examples}
\begin{itemize}
\item Independent binomial treatment outcomes in a clinical trial
\item Competitive sports under the Bradley--Terry model
\item Comparing the variances of independent normal populations
\end{itemize}
\end{frame}

\section{Proof Sketches}

\begin{frame}{Key ideas in proof}
\begin{enumerate}
\item Selective inference: Conditioning on the selection event \citep{Fithian:2014ws}
\item Multiple comparison: Union null, only largest $p$-value needed
\end{enumerate}
\end{frame}

\begin{frame}{Selective inference}
\begin{itemize}
\item Question only asked about candidate $i$ when $X_i > X_j$ for all $j \ne i$
\item The corresponding event is thus
\[
\{X_i > \max_{i \ne j} X_j\}
\]
\end{itemize}
\end{frame}

\begin{frame}{Multiple comparison}
\begin{itemize}
\item Construct a $p$-value $p_{ij}$ for the winner against each candidate
\item The null ``the winner is not the best'' is a union null
\item Suffices to look at the largest $p$-values
\item Suffices to show that the largest $p$-value is obtained by comparing the winner and the runner-up
\end{itemize}
\end{frame}

\begin{frame}{Nuisance parameters}
In constructing $p_{ij}$,
\begin{itemize}
\item Parameter of interest: $\theta_i - \theta_j$
\item Nuisance parameters: $\theta_i + \theta_j$, and $\theta_k$ for all $k \ne i, j$
\item Condition on $2M_{ij} = X_i + X_j$, $X_{\setminus\{i, j\}}$.
\item Use $2D_{ij} = X_i - X_j$ as the test statistic
\end{itemize}
\end{frame}

\begin{frame}{Proof by pictures}
\begin{itemize}
\item Graphical representation of $p_{ij}$ and $p_{ik}$ for comparison
\item WLOG assume that $i = 1$ is the winner, $j = 2$ is the runner-up, and $k = 3$
\item Under the conditioning, $X_1 + X_2 + X_3$ and $X_{\setminus\{1, 2, 3\}}$ are held constant
\item Everything can fit on a 2D picture!
\end{itemize}
\end{frame}

\begin{frame}{Proof by pictures}
\centering
\begin{tikzpicture}
	\coordinate (C1) at (60:5);
	\coordinate (C2) at (300:3);
	\coordinate (A) at (60:3);
	\coordinate (B) at ($(A) + (330:3)$);
	\coordinate (C) at ($(0, 0)!(B)!(C2)$);
	\coordinate (D) at ($(A) + (150:1)$);
	\draw[dashed] (0, 0) -- (C1);
	\draw[dashed] (0, 0) -- (C2);
	\fill[mid_purple] (0, 0) -- (C1) -- ($(C1) + (6.5, 0)$) -- ($(C2) + (7.5, 0)$) -- (C2) -- cycle;
	\node[above left] at ($(C2) + (7.5, 0)$) {$A_1$};
	\draw[thick] (A) -- (B) node[midway, above right] {$A$};
	\draw[thick, ->] (B) -- ++(330:5) node[midway, below left] {$B$};
	\fill (A) circle(2pt) node[above right] {$\left(M_{12}, M_{12}, X_3\right)$};
	\fill (B) circle(2pt) node[right] {$\left(X_1, X_2, X_3\right)$};
	\fill (0, 0) circle(2pt);
	\draw[thick, ->] (0, 0) -- (0.5, 0) node[right] {\tiny $x_1 +$};
	\draw[thick, ->] (0, 0) -- (120:0.5) node[above] {\tiny $x_2 +$};
	\draw[thick, ->] (0, 0) -- (240:0.5) node[below] {\tiny $x_3 +$}; \pause
	\draw[thick] (C) -- (B) node[midway, below right] {$C$};
	\node[below] at (C) {$\left(M_{13}, X_2, M_{13}\right)$};
	\draw[thick, ->] (B) -- ++(30:5) node[midway, above left] {$D$};
	\fill ($(0, 0)!(B)!(C2)$) circle(2pt); \pause
	\draw[thick, dashed] (A) -- (D) node[midway, below left] {$\tilde{A}$};
	\fill (D) circle(2pt) node[above] {$\left(M_{13}, X_2 + D_{13}, X_3\right)$};
	\draw[thick, dotted] (C) -- (D) node[midway, below, rotate=-90] {$\succeq$};
	\draw[thick, dotted] (A) -- ++(0, -3) node[midway, below, rotate=-90] {$\succeq$};
	\draw[thick, dotted] ($(B) + (30:4)$) -- ($(B) + (330:4)$) node[midway, below, rotate=-90] {$\succeq$};
\end{tikzpicture}
\end{frame}

\begin{frame}{Power comparison}
\begin{itemize}
\item \citet{Gupta:1967wg} provided a subset selection procedure for the multinomial problem
\item Can be used as a test for if the winner is the best
\item Tested on parameters in form of
\[
(e^\delta, \underbrace{1, 1, \ldots, 1}_{n - 1})
\]
\end{itemize}
\end{frame}

\begin{frame}{Power comparison}
\centering
\includegraphics[width=0.95\textwidth]{multinomial-power.png}
\end{frame}

\begin{frame}[allowframebreaks]{References}
\footnotesize{\bibliography{papers}\bibliographystyle{plainnat}}
\end{frame}

\begin{frame}
\centering
{\Large Thanks!}
\end{frame}

\end{document}

### 2017-06-23 verifying-winner.tex
readied for submission to aos; bib updated to include stefansson

@@
-\documentclass[11pt]{article}
+\documentclass[aos, authoryear]{imsart}
+
 \usepackage{amsmath}
@@
 \usepackage{amsthm}
-\usepackage{caption}
 \usepackage{enumitem}
-\newlist{inlinelist}{enumerate*}{1}
-\setlist*[inlinelist]{label=(\arabic*)}
 \usepackage[totalwidth=450pt, totalheight=630pt]{geometry}
@@
 \usepackage{mathrsfs}
-\usepackage[round]{natbib} % natbib must be loaded before algorithm2e
+\usepackage{natbib} % natbib must be loaded before algorithm2e
 \usepackage[linesnumbered, ruled]{algorithm2e} % algorithm2e must be loaded before cleveref
@@
 \usepackage{xcolor}
+
+% arXiv number
+\arxiv{arXiv:1610.03944}
+
+% custom definitions
+\startlocaldefs
+
+% enumitem
+\newlist{inlinelist}{enumerate*}{1}
+\setlist*[inlinelist]{label=(\arabic*)}
+
+% algorithm2e
+\SetAlgoCaptionSeparator{.}
+\renewcommand\AlCapFnt{\normalfont\scshape}
+
+% xcolor
 \definecolor{mid_green}{HTML}{99d8c9}
-
-\captionsetup{width=0.8\textwidth}
 
@@
 
+\endlocaldefs
+
 \begin{document}
 
+\begin{frontmatter}
+
 \title{Rank Verification for Exponential Families}
-\author{Kenneth Hung \and William Fithian}
-\date{\today}
-\maketitle
+\runtitle{Rank Verification for Exp. Families}
+
+\begin{aug}
+  \author{\fnms{Kenneth} \snm{Hung}\corref{}\ead[label=e1]{kenhung@berkeley.edu}}
+  \and
+  \author{\fnms{William} \snm{Fithian}\ead[label=e2]{wfithian@berkeley.edu}}
+
+  \runauthor{K. Hung and W. Fithian}
+
+  \affiliation{University of California, Berkeley}
+
+  \address{Department of Mathematics\\ 951 Evans Hall, Suite 3840\\ Berkeley, CA 94720-3840\\
+  \printead{e1}}
+
+  \address{Department of Statistics\\ Evans Hall\\ Berkeley, CA 94720\\
+          \printead{e2}}
+
+\end{aug}
 
@@
 \end{abstract}
+
+\begin{keyword}[class=MSC]
+\kwd[Primary ]{62F07}
+\kwd[; secondary ]{62F03}
+\end{keyword}
+
+\begin{keyword}
+\kwd{ranking}
+\kwd{selective inference}
+\kwd{exponential family}
+\end{keyword}
+
+\end{frontmatter}
 
@@
 Nevertheless, if we blithely ignore the selection issue, we might carry out the following analyses to answer the questions we posed before at significance level $\alpha = 0.05$.
-We assume for simplicity that the poll represents a simple random sample of Iowa Republicans; i.e., that the data are a multinomial sample of size $890$ and underlying probabilities $\left(\pi_{\text{Trump}}, \pi_{\text{Cruz}}, \ldots\right)$.\footnote{The reality is a bit more complicated: before releasing the data, Quinnipiac has post-processed it to make the reported result more representative of likely caucus-goers.
-The raw data is proprietary.}
+We assume for simplicity that the poll represents a simple random sample of Iowa Republicans; i.e., that the data are a multinomial sample of size $890$ and underlying probabilities $\left(\pi_{\text{Trump}}, \pi_{\text{Cruz}}, \ldots\right)$.
+(The reality is a bit more complicated: before releasing the data, Quinnipiac has post-processed it to make the reported result more representative of likely caucus-goers.
+The raw data is proprietary.)
 
@@
 We call this test the (two-tailed) {\em unadjusted pairwise test} since it makes no explicit adjustment for selection.
-Similarly, inverting this test for other values of $\theta_j-\theta_k$ yields an {\em unadjusted pairwise confidence interval}.\footnote{To avoid trivialities in the discrete case, we assume these procedures are appropriately randomized at the rejection thresholds to give exact level-$\alpha$ control.}
+Similarly, inverting this test for other values of $\theta_j-\theta_k$ yields an {\em unadjusted pairwise confidence interval}.
+(To avoid trivialities in the discrete case, we assume these procedures are appropriately randomized at the rejection thresholds to give exact level-$\alpha$ control.)
 
@@
 \end{align*}
-The conditional law of $D_{1j}$ in \eqref{eq:condlaw}, in particular, is a truncated distribution\footnote{Here consider this as a one-dimensional distribution of $D_{1j}$ on $\RR$, where $M_{1j}$ and $X_{\setminus\left\{1, j\right\}}$ are treated as fixed.}
+The conditional law of $D_{1j}$ in \eqref{eq:condlaw}, in particular, is a truncated distribution.
 \begin{align*}
@@
 where at step (a), conditioning on $X_{\setminus\left\{1, j\right\}}$ and $M_{1j}$ removes dependence on $\theta_{\setminus\left\{1, j\right\}}$ and $\theta_1 + \theta_j$ respectively, while $\theta_1 - \theta_j$ is taken to be $0$ under our null hypothesis.
+Note that we consider this as a one-dimensional distribution of $D_{1j}$ on $\RR$, where $M_{1j}$ and $X_{\setminus\left\{1, j\right\}}$ are treated as fixed.
 
@@
 In reality, we can always just adopt Procedure 2' in the case when Procedure 1 rejects.
-In fact, by Procedure 2', the multinomial example for polling in \Cref{sec:iowa} can give a stronger lower confidence bound, that $\pi_{\text{Trump}} \ge \max_{j \ne \text{Trump}} \pi_{j} \ge 1.108$ (Trump leads the field by at least $10.8\%$).
+In fact, by Procedure 2', the multinomial example for polling in \Cref{sec:iowa} can give a stronger lower confidence bound, that $\pi_{\text{Trump}} / \max_{j \ne \text{Trump}} \pi_{j} \ge 1.108$ (Trump leads the field by at least $10.8\%$).
 
@@
 \item $\theta_k \le \theta_{k+1}$ for $k = 1, \ldots, j-1$, and
-\item $\theta_j \le \theta_k$ for $k = j+1, \ldots, n$.\footnote{The union of these null hypotheses is $\widetilde{H}_{0j}$.}
+\item $\theta_j \le \theta_k$ for $k = j+1, \ldots, n$. (The union of these null hypotheses is $\widetilde{H}_{0j}$.)
 \end{enumerate}
@@
 \Urlmuskip=0mu plus 1mu\relax
-\bibliographystyle{plainnat}
+\bibliographystyle{imsart-nameyear}
 \bibliography{papers}

### 2017-06-24 response.tex
major revision

\documentclass[]{article}

\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amsthm}
\usepackage{amssymb}
\usepackage{cleveref}
\usepackage{courier}
\usepackage{natbib}
\usepackage{subcaption}

\DeclareMathOperator{\var}{var}
\DeclareMathOperator*{\argmax}{arg\,max}

\setlength{\parindent}{15pt}
\newtheorem{theorem}{Theorem}
\newtheorem{lemma}{Lemma}
\newtheorem{corollary}{Corollary}
\newtheorem{definition}{Definition}
\theoremstyle{remark}
\newtheorem*{remark}{Remark}

\newcommand{\EE}{\mathbb{E}}
\newcommand{\PP}{\mathbb{P}}
\newcommand{\RR}{\mathbb{R}}
\newcommand*{\vertbar}{\rule[-1ex]{0.5pt}{2.5ex}}
\newcommand*{\horzbar}{\rule[.5ex]{2.5ex}{0.5pt}}
\DeclareMathOperator{\tr}{tr}
\DeclareMathOperator{\diag}{diag}

\begin{document}

\begin{itemize}

\item Kenneth Hung
\item Response to reviews
\item Reference: Rank verification for exponential families

\end{itemize}

\section{Response to Reviewer 1}

\begin{itemize}

\item {\em Then they are offering a test based on the first two order statistics. If that is the case they should say so.}

We adopted this suggestion.

\item {\em It is said that we would be asking different questions if Cruz had led the race? What are they? Wouldn't we still be asking if Cruz was really winning?}

We clarified what we refer to as different questions in the paper.

\item {\em Why would we stop with a failure to reject? Could we not obtain later orders? What if we wanted to know who was last?}

This is to stay in line with BasicStop \citep{Fithian:2015uj}, also known as the partition test, where we reject a sequence of null hypothesis and halt whenever we can no longer reject.

In the case where we want to know who was last, we can take $-X$ as the observations and $-\theta$ as the parameter. Applying our procedure will thus infer about the last. This is mentioned in Section 1.2 and a similar idea was included in \citet{Stefansson:1988wj} as well.

\item {\em In primary voting, the second place finisher is not necessarily the second choice. If the choice of Trump was removed it is not clear that Cruz would move to first.}

We are not inferring that Cruz (the first running-up in polls) to be the second choice. We are testing that Cruz has the second largest support. This is not clarified in Section 1.2 where we define what ``best'', ``second best'', ``winner'' and ``runner-up'' mean.

\item {\em What is the definition of a ”valid” test being used here?}

A valid test should control the Type I error rate (in the case of just testing for the best), and FWER (in the case of verifying multiple ranks). This has been made more explicit in the paper.

\item {\em On line 17 from the bottom of page 4, the sentence beginning with ``Berger (1980) ...'' does not seem to make any sense.}

Thanks for catching that. It is now fixed.

\item {\em What can be said about using all the data? Suppose there were just 3 populations and you decided that the first two were different. Would you feel the same way about the difference of the first two if you next found that the 2nd and 3rd were not different?}

We would not feel any different about the population. We are performing a test to establish the winner as the best by comparing the top two order statistics. Even the third population is closer to the second population, the test remains statistically valid, and we can establish the same conclusion.

In a case with a more complex joint distribution, changing $X_3$ would alter the test, as the test comparing $X_1$ and $X_2$ conditions on $X_3$. The test procedure remains the same.

\item {\em This is not a step-down procedure in the sense of multiple testing. There the order used to test hypotheses depends on the individual p-values.}

That is a point quite valid. We agree that calling this a step-down procedure can be misleading. We have changed this to ``stepwise procedure''. However, if there is a wider known name for this type of ``reject until we can no longer reject'' procedure, we would gladly change the name again.

\item {\em Again suppose there were just a few populations and you wanted to know about all the ranks. As the authors point out, the method works beginning either with the maximum or minimum. However they need not give the same result. How would their performance differ?}

Since it is a stepwise procedure, it will ``get stuck'' in cases with parameters clustered together. The performance of starting from either end depends largely on the distribution of the parameters. If a few parameters are clustered on the lower end, the starting the test from the minimum will result in acceptance of the unadjusted pairwise test and no further ranks will be verified. On the other hand, if the tests are performed from the maximum, then most of the rank can be verified, save for the few clustered in the lower end. We believe in most applications there is one end that holds more significance (e.g.\ drug trial).

\end{itemize}

\section{Response to Reviewer 2}

\begin{itemize}

\item {\em The main reason for pointing out this reference is its technique for constructing a confidence set is by what is called Partitioning, a technique which has turned out to be fundamentally useful in multiple comparisons.}

We included this reference and credited this reference for its test on comparison with sample best under location family with monotone likelihood ratio.

\end{itemize}

\bibliographystyle{plainnat}
\bibliography{papers}

\end{document}

### 2017-06-24 verifying-winner.tex
major revision

@@
 This article concerns the problem of {\em rank verification} --- post hoc significance tests of whether the orderings discovered in the data reflect the population ranks.
-For exponential family models, we show under mild conditions that an unadjusted two-tailed pairwise test comparing the top two observations (i.e., comparing the ``winner'' to the ``runner-up'') is a valid test of whether the winner is truly the best.
+For exponential family models, we show under mild conditions that an unadjusted two-tailed pairwise test comparing the first two order statistics (i.e., comparing the ``winner'' to the ``runner-up'') is a valid test of whether the winner is truly the best.
 We extend our analysis to provide equally simple procedures to obtain lower confidence bounds on the gap between the winning population and the others, and to verify ranks beyond the first.
@@
 To compute the last column (Votes), we make the simplifying assumption that the reported percentages in the third column (Result) are raw vote shares among survey respondents.
-The asterisks indicate that the rank is verified at level $0.05$ by a step-down procedure.}
+The asterisks indicate that the rank is verified at level $0.05$ by a stepwise procedure.}
 \label{tbl:poll}
@@
 Furthermore, is Cruz really in second, is Rubio really in third, and so on?
-Note that there is implicitly a problem of multiple comparisons here, because if Cruz had led the poll instead, we would be asking a different set of questions.
+Note that there is implicitly a problem of multiple comparisons here, because if Cruz had led the poll instead, we would be asking a different set of questions, such as ``Is Cruz really winning?'', etc..
 Indeed, the selection issue appears especially pernicious due to the so-called ``winner's curse'': given that Trump leads the poll, it more likely than not overestimates his support.
@@
 Surprisingly, all of the three procedures described above are statistically valid despite their ostensibly ignoring the implicit multiple-comparisons issue.
-The remainder of this article is dedicated to justifying these procedures for the multinomial family, and analogous procedures in other settings.
+In other words, the Procedure 1 controls the Type I error rate at $\alpha$ and Procedure 3 controls the familywise error rate (FWER) at $\alpha$.
+The remainder of this article is dedicated to justifying these procedures for the multinomial family, and extending to analogous procedures in other settings.
 
@@
 As we will see, $\theta_j \ge \theta_k$ if and only if $X_j$ is stochastically larger than $X_k$; thus, there is a well-defined stochastic ordering of the populations that matches the ordering of the entries of $\theta$.
-We will refer to the population with maximal $\theta_j$ as the {\em best}, the one with maximal $X_j$ as the {\em winner}, and the one with the second-largest $X_j$ as the {\em runner-up}, where ties between observations are broken randomly to obtain a full ordering.
+We will refer to the population with maximal $\theta_j$ as the {\em best}, the population with second largest $\theta_j$ as the {\em second best}, the one with maximal $X_j$ as the {\em winner}, and the one with the second-largest $X_j$ as the {\em runner-up}, where ties between observations are broken randomly to obtain a full ordering.
 Following the convention in the ranking and selection literature, we assume that if there are multiple largest $\theta_j$, then one is arbitrarily marked as the best.
@@
 \item {\em By how much?} Construct the unadjusted pairwise confidence interval comparing the winner to the runner-up, and report the lower confidence bound obtained for $\theta_{[1]} - \theta_{[2]}$ if it is nonnegative, report $-\infty$ otherwise.
-\item {\em Is the runner-up really the second best, etc.?} Continue by comparing the runner-up to the second-runner-up, again using the unadjusted pairwise test, and so on down the list comparing adjacent values.
+\item {\em Is the runner-up really the second best, etc.?} Continue by comparing the runner-up to the second runner-up, again using the unadjusted pairwise test, and so on down the list comparing adjacent values.
 Stop the first time the test accepts.
@@
 \item Procedure 2 gives a conservative $1-\alpha$ lower confidence bound for $\theta_{[1]} - \max_{j \ne [1]} \theta_{j}$.
-\item Procedure 3 is a conservative step-down procedure with familywise error rate (FWER) no larger than $\alpha$.
+\item Procedure 3 is a conservative stepwise procedure with FWER no larger than $\alpha$.
 \end{enumerate}
@@
 \citet{Bofinger:1991hv, Maymin:1992fz, Karnnan:2009iv} give similar results for other models including scale and location-scale families.
+With this inference problem under the name Comparison with Sample Best (CSB), \citet{Stefansson:1988wj} provide a powerful test and a lower confidence bound for location family with monotone likelihood ratio through the partitioning principle.
 These results use very different technical tools than the ones we use here, require independence between the different groups (ruling out, for example, the multinomial family), and do not address the exponential family case.
@@
 For the multinomial case, \citet{Gupta:1967wg}, discussed in \Cref{sec:subsetsel}, remain the state of the art in finite-sample tests; \citet{Gupta:1976vd} discuss related approaches for Poisson models.
-\citet{Berger:1980ev} mentions an alternative, simpler rule which performs a binomial test on each population, but its power does not necessarily as the size $m$ of observations increases in cases like $\text{Multinomial}(m; 2/3, 1/3, 0, \ldots, 0)$.
+\citet{Berger:1980ev} mentions an alternative, simpler rule which performs a binomial test on each population, but its power does not necessarily increase as the size $m$ of observations increases in cases like $\text{Multinomial}(m; 2/3, 1/3, 0, \ldots, 0)$.
 \citet{Nettleton:2009ht} proves validity for an asymptotic version of the winner-versus-runner-up test, and \citet{Gupta:1989fe} consider an empirical Bayes approach for selecting the best binomial population wherein a parametric prior distribution is assumed for the success probabilities for the different populations.
@@
 \Cref{sec:winnerbest} justifies Procedure 1 and compares its power to that of \citet{Gupta:1967wg}.
-\Cref{sec:confbound,sec:stepdown} justify Procedures 2 and 3 respectively, and \Cref{sec:disc} concludes.
+\Cref{sec:confbound,sec:stepwise} justify Procedures 2 and 3 respectively, and \Cref{sec:disc} concludes.
 
@@
 \section{Verifying Other Ranks: Is the Runner-Up Really the Second Best, etc.?}
-\label{sec:stepdown}
+\label{sec:stepwise}
 
@@
 \begin{theorem}
-Procedure 3' is a step-down procedure that an estimate $\hat{j}_0$ of $j_0$ at the FWER controlled at $\alpha$, where $j_0$ is given by
+Procedure 3' is a stepwise procedure that an estimate $\hat{j}_0$ of $j_0$ at the FWER controlled at $\alpha$, where $j_0$ is given by
 \[j_0 = \max_j \left\{\theta_{[1]} > \cdots > \theta_{[j]} > \max_{k>j} \theta_{[k]}\right\}.\]
@@
 \begin{customthm}[Part 3 of \Cref{thm:main}]
-Assume the model~\eqref{eq:expfam} holds and $g\left(x\right)$ is a Schur-concave function. Procedure 3 is a conservative step-down procedure with FWER no larger than $\alpha$.
+Assume the model~\eqref{eq:expfam} holds and $g\left(x\right)$ is a Schur-concave function. Procedure 3 is a conservative stepwise procedure with FWER no larger than $\alpha$.
 \end{customthm}

### 2017-06-28 response.tex
Will's changes to the revision

@@
 
+We thank both referees for their thoughtful questions and helpful suggestions. Please find a point-by-point response below.
+
 \section{Response to Reviewer 1}
@@
 
-We adopted this suggestion.
+Thank you, this is a clearer way of stating our goal and we have adopted the suggestion.
 
@@
 
-We clarified what we refer to as different questions in the paper.
+We meant to say that we would be asking the same question, except we would be asking it about Cruz. We've clarified this in the paper.
 
@@
 
-This is to stay in line with BasicStop \citep{Fithian:2015uj}, also known as the partition test, where we reject a sequence of null hypothesis and halt whenever we can no longer reject.
+We can keep going if we want, but we only control FWER if we stop at the first acceptance.
+The FWER proof of \citep{Fithian:2015uj} unfortunately fails without this restriction, and FWER is not controlled.
 
 In the case where we want to know who was last, we can take $-X$ as the observations and $-\theta$ as the parameter.
-Applying our procedure will thus infer about the last.
-This is mentioned in Section 1.2 and a similar idea was included in \citet{Stefansson:1988wj} as well.
+Applying our procedure will thus make inferences about the last, second last, and so on.
+This is mentioned in Section 1.2.
 
@@
 
-We are not inferring that Cruz (the first running-up in polls) to be the second choice.
-We are testing that Cruz has the second largest support.
-This is not clarified in Section 1.2 where we define what ``best'', ``second best'', ``winner'' and ``runner-up'' mean.
+We are not inferring that Cruz (the first running-up in polls) would win in an election if Trump were disqualified; rather we are testing that Cruz has the second-most voters for whom he is the first choice (i.e., the second largest parameter in the multinomial distribution).
+This is now clarified in Section 1.2 where we define what ``best'', ``second best'', ``winner'' and ``runner-up'' mean.
 
@@
 
-A valid test should control the Type I error rate (in the case of just testing for the best), and FWER (in the case of verifying multiple ranks). This has been made more explicit in the paper.
+We've clarified the error rates we are controlling in the paper.
 
@@
 
-We would not feel any different about the population.
-We are performing a test to establish the winner as the best by comparing the top two order statistics.
-Even the third population is closer to the second population, the test remains statistically valid, and we can establish the same conclusion.
+If the first test rejects then we have concluded that (say) population 1 is ``better'' than {\em both} populations 2 and 3.
+The test compares only the top two sample ranks, but the conclusion involves all 3 populations.
+If we then decide we can't distinguish between populations 2 and 3, it would not threaten that conclusion.
 
-In a case with a more complex joint distribution, changing $X_3$ would alter the test, as the test comparing $X_1$ and $X_2$ conditions on $X_3$. The test procedure remains the same.
+% In a case with a more complex joint distribution, changing $X_3$ would alter the test, as the test comparing $X_1$ and $X_2$ conditions on $X_3$. The test procedure remains the same.
+
+%Kenneth, I don't understand what you mean in the commented paragraph.
 
@@
 
-That is a point quite valid.
-We agree that calling this a step-down procedure can be misleading.
-We have changed this to ``stepwise procedure''.
-However, if there is a wider known name for this type of ``reject until we can no longer reject'' procedure, we would gladly change the name again.
+Thank you, we have stopped calling it a step-down procedure.
+We have changed the term to ``stepwise procedure''.
+If you know of a better name for this type of ``reject until we can no longer reject'' procedure, we would be happy to correct our terminology.
 
@@
 
-Since it is a stepwise procedure, it will ``get stuck'' in cases with parameters clustered together.
+This is an interesting question.
+Suppose that every (two-tailed) unadjusted pairwise test between adjacent populations is significant; then our conservative Procedure 3 will verify that all of the sample ranks coincide with population ranks.
+If some populations are hard to distinguish from each other, however, then it matters whether we start from the top or the bottom.
+
+For example, if populations are spread out at the top but cluster together at the bottom, then we will usually get farther by starting with the maximum, and vice versa.
+Another factor is that there might be more information for comparisons at one end: in the multinomial case, for example, comparisons between large probabilities may be more powerful than comparisons between small probabilities because the conditional ``sample size'' is larger.
+
+In any case, there is often a compelling scientific reason to care more about comparisons at one or the other end of the ranked list, in which case we should begin at the prioritized end.
+
+% in cases with parameters clustered together.
 The performance of starting from either end depends largely on the distribution of the parameters.
-If a few parameters are clustered on the lower end, the starting the test from the minimum will result in acceptance of the unadjusted pairwise test and no further ranks will be verified.
+If a few parameters are clustered on the lower end, then starting the test from the minimum will result in acceptance of the unadjusted pairwise test and no further ranks will be verified.
 On the other hand, if the tests are performed from the maximum, then most of the rank can be verified, save for the few clustered in the lower end.
@@
 
-We included this reference and credited this reference for its test on comparison with sample best under location family with monotone likelihood ratio.
+Thank you, we have included this reference and included the connection to partitioning.
+
+\item {\em (As an aside, the authors are presumably aware that the two approaches to traditional Ranking and Selection turns out to be two sides of the confidence bounds in Multiple Comparisons with the Best, as described in chapter 4 or Hsu 1996.)}
+
+Thank you, we have mentioned this connection in the text.
 

### 2017-06-28 verifying-winner.tex
Will's changes to the revision

@@
 
-  \address{Department of Statistics\\ Evans Hall\\ Berkeley, CA 94720\\
+  \address{Department of Statistics\\ 301 Evans Hall\\ Berkeley, CA 94720\\
           \printead{e2}}
@@
 Furthermore, is Cruz really in second, is Rubio really in third, and so on?
-Note that there is implicitly a problem of multiple comparisons here, because if Cruz had led the poll instead, we would be asking a different set of questions, such as ``Is Cruz really winning?'', etc..
+Note that there is implicitly a problem of multiple comparisons here, because if Cruz had led the poll instead, we would be asking a different set of questions (``Is Cruz really winning,'' etc.).
 Indeed, the selection issue appears especially pernicious due to the so-called ``winner's curse'': given that Trump leads the poll, it more likely than not overestimates his support.
@@
 
-Surprisingly, all of the three procedures described above are statistically valid despite their ostensibly ignoring the implicit multiple-comparisons issue.
-In other words, the Procedure 1 controls the Type I error rate at $\alpha$ and Procedure 3 controls the familywise error rate (FWER) at $\alpha$.
-The remainder of this article is dedicated to justifying these procedures for the multinomial family, and extending to analogous procedures in other settings.
+Perhaps surprisingly, all of the three procedures described above are statistically valid despite their ostensibly ignoring the implicit multiple-comparisons issue.
+In other words, Procedures 1 and 2 control the Type I error rate at level $\alpha$ and Procedure 3 controls the familywise error rate (FWER) at level $\alpha$.
+The remainder of this article is devoted to justifying these procedures for the multinomial family, and extending to analogous procedures in other exponential family settings.
+While methods analogous to Procedures 1 and 2 have been justified previously for balanced independent samples from log-concave location families \citep{Gutmann:1987fk,Stefansson:1988wj}, they have not been justified in exponential families before now.
 
@@
 \begin{enumerate}
-\item {\em Is the winner really the best?} Carry out the unadjusted pairwise test comparing the winner to the runner-up.
-If the test rejects at level $\alpha$, conclude that the winner is really the best.
-\item {\em By how much?} Construct the unadjusted pairwise confidence interval comparing the winner to the runner-up, and report the lower confidence bound obtained for $\theta_{[1]} - \theta_{[2]}$ if it is nonnegative, report $-\infty$ otherwise.
+\item {\em Is the winner really the best?} To test the hypothesis $H:\; \theta_{[1]} \leq \max_{j \neq [1]} \theta_j$: Carry out the unadjusted pairwise test comparing the winner to the runner-up.
+If the test rejects at level $\alpha$, reject $H$ and declare that the winner is really the best.
+\item {\em By how much?} To construct a lower confidence bound for $\theta_{[1]} - \max_{j \neq [1]} \theta_j$: Construct the unadjusted pairwise confidence interval comparing the winner to the runner-up, and report the lower confidence bound obtained for $\theta_{[1]} - \theta_{[2]}$ if it is nonnegative, report $-\infty$ otherwise.
 \item {\em Is the runner-up really the second best, etc.?} Continue by comparing the runner-up to the second runner-up, again using the unadjusted pairwise test, and so on down the list comparing adjacent values.
-Stop the first time the test accepts.
+Stop the first time the test does not reject; if there are $j$ rejections, declare that
+\[
+\theta_{[1]} > \theta_{[2]} > \cdots > \theta_{[j]} > \max_{k > j} \theta_{[j]}
+\]
 \end{enumerate}
@@
 \begin{enumerate}
-\item Procedure 1 has level $\alpha$ conditional on the best population not winning (otherwise a Type I error is impossible).
+\item Procedure 1 has exact level $\alpha$ conditional on $H$ being true (conditional on the best population not winning), and marginally has level $\alpha\PP(H \text{ is true}) \leq \alpha \left(1-\frac{1}{n}\right)$.
 \item Procedure 2 gives a conservative $1-\alpha$ lower confidence bound for $\theta_{[1]} - \max_{j \ne [1]} \theta_{j}$.
@@
 \end{theorem}
+
+Note that Theorem~\ref{thm:main} implies that we could actually replace $\alpha$ with $\alpha \frac{n}{n-1}$ to obtain a more powerful version of Procedure 1 when $n$ is not too large.
 
@@
 
-\subsection{Related work}
+\subsection{Related work}\label{sec:related}
 
-Rank verification, especially for the first rank, has been studied extensively in the ranking and selection literature; see \citet{Gupta:1971wk, Gupta:1985bj}, and \citet{Hsu:1996} for surveys.
-In particular, \citet{Gutmann:1987fk} prove a result analogous to our main result in a different setting: that a two-tailed test comparing the winner to the runner-up is valid for log-concave location families.
-\citet{Bofinger:1991hv, Maymin:1992fz, Karnnan:2009iv} give similar results for other models including scale and location-scale families.
-With this inference problem under the name Comparison with Sample Best (CSB), \citet{Stefansson:1988wj} provide a powerful test and a lower confidence bound for location family with monotone likelihood ratio through the partitioning principle.
+Rank verification has been studied extensively in the ranking and selection literature.
+See \citet{Gupta:1971wk, Gupta:1985bj} for surveys of the subset selection literature.
+The two main formulations of ranking and selection are closely related to procedures for multiple comparisons with the best treatment \citep{edwards1983multiple,hsu1984constrained},  but more powerful methods are available in some cases for procedures involving only the first sample rank, the problem of comparisons with the sample best; see \citet{Hsu:1996} for an overview and discussion of the relationships between these problems.
+
+Comparisons with the sample best have been especially well-studied and the validity of Procedures 1 and 2 have been established in a different setting: balanced independent samples from log-concave location families.
+\citet{Gutmann:1987fk} prove the validity of Procedure 1 in this setting, and \citet{Bofinger:1991hv,Maymin:1992fz, Karnnan:2009iv} give similar results for other models including scale and location-scale families.
+\citet{Stefansson:1988wj} provide an alternative proof for the validity of Procedure 1 in the same setting, leading to a lower confidence bound analogous to that of Procedure 2; interestingly, the proof involves a very early application of the partitioning principle, later developed into fundamental technique in multiple comparisons \citep{finner2002partitioning}.
 These results use very different technical tools than the ones we use here, require independence between the different groups (ruling out, for example, the multinomial family), and do not address the exponential family case.

### 2017-06-28 verifying-winner.tex
finishing touches

@@
 \begin{enumerate}
-\item Procedure 1 has exact level $\alpha$ conditional on $H$ being true (conditional on the best population not winning), and marginally has level $\alpha\PP(H \text{ is true}) \leq \alpha \left(1-\frac{1}{n}\right)$.
+\item Procedure 1 has exact level $\alpha$ conditional on $H$ being true (conditional on the best population not winning), and marginally has level $\alpha \cdot \PP(H \text{ is true}) \leq \alpha \left(1-\frac{1}{n}\right)$.
 \item Procedure 2 gives a conservative $1-\alpha$ lower confidence bound for $\theta_{[1]} - \max_{j \ne [1]} \theta_{j}$.
@@
 
-Note that Theorem~\ref{thm:main} implies that we could actually replace $\alpha$ with $\alpha \frac{n}{n-1}$ to obtain a more powerful version of Procedure 1 when $n$ is not too large.
+Note that Theorem~\ref{thm:main} implies that we could actually replace $\alpha$ with $\frac{n}{n-1} \alpha$ to obtain a more powerful version of Procedure 1 when $n$ is not too large.
 
@@
 
-\subsection{Related work}\label{sec:related}
+\subsection{Related work}
+\label{sec:related}
 

### 2017-06-30 verifying-winner.tex
papers.bib updated

@@
 See \citet{Gupta:1971wk, Gupta:1985bj} for surveys of the subset selection literature.
-The two main formulations of ranking and selection are closely related to procedures for multiple comparisons with the best treatment \citep{edwards1983multiple,hsu1984constrained},  but more powerful methods are available in some cases for procedures involving only the first sample rank, the problem of comparisons with the sample best; see \citet{Hsu:1996} for an overview and discussion of the relationships between these problems.
+The two main formulations of ranking and selection are closely related to procedures for multiple comparisons with the best treatment \citep{Edwards:1983eo,Hsu:1984gb},  but more powerful methods are available in some cases for procedures involving only the first sample rank, the problem of comparisons with the sample best; see \citet{Hsu:1996} for an overview and discussion of the relationships between these problems.
 
@@
 \citet{Gutmann:1987fk} prove the validity of Procedure 1 in this setting, and \citet{Bofinger:1991hv,Maymin:1992fz, Karnnan:2009iv} give similar results for other models including scale and location-scale families.
-\citet{Stefansson:1988wj} provide an alternative proof for the validity of Procedure 1 in the same setting, leading to a lower confidence bound analogous to that of Procedure 2; interestingly, the proof involves a very early application of the partitioning principle, later developed into fundamental technique in multiple comparisons \citep{finner2002partitioning}.
+\citet{Stefansson:1988wj} provide an alternative proof for the validity of Procedure 1 in the same setting, leading to a lower confidence bound analogous to that of Procedure 2; interestingly, the proof involves a very early application of the partitioning principle, later developed into fundamental technique in multiple comparisons \citep{Finner:2002ju}.
 These results use very different technical tools than the ones we use here, require independence between the different groups (ruling out, for example, the multinomial family), and do not address the exponential family case.

### 2017-07-19 slides.tex
minor update before poster

@@
 
+\usepackage{booktabs}
 \usepackage{graphicx}
-\usepackage{booktabs}
 \usepackage{natbib}
@@
 }
-\date{June 23, 2017 @ MCP2017}
+\date{[Insert date]}
 
@@
 
-\begin{frame}{Related work}
+\begin{frame}{Selected related work}
 \begin{itemize}
-\item Ranking and selection: \citet{Gupta:1971wk,Gupta:1985bj,Gutmann:1987fk}
-\item Location-scale families: \citet{Gutmann:1987fk,Bofinger:1991hv,Maymin:1992fz,Karnnan:2009iv}
-\item CSB for location family using partition: \citet{Stefansson:1988wj}
-\item Multinomial families: \citet{Gupta:1967wg,Gupta:1976vd,Berger:1980ev,Nettleton:2009ht,Gupta:1989fe,Ng:2007cn,Gupta:1967wg}
-
+\item Test for log-concave location families: \citet{Gutmann:1987fk}
+\item Test for scale and location-scale families: \citet{Bofinger:1991hv,Maymin:1992fz,Karnnan:2009iv}
+\item Test and lower bound for log-concave location families, using partition principle from \citet{Finner:2002ju}: \citet{Stefansson:1988wj}
+\item Multinomial families: \citet{Gupta:1967wg}
 \item Conditional selective inference: \citet{Fithian:2014ws}
@@
 \begin{frame}[allowframebreaks]{References}
-\footnotesize{\bibliography{papers}\bibliographystyle{plainnat}}
+\footnotesize{
+\bibliography{papers}
+\bibliographystyle{plainnat}
+}
 \end{frame}

### 2017-07-30 poster.tex
poster added, figures now in pdf

% Jacobs Portrait Poster
% LaTeX Template
% Version 1.0 (31/08/2015)
% (Based on Version 1.0 (29/03/13) of the landscape template
%
% Created by:
% Computational Physics and Biophysics Group, Jacobs University
% https://teamwork.jacobs-university.de:8443/confluence/display/CoPandBiG/LaTeX+Poster
% 
% Further modified by:
% Nathaniel Johnston (nathaniel@njohnston.ca)
%
% Portrait version by:
% John Hammersley
%
% The landscape version of this template was downloaded from:
% http://www.LaTeXTemplates.com
%
% License:
% CC BY-NC-SA 3.0 (http://creativecommons.org/licenses/by-nc-sa/3.0/)

\documentclass[final]{beamer}

\usepackage[scale=1.24]{beamerposter}

\usetheme{confposter}
\newlength{\sepwid}
\newlength{\onecolwid}
\newlength{\twocolwid}
\newlength{\threecolwid}
\setlength{\paperwidth}{36in}
\setlength{\paperheight}{48in}
\setlength{\sepwid}{0.024\paperwidth}
\setlength{\onecolwid}{0.22\paperwidth}
\setlength{\twocolwid}{0.464\paperwidth}
\setlength{\threecolwid}{0.708\paperwidth}
\setlength{\topmargin}{-0.5in}

\usepackage{booktabs}
\usepackage{graphicx}
\usepackage{natbib}
\usepackage{tikz}
\usetikzlibrary{calc}

\newcommand{\EE}{\mathbb{E}}
\newcommand{\PP}{\mathbb{P}}
\newcommand{\RR}{\mathbb{R}}
\newcommand{\ZZ}{\mathbb{Z}}
\DeclareMathOperator*{\argmax}{arg\,max}

\title{Rank Verification for Exponential Families}

\author{Kenneth Hung \and William Fithian}

\institute{
University of California, Berkeley \\
{\tt \{kenhung, wfithian\}@berkeley.edu}
}

\begin{document}

\addtobeamertemplate{block end}{}{\vspace*{2ex}}
\addtobeamertemplate{block alerted end}{}{\vspace*{2ex}}

\setlength{\belowcaptionskip}{2ex}
\setlength\belowdisplayshortskip{2ex}

\begin{frame}[t]

\begin{columns}[t]

\begin{column}{\sepwid}\end{column}

% column 1
\begin{column}{\onecolwid}

\begin{alertblock}{Objectives}

We extend the classical result on Comparison with Sample Best (CSB) in \citet{Stefansson:1988wj} to a general class of exponential families. We provide procedures for the following three inferences:
\begin{enumerate}
	\item Is the sample best ({\em winner}) the true best ({\em best})?
	\item By how much is the same best better than the rest?
	\item Is the sample second ({\em runner-up}) the true second ({\em second best}), the sample third the true third, etc.?
\end{enumerate}

\end{alertblock}

\begin{block}{Introduction}

\begin{table}[htbp]
\centering
\begin{tabular}{c c c c}
	\hline
	Rank & Candidate & Result & Votes \\
	\hline
	$1$ & Trump & $31\%$ & $276$ \\
	$2$ & Cruz & $24\%$ & $214$ \\
	$3$ & Rubio & $17\%$ & $151$ \\
	$4$ & Carson & $8\%$ & $71$ \\
	$5$ & Paul & $4\%$ & $36$ \\
	$6$ & Bush & $4\%$ & $36$ \\
	$7$ & Huckabee & $3\%$ & $27$ \\
	$\vdots$ & $\vdots$ & $\vdots $ & $\vdots$ \\
	\hline
\end{tabular}
\caption{Simplified results from a February 1, 2016 Quinnipiac University poll of $890$ Iowa Republicans. We assume that the number of votes follows a multinomial distribution.}
\label{tbl:poll}
\end{table}

Questions that one might ask, {\em post hoc}:
\begin{enumerate}
	\item Verifying winner as best: Does Trump have the largest support? (a.k.a.\ multiple comparison with sample best (CSB) in \citet{Stefansson:1988wj})
	\item By how much: How much larger is Trump's support compared to other candidates?
	\item Verifying other ranks: Does Cruz (Rubio, etc.) have the second (third, etc.) largest support?
\end{enumerate}

\end{block}

\begin{block}{Selected Related Work}

\begin{itemize}
	\item Test and lower bound for log-concave location families, using partition principle from \citet{Finner:2002ju}: \citet{Stefansson:1988wj}
	\item Multinomial families: \citet{Gupta:1967wg}
	\item Conditional selective inference: \citet{Fithian:2014ws}
\end{itemize}

\end{block}

\end{column}

\begin{column}{\sepwid}\end{column}

% column 2
\begin{column}{\onecolwid}

\begin{block}{Challenges}

\begin{itemize}
	\item {\em Multiple comparison}: Comparing the winner to the rest involves $n-1$ pairwise comparisons.
	\item {\em Selective inference}: We will only test the hypothesis about the winner, and the winner depends on the sample.
\end{itemize}

\end{block}

\begin{block}{Schur-Concave Exponential Families}

Canonical form exponential families with observations as sufficient statistics:
\begin{align*}
&~ p(x_1, \ldots, x_n; \theta_1, \ldots, \theta_n) \\
= &~ \exp(\theta_1 x_1 + \cdots + \theta_n x_n \\
&~ ~~~~ - \log A(\theta_1, \ldots, \theta_n)) h(x_1, \ldots, x_n)
\end{align*}
\begin{itemize}
\item $x_i$ are the observations
\item $\theta_i$ are the natural parameter being ranked and tested
\item $h(\cdot)$ is the carrier distribution
\item $A(\cdot)$ is the normalizing constant
\end{itemize}

Schur-concave exponential families require $h(\cdot)$ to be Schur-concave, i.e.
\[
h(x) \le h(y) ~~~~ \text{if} ~~~~ x \succeq y,
\]
where $x \succeq y$ is the majorization order in $\RR^n$.

\end{block}

\begin{block}{Examples}

\begin{itemize}
	\item Independent binomial treatment outcomes in a clinical trial
	\item Competitive sports under the Bradley--Terry model
	\item Comparing the variances of independent normal populations
\end{itemize}

\end{block}

\begin{alertblock}{Procedures}

For observations from a Schur-concave exponential family, we provide the following three procedures for the three inferences above:
\begin{enumerate}
	\item {\bf Two}-tailed level-$\alpha$ test comparing winner (Trump) to runner-up (Cruz)
	\item Invert the test above
	\item {\bf Two}-tailed level-$\alpha$ test comparing first runner-up (Cruz) to second runner-up (Rubio), etc., using a stepwise procedure
\end{enumerate}

A two-tailed level-$\alpha$ test here refers to the conditional exact test for exponential families.

\end{alertblock}

\end{column}

\begin{column}{\sepwid}\end{column}

% column 3
\begin{column}{\onecolwid}

\begin{block}{Key Ideas in Proof}

\begin{itemize}
	\item {\em Multiple comparison}: Null hypothesis is ``the winner is not the best'', a union null of hypothesis that the winner is not better than each of the rest
	\item Construct a $p$-value $p_{ij}$ for comparing winner $i$ to each of the rest, $j$; do a significance test based on the combined $p$-value $\max_{j \ne i} p_{ij}$.
	\item {\em Selective inference}: Construct $p_{ij}$ by conditioning on the selection event \citep{Fithian:2014ws}, given by
	\[
	\{X_i > \max_{i \ne k} X_k\}
	\]
	\item Condition also on sufficient statistics for nuisance parameters, $X_{\setminus\{i, j\}}$ and $X_i + X_j$, for an exact test
\end{itemize}

\end{block}

\begin{alertblock}{Goal in Proof}

It suffices to show
\begin{itemize}
	\item $\max_{k \ne i} p_{ik} = p_{ij}$, where $i$ is the winner and $j$ is the first runner-up.
	\item $p_{ij}$ is the $p$-value obtained from a two-sided exact test comparing only winner $i$ and runner-up $j$.
\end{itemize}

\end{alertblock}

\begin{block}{Proof by Picture}
\begin{itemize}
	\item Graphical representation of $p_{ij}$ and $p_{ik}$ for comparison
	\item WLOG assume that $i = 1$ is the winner, $j = 2$ is the runner-up, and $k = 3$ is any other candidate
	\item Under the conditioning, $X_1 + X_2 + X_3$ and $X_{\setminus\{1, 2, 3\}}$ are held constant
	\item Everything can fit on a 2D picture!
\end{itemize}

\centering
\begin{tikzpicture}[scale=1.9,every node/.style={scale=0.7}]
	\coordinate (C1) at (60:5);
	\coordinate (C2) at (300:3);
	\coordinate (A) at (60:3);
	\coordinate (B) at ($(A) + (330:3)$);
	\coordinate (C) at ($(0, 0)!(B)!(C2)$);
	\coordinate (D) at ($(A) + (150:1)$);
	\draw[dashed] (0, 0) -- (C1);
	\draw[dashed] (0, 0) -- (C2);
	\fill[byzantium!50] (0, 0) -- (C1) -- ($(C1) + (6.5, 0)$) -- ($(C2) + (7.5, 0)$) -- (C2) -- cycle;
	\node[above left] at ($(C2) + (7.5, 0)$) {$A_1$};
	\draw[thick] (A) -- (B) node[midway, above right] {$A$};
	\draw[thick, ->] (B) -- ++(330:5) node[midway, below left] {$B$};
	\fill (A) circle(2pt) node[above right] {$\left(M_{12}, M_{12}, X_3\right)$};
	\fill (B) circle(2pt) node[right] {$\left(X_1, X_2, X_3\right)$};
	\fill (0, 0) circle(2pt);
	\draw[thick, ->] (0, 0) -- (0.5, 0) node[right] {\scriptsize $x_1 +$};
	\draw[thick, ->] (0, 0) -- (120:0.5) node[above] {\scriptsize $x_2 +$};
	\draw[thick, ->] (0, 0) -- (240:0.5) node[below] {\scriptsize $x_3 +$};
	\draw[thick] (C) -- (B) node[midway, below right] {$C$};
	\node[below] at (C) {$\left(M_{13}, X_2, M_{13}\right)$};
	\draw[thick, ->] (B) -- ++(30:5) node[midway, above left] {$D$};
	\fill ($(0, 0)!(B)!(C2)$) circle(2pt);
	\draw[thick, dashed] (A) -- (D) node[midway, below left] {$\tilde{A}$};
	\fill (D) circle(2pt) node[above] {$\left(M_{13}, X_2 + D_{13}, X_3\right)$};
	\draw[thick, dotted] (C) -- (D) node[midway, below, rotate=-90] {$\succeq$};
	\draw[thick, dotted] (A) -- ++(0, -3) node[midway, below, rotate=-90] {$\succeq$};
	\draw[thick, dotted] ($(B) + (30:4)$) -- ($(B) + (330:4)$) node[midway, below, rotate=-90] {$\succeq$};
\end{tikzpicture}

\begin{itemize}
	\item $p_{12} = \frac{B}{A+B}$ and $p_{13} = \frac{D}{C+D}$
	\item Schur concavity implies $A + \tilde{A} \le C$ and $D \le B$
	\item So $p_{12} \ge p_{13}$
	\item The values are symmetric about the $x_1 = x_2$ line, so $\frac{B}{A+B}$ is equivalent to a two-tailed $p$-value.
\end{itemize}

\end{block}

\end{column}

\begin{column}{\sepwid}\end{column}

% column 4
\begin{column}{\onecolwid}

\begin{block}{Brief Sketch for Other Two Inferences}

\begin{itemize}
	\item A test can be built, similarly for the hypothesis that winner is not at least $\delta$ larger than the rest; inverting this test yields the second procedure
	\item Adopting the framework in \citet{Fithian:2015uj}, we can perform a sequence of similar selective inferences
\end{itemize}

\end{block}

\begin{block}{Power Comparison}

\begin{itemize}
\item \citet{Gupta:1967wg} provided a subset selection procedure for the multinomial problem
\item Convert into a test for if the winner is the best by rejecting the null hypothesis if only the winner is selected
\item Tested on parameters in form of
\[
\text{prob} \propto (e^\delta, \underbrace{1, 1, \ldots, 1}_{n - 1}), ~~~~ \text{num} = m
\]
\end{itemize}

\centering
\includegraphics[width=\textwidth]{multinomial-power.pdf}

\begin{itemize}
	\item Our test performs better than \citet{Gupta:1967wg}
	\item Difference in performance increases with $m$ and $n$
	\item We attribute the improvement to our test adapting to the observations for winner and runner-up
\end{itemize}

\end{block}

\begin{block}{Selected References}

\small{
\bibliography{papers}
\bibliographystyle{abbrvnat}
\vspace{0.75in}
}

\end{block}

\end{column}

\end{columns}

\end{frame}

\end{document}

### 2017-07-30 slides.tex
poster added, figures now in pdf

@@
 \item By how much: Invert the test above
-\item Verifying other ranks: One-tailed level-$\alpha$ test comparing first runner-up to second runner-up, etc., using a step-down procedure.
+\item Verifying other ranks: One-tailed level-$\alpha$ test comparing first runner-up to second runner-up, etc., using a stepwise procedure.
 \end{itemize}
@@
 \item By how much: Invert the test above
-\item Verifying other ranks: {\bf Two}-tailed level-$\alpha$ test comparing first runner-up to second runner-up, etc., using a step-down procedure
+\item Verifying other ranks: {\bf Two}-tailed level-$\alpha$ test comparing first runner-up to second runner-up, etc., using a stepwise procedure
 \end{itemize}
@@
 \centering
-\includegraphics[width=0.95\textwidth]{multinomial-power.png}
+\includegraphics[width=0.95\textwidth]{multinomial-power.pdf}
 \end{frame}

### 2017-07-30 multinomial-power.r

@@ -114,7 +114,7 @@ p5 <- PlotMultinomialPower(250, 25, alpha, num.sample)
 p6 <- PlotMultinomialPower(250, 50, alpha, num.sample)
 
 # Saving the plot
-png("multinomial-power.png", width = 7, height = 5, units = 'in', res = 300)
+pdf("multinomial-power.pdf", width = 7, height = 5)
 grid.arrange(arrangeGrob(p1, p2, p3, p4, p5, p6, ncol = 3,
                          left = textGrob("Power", rot = 90, vjust = 1),
                          bottom = textGrob(expression(delta))))

### 2017-08-28 poster.tex
minor fixes, new keywords added

@@
 \begin{itemize}
-	\item {\em Multiple comparison}: Null hypothesis is ``the winner is not the best'', a union null of hypothesis that the winner is not better than each of the rest
+	\item {\em Multiple comparison}: Null hypothesis is ``the winner is not the best'', a union of null hypotheses, each stating that the winner is not better than one other candidate
 	\item Construct a $p$-value $p_{ij}$ for comparing winner $i$ to each of the rest, $j$; do a significance test based on the combined $p$-value $\max_{j \ne i} p_{ij}$.
@@
 
-\begin{block}{Brief Sketch for Other Two Inferences}
+\begin{block}{Proof Sketch for Other Two Procedures}
 
@@
 \centering
-\includegraphics[width=\textwidth]{multinomial-power.pdf}
+\includegraphics[width=\textwidth]{multinomial-power.eps}
 

### 2017-08-28 multinomial-power.r

@@ -85,7 +85,9 @@ GnPower <- function(m, n, delta, alpha, num.sample) {
 PlotMultinomialPower <- function(m, n, alpha, num.sample) {
     # delta ranges from 0 to 2
     delta <- (0:200) / 100
-    sel <- sapply(delta, function(d) SelectivePower(m, n, d, alpha / (n - 1) * n, num.sample))
+    sel <- sapply(delta,
+                  function(d) SelectivePower(m, n, d, alpha / (n - 1) * n,
+                                             num.sample))
     gn <- GnPower(m, n, delta, alpha, num.sample)
     power <- melt(data.frame(delta, sel, gn), id.vars = "delta")
     return(ggplot(data = power, aes(x = delta,
@@ -114,7 +116,8 @@ p5 <- PlotMultinomialPower(250, 25, alpha, num.sample)
 p6 <- PlotMultinomialPower(250, 50, alpha, num.sample)
 
 # Saving the plot
-pdf("multinomial-power.pdf", width = 7, height = 5)
+setEPS()
+postscript("multinomial-power.eps", width = 7, height = 5)
 grid.arrange(arrangeGrob(p1, p2, p3, p4, p5, p6, ncol = 3,
                          left = textGrob("Power", rot = 90, vjust = 1),
                          bottom = textGrob(expression(delta))))
